### 2017-06-02 KellyDouglass/Thesis/CV.tex
Papers 1,2, small-scale results-conclusions

\newcommand{\sectionrule}{\noindent \hfil\rule{\textwidth}{.6pt}\hfil}

\iffinal{}{\newpage}

\begin{vita}

{\Large\bf Kelly A. Douglass}

\singlespacing

\noindent
{\large\bf {\sc Education}}

\sectionrule
\vspace{1mm}

\begin{description}[noitemsep]
    \item[Drexel University] Philadelphia, Pennsylvania USA
    \begin{description}[noitemsep]
	    \item[] Ph.D., Physics, July 2017
	    \item[] M.S., Physics, June 2013
    \end{description}
    \item[Cornell University] Ithaca, New York USA
    \begin{description}
	    \item[] B.A., Physics, May 2011
    \end{description}
\end{description}

\noindent
{\large\bf {\sc Publications}}

\sectionrule

\begin{itemize} %\itemsep -2pt
	\item ``Large-scale environmental dependence of the abundance ratio of nitrogen to oxygen in blue, star-forming galaxies fainter than $L_*$". \href{https://doi.org/10.3847/1538-4357/aa5e53}{ApJ, 837: 42--55}, 2017
	\item ``Determining the large-scale environmental dependence of gas-phase metallicity in dwarf galaxies". \href{https://doi.org/10.3847/1538-4357/834/2/186}{ApJ, 834: 186--198}, 2017
\end{itemize}

\noindent
{\large\bf {\sc Awards}}

\sectionrule

\begin{itemize}[noitemsep]
    \item Drexel University College of Arts \& Sciences Outstanding Dissertation Award, 2017
    \item AAS Chambliss Astronomy Achievement Student Award, 2014
    \item Drexel University Continuing Teaching Excellence Award, 2014
    \item Drexel University Teaching Excellence Award, 2013
    \item Drexel University Teaching Excellence Award --- Highly Commended, 2012
    \item Drexel University Department of Physics First Year Graduate Student Award, 2012
    \item Drexel University College of Arts \& Sciences Dean's Scholarship, 2011--13
\end{itemize}

\noindent
{\large\bf {\sc Teaching Experience}}

\sectionrule

\begin{description}[noitemsep]
    \item[Teaching Assistant] Physics 135: How Things Work, Drexel University
    \item[Teaching Assistant] Physics 113, 114, 115: Contemporary Physics I, II, III, Drexel University
    \item[Teaching Assistant] Physics 102, 201: Fundamentals of Physics II, III, Drexel University
    \item[Teaching Assistant] Education T580: TA Orientation and Preparation, Drexel University
    \item[Teaching Assistant \& Consultant] Computer Science 1112: Introduction to MATLAB, Cornell University
    \item[Grader] Honors 301: Special Theory of Relativity, Drexel University
    \item[Grader] Physics 428: Quantum Mechanics III, Drexel University
\end{description}

\noindent
{\large\bf {\sc Public Outreach}}

\sectionrule

\begin{itemize}[noitemsep]
	\item \textbf{Professor Bob's Hands-On Science} \hfill \textit{June 2015 to August 2016}
	\item \textbf{Volunteer at the Lynch Observatory} \hfill \textit{September 2011 to July 2017}
\end{itemize}

\end{vita}

### 2017-06-02 KellyDouglass/Thesis/Tables/Paper1/XMPtable.tex
Papers 1,2, small-scale results-conclusions

\begin{table}
\centering

\begin{tabu} to 0.75\linewidth {ccccccc}
Index\footnote[1]{KIAS-VAGC galaxy index number} & R.A. & Decl. & Redshift & \multicolumn{2}{c}{$12 + \log \left( \frac{\text{O}}{\text{H}} \right)$} & Void/Wall \\
\hline \\
268470 & \RA{13}{18}{17}{.82} & +\dec{02}{12}{59}{.83} & 0.0252 & 7.06 & $\pm$0.37 & Void \\
1422637 & \RA{14}{18}{12}{.14} & +\dec{13}{59}{33}{.98} & 0.0261 & 7.15 & $\pm$0.41 & Wall \\
839665 & \RA{08}{09}{53}{.53} & +\dec{29}{17}{04}{.82} & 0.0281 & 7.18 & $\pm$0.44 & Void \\
1168448 & \RA{11}{06}{41}{.00} & +\dec{45}{19}{09}{.28} & 0.0220 & 7.19 & $\pm$0.46 & Wall \\
1299291 & \RA{12}{17}{14}{.02} & +\dec{43}{18}{53}{.36} & 0.0233 & 7.21 & $\pm$0.42 & Wall \\
1170573 & \RA{11}{05}{39}{.42} & +\dec{46}{03}{28}{.37} & 0.0250 & 7.24 & $\pm$0.34 & Wall \\
2288717 & \RA{10}{46}{12}{.18} & +\dec{21}{31}{37}{.37} & 0.0248 & 7.27 & $\pm$0.48 & Wall \\
955643 & \RA{11}{42}{03}{.02} & +\dec{49}{21}{25}{.18} & 0.0244 & 7.28 & $\pm$0.44 & Wall \\
1344311 & \RA{12}{33}{13}{.64} & +\dec{11}{10}{28}{.46} & 0.0245 & 7.29 & $\pm$0.50 & Wall \\
1254352 & \RA{13}{29}{02}{.45} & +\dec{10}{54}{55}{.80} & 0.0237 & 7.30 & $\pm$0.44 & Wall \\
1857820 & \RA{08}{45}{00}{.34} & +\dec{27}{16}{47}{.04} & 0.0257 & 7.31 & $\pm$0.48 & Wall \\
866876 & \RA{09}{04}{57}{.96} & +\dec{41}{29}{36}{.42} & 0.0240 & 7.32 & $\pm$0.40 & Wall \\
833588 & \RA{08}{43}{10}{.71} & +\dec{43}{08}{53}{.58} & 0.0245 & 7.34 & $\pm$0.41 & Wall \\
283263 & \RA{14}{14}{12}{.88} & +\dec{01}{50}{12}{.88} & 0.0255 & 7.35 & $\pm$0.43 & Wall \\
184308 & \RA{09}{39}{09}{.38} & +\dec{00}{59}{04}{.15} & 0.0244 & 7.36 & $\pm$0.43 & Wall \\
1389829 & \RA{14}{31}{01}{.38} & +\dec{38}{04}{21}{.50} & 0.0269 & 7.41 & $\pm$0.46 & Wall \\
858951 & \RA{09}{31}{39}{.60} & +\dec{49}{49}{56}{.85} & 0.0251 & 7.46 & $\pm$0.46 & Wall \\
1270221 & \RA{13}{27}{39}{.85} & +\dec{50}{54}{09}{.69} & 0.0295 & 7.49 & $\pm$0.43 & Wall \\
431383 & \RA{08}{58}{44}{.96} & +\dec{50}{29}{58}{.98} & 0.0230 & 7.52 & $\pm$0.60 & Void \\
75442 & \RA{13}{13}{24}{.25} & +\dec{00}{15}{02}{.95} & 0.0264 & 7.55 & $\pm$0.35 & Void \\
1322765 & \RA{14}{15}{05}{.58} & +\dec{36}{22}{57}{.77} & 0.0273 & 7.57 & $\pm$0.40 & Wall\\
\end{tabu}

\caption[Extreme low-metallicity dwarf galaxies]{Details of the 21 extreme low gas-phase metallicity ($12 + \log(\text{O}/\text{H}) < 7.6$) galaxies found.  Four of these galaxies are located in voids (about 10\% of the void dwarf population measured) and seventeen are in more dense regions (about 19\% of the wall dwarf population measured); thus, there does not seem to be a special population of extreme low-metallicity galaxies in voids.  Further study of these galaxies is recommended to confirm metallicity values and identify any shared characteristics.}

\label{tab:lowZ_P1}

\end{table}

### 2017-06-02 KellyDouglass/Thesis/Tables/Paper1/results_table_short.tex
Papers 1,2, small-scale results-conclusions

\begin{table}
\centering

\begin{tabu} to 0.75\linewidth {cccccccc}
Index\footnote[1]{KIAS-VAGC galaxy index number} & R.A. & Decl. & Redshift & $M_r$ & \multicolumn{2}{c}{$12 + \log \left( \frac{\text{O}}{\text{H}} \right)$} & Void/Wall \\
\hline \\
63713 & \RA{09}{20}{04}{.27} & -\dec{00}{30}{08}{.97} & 0.0257 & -16.73 & 7.80 & $\pm$0.41 & Wall \\
73537 & \RA{09}{25}{24}{.23} & +\dec{00}{12}{40}{.39} & 0.0250 & -16.94 & 7.94 & $\pm$0.34 & Wall \\
75442 & \RA{13}{13}{24}{.25} & +\dec{00}{15}{02}{.95} & 0.0264 & -16.81 & 7.55 & $\pm$0.35 & Void \\
168874 & \RA{11}{45}{13}{.16} & -\dec{01}{48}{17}{.68} & 0.0273 & -16.99 & 8.16 & $\pm$0.31 & Wall \\
184308 & \RA{09}{39}{09}{.38} & +\dec{00}{59}{04}{.15} & 0.0244 & -16.73 & 7.36 & $\pm$0.43 & Wall\\
\end{tabu}

\caption[Dwarf galaxy properties]{Five of the 135 dwarf galaxies analyzed from SDSS DR7.  The flux values for all required emission lines can be found in the MPA-JHU value-added catalog.  Metallicity values are calculated using the direct $T_e$ method, with error estimates via a Monte Carlo method.  The void catalog of \cite{Pan12} is used to classify the galaxies as either Void or Wall.  If a galaxy is located too close to the boundary of the SDSS survey to identify whether or not it is inside a void, it is labeled as Uncertain.  Table \ref{tab:Results_P1} is published in its entirety online in a machine-readable format.  A portion is shown here for guidance regarding its form and content.}

\label{tab:Results_P1}

\end{table}

### 2017-06-02 KellyDouglass/Thesis/Tables/Paper2/results_table_short.tex
Papers 1,2, small-scale results-conclusions

\begin{sidewaystable}
\centering

\begin{tabu} to \textwidth {cccccccccccc}
Index\footnote[1]{KIAS-VAGC galaxy index number} & R.A. & Decl. & Redshift & $M_r$ & \multicolumn{2}{c}{$12 + \log \left( \frac{\text{O}}{\text{H}} \right)$} & \multicolumn{2}{c}{$12 + \log \left( \frac{\text{N}}{\text{H}} \right)$} & \multicolumn{2}{c}{$\log \left( \frac{\text{N}}{\text{O}} \right)$} & Void/Wall \\
\hline \\
63713 & \RA{09}{20}{04}{.27} & -\dec{00}{30}{08}{.97} & 0.0257 & -16.73 & 7.80 & $\pm$0.41 & 6.83 & $\pm$0.28 & -0.97 & $\pm$0.49 & Wall \\
73537 & \RA{09}{25}{24}{.23} & +\dec{00}{12}{40}{.39} & 0.0250 & -16.94 & 7.94 & $\pm$0.34 & 6.76 & $\pm$0.24 & -1.18 & $\pm$0.41 & Wall \\
75442 & \RA{13}{13}{24}{.25} & +\dec{00}{15}{02}{.95} & 0.0264 & -16.81 & 7.55 & $\pm$0.35 & 6.73 & $\pm$0.24 & -0.82 & $\pm$0.42 & Void \\
168874 & \RA{11}{45}{13}{.16} & -\dec{01}{48}{17}{.68} & 0.0273 & -16.99 & 8.16 & $\pm$0.31 & 6.94 & $\pm$0.21 & -1.21 & $\pm$0.37 & Wall \\
184308 & \RA{09}{39}{09}{.38} & +\dec{00}{59}{04}{.15} & 0.0244 & -16.73 & 7.36 & $\pm$0.43 & 6.71 & $\pm$0.31 & -0.65 & $\pm$0.53 & Wall\\
\end{tabu}

\caption[Analyzed dwarf galaxies]{Five of the 135 dwarf galaxies analyzed from SDSS DR7.  The flux values for all required emission lines can be found in the MPA-JHU value-added catalog.  Metallicity values are calculated using the direct $T_e$ method, with error estimates via a Monte Carlo method.  The void catalog of \cite{Pan12} is used to classify the galaxies as either Void or Wall.  If a galaxy is located too close to the boundary of the SDSS to identify whether or not it is inside a void, it is labeled as Uncertain.  (This table is available in its entirety in machine-readable form.)}

\label{tab:Results_P2}

\end{sidewaystable}

### 2017-06-02 KellyDouglass/Thesis/Thesis_checklist.tex
Papers 1,2, small-scale results-conclusions

\documentclass{article}

\begin{document}

% Title
\title{Thesis checklist}
\author{Kelly Douglass, Michael S. Vogeley, advisor}
\date{21 June 2016}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Checkist

\section*{Papers}
\begin{itemize}
    \item April 2016 --- Submitted first paper to ApJ
    \item June 2016 --- Resubmit Paper 1 to ApJ (after applying referee suggestions)
    \item July 2016 --- Submit Paper 2 --- environmental dependence on N/O abundance in dwarf galaxies
    \item September 2016 --- Submit Paper 3 --- metallicity trend paper
    \item Winter/Spring 2017 --- (possible) Paper 4 --- environmental dependence on abundances in SHELS galaxies
    \item Spring 2017 --- (possible) Paper 5 --- small-scale environmental dependence on abundances in dwarf galaxies
\end{itemize}

\section*{Research}
\begin{itemize}
    \item Collaboration with Margaret Geller, Jabran Zahid using Hectospec data of SHELS galaxies
    \item Study metallicity relation between dwarf galaxies and their nearest bright neighbor
    \item Look at star formation history (metallicity), star formation rates, neutral gas content, morphology as related to large-scale environment
    \item (possibly) Compare results to dark matter halo simulations
\end{itemize}

\end{document}

### 2017-06-02 KellyDouglass/Thesis/Thesis_outline.tex
Papers 1,2, small-scale results-conclusions

\documentclass{article}

\begin{document}

% Title
\title{Thesis outline}
\author{Kelly Douglass, Michael S. Vogeley, advisor}
\date{21 June 2016}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Outline

\section{Large-scale environmental dependence of gas-phase metallicity in dwarf galaxies}
\begin{itemize}
    \item Submission dates
    \begin{itemize}
        \item Submitted April 2016
        \item To be resubmitted June 2016
    \end{itemize}
    \item Remaining work
    \begin{itemize}
        \item Apply referee suggestions
    \end{itemize}
\end{itemize}

\section{Large-scale environmental dependence of the abundance ratio of nitrogen to oxygen in dwarf galaxies}
\begin{itemize}
    \item Submission date --- July 2016
    \item Remaining work
    \begin{itemize}
        \item Revisions to make publication-ready
    \end{itemize}
\end{itemize}

\section{Approximation for the abundance of singly-ionized oxygen in SDSS galaxies}
\begin{itemize}
    \item Submission date --- September 2016
    \item Remaining work
    \begin{itemize}
        \item The purpose of this paper will be to use the approximation to bolster the low-mass end of my galaxy sample, with which I can therefore do full comparisons with previous works.  It will concentrate on both the dwarf galaxy characteristics as well as the full galaxy trends (in N/O).  
        \item Repeat dwarf galaxy large-scale environment analysis (oxygen, nitrogen, N/O) with ~2000 dwarf galaxies with approximated abundances (abundances already calculated)
        \item Finish composing paper, revisions for publication
    \end{itemize}
\end{itemize}

\section{Large-scale environmental dependence of gas-phase abundances in dwarf galaxies from SHELS}
\begin{itemize}
    \item Submission date --- Winter/Spring 2017
    \item Remaining work
    \begin{itemize}
        \item The direct method does not work with this data, since the S/N is too low to measure the [O{\sc iii}] $\lambda 4363$ auroral line.  I need to settle on a second-best method for abundance calculations that can be used on these galaxies (probably those from Brown, Martini, and Andrews (2016)).
    \end{itemize}
\end{itemize}

\section{(possible) Small-scale environmental dependence of gas-phase abundances in dwarf galaxies}
\begin{itemize}
    \item Submission date --- Winter/Spring 2017
    \item Remaining work
    \begin{itemize}
        \item Look through Brean's code and work and pick up where she left off.
    \end{itemize}
\end{itemize}

\section{(possible) The chemical evolution of AGNs}
\begin{itemize}
    \item Submission date --- Spring 2017
    \item Remaining work
    \begin{itemize}
        \item The oxygen abundance estimates for AGN are normal, but the nitrogen abundance is much higher than in star-forming galaxies.  I want to see if I can determine the cause of this discrepancy, so that the same analysis on the abundances can be done on AGN, including any large-scale dependence.
    \end{itemize}
\end{itemize}

\end{document}

### 2017-06-02 KellyDouglass/Thesis/Thesis_sections/GV.tex
Papers 1,2, small-scale results-conclusions

\chapter[Green valley galaxies]{Green valley galaxies}

This work was done in collaboration with Jinfu Dai for his senior thesis 
``Exploring the green valley.''

\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    STATEMENT OF PROBLEM
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Chemical evolution and the green valley}

The enrichment of the interstellar medium (ISM) and circumgalactic medium (CGM) 
of a galaxy involves many complicated astrophysical processes, the interplay of 
which is not yet well understood.  A critical problem in galaxy formation is to 
understand how galaxies transition from the blue sequence to the red cloud of 
the optical color-magnitude diagram.  Star formation is thought to be quenching 
in galaxies moving through the green valley, but the relevant baryonic processes 
(gas cooling, feedback, etc.) are very complex and heavily interdependent.  
Investigating the star formation history and chemical evolution of galaxies in 
the green valley should provide clues as to the evolution of a galaxy through 
the color-magnitude diagram.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    BACKGROUND AND RELEVANCE TO PREVIOUS WORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{The color-magnitude diagram: Galaxies in the green valley}

Large galaxy surveys \citep[like the Sloan Digital Sky Survey;][]{York00} 
revealed the structure of the color-magnitude diagram (CMD).  As seen in Fig. 
\ref{fig:ur_CMD}, the $u-r$ CMD is dominated by two major subgroups of galaxies: 
the red cloud and the blue sequence \citep{Strateva01, Baldry04}.  Most galaxies 
that reside in the red cloud appear to be older, elliptical galaxies that are no 
longer making stars (``red and dead'').  On the other hand, the blue sequence 
consists of mostly spiral and irregular galaxies which are actively forming stars.

% u-r CMD
\begin{figure}
    \includegraphics[width=0.49\textwidth]{Images/GV/ur_CMD_contour}
    \includegraphics[width=0.49\textwidth]{Images/GV/ur_hist}
    \caption[Optical color-magnitude diagram and histogram of $u-r$ in SDSS]{The 
    optical color-magnitude diagram (left) and histogram of $u-r$ colors (right) 
    of galaxies in SDSS DR7.  There are two groups of galaxies, the populations 
    of which are well fit by the sum of two Gaussians.  They are aptly named the 
    ``red cloud'' and the ``blue sequence.''}
    \label{fig:ur_CMD}
\end{figure}

% VOGELEY THINKS THIS DESCRIPTION IS TOO SIMPLISTIC
%The current theory of galactic evolution describes a process in which a small 
%galaxy forms many stars in the beginning of its life.  As the galaxy merges with 
%others, it converts most of its hydrogen to heavier elements through 
%nucleosynthesis, and its rate of star formation slowly decreases.  The red, 
%elliptical galaxies we currently observe are hypothesized to be the remnants of 
%galaxies which have burned through the majority of their hydrogen; without fuel 
%for new stars, the galaxy's star formation rate eventually declines to a 
%negligible value.  As a result, most of the hot, massive blue stars have 
%expired, leaving behind smaller, cooler, more red stars.  These galaxies have a 
%redder color than their blue, star-forming predecessors.

% Feedback from AGN (strongly affects massive galaxies)
% Feedback from SN (dominates feedback in dwarfs)
% gas stripping interactions
% tidally-triggered star formation
There are a number of different astrophysical processes which simultaneously 
evolve a galaxy's stellar and gas content.  AGN feedback strongly affects 
massive galaxies, while dwarf galaxy feedback is dominated by supernovae.  Both 
AGN and supernovae can inject enough energy into a galaxy's ISM to prevent its 
cooling, thereby quenching star formation.  In addition to internal mechanisms, 
galaxies will often experience interactions in more dense regions.  Depending on 
the properties of the galaxies involved (mass, speed, etc.), these interactions 
can either strip gas from the galaxy (removing a primary source of fuel for 
future star formation), or they can trigger a burst of star formation.

Our current theory of galactic evolution necessitates the existence of a 
transition period in a galaxy's lifetime, when the galaxy migrates from the 
star-forming blue sequence to the red cloud on the optical CMD.  However, the 
$u-r$ CMD is very well fit by the sum of only two Gaussians \citep{Strateva01, 
Baldry04}; an intermediate population is not present in the optical CMD.  Early 
explanations developed to reconcile this apparent discrepancy between theory and 
observation included a sudden transition from the blue sequence to the red 
cloud, often associated with some star-formation quenching mechanism.

Dubbed the ``green valley,'' it is thought that star formation 
is being quenched in the galaxies moving through the green valley 
\citep{Martin07}.  So far, results of studies done with these green valley 
galaxies have been inconclusive as to why or how this is occurs.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section[Data]{SDSS and GALEX data}

\subsection{Optical data --- SDSS}
%  - KIAS-VAGC (morphological classification)
% Should we use NSA for abs. mag. instead?
SDSS \citep{Abazajian09} (absolute magnitudes courtesy of the MPA-JHU 
catalog\footnote{http://www.mpa-garching.mpg.de/SDSS/DR7/})

The KIAS Value-Added Galaxy Catalog 
\citep[KIAS-VAGC]{Choi10} attempted to calculate a morphological class and type 
for all galaxies in SDSS DR7 based on the color $u-r$, color gradient 
$\Delta (g-r)$, and inverse concentration index.

\subsection{UV data --- GALEX}
\citep{Martin05}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section[Results]{Results}

Combining the results of GALEX with the optical photometry of SDSS, we construct 
a NUV$-r$ CMD.  Probing light from even younger stars in the galaxies, GALEX is 
able to increase the separation of the blue sequence and red cloud populations 
of the optical CMD, revealing a third, smaller population of galaxies 
\citep{Wyder07}.

% CMD in NUV-r, showing where green valley galaxies live
\begin{figure}
    \includegraphics[width=0.65\textwidth]{Images/GV/NUVr_CMD_3pop_scatter}
    \caption[NUV-$r$ color-magnitude diagram of SDSS galaxies]{The NUV$-r$ 
    color-magnitude diagram of galaxies in SDSS DR7.  Those galaxies in the red 
    contours have morphological classifications of either normal early types 
    (aimc $=1$) or blue early types (aimc $=2$), as determined by the KIAS-VAGC.  
    The green points represent a subset of the normal late type galaxies (aimc 
    less than 25, excluding those with values of 1 or 2), and the blue contours 
    represents the remaining normal late type galaxies (aimc greater than 25).  
    It is clear that this morphological classification defines those galaxies 
    that are transitioning from the blue sequence to the red cloud.}
    \label{fig:NUVr_CMD}
\end{figure}

Preliminary analysis of mine reveals a population of galaxies that lie in the 
Green Valley on the NUV$-r$ color-magnitude diagram, identified independent of 
their location on the diagram.  I find that, rather than being 
classified based on arbitrary limits placed on the NUV$-r$ values, the galaxies 
can be easily separated into three distinct populations based on the galaxies' 
morphological types as calculated in the KIAS-VAGC; this can be seen in Fig. 
\ref{fig:NUVr_CMD}.  Defined by the $u-r$ color and the color gradient 
$\Delta (g-i)$, it is novel that an estimate of the morphological type of the 
galaxies is an adequate classification for the three populations of the NUV$-r$ 
CMD.  In addition, Fig. \ref{fig:NUVr_hist} shows a histogram of the galaxies 
which overlap in both GALEX and SDSS, separated by their morphological 
classification from the KIAS-VAGC.  It shows that the three populations are well 
fit by three Gaussians --- the new population in the middle is the transient 
galaxy population originally ``missing'' from the optical CMD.

% Histogram of NUV-r, with all, red, blue, green galaxies (aimc values)
\begin{figure}
    \includegraphics[width=0.65\textwidth]{Images/GV/NUVr_CMDclassifications}
    \caption[Distribution of NUV-$r$ of SDSS galaxies]{A histogram of the 
    NUV$-r$ color of those SDSS DR7 galaxies which are also detected in GALEX.  
    The red cloud, blue sequence, and green valley populations are separated by 
    the morphological types as defined by the KIAS-VAGC.  It is readily apparent 
    that the green valley galaxies exist in the space between the red cloud and 
    blue sequence.}
    \label{fig:NUVr_hist}
\end{figure}

\subsection{Large-scale environmental dependence of dwarf galaxy evolution}

Estimates of the gas-phase chemical abundances of galaxies probe their 
integrated star formation histories, which can provide insight into the 
enrichment of the ISM and CGM.  Dwarf galaxies ($M_r > -17$) have a 
slightly different evolutionary history than galaxies of large stellar masses, 
especially when looking at environmental factors.  The lower stellar masses of 
these galaxies makes them more susceptible to damage from galactic interactions 
and supernovae feedback, since they have smaller gravitational potential wells.  
My current work involves studying the large-scale environmental dependence of 
the chemical evolution of dwarf galaxies \citep{Douglass17a,Douglass17b}.  I estimate gas-phase 
metallicities (the oxygen abundance of a galaxy relative to hydrogen) with the 
Direct $T_e$ method, known for its accuracy and unbiased results.  This method 
``directly'' estimates the temperature of the electrons in an H{\sc ii} 
region from a ratio of the [O{\sc iii}] $\lambda$4363 aural line and the 
[O{\sc iii}] $\lambda \lambda$4959,5007 doublet \citep[as discussed in][this ratio 
is sensitive to the temperature of the ionized gas in an H{\sc ii} 
region]{Osterbrock89,Douglass17a}; with the temperature and density, abundance estimates can 
be made based on emission line ratios from the galaxy.  It can be very difficult 
to use, however, as it relies on a relatively strong detection of the weak [O 
{\sc iii}] $\lambda 4363$ auroral line --- the uncertainty in the measured flux 
of this emission line is the greatest source of error when using this method to 
estimate the chemical abundances.  Consequently, it is used most often on blue, 
star-forming galaxies.  A detailed description of the Direct $T_e$ method can be 
found in \cite{Douglass17a}.  We use a BPT diagram \citep{Baldwin81} to determine if a 
galaxy is star-forming or has traces of an AGN in its spectrum.  BPT diagrams 
measure the hardness of a galaxy's spectrum based on the relationship between 
ratios of some of the galaxy's emission lines.  Our star-forming classification 
is a result of the work done by \cite{Brinchmann04}.

A few of the galaxies for which I am able to estimate metallicities reside in 
the green valley.  When compared with the metallicities of galaxies in the blue 
sequence and red cloud, Fig. \ref{fig:Z_hist} shows that the star-forming green 
valley galaxies have much lower oxygen abundances than star-forming galaxies in 
the blue sequence and red cloud.  With nitrogen abundances that fall within the 
same range as the other two galaxy populations, this shift causes the N/O ratio 
to be much higher in green valley galaxies than in the others.

% Histogram of metallicity for red, blue, green galaxies
\begin{figure}
    \includegraphics[width=0.49\textwidth]{Images/GV/Z12logOH_I06relations_SF_t3}
    \includegraphics[width=0.49\textwidth]{Images/GV/N12logNH_I06relations_SF_t3}
    \includegraphics[width=0.49\textwidth]{Images/GV/logNO_I06relations_SF_t3}
    \caption[Distribution of gas-phase chemical abundances in cross-matched SDSS 
    DR7 -- GALEX galaxies]{Histograms of the oxygen abundance (top left), 
    nitrogen abundance (top right), and N/O ratio (bottom center) of the 
    cross-matched SDSS DR7 -- GALEX galaxies (both dwarf galaxies and brighter 
    systems), separated into their locations on the NUV$-r$ color-magnitude 
    diagram according to the morphological type listed in the KIAS-VAGC.  It is 
    readily apparent that the green valley galaxies have much lower oxygen 
    abundances than those in the blue sequence or red cloud.  This, therefore, 
    corresponds to them having the highest N/O values of the three categories.}
    \label{fig:Z_hist}
\end{figure}

When we separate the galaxies in each of the three populations by their 
large-scale environment, we discover a variation in these populations as a 
function of luminosity.  Galaxies are divided into one of two categories for 
their large-scale environment: voids or walls (more dense regions) based on the 
void catalog compiled by \cite{Pan12}.  This void catalog is constructed from 
SDSS DR7 using the VoidFinder algorithm of \cite{Hoyle02}.  As we see in Fig. 
\ref{fig:Mr_bin}, the fraction of galaxies in the green valley depends on the 
large-scale environment, even at fixed stellar mass or luminosity.  A larger 
fraction of wall dwarf galaxies are found in the green valley than for void 
dwarf galaxies.

% Fraction of red, green, blue galaxies binned by Mr in voids, walls
\begin{figure}
    \includegraphics[width=0.49\textwidth]{Images/GV/voidFrac_CMD}
    \includegraphics[width=0.49\textwidth]{Images/GV/wallFrac_CMD}
    \caption[Fraction of galaxies in CMD populations by morphological type]
    {Fraction of void (left) and wall (right) galaxies in each of the three CMD 
    populations, classified by the morphological type listed in the KIAS-VAGC.  
    There is a higher fraction of green valley dwarf galaxies ($M_r > -17$) 
    found in the more dense environments than in the voids.  This would indicate 
    that void galaxies are slightly behind wall galaxies in their evolution, 
    matching predictions based on the $\Lambda$CDM cosmology.}
    \label{fig:Mr_bin}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section[Discussion]{Discussion}

\subsection{Morphological classification and gas content indicators}

% classical classification of morphology v. aimc (aimc appaers to be a good indication of the transition in galaxy evolution
% Are there other markers in the gas content of these galaxies?

The morphological classification that we use to isolate the green valley 
population is relatively unique in that it is analytic; morphological 
classification attempts are often completed in a more subjective manner 
\citep[such as the GalaxyZoo,][]{Lintott11}.  In particular, the 
morphological type provided in KIAS-VAGC is a combination of the color $u-r$ and 
the color gradient $\Delta (g-i)$.  Both these quantities are independent of the 
NUV$-r$ CMD, which is part of the novelty behind why this measure separates the 
galaxies into the three evolutionary stages of the CMD so well.

%I also plan to search for other markers in the gas content of the galaxies in 
%the green valley.  
If a galaxy's star formation is quenched due to a loss of 
cold gas, then its H{\sc i} content will be lower than other galaxies of a 
similar stellar mass and large-scale environment.  If it is quenched due to a 
high gas temperature (from AGN or supernovae feedback), then the temperature of 
the gas will be higher than others of a similar size.  These factors will also 
help to determine when and why a galaxy transitions from star-forming to 
quiescent (and maybe back to star-forming).

\subsection{Testing for evidence of AGN feedback}

During my estimation of the chemical content of galaxies with $M_r > -20$, I 
note that the oxygen abundances of galaxies classified as AGN by their 
emission line ratios in the BPT diagrams exhibit extremely low oxygen abundances 
(but normal nitrogen abundance values) when compared to star-forming galaxies of 
a similar stellar mass and large-scale environment.  The same abundance 
signature is seen in the the oxygen and nitrogen abundance results seen in Fig. 
\ref{fig:Z_hist} of the green valley galaxies.  This might indicate a 
link between some dwarf green valley galaxies and a host AGN.  This 
would support other studies of the transition of galaxies from the blue sequence 
to the red cloud, which attribute the quenching of star formation to accretion 
of a central black hole.

I expect to find a large-scale environmental effect on the star formation 
quenching mechanism in addition to the AGN effects.  Giving us feedback on the 
role of the environment in a galaxy's evolution, these results will have great 
impact on the input parameters of large hydrodynamic simulations.  This project 
will serve as an example of the possible science that will be able to be done 
with the future James Webb Space Telescope.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section[Conclusion]{Conclusion}

### 2017-06-02 KellyDouglass/Thesis/Thesis_sections/Paper1.tex
Papers 1,2, small-scale results-conclusions

\chapter[Metallicity of dwarf galaxies]{Determining the large-scale environmental dependence of gas-phase metallicity in dwarf galaxies}

This paper is published in the \emph{Astrophysical Journal}, 2017 (Vol. 834, 
pages 186--198).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
% Why is it important?

% voids are special environment

Galaxy redshift surveys have shown that the large-scale structure of the galaxy 
distribution is similar to that of a three-dimensional cosmic web \citep{Bond96} 
in which the voids (large, underdense regions that fill upwards of 60\% of 
space) separate galaxy clusters connected by thin filaments of galaxies.  The 
voids found in early surveys \citep[e.g.,][]{Gregory78, Kirshner81, 
deLapparent86} proved to be an ubiquitous feature of large-scale structure.  
Analyses of the Sloan Digital Sky Survey \citep{Abazajian09, Ahn12} have yielded 
catalogs of $10^3$ voids \citep{Pan12, Sutter14}.

%theoretical reasons to think galaxy evolution is different
%  simulations

These cosmic voids are an important environment for studying galaxy formation 
(see \cite{vandeWeygaert11} for a review).  Gravitational clustering within a 
void proceeds as if in a very low density universe, in which aggregation of 
gravitationally bound dark matter halos ends relatively early and there is 
relatively little subsequent interaction between galaxies, both because of the 
lower density and the faster local Hubble expansion.  Thus, the $\Lambda$CDM 
cosmology predicts that galaxies formed in voids should have lower mass and may 
be retarded in their star formation when compared to those in more dense 
environments \citep[e.g.,][]{Gottlober03, Goldberg05, Cen11}.  \cite{Goldberg04} 
show that the interior of a spherical void with 10\% of the mean density in a 
$\Omega_{matter} = 0.3$, $h = 0.7$ universe evolves dynamically like an 
$\Omega_{matter} = 0.02$, $\Omega_{\Lambda} = 0.48$, $h = 0.84$ universe.  
Hydrodynamical cosmological simulations by \cite{Cen11} show that the gas in 
voids remains below the critical entropy threshold, allowing the void galaxies 
to continue forming stars.  While the more dense environment of cluster galaxies 
drastically alters their chemical composition and future evolution through the 
relatively frequent occurrences of mergers, tidal stripping, and/or ram-pressure 
stripping, void galaxies evolve in a relatively pristine environment where 
interactions are far less frequent and star formation may proceed up to the 
present epoch because void galaxies are able to retain their gas.

% dwarfs in particular very sensitive

The effects of the void environment should be most obvious in the dwarf 
galaxies.  Dwarf galaxies are sensitive to many astrophysical effects, including 
cosmological reionization, internal feedback from supernova and photoheating 
from star formation, external effects from tidal interactions and ram pressure 
stripping, small-scale details of dark matter halo assembly, and properties of 
dark matter. Many of these effects have been invoked to attempt to resolve the 
discrepancy between the mass function of galaxy halos predicted by $\Lambda$CDM 
and the observed, much smaller density of dwarf galaxies observed in voids (see, 
e.g., \cite{Kravtsov09} for a review).  It is critical to explore dwarfs in 
voids to complement studies of dwarfs in groups and clusters because the 
assembly histories of low-mass galaxies are predicted to be very different 
\citep[e.g.,][]{Gao07, Lackner12} and observations to date show that the 
properties of dwarfs vary dramatically with environment \citep[e.g.,][]{Ann08, 
Geha12}.  Diffuse cold-mode accretion, rather than mergers, has been suggested 
to be the dominant mechanism for growing dark matter halos in voids 
\citep[e.g.,][]{Keres05, Fakhouri09}.  Late-time gas accretion may be possible 
in voids if void galaxies retain a baryonic reservoir up to the present epoch.  
Thus, these few, lonely, faint galaxies test important features of the structure 
formation model and our understanding of galaxy formation ``gastrophysics.''

%observational evidence about void galaxies
%  our work
%  others

Observational studies of void galaxies have included examination of photometric 
properties such as luminosity \citep{Hoyle05, Croton05, Moorman15}, color and 
morphological type \citep{Grogin00, Rojas04, Patiri06, Park07, 
vonBendaBeckmann08, Hoyle12} star formation rates estimated from optical 
spectroscopy and UV photometry \citep{Rojas05, Moorman15, Beygu16}, and gas 
content \citep{Kreckel12, Moorman16, Jones16}.  Void galaxies tend to be of 
lower luminosity, of late morphological type, blue, have relatively high rates 
of star formation per stellar mass, and gas rich.

% metallicity as measure of SF history

Another important diagnostic of galaxy formation is metallicity, which is a 
measure of the integrated star formation history and is frequently characterized 
by the ratio of the oxygen to hydrogen atomic density (often 
$Z = 12 + \log (\text{O}/\text{H})$, though sometimes given in units of the 
solar metallicity, $Z/Z_{\odot}$).  The metallicity should depend on the 
galaxy's star formation history, specifically the percentage of the galaxy's gas 
that has been processed in stars \citep{Guseva09}.  If void galaxies have only 
recently started forming stars or have recently accreted unprocessed gas, we 
would expect these galaxies to have a lower metallicity than those in more dense 
regions (whose star formation started earlier due to e.g., tidally-triggered 
star formation).  Furthermore, gas-phase metallicity is affected by the 
evolution of a galaxy's stellar population and the composition of its 
interstellar medium (ISM).  It reveals a galaxy's history of releasing metals 
into the ISM via supernovae and stellar winds, ejecting gas via galactic 
outflows, and accreting gas from the surrounding environment 
\citep[see, e.g.,][and references therein]{Cooper08,Cybulski14,Hirschmann14}.  
Understanding the evolution of metallicity in galaxies is therefore crucial in 
uncovering the details of galactic evolution.

% earlier metallicity obs's with small samples
% can now do this with SDSS void galaxies

Observations by \cite{Cooper08, Deng11, Filho15, Pustilnik06, Pustilnik11a, 
Pustilnik11b, Pustilnik13, Pustilnik14} appear to support the hypothesis of 
lower metallicity in void galaxies, while \cite{Kreckel15} find no effect of the 
void environment on their sample of eight void dwarf galaxies.  Most of the 
conclusions of previous work are based on samples containing only a handful of 
galaxies.  Because large sky surveys like SDSS contain a substantial collection 
of dwarf galaxies, we can now analyze the dwarf galaxy population in the 
relatively nearby universe to test this hypothesis with more statistical 
significance.  In particular, the main galaxy sample of SDSS DR7 covers a large 
enough volume to identify over 1000 voids \citep{Pan12} and provides 
spectroscopy to permit metallicity estimates of void dwarf galaxies.  We make 
use of the reprocessed spectroscopic data from the MPA-JHU 
catalog\footnote{Available at \url{http://www.mpa-garching.mpg.de/SDSS/DR7/}} to 
study the metallicity of the large collection of dwarf galaxies in SDSS DR7.  As 
explained by \cite{Tremonti04}, the spectra in the MPA-JHU catalog are analyzed 
with a more detailed stellar continuum, permitting the weaker emission lines to 
become more apparent.  With the dependence of our analysis on weak emission 
lines (especially [O{\sc iii}] $\lambda 4363$), this detailed treatment of the 
weak emission lines should produce more accurate results.  We study the 
metallicity of these galaxies as a function of large-scale environment, testing 
the hypothesis that void dwarf galaxies have lower gas-phase metallicities than 
dwarf galaxies in more dense regions.

Our paper is organized as follows.  Section 2 describes the theory and method 
for using various emission lines to estimate the metallicity of galaxies.  We 
review the source of our data and errors in Section 3.   Section 4 includes the 
results of our metallicity calculations, and we discuss the likelihood of any 
large-scale environmental influence on these results in Section 5.  Finally, 
Section 6 summarizes our conclusions and discusses future work.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Theory]{Estimation of galaxy metallicity from optical spectroscopy}
\label{sec:Theory_P1}
% What is the physics?

\subsection{Overview of Methods}

We characterize the galaxy metallicity using oxygen because it is relatively 
abundant, it emits strong lines for several ionization states in the optical 
regime, and a ratio of its lines provides a good estimate of the electron 
temperature \citep{Kewley02}.  Here, we describe the theory and method we employ 
to estimate oxygen abundances in dwarf galaxies.

UV photons from young stars in an H{\sc ii} region keep the interstellar gas 
partially ionized.  Optical photons are either absorbed and re-emitted 
throughout the region at resonant frequencies (resulting in classically 
permitted electron transitions), or the electrons are collisionally excited 
(resulting in classically forbidden electron transitions).  Collisional 
excitation of the lower energy levels of metal ions is possible because these 
levels are only a few eV above the ground state \citep{DeRobertis87}.  
Consequently, the UV-optical spectrum contains some of the most useful 
diagnostic emission lines.  Due to observational constraints of SDSS DR7 (the 
spectrometer's wavelength range and the signal-to-noise of the resulting 
spectra; see Section \ref{sec:Data}), not all these emission lines are easily 
measured.

Three classes of methods have been developed to estimate the gas-phase 
metallicity of a galaxy, which we label as direct, theoretical, and empirical.  
Direct-$T_e$ methods are based on a measurement of the [O{\sc iii}] 
$\lambda 4363$ auroral line, from which a ``direct'' estimate of the electron 
temperature can be made \citep[e.g.,][]{Izotov06, Kniazev08, Pilyugin07, Yin07}.  
Theoretical methods are based on photoionization models 
\citep[e.g.,][]{Kewley02}.  Empirical methods make an indirect estimate of the 
electron temperature based on calibrated relationships between direct 
metallicity estimates and other strong-line ratios in H{\sc ii} regions 
\citep[see, for example,][]{Pettini04, Pilyugin11, Dopita13, LaraLopez13, 
Marino13}.  While each of these methods provides an estimate for the 
metallicity, they are all developed for use on sets of galaxies with different 
characteristics (stellar mass or gas-phase metallicity, for example).  
Previously, most theoretical and empirical methods have been calibrated with 
galaxies of larger stellar mass and higher luminosity.  Because the properties 
of dwarf galaxies differ from those of higher luminosity (and larger stellar 
mass), most of these methods drastically over- or under-estimate the gas-phase 
metallicity for dwarf galaxies.  Consequently, we must exercise caution when 
applying these various calculation methods for estimating the metallicity of 
dwarf galaxies.  We attempt to avoid any calibration issues by estimating 
gas-phase metallicity using the direct-$T_e$ method.  This method relies on the 
weak [O{\sc iii}] $\lambda 4363$ emission line, which limits the number of dwarf 
galaxies we can analyze.  However, because this method provides more reliable 
metallicity estimates than any of the others for dwarf galaxies, we chose 
quality over quantity in our results.

%-------------------------------------------------------------------------------
% Oxygen
\subsection{[O{\sc iii}]}\label{sec:O3}

\begin{figure}
	\centering
    \includegraphics[width=0.5\textwidth]{Images/Paper1/energy_level_diagram-figure0}
	\caption[{[\ion{O}{3}] and [\ion{S}{2}] energy-level diagram}]{Energy-level 
	diagram for [O{\sc iii}] $(2p^2)$ and [S{\sc ii}] $(3p^3)$ ions.  The most 
	important transitions are shown; all are in the visible spectrum.  These 
	forbidden transitions in oxygen provide an estimate of the electron temperature 
	in the interstellar gas, while the forbidden sulfur transitions provide an 
	estimate of the electron number density.  With estimates of the electron 
	temperature and number density, we can convert emission line flux ratios into 
	chemical abundance ratios.}
	\label{fig:transitions_P1}
\end{figure}

% Gordon commented that this paragraph's phrasing needs to be modified if it is going into a paper, but it is fine for a thesis.  Is it too technical for a published paper?  What modifications might need to be made?
There are three significant emission lines for doubly-ionized oxygen.  The 
relative excitation rates to the $^1$S and $^1$D energy levels depend very 
strongly on the electron temperature, $T_e$; therefore, the relative strengths 
of these emitted lines can be used to measure the electron temperature 
\citep{Osterbrock89}.  In the low-density limit $(n_e < 10^5 \text{ cm}^{-3})$, 
most excitations to the $^1$D level result in an emission of a photon with a 
wavelength of either $5007\text{\AA}$ or $4959\text{\AA}$, as shown in Fig. 
\ref{fig:transitions_P1}.  Most excitations up to $^1$S produce a photon of 
wavelength $4363\text{\AA}$, followed by a photon of either of the two previous 
wavelengths (since the electron is now in the $^1$D level).

At higher densities, collisional de-excitation begins to influence these 
emission rates \citep{Osterbrock89}.  Because the $^1$D level has a longer 
lifetime than the $^1$S state, it is collisionally de-excited at lower electron 
densities.  This weakens the $\lambda 4959$ and $\lambda 5007$ emission lines.  
At the same time, the additional collisional excitations of the $^1$D state 
permitted by the higher electron densities strengthen the $\lambda 4363$ 
emission line.

[O{\sc iii}] $\lambda 4363$ is a temperature-sensitive forbidden transition line 
of doubly-ionized oxygen that is the preferred line to use when measuring the 
metallicity of galaxies.  Since the most effective cooling channel in these 
H{\sc ii} regions is oxygen line emission, lower metallicity regions have higher 
temperatures  \citep{Saintonge07}.  Collisional excitations up to this energy 
level are more common at higher temperatures, since there are more electrons 
with the kinetic energy required to excite the O$^{++}$ ion to this energy 
level.  As a result, the line strength of [O{\sc iii}] $\lambda 4363$ correlates 
with the region's temperature and is therefore anticorrelated with the 
metallicity of the galaxy.  [O{\sc iii}] $\lambda 4363$ is already one to two 
orders of magnitude weaker than the [O{\sc iii}] $\lambda \lambda 4959, 5007$ 
doublet, so it is very difficult to obtain an accurate ratio with this line.  It 
is for these reasons that other ``empirical'' relations were developed for 
metallicity calculations, eliminating the need for an electron temperature 
estimate from this emission line.

Given an electron temperature and density, the flux ratio of the [O{\sc iii}] 
$\lambda \lambda 4959, 5007$ doublet to H$\beta$ provides an abundance estimate 
for doubly-ionized oxygen.

%-------------------------------------------------------------------------------
\subsection{[O{\sc ii}]}
A less temperature-sensitive line than [O{\sc iii}] $\lambda 4363$, the 
[O{\sc ii}] $\lambda 3727$ forbidden transition doublet of singly-ionized 
oxygen is often used in metallicity calculations.  With an electron temperature 
and density, its flux provides an estimate of the abundance of singly-ionized 
oxygen.  In SDSS spectra, this line can be observed for objects with a redshift 
greater than 0.02.  However, because dwarf galaxies are inherently faint objects 
($M_r > -17$), they are targeted for spectroscopy in SDSS only out to redshift 
$z\sim 0.03$, thus we can only estimate the metallicity of dwarf galaxies in the 
redshift range $0.02 < z < 0.03$.

%-------------------------------------------------------------------------------
% Sulfur
\subsection{[S{\sc ii}]}
Just as we are able to measure the electron temperature from [O{\sc iii}] 
transitions, we can estimate the electron number density from [S{\sc ii}] 
transitions.  Below a density of about $100 \text{ cm}^{-3}$, the [S{\sc ii}] 
$\lambda 6716 / \lambda 6731$ ratio has a weak dependence on the density.  All 
our galaxies fall within this low-density regime, so we assume a low-density 
limit of $n_e = 100 \text{ cm}^{-3}$.

%Similar to the sensitivity of the doubly-ionized oxygen ion transitions to the 
%electron temperature of the surrounding gas, the transitions for singly-ionized 
%sulfur are sensitive to electron number density.  The relative excitation rates 
%depend only on the ratio of the collision strengths when two emission lines 
%(from the same ion) with nearly identical excitation energies are compared 
%\citep{Osterbrock89}.  If the two levels have different transition probabilities 
%and/or different collisional de-excitation rates, their ratio depends on the 
%density.
%
%The relative excitation rates of the two lines shown in Fig. 
%\ref{fig:transitions_P1} are proportional to their statistical weights; thus, the 
%ratio of the line intensities is a constant in the low-density limit 
%\citep{Osterbrock89}.  In the high-density regime, this ratio is best accurately 
%described by a Boltzmann population ratio.  There is a critical density for the 
%energy levels which describes the turning point between these two extremes.

%-------------------------------------------------------------------------------
\subsection{Direct $T_e$ method}
We use the method published by \cite{Izotov06}, which is based on the 
astrophysics in \cite{Osterbrock89}.  It makes use of the [O{\sc iii}] 
$\lambda 4363$, $\lambda \lambda 4959, 5007$ lines and the [O{\sc ii}] 
$\lambda 3727$ doublet.  While often regarded as the most accurate estimate of 
the metallicity, it is difficult to employ due to the restrictions on 
[O{\sc iii}] $\lambda 4363$.  Consequently, this method is best suited for 
low-redshift, low-metallicity galaxies.  The electron temperature is derived by 
solving the following system of equations:
\begin{equation}
	t_3 = \frac{1.432}{\log[(\lambda 4959 + \lambda 5007)/\lambda 4363] - \log C_T}
\end{equation}
where $t_3 = 10^{-4} T_e(\text{O}^{++})$ and
\begin{equation}
	C_T = (8.44 - 1.09t_3 + 0.5t_3^2 - 0.08t_3^3)\frac{1 + 0.0004x_3}{1 + 0.044x_3}
\end{equation}
where $x_3 = 10^{-4} n_e t_3^{-0.5}$.  The ionic abundances are then found with 
the equations
\begin{align}
	12 + \log \left( \frac{\text{O}^+}{\text{H}^+} \right) &= \log \frac{\lambda 3727}{\text{H}\beta} + 5.961 + \frac{1.676}{t_2} - 0.40\log t_2 - 0.034t_2 + \log (1+1.35x_2) \\
	12 + \log \left( \frac{\text{O}^{++}}{\text{H}^+} \right) &= \log \frac{\lambda 4959 + \lambda 5007}{\text{H}\beta} + 6.200 + \frac{1.251}{t_3} - 0.55\log t_3 - 0.014t_3
\end{align}
where $t_2 = 10^{-4} T_e(\text{O}^+)$, $t_2 = 0.7t_3 + 0.3$ \citep{Garnett92}, 
and $x_2 = 10^{-4} n_e t_2^{-0.5}$.  \cite{Andrews13} show that this relation 
between $T_e(\text{O}^+)$ and $T_e(\text{O}^{++})$ may overestimate the 
temperature in the low ionization zone, causing the calculated metallicities to 
be underestimated.  Because we care only about the relative metallicity values 
of the galaxies, this effect will only affect our results in galaxies where 
O$^+$ dominates the oxygen abundance (where O$^+$/O$^{++} > 1$) in higher 
temperature regions (or low metallicities).  As shown in Fig. 
\ref{fig:O2O3_ratio}, this affects perhaps fifteen galaxies and does not change 
our conclusions.

\begin{figure}
    \includegraphics[width=0.5\textwidth]{Images/Paper1/1sig_I06_dwarf_SF_t3_OpOpp_Z12logOH}
    \caption[O$^+$/O$^{++}$ versus metallicity]{Metallicity of our 135 dwarf 
    galaxies as a function of O$^+$/O$^{++}$.  While either O$^+$ or O$^{++}$ 
    can dominate our galaxies' oxygen abundances, only those with low 
    metallicities (high temperatures) and with O$^+$ dominating the abundance 
    will be affected by the temperature overestimate of the low-ionization zone 
    as found by \cite{Andrews13}.  The small number of galaxies (15/135) that 
    may suffer from this possible temperature overestimate do not affect our 
    results.}
    \label{fig:O2O3_ratio}
\end{figure}

The total gas-phase oxygen abundance is equal to the sum of the abundances of 
each of the ionized populations:
\begin{equation}
	\frac{\text{O}}{\text{H}} = \frac{\text{O}^{++}}{\text{H}^+} + \frac{\text{O}^+}{\text{H}^+}
\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Data]{SDSS data and galaxy selection}\label{sec:Data}
% What are the assumptions?
The SDSS Data Release 7 (DR7) \citep{Abazajian09} is a wide-field multi-band 
imaging and spectroscopic survey, using drift scanning to map approximately 
one-quarter of the northern sky.  Photometric data in the five band SDSS system 
--- $u$, $g$, $r$, $i$, and $z$ --- are taken with a dedicated 2.5-meter 
telescope at the Apache Point Observatory in New Mexico \citep{Fukugita96, 
Gunn98}.  Galaxies with a Petrosian $r$-band magnitude $m_r < 17.77$ are 
selected for spectroscopic analysis \citep{Lupton01, Strauss02}.  The spectra 
have an observed wavelength range of $3800\text{\AA}$ to $9200\text{\AA}$ with a 
resolution $\lambda / \Delta \lambda \sim 1800$, and are taken using two 
double fiber-fed spectrographs and fiber plug plates with a minimum fiber 
separation of 55 arcseconds \citep{Blanton03}.  The emission line flux data used 
in this study are from the MPA-JHU value-added catalog, which is based on the 
SDSS DR7 sample of galaxies.  Absolute magnitudes, colors, and all other 
additional data are from the KIAS value-added galaxy catalog \citep{Choi10}.

%-------------------------------------------------------------------------------
\subsection{Spectroscopic selection}

To satisfy the needs of our analysis, we make the following cuts to our sample.  
All analyzed galaxies must have relatively recent star formation, since UV 
photons are needed to excite the interstellar gas to produce the required 
emission lines.  As a result, each galaxy must have a star-forming BPT 
classification by \cite{Brinchmann04}.  In addition, because we analyze only 
dwarf galaxies ($M_r > -17$), there is a natural redshift upper limit of 0.03 on 
the samples; dwarf galaxies at higher redshifts are not bright enough to be 
included in the spectroscopic data of SDSS.  For a galaxy to be analyzed, we 
require a minimum $5\sigma$ detection of the H$\beta$ emission line and at least 
a $1\sigma$ detection of the [O{\sc iii}] $\lambda 4363$ forbidden transition.  
The restriction on both these lines eliminate those galaxies with a low S/N 
spectrum.  This is particularly important for [O{\sc iii}] $\lambda 4363$, as it 
is inherently a weak emission line.  We are aware that implementing this 
restriction on [O{\sc iii}] $\lambda 4363$ eliminates those galaxies with higher 
metallicities, since the strength of this line is inversely proportional to the 
metallicity of the galaxy (see Sec. \ref{sec:O3} for details).  However, we show 
that this restriction does not affect our conclusions on the large-scale 
environmental dependence on the gas-phase metallicity.

In addition, we also eliminate galaxies with temperature estimates 
$T_e (\text{O{\sc iii}}) > 3\times 10^4\text{ K}$.  Gas temperatures above this 
threshold are not physical for an H{\sc ii} region \citep[inferred 
from][]{Osterbrock89, Izotov06, Luridiana15}.

For the dwarf galaxies in our sample, the [O{\sc ii}] $\lambda 3727$ spectral 
line is very close to the edge of the spectrometer due to their maximum redshift 
$z < 0.03$.  Consequently, its flux measurement is not always reliable.  
Therefore, the flux values labeled \texttt{oii\_flux} in the MPA-JHU catalog are 
used instead of the combined flux values measured for the [O{\sc ii}] 
$\lambda \lambda 3726,3729$ doublet.  Because the velocity dispersion is not 
fixed when measuring the flux found in \texttt{oii\_flux}, the resulting 
measurements tend to be more realistic than those measured with the fixed 
dispersion (C. Tremonti, private communication).  In addition, those galaxies 
with remaining erroneous measurements for the [O{\sc ii}] $\lambda 3727$ 
doublet were removed by hand, after comparing the listed flux values to the 
spectra by eye.  All spectral lines used in the analysis must have a flux 
greater than 0, to ensure that they are emission lines.

%-------------------------------------------------------------------------------
\subsection{Void classification}

Void galaxies are identified using the void catalog compiled by \cite{Pan12}, 
which was built based on the galaxies in SDSS DR7 catalog.  Starting with 
galaxies with absolute magnitudes $M_r < -20$, the VoidFinder algorithm of 
\cite{Hoyle02} removes all isolated galaxies (defined as having the third 
nearest neighbor more than 7 $h^{-1}$ Mpc away).  After applying a grid to the 
remaining galaxies, spheres are grown from all empty grid cells (cells 
containing no galaxies).  A sphere reaches its maximum size when it encounters 
four galaxies on its surface.  To be classified as a void (or part of one), a 
sphere must have a minimum 10 Mpc radius.  If two spheres overlap by more than 
10\%, they are considered part of the same void.  See \cite{Hoyle02} for a more 
detailed description of the VoidFinder algorithm.  Those galaxies that fall 
within these void spheres are classified as void galaxies.  Those galaxies that 
lie outside the spheres are classified as wall galaxies.  Because we cannot 
identify any voids within 10 Mpc of the edge of the survey, we do not include 
the galaxies that fall within this region in either the void or wall sample 
(throughout this paper, these galaxies are labeled as ``Uncertain'').

Of the $\sim$ 800,000 galaxies with spectra available in SDSS DR7, 9519 are 
dwarf galaxies.  Applying the spectroscopic cuts, 42 void dwarf galaxies, 89 
wall dwarf galaxies, and 4 dwarf galaxies with uncertain large-scale 
environments are left to analyze (for a total of 135 dwarf galaxies, 131 of 
which are used in the environmental tests).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Results]{Metallicity analysis and results}

Our primary objective is to perform a relative measurement of metallicity of 
dwarf galaxies to discern how the large-scale environment affects their chemical 
evolution.  As discussed in Section \ref{sec:Theory_P1}, the strength of and 
ability to observe different spectral lines between various surveys and 
observations require multiple methods to be developed for metallicity 
calculations.  In this paper, we use only the Direct $T_e$ method, because no 
other method has yet been calibrated using dwarf galaxies.  The results from the 
various methods are not directly comparable; while they all return metallicities 
within the same range, the same galaxy can have very different metallicity 
values depending on which method is used.  Conversions between methods have been 
developed \citep[see][]{Kewley08}, but it is not clear that these conversions 
would be accurate for dwarf galaxies.  Unfortunately, there are not enough 
galaxies available in our sample to calibrate these other methods for dwarf 
galaxies.

All line ratios listed are ratios of the emission line fluxes.  Galaxies with 
low metallicities have $Z = 12 + \log (\text{O}/\text{H}) < 7.6$ 
\citep{Pustilnik06}; galaxies with high metallicities have $Z > 8.2$ 
\citep{Pilyugin06}.  The solar metallicity is $Z_{\odot} = 8.69\pm 0.05$ 
\citep{Asplund09}.

%-------------------------------------------------------------------------------
\subsection{Estimation of uncertainties and confirmation of our method}

% Uncertainties
We estimate uncertainties in the computed metallicity using a Monte-Carlo 
method.  Using the measured line fluxes and scaled uncertainty 
estimates\footnote{As described at 
\url{http://wwwmpa.mpa-garching.mpg.de/SDSS/DR7/raw_data.html}} from the 
MPA-JHU catalog, 100,000 different metallicities are calculated for a given 
galaxy.  For each estimate, the flux of a line is drawn from a normal 
distribution, with the expectation value being the original measured flux and 
the standard deviation being the given error in the flux measurement.  
We require all simulated line fluxes to be positive, as negative flux values 
would result in erroneous metallicity values.  The standard deviation in the set 
of these 100,000 calculated values is used as the error in the metallicity 
estimate for the galaxy.  As a result, these uncertainties tend to be larger 
than those quoted in other sources, as they include more information than just 
the quality of the fit used to derive the metallicity.

% Comparison to Yin07 metallicities for their galaxies
We compare results of our analysis of the same set of SDSS galaxies that 
\cite{Yin07} analyze to confirm that our code was working properly, since 
\cite{Yin07} also uses the metallicity method outlined in \cite{Izotov06}.  The 
results of this comparison can be seen in Fig. \ref{fig:Yin07_comp}.  
\cite{Yin07} also uses the MPA-JHU catalog as the source for their data, so our 
results should be identical.

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{Images/Paper1/Yin07_comparison_fit}
    \caption[Metallicity comparison to \cite{Yin07}]{Metallicity (\OH) 
    comparison between our calculated estimates and those made by \cite{Yin07}.  
    Error bars have been omitted for clarity.  These are not the dwarf galaxies 
    analyzed in this paper, but rather the sample of galaxies analyzed by 
    \cite{Yin07} to confirm that our version of the calculation is correct.  
    Both \cite{Yin07} and we have used the metallicity method outlined by 
    \cite{Izotov06}.}
    \label{fig:Yin07_comp}
\end{figure}

%-------------------------------------------------------------------------------
\subsection{Results}

\begin{figure*}
    \centering
    \includegraphics[width=0.49\textwidth]{Images/Paper1/1sig_dwarf_SF_t3_12logOH_hist}
    \includegraphics[width=0.49\textwidth]{Images/Paper1/1sig_dwarf_SF_t3_12logOH_CDF}
    \caption[Metallicity distribution of 135 dwarf galaxy sample]{Histogram and 
    associated cumulative distribution function of the gas-phase metallicity of 
    void dwarf (red solid line) and wall dwarf (black dashed line) galaxies.  A 
    two-sample KS test of the two data sets results in an asymptotic $p$-value 
    of 0.67, indicating a 67\% probability that a test statistic greater than 
    the observed value of 0.13 will be seen.  This is reflected visually, as 
    there appears to be very little difference in the two populations, 
    indicating that there is little large-scale environmental influence on the 
    metallicity of dwarf galaxies.}
    \label{fig:met1sig}
\end{figure*}

Metallicities calculated using the Direct $T_e$ method for our dwarf galaxy 
sample are listed in Table \ref{tab:Results_P1}, along with other key 
identification for the galaxies (including whether they are a void or wall 
galaxy).  A histogram of the resulting metallicities is shown in Fig. 
\ref{fig:met1sig}.  As can be seen in Fig. \ref{fig:met1sig}, there is very 
little difference in the spread of metallicity values in dwarf galaxies between 
voids and walls.  A two-sample Kolmogorov-Smimov (KS) test quantifies this 
observation --- it produced a test statistic of 0.13, corresponding to a 
probability of 67\% that a test statistic greater than or equal to that observed 
will be measured if the void sample were drawn from the wall sample; the 
cumulative distribution function (CDF) of these samples can be seen on the right 
in Fig. \ref{fig:met1sig}.

% Results table
\input{Tables/Paper1/results_table_short}

The requirement of a minimum $1\sigma$ detection of [O{\sc iii}] $\lambda 4363$ 
eliminates galaxies with a low-quality spectrum and those with a weak 
[O{\sc iii}] $\lambda 4363$ line.  Since this line is inversely proportional to 
the oxygen abundance in the interstellar gas, this biases the sample towards 
more low-metallicity galaxies.  To see how much this cut affects the results, we 
perform the same analysis with no minimum detection limit of [O{\sc iii}] 
$\lambda 4363$.  As can be seen in Fig. \ref{fig:met0sig}, this adds a 
substantial number of galaxies to the sample (there are now 126 void galaxies 
and 270 wall galaxies analyzed), predominately in the high-metallicity regime.  
As Table \ref{tab:Percents} makes apparent, there is now a higher percentage of 
void dwarf galaxies with high metallicities than wall dwarf galaxies.  However, 
the uncertainties in the metallicity estimates for 
$12 + \log (\text{O}/\text{H}) > 8.2$ are almost 0.5 dex, due to the extremely 
weak [O{\sc iii}] $\lambda 4363$ auroral line.  Because of these uncertainties, 
the difference in the distributions may not be statistically significant.

\begin{figure*}
    \centering
    \includegraphics[width=0.49\textwidth]{Images/Paper1/0sig_dwarf_SF_t3_12logOH_hist}
    \includegraphics[width=0.49\textwidth]{Images/Paper1/0sig_dwarf_SF_t3_12logOH_CDF}
    \caption[{Metallicity distribution with no restriction on [\ion{O}{3}] 
    $\lambda 4363$}]{Histogram and associated cumulative distribution function 
    comparing the gas-phase metallicity of void dwarf (red solid line) and wall 
    dwarf (black dashed line) galaxies, testing the effect of the S/N 
    restriction on the auroral [O{\sc iii}] $\lambda 4363$ line.  The galaxies 
    here have no minimum detection of [O{\sc iii}] $\lambda 4363$ line.  As 
    expected, eliminating the restriction on this line includes more high 
    metallicity galaxies to the sample, shifting the void dwarf galaxy 
    distribution to have higher metallicities than the wall dwarf galaxies.  
    However, due to the significant uncertainties in the metallicity estimates 
    for $12 + \log (\text{O}/\text{H}) > 8.2$ due to the weak [O{\sc iii}] 
    $\lambda 4363$ auroral line, this difference in the distributions may not be 
    statistically significant.}
	\label{fig:met0sig}
\end{figure*}

\begin{table}
    \centering
    \begin{tabular}{cccc}
        \hline \\
         & $Z < 7.6$ & $7.6 \leq Z < 8.2$ & $Z \geq 8.2$\\
        \hline \\
        \hline \\
        \multicolumn{4}{c}{$1 \sigma$ restriction on [O{\sc iii}] $\lambda 4363$}\\
        \hline \\
        Void & 9.52\% (4)   & 66.67\% (28) & 23.81\% (10)\\
        Wall & 19.10\% (17) & 59.55\% (53) & 21.35\% (19)\\
        \hline \\
        \multicolumn{4}{c}{No restriction on [O{\sc iii}] $\lambda 4363$}\\
        \hline \\
        Void & 13.33\% (16) & 45.83\% (55)  & 40.83\% (49)\\
        Wall & 23.26\% (60) & 46.12\% (119) & 30.62\% (79)\\
        \hline
    \end{tabular}
    \caption[Metallicity distribution of 135 dwarf galaxy sample]{Percentages of 
    galaxies with calculated metallicities within the labeled metallicity 
    ranges, with the number of galaxies in each category in parentheses.  
    Removing the S/N restriction on [O{\sc iii}] $\lambda 4363$ especially 
    increases the number of dwarf galaxies with high metallicities, changing the 
    distribution so that void dwarf galaxies have higher metallicities than wall 
    dwarf galaxies.  However, due to the large uncertainties in the metallicity 
    estimates for $12 + \log (\text{O}/\text{H}) > 8.2$, this difference in the 
    distributions may not be statistically significant.\label{tab:Percents}}
\end{table}

%-------------------------------------------------------------------------------
\subsection{Sources of systematic error}

It is well-known that many physical properties of galaxies vary with the 
distance from the center of the galaxy \citep{Bell00}.  Therefore, a metallicity 
measurement is dependent on the location of the spectroscopic fiber on the 
galaxy.  If not all the light of the galaxy is contained within the fiber of the 
spectrograph, the estimated metallicity will not necessarily be representative 
of a global metallicity value.  Indeed, it has been shown that different parts 
of a galaxy have different metallicity values \citep{Bell00}.  In SDSS, the 
fiber size is 3 arcseconds -- this corresponds to a physical diameter between 
1.29 kpc and 1.93 kpc at redshifts $0.02 < z < 0.03$.  For many of the dwarf 
galaxies, this covers more than 50\% of the galaxy's luminous surface.  The 
fiber is almost always centered on the brightest spot of the galaxy.  For spiral 
and elliptical galaxies, this is often the center of the galaxy.  Since 
the metallicity of the center of a galaxy is often higher than at its edge, 
these metallicity values may be overestimates of the global metallicity.  Many 
dwarf galaxies are irregular galaxies, where the fiber is instead focused on a 
bright H{\sc ii} region.
% Consider rewording this part, to make it more concise and less wordy.

Due to the requirements we place on the emission lines for the galaxies, we are 
inherently limiting our sample to only blue, star-forming galaxies.  This is not 
a representative sample of the dwarf galaxy population.  Rather, in this study 
we are only able to comment on the large-scale environmental influence on blue, 
star-forming dwarf galaxies in a narrow redshift range.  Unfortunately, we 
cannot measure the metallicity of red dwarf galaxies with the Direct $T_e$ 
method, since we need the UV photons from young stars to excite the interstellar 
gas.

%Since SDSS is a magnitude-limited survey, there are many selection effects 
%inherent in the included galaxies.  Fortunately, since we are looking at only 
%dwarf galaxies with particular spectral lines, some of these selection effects 
%are eliminated, but includes others.  While these effects are expected to be 
%relatively minor, further study with other surveys will help determine if any of 
%these selection effects, especially aperture bias, have a significant influence 
%on our final results.

%-------------------------------------------------------------------------------
\subsection{Comparison to previously published metallicity measurements}

To place our metallicity measurements in the context of previous work, we 
compare our results to the metallicity values measured by \cite{Tremonti04}.  
While we both use data from the MPA-JHU value-added catalog, \cite{Tremonti04} 
employs an empirical method for estimating the metallicity, which is based on 
calibrated relationships between direct metallicity values and strong-line 
ratios.  The results of this comparison are shown in Figure \ref{fig:T04comp}.  
Unfortunately, the range of metallicity values found by \cite{Tremonti04} is 
limited to those galaxies with high metallicities 
$(12 + \log(\text{O}/\text{H}) > 8.5)$, due to the characteristics of their 
sample and their method; they found less than 2\% of their total sample to have 
metallicities less than 8.5.  \cite{Kennicutt03} shows that methods which make 
extensive use of the strong emission lines (so-called ``strong-line'' methods) 
can overestimate the metallicity abundances by as much as 0.3 dex.  A similar 
comparison is made in \cite{Yin07}, where they too find that the metallicity 
estimates of \cite{Tremonti04} are overestimated by 0.34 dex on average.  This 
can be seen quite clearly in Figure \ref{fig:T04comp}, as there is no 
correlation between galaxies with our estimates of 
$12 + \log (\text{O}/\text{H}) < 8$ and the metallicities measured by 
\cite{Tremonti04}, since their metallicities are much higher than ours.  The 
formal correlation coefficient between these two data sets is $0.00 \pm 0.087$; 
the correlation coefficient for those galaxies we measure to have metallicities 
greater than 7.6 (so excluding the low-metallicity galaxies) is 
$0.12 \pm 0.093$.  While this shows a slightly stronger correlation, we realize 
that these galaxies cover a limited range of metallicity values.  As a result, 
any scatter due to the errors in the calculations will result in a low 
correlation coefficient, which is what we see.  Therefore, by Fig. 
\ref{fig:T04comp}, we can see that there is a reasonable agreement between our 
metallicity values and those of \cite{Tremonti04}, excluding those galaxies we 
found to have extremely low metallicity values.

While it is known that there are systematic offsets between different 
metallicity calculation methods \citep{Kewley08}, that does not seem to be the 
case in the relation between our metallicities (measured with the Direct $T_e$ 
method) and those of \cite{Tremonti04} (measured with a combination of 
``strong-line'' methods).  While the metallicity estimates by \cite{Tremonti04} 
do not appear to be significantly biased at 
$8 < 12 + \log (\text{O}/\text{H}) < 8.5$, they overestimate the metallicities 
for low-metallicity galaxies.

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{Images/Paper1/1sig_dwarf_I06_SF_t3_T04comparison}
    \caption[Metallicity comparison to \cite{Tremonti04}]{Metallicity (\OH) 
    comparison between our calculated estimates and those made by 
    \cite{Tremonti04}.  Error bars have been omitted for clarity.  Excepting the 
    extreme low-metallicity galaxies we found, most galaxies agree reasonably 
    well with the values already published.  It is important to note that the 
    strong-line methods \citep[like those used by][]{Tremonti04} are not 
    calibrated for low-metallicity values and are known to overestimate the 
    metallicity by as much as 0.3 dex \citep{Kennicutt03}.  Thus, it is not 
    surprising that oxygen abundances measured using the direct method find 
    lower metallicity, particularly at very low metallicities.}
    \label{fig:T04comp}
\end{figure}

% None of the galaxies analyzed by Kreckel15 have SDSS spectra - they all have 
% magnitudes fainter than 17.77 (so they are too faint for the SDSS 
% spectrometer).

% None of the galaxies analyzed by Kniazev03 are in our sample - they are either 
% too close to measure [OII] 3727, or they are brighter than our absolute 
% magnitude limit.

%-------------------------------------------------------------------------------
\subsection{Mass-metallicity relation}

A strong correlation between the stellar mass and metallicity of galaxies 
reflects the fundamental connection between galactic mass and the chemical 
evolution of galaxies.  We use stellar mass estimates from the MPA-JHU catalog 
to examine the mass-metallicity relation in our sample of 135 dwarf galaxies.  
We have also included those galaxies from the MPA-JHU catalog with metallicity 
estimates from \cite{Tremonti04} to place our sample in context.  Due to the 
narrow range of masses in our sample, it is difficult to derive an accurate fit 
to the data.  However, we make comparisons to three published mass-metallicity 
relations \citep{Tremonti04, Mannucci10, Andrews13}.  As can be seen in Fig. 
\ref{fig:MZrelation}, the fit by \cite{Mannucci10} diverges at the low-mass 
limit, and the relations of \cite{Tremonti04} and \cite{Andrews13} predict 
metallicities that are higher than measured for most galaxies in this sample.  
It is important to note that two of these relations are only calibrated down to 
a stellar mass of $10^{8.5} M_{\odot}$.  In Fig. \ref{fig:MZrelation}, these 
relations have been extended to $10^{7.5} M_{\odot}$, in order to continue past 
our galaxy sample.

In addition to looking at the overall mass-metallicity relation for dwarf 
galaxies, we can also investigate the difference in the relation between 
galaxies in voids and those in more dense regions.  There appear to be no 
significant differences in the two populations, indicating minimal influence 
from the large-scale environment on the mass-metallicity relation of these dwarf 
galaxies.  \cite{Hughes13} also find that the stellar mass-metallicity relation 
is independent of large-scale environment.  This prompts the conclusion that the 
internal evolutionary processes of a galaxy have a greater influence on its 
chemical evolution than its large-scale environment.  We expect this dependence 
of the chemical content of a galaxy on its stellar mass, since the accumulated 
metals reflect the integrated history of star formation.  However, we would 
expect an environmental dependence to appear as well, if void galaxies are in an 
earlier stage of evolution and/or are continuing to accrete fresh gas.

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{Images/Paper1/MZ_1sig_I06_dwarf_SF_t3_python}
    \caption[Stellar mass versus metallicity for 135 dwarf galaxy sample]
    {Stellar mass versus metallicity of the 135 analyzed dwarf galaxies.  Error 
    bars have been omitted for clarity.  Due to the limited range of mass (all 
    our galaxies are within a small range of masses, since we are looking only 
    at dwarf galaxies), we cannot derive our own relation between the mass and 
    metallicity.  Some previously published relations are plotted over our data 
    for comparison.  To place our sample in context, we have also included (grey 
    contours) those galaxies from the MPA-JHU catalog with metallicity estimates 
    by \cite{Tremonti04}.  It was from these galaxies that the published 
    relation of \cite{Tremonti04} was derived.}
    \label{fig:MZrelation}
\end{figure}

%-------------------------------------------------------------------------------
\subsection{SFR-metallicity relation}

A fundamental diagnostic of the star formation history of galaxies is the 
relation between stellar mass, metallicity, and star formation rate.  Therefore, 
we also look at the relationship between the (specific) star formation rate and 
metallicity of these 135 dwarf galaxies.  The total (specific) star formation 
rate estimates for these galaxies are from the MPA-JHU value-added catalog, 
based on the technique discussed in \cite{Brinchmann04}.  For low-mass galaxies, 
\cite{Henry13} show that the metallicity is inversely proportional to the star 
formation rate of a galaxy.  However, this is not what is observed in our data, 
as seen in Fig. \ref{fig:SFRZ_relation}.  The correlation coefficient between 
the total (specific) star formation rate and the metallicity 
$r_{sSFR} = 0.49 \pm 0.066$ and $r_{SFR} = 0.52 \pm 0.063$, showing a positive 
correlation between the two properties.  Indeed, those galaxies with the lowest 
metallicities have some of the lowest (specific) star formation rates among the 
dwarf galaxies in our sample.  Since we are limiting our sample to only 
star-forming galaxies, the (s)SFR must be relatively high to emit the UV photons 
needed to ionize the gas.  As a result, all low (s)SFR galaxies will be 
eliminated from our sample, as seen in Fig. \ref{fig:SFR_distribution}.  In 
addition, due to the behavior of the [O{\sc iii}] $\lambda 4363$ auroral line, 
all galaxies with metallicities $12 + \log (\text{O}/\text{H}) \gtrsim 8.5$ are 
also eliminated from the sample.  As a result, we are only calculating the 
metallicity of galaxies in the lower right corners of the (s)SFR plots in Fig. 
\ref{fig:SFRZ_relation}, which is why we see the unexpected correlation.  There 
does not seem to be a difference between the void and wall galaxies in this 
relation, indicating no large-scale environmental influence on the (s)SFR--Z 
relation.

\begin{figure*}
    \centering
    \includegraphics[width=0.49\textwidth]{Images/Paper1/SFR_OH_1sig_I06_dwarf_SF_t3}
    \includegraphics[width=0.49\textwidth]{Images/Paper1/sSFR_OH_1sig_I06_dwarf_SF_t3}
    \caption[(s)SFR versus metallicity for 135 dwarf galaxy sample]{Total star 
    formation rate (SFR) and specific star formation rate (sSFR) versus 
    metallicity of the 135 analyzed dwarf galaxies.  Error bars have been 
    omitted for clarity.  We also plot (grey stars) dwarf galaxies ($M_r > -17$) 
    with metallicity estimates by \cite{Tremonti04}, to place our results in 
    context.  It is significant to note that the majority of our galaxies are on 
    the upper end of the SFR and sSFR for dwarf galaxies, as shown in Fig. 
    \ref{fig:SFR_distribution}.  Note that those galaxies with metallicities 
    $12 + \log(\text{O}/\text{H}) < 7.6$ are on the lower end of the range of 
    sSFR of the dwarf galaxies in our sample.}
    \label{fig:SFRZ_relation}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[width=0.49\textwidth]{Images/Paper1/1sig_I06_SF_t3_SFR_scaled}
    \includegraphics[width=0.49\textwidth]{Images/Paper1/1sig_I06_SF_t3_sSFR_scaled}
    \caption[Distribution of (s)SFR for 135 dwarf galaxy sample compared to SDSS]
    {Distribution of the total star formation rate (SFR) and specific star 
    formation rate (sSFR) for void and wall dwarf galaxies in SDSS are shown in 
    the red solid and black dashed lines, respectively.  Our sample of dwarf 
    galaxies (with metallicity values) is shown in the red and black bars 
    (scaled by a factor of 5 for greater visibility).  We are looking only at 
    the highest SFR found in dwarf galaxies; the sSFR for our sample of dwarf 
    galaxies follows the distribution of all dwarf galaxies.  There is clearly a 
    selection bias against lower SFR.}
    \label{fig:SFR_distribution}
\end{figure*}

%-------------------------------------------------------------------------------
\subsection{Color-metallicity relation}

Metallicity is expected to have a positive correlation with color, as older 
galaxies are expected to have higher metallicities, since they have had more 
time to convert their gas into heavier elements through star formation.  
Therefore, we also look at the color--metallicity relation of our sample of 
135 galaxies -- these relations can be seen in Fig. \ref{fig:colorZ_relation}.  
To place our galaxies in the context of other dwarf galaxies, we have included 
the sample of dwarf galaxies for which \cite{Tremonti04} has estimated 
metallicities (grey stars in the figures).

As we can see in Fig. \ref{fig:colorHist}, by overlaying our distribution of 
dwarf galaxies on Fig. 4 of \cite{Hoyle12}, all of our dwarf galaxies are 
members of the blue dwarf galaxy population.  (The Gaussian parameters for the 
curves are taken from Table 3 in \cite{Hoyle12}.)  This is as expected, since 
the Direct $T_e$ method requires measurements of the emission lines of the 
galaxies; these emission lines are caused by the UV photons of newly formed 
stars, indicating a star-forming galaxy and giving the galaxy a blue color.

While the majority of our galaxies follow the positive correlation between color 
and metallicity, the group of extremely low-metallicity galaxies is less blue 
than their metallicities would indicate.  However, when compared to the red/blue 
curves in Fig. \ref{fig:colorHist}, these galaxies occupy the typical range of 
blue dwarf galaxies, so their colors are not unique.  There is no clear 
separation between the void and wall dwarf galaxies in Fig. 
\ref{fig:colorZ_relation}, indicating that there is little or no large-scale 
environmental influence on the color-metallicity relation of these galaxies.

\begin{figure*}
    \centering
    \includegraphics[width=0.49\textwidth]{Images/Paper1/ur_OH_1sig_I06_dwarf_SF_t3}
    \includegraphics[width=0.49\textwidth]{Images/Paper1/gr_OH_1sig_I06_dwarf_SF_t3}
    \caption[Color versus metallicity for 135 dwarf galaxy sample]{Color (u--r 
    and g--r) versus metallicity of the 135 analyzed dwarf galaxies.  Error bars 
    have been omitted for clarity.  Metallicity is expected to have a positive 
    correlation with color, as older galaxies are expected to have higher 
    metallicities.  To place our galaxies in the context of the dwarf galaxy 
    population, we also plot (grey stars) dwarf galaxies ($M_r > -17$) with 
    metallicity estimates by \cite{Tremonti04}.  We find no significant 
    difference between the void and wall dwarf galaxies, indicating little to no 
    large-scale environmental influence on the color-metallicity relation.}
    \label{fig:colorZ_relation}
\end{figure*}

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{Images/Paper1/urHist_1sig_I06_dwarf_SF_t3}
    \caption[Color distribution of 135 dwarf galaxy sample compared to SDSS]{The 
    $u-r$ color distribution of our 135 dwarf galaxies (red/black histograms) as 
    compared to the color distribution of all SDSS dwarf galaxies as found in 
    Fig. 4 of \cite{Hoyle12} (red/blue curves).  It is clear that our galaxies 
    are among the bluest dwarf galaxies in SDSS.}
    \label{fig:colorHist}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}
% Is there any point in actually running these calculations?

%-------------------------------------------------------------------------------
\subsection{Comparison to literature results}

We find no clear distinction between the metallicities of dwarf galaxies in 
voids and dwarf galaxies in more dense regions.  This result agrees with the 
results of \citet{Mouhcine07, Cooper08, Nicholls14a, Kreckel15} but disproves 
our initial hypothesis and contradicts the published results of 
\cite{Pustilnik06, Pustilnik11a, Pustilnik14, SanchezAlmeida16}.  
\cite{Cooper08} concludes that metal-rich galaxies preferentially reside in 
high-density regions.  Due to our requirement on the [O{\sc iii}] $\lambda 4363$ 
auroral line, we have very few dwarf galaxies with high metallicities.  As a 
result, we are not able to confirm their conclusions. \cite{Deng11} also reports 
a relationship between environment and metallicity.  However, he highlights a 
large difference in metallicity as a function of redshift which correlates with 
his two samples.  It is possible that the dependence he found is actually the 
result of a systematic dependence on redshift in their metallicity calculation.

Many studies suggest that the metallicity of void galaxies should, on average, 
be lower than that of galaxies in more dense regions.  \cite{Mouhcine07} and 
\cite{Cooper08} both perform statistical studies of this relationship on SDSS 
DR4, and \cite{Deng11} repeats this with the DR7 data (only looking at galaxies 
with a redshift $z > 0.02$).  \cite{Mouhcine07} conclude that the relation 
between stellar mass and metallicity is much stronger than that between a 
galaxy's environment and its metallicity.  \cite{Cooper08} find a more 
substantial correlation between a galaxy's environment and its metallicity, but 
point out that the noise of the different methods used to calculate metallicity 
is larger than any environment-metallicity relation.  Our analysis shows that 
there is very little difference between void and wall dwarf galaxies, suggesting 
that the large-scale environment does not strongly influence a dwarf galaxy's 
chemical evolution.

%-------------------------------------------------------------------------------
\subsection{Large-scale environmental influence}
% What does this mean?

% Description of void galaxies (theory)
Consideration of interactions between the interstellar medium (ISM), 
circumgalactic medium (CGM), and intergalactic medium (IGM) suggests that void 
galaxies should have relatively lower metallicity than galaxies in denser 
environments.  We find no such trend, perhaps because the IGM around 
star-forming ``wall galaxies'' in our sample is similar to that of void 
galaxies.

Simulations by \cite{Cen11} show that the entropy of gas in the IGM in voids 
remains below the critical entropy (defined to be when the cooling time of the 
gas is equal to the Hubble time), so the gas from the IGM can cool and fall into 
a void galaxy's CGM.  In a galaxy's ISM, supernovae expel gas (primarily 
metal-rich) into the CGM.  This gas has a higher metallicity than the average 
metallicity of the ISM \citep[shown by][]{Muratov17}.  While some of this gas 
reaches the outer edge of the CGM, most of it cools and falls back onto the 
galaxy's ISM, after having mixed with the hydrogen that has entered the CGM from 
the IGM.  Therefore, the gas falling back into the galaxy's ISM has a lower 
metallicity than the galaxy's ISM.

% Description of wall galaxies (theory)
In contrast to the void galaxies, the IGM around most wall galaxies is not cool 
enough to fall back onto the CGM.  \cite{Cen11} shows that, in general, the IGM 
of a wall galaxy has an entropy higher than the threshold for cooling.  As a 
result, most of the gas that falls back onto a wall galaxy's ISM is not as 
diluted as what falls onto a void galaxy's ISM.  This is where our hypothesis 
originated: because wall galaxies no longer have a source of cool hydrogen in 
the IGM, their metallicities will be higher than that of the void galaxies (for 
a fixed stellar mass).

% What do we actually see, and why?
However, Fig. \ref{fig:met1sig} does not reveal a lower metallicity in void 
galaxies.  Instead, our results indicate that there is no difference in the 
distribution of metallicities in wall and void galaxies.  In detail, Fig. 10 of 
\cite{Cen11} shows that not all wall galaxies rise above the entropy threshold.  
This is also coincident with the sSFR of the galaxies --- those galaxies with 
higher sSFRs are below the entropy threshold, while those with low sSFRs are 
above (independent of their large-scale environment).  Since all our galaxies 
have relatively high sSFRs (as required by the analysis --- star formation is 
required to detect the emission lines necessary for the metallicity 
calculations), it is possible that our population of wall dwarf galaxies is 
still surrounded by a cool IGM, similar to that of the void galaxies.  As a 
result, the wall galaxies still have a source of cool hydrogen, so the resulting 
distribution of the metallicities in the wall and void dwarf galaxies is the 
same.  \cite{Brisbin12} show that most star-forming galaxies with 
$M_* < 2.0\times 10^{10} M_{\odot}$ appear to be fed by the infall of pristine 
or low-metallicity gas.  \cite{Moran12} also find that the lowest-mass galaxies 
($\log(M_*) < 10.2 M_{\odot}$) have a sharp decline in their metallicity at 
large radii; coupled with a strong correlation to the galaxies' H{\sc i} masses, 
they concluded that this indicates newly accreted pristine gas in the galaxies.  
It appears that the large-scale (10 $h^{-1}$ Mpc) has little effect on the 
chemical evolution of galaxies; a galaxy's medium-scale (2 $h^{-1}$ Mpc) 
environment might have much more influence on its chemical evolution.

%There are a few possible explanations as to why there is no difference in the 
%metallicity of void and wall dwarf galaxies.  The recycling of the interstellar 
%medium (ISM) of a galaxy can be described by models that lie at two extremes: a 
%``closed box'' and an ``open box'' model.  In its simplest form, the closed box 
%model \citep{Talbot71} describes a galaxy that has no interaction with its 
%environment --- no material enters or leaves the region.  A galactic fountain 
%\citep{Shapiro76} is a good visualization of the closed box model --- any gas 
%expelled during a supernova falls back onto the galaxy.  In this model, the gas 
%is very turbulent and thus stays well-mixed throughout the galaxy.  Due to the 
%retention of all metals produced by the stars, a galaxy's metallicity will 
%continue to increase through time \citep[evidence for which was recently shown 
%by][]{Zahid12b}.
%
%In the open box model \citep{Hartwick76}, a galaxy's ISM is regularly influenced 
%by the surrounding environment.  Here, pristine gas falls onto the galaxy, 
%providing a constant supply of fresh gas from which to form stars.  In addition, 
%gas expelled in supernovae can be driven from the galaxy.  As a result, a galaxy 
%following an open box model could have a metallicity value that evolves very 
%little with time, if it is constantly accreting pristine gas and if it retains 
%only a fraction of the heavy metals its stars generate.
%
%Due to their large-scale environment, void galaxies undergo fewer galactic 
%interactions and are much more isolated than wall galaxies.  As a result, we 
%expect them to evolve as relatively closed systems, with the possible and 
%significant exception of pristine gas infall up through the present epoch.  Wall 
%galaxies, on the other hand, behave more as an open box model: they frequently 
%interact with other wall galaxies and may be strongly influenced by the local 
%intergalactic medium (e.g., hot gas in clusters).  Consequently, they are 
%constantly being manipulated by their surroundings, causing them to evolve more 
%as an open box galaxy model.
%
%Possible processes that can change the metallicity of a galaxy include:
%\begin{enumerate}
%    \item{Increases metallicity}
%    \begin{enumerate}
%        \item{Supernovae from recent star formation release metal-rich gas into 
%        the ISM}
%        \item{Metal-rich gas expelled from earlier supernovae falls back into 
%        the galaxy (galactic fountain)}
%        \item{Galactic interactions induce a burst of star formation}
%        \item{Star formation due to internal secular evolution}
%    \end{enumerate}
%    \item{Decreases metallicity}
%    \begin{enumerate}
%        \item{Relatively pristine gas falls onto the galaxy}
%        \item{A supernova-driven wind blows metal-rich gas out of the 
%        gravitational potential of the galaxy}
%        \item{Interactions with another galaxy strip metal-rich gas expelled 
%        from supernovae from the galaxy before it has a chance to fall back on 
%        the galaxy (strangulation, harassment, and/or ram-pressure stripping)}
%    \end{enumerate}
%\end{enumerate}
%Due to their large-scale environment, items 1c and 2c are less relevant for void 
%galaxies, and item 2a is less likely for wall galaxies.  Thus, in contrast with 
%our findings, we expect void galaxies to have lower metallicities than wall 
%galaxies.  What follows are a few possible explanations for why we find the 
%distribution of metallicities to be similar between the two environments.
%
%The void galaxies may be recycling their own gas, since there are relatively 
%fewer interactions to remove the metals released by supernovae.  Recently, 
%\cite{McQuinn15} demonstrated that the isolated dwarf galaxy Leo P has retained 
%significantly more of its metals than dwarf galaxies in more dense regions, 
%particularly the gas-phase metals.  Since dwarf galaxies have a smaller 
%gravitational potential than larger galaxies, the supernovae might blow these 
%metal-enriched gases further from the center of the galaxy.  Recent simulations 
%by \cite{Melioli15} on the influence of star formation and supernovae on dwarf 
%galaxy outflows and chemical enrichment appear to support this theory; they find 
%that the metal-rich SN ejecta are thrown far from the galactic plane of dwarf 
%galaxies, even for low SN rates ($7\times 10^{-5}$ to $7\times 10^{-4}$ 
%yr$^{-1}$).  In galaxies in more dense regions, this would increase the 
%opportunity for other galaxies to gather that gas, stripping it from the source 
%galaxy (and thus not allowing it to contribute to the metallicity of the source 
%galaxy).  In contrast, in voids, this gas could eventually fall back onto the 
%dwarf galaxies, as there are significantly fewer surrounding galaxies that could 
%strip this gas away.
%
%In addition, void galaxies may also have a more constant supply of pristine gas 
%to support star formation for longer episodes than those galaxies in more dense 
%regions.  \cite{Brisbin12} have shown that most star-forming galaxies with 
%$M_* < 2.0\times 10^{10} M_{\astrosun}$ appear to be fed by the infall of 
%pristine or low-metallicity gas.  \cite{Moran12} also found that the lowest-mass 
%galaxies ($\log(M_*) < 10.2 M_{\astrosun}$) have a sharp decline in their 
%metallicity at large radii; coupled with a strong correlation to the galaxies' 
%H{\sc i} masses, they concluded that this indicates newly accreted pristine 
%gas in the galaxies.  Since all our dwarf galaxies recently experienced star 
%formation, they most likely have recently acquired some quantity of pristine 
%gas.  Because void galaxies are more isolated than wall galaxies, their supply 
%is probably more constant, allowing for a more constant rate of star formation 
%throughout their history.  In addition, \cite{Moorman16} have found a slightly 
%higher SFE for void dwarf galaxies.  Combined with the more constant gas supply, 
%this might contribute to the similar metallicity distribution in the void and 
%wall dwarf galaxy populations.
%
%To summarize, while it is the case that wall galaxies may experience more star 
%forming episodes due to collisions with other galaxies (increasing their 
%metallicity), and void galaxies gain more pristine gas (decreasing their 
%metallicity), these effects may be canceled by the higher retention rate of gas 
%and longer star formation episodes experienced by void galaxies.  Therefore, the 
%large-scale environment has very little influence on the metallicity of dwarf 
%galaxies.

%-------------------------------------------------------------------------------
\subsection{Extreme low-metallicity galaxies}

Based on observations of six extremely low-metallicity galaxies found in voids, 
\citet{Pustilnik06, Pustilnik11a, Pustilnik13} infer that there is a 
fractionally larger population of metal-poor galaxies located in voids than in 
more dense regions.  \citet{Filho15} study the environment of 140 extremely 
metal-poor galaxies and find that they preferentially reside in low-density 
environments in the local universe.  Of the 135 galaxies we analyze, twenty-one 
have extremely low gas-phase metallicity values 
($12 + \log(\text{O}/\text{H}) < 7.6$); they are highlighted in Table 
\ref{tab:lowZ_P1}.  Of these twenty-one galaxies, only four are found in voids 
(roughly 10\% of the dwarf void population measured) and seventeen are located 
in more dense regions (about 19\% of the dwarf wall population measured).  These 
population fractions do not support the existence of a special population of 
extreme metal-poor galaxies in voids, although the statistics are very small.  
None of these galaxies share the same local environment (none are neighbors to 
each other).  In addition, Fig. \ref{fig:met1sig} shows no evidence to support a 
special population of extremely metal-poor galaxies in the voids, as extremely 
metal-poor galaxies are more prevalent in the more dense regions.

\input{Tables/Paper1/XMPtable}

We find that these twenty-one extremely metal-poor galaxies are redder and have 
a lower (s)SFR than the others when looking at the color (Fig. 
\ref{fig:colorZ_relation}) and (specific) star formation rate (Fig. 
\ref{fig:SFRZ_relation}) of the 135 analyzed galaxies.  The [O{\sc iii}] 
$\lambda 4363$ auroral line is within the noise of the spectra in thirteen of 
these extremely metal-poor dwarf galaxies.  While normally such a weak detection 
of this line corresponds to a high metallicity (see Sec. \ref{sec:O3} for 
details), most of the spectra of these twenty-one galaxies have very low S/N 
overall.  As a result, it is not surprising that [O{\sc iii}] $\lambda 4363$ is 
within the noise here.  Further study of these twenty-one galaxies is 
recommended, to confirm these low metallicity values.
% Vogeley thinks this speculation is unrealistic, since this duration would be very small.
%This could be an 
%indication that these galaxies have just had a fresh infall of pristine gas, but 
%they have not yet formed stars as a result of this addition.
%%
%green peas --- star-forming 
%galaxies which have a green color in SDSS composite images (due to a 
%redshifted and unusually large [O{\sc iii}] $\lambda 5007$ line).
%%
%older than the others in this data set and have lost their metal-rich gas, 
%possibly due to their small gravitational potential well.  These might be 
%indicative of the future of other dwarf galaxies, regardless of their 
%large-scale environment.

%Two of these ten dwarf galaxies have metallicities 
%$12 + \log(\text{O}/\text{H}) < 7.0$, which would make them the most metal-poor 
%galaxies yet discovered.  The detection of the temperature-sensitive 
%[O{\sc iii}] $\lambda 4363$ emission line is very weak in each of these 
%galaxies; with such a strong dependence on this line for the calculation of the 
%metallicity, a high-resolution, high quality spectum is necessary.  The flux of 
%this line as calculated from the SDSS DR7 pipeline is larger than the fluxes 
%from the MPA-JHU catalog -- for all ten of these extreme low-metallicity 
%galaxies, the average difference between these two sources is 
%$2.2\times 10^{-17} \text{ erg/s/cm}^2$.  If the SDSS DR7 data had instead been 
%used in this analysis, the metallicity of these ten galaxies would have been 
%even smaller.  Further study of these two galaxies in particular is recommended, 
%to confirm these metallicity values and discover why the metallicities are so 
%low.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
Using spectroscopic line flux measurements of galaxies in the SDSS DR7 sample 
available through the MPA-JHU catalog, we estimate the metallicity of dwarf 
galaxies based on the Direct $T_e$ method.  From the 135 galaxies analyzed, 
there appears to be no large-scale environmental dependence of the metallicity 
of these galaxies, as the distributions of metallicity values are very similar 
for those residing in voids and those in more dense regions.  Thus, the 
large-scale ($\sim 10\text{ Mpc}$) environment does not appear to strongly 
influence the chemical evolution of dwarf galaxies.

We examine the relationship between metallicity and other physical 
characteristics of our dwarf galaxies.  In the mass-metallicity relation, our 
galaxies are at the low-mass extreme; the extreme low metallicity galaxies we 
found are scattered below this relation.  All our dwarf galaxies are at the 
upper limit in total (s)SFR, and they are on the blue end of the color spectrum.  
There is no large-scale environmental dependence of the metallicity in any of 
these categories.

No special population of extremely metal-poor galaxies is found in the voids, as 
extremely metal-deficient galaxies are found in both voids and walls.  A more 
detailed study of these twenty-one galaxies is recommended, to confirm their 
metallicity values and discover characteristics shared by the population.

Although over 800,000 galaxies in SDSS DR7 have spectroscopic observations, only 
135 are dwarf galaxies with metal line fluxes necessary to estimate gas-phase 
oxygen abundances using the Direct $T_e$ method.  Unfortunately, this was not 
enough to re-calibrate any of the more common methods used to calculate 
metallicity for use on dwarf galaxies.  Better data are required to discern the 
metallicity of a larger selection of dwarf galaxies, from which accurate 
calibrations can be developed.  These estimated ionic abundances can then be 
compared with predictions of the environmental dependence of star formation and 
metallicity from high-resolution hydrodynamic simulations.

### 2017-06-02 KellyDouglass/Thesis/Thesis_sections/Paper2.tex
Papers 1,2, small-scale results-conclusions

\chapter[N/O ratio in dwarf galaxies]{Large-scale environmental dependence of the abundance ratio of nitrogen to oxygen in blue, star-forming galaxies fainter than $L_*$}

This paper is published in the \emph{Astrophysical Journal}, 2017 (Vol. 837, 
pages 42--55).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%    INTRODUCTION
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

% Production of N in stars (primary v. secondary) and its relation to O
The measurement of the abundance of heavier elements relative to hydrogen in a 
galaxy can indicate the galaxy's evolutionary stage.  As stars evolve, they 
slowly convert hydrogen into heavier elements, increasing the ratio of the 
heavier elements (oxygen, nitrogen, etc.) to hydrogen.  The ratio of oxygen to 
hydrogen is often used to determine the chemical evolution of a galaxy because 
oxygen is the most abundant element in the universe (after hydrogen and helium) 
and because oxygen has very strong emission lines in the optical regime that 
cover a range of ionization states \citep{Kewley02}.

It is instructive to also study the relative abundances of the heavy elements in 
a galaxy.  Rather than indicating the amount of hydrogen converted to heavier 
elements, the ratio of two heavy elements can reveal important details about the 
nucleosynthesis process and the chemical conditions of the galaxy when the last 
star formation episode occurred \citep{Izotov99}.  One of the easiest and most 
informative ratios to study is nitrogen to oxygen.

From what we currently understand of stellar nucleosynthesis, we can group its 
products into two classes: primary and secondary elements.  The yields of 
primary elements (carbon and oxygen, for example) are independent of the initial 
metallicity of the star, while the yields of secondary elements depend on the 
initial abundance of heavy elements in the star.  Nitrogen is unique --- it can 
behave as both a primary and secondary element \citep{Matteucci86}.  Nitrogen is 
produced during the CNO cycle, which is one of the two main processes of 
hydrogen burning in a star.  The CNO cycle fuses four protons into a helium atom 
with two positrons and two electron neutrinos as by-products.  It tends to occur 
in more massive stars than our Sun, due to the higher temperature required for 
the fusion processes involved.  Carbon is a catalyst of the CNO cycle, not a 
product.  As a result, if carbon is not initially present within the star, then 
nitrogen is produced in the same relative abundance as carbon and oxygen --- 
nitrogen behaves as a primary element.  However, if the interstellar medium 
(ISM) has a relatively high abundance of heavier elements from previous star 
formation episodes, then nitrogen behaves as a secondary element, since its 
production is based on carbon and oxygen produced prior to the star's creation.

The majority of the production of oxygen and nitrogen is thought to occur in 
different mass stars --- nitrogen is produced in the CNO cycle of 
intermediate-mass stars ($4M_{\odot} < M_* < 8M_{\odot}$), while oxygen is 
primarily produced in the helium-, carbon-, and neon-burning stages of 
higher-mass stars ($M_* > 4M_{\odot}$) \citep{Henry00,Henry06}.  The CNO cycle 
can occur in lower-mass stars (the minimum temperature is only 
$1.5\times 10^7$K), but it requires carbon as a catalyst.  If there is already 
carbon present in a star at its birth, the CNO cycle can commence much earlier 
in the star's lifetime than if it is composed primarily of hydrogen at its 
birth.

% Why are we looking at N/O?  What does a high v. low N/O mean?
A measurement of the N/O ratio indicates where a galaxy is in its chemical 
evolution.  The relative amounts of these two elements can be influenced by 
nucleosynthesis, a galaxy's star formation history, and/or a varying initial 
mass function (IMF), for example.  The star formation history of a galaxy can be 
strongly influenced by the galaxy's environment.  Galactic interactions can 
cause bursts of star formation in addition to secular star formation.  Due to 
the time delay in the release of nitrogen and oxygen from the stellar 
population, galaxies that have more recently experienced star formation will 
result in lower N/O ratios (since oxygen is released sooner than nitrogen, due 
to higher-mass stars being responsible for the production of oxygen).  In 
addition to this time delay, if a galaxy has enough heavy elements present in 
its gas at the time of the stars' births, secondary nitrogen will be produced in 
addition to primary.  This would result in higher N/O ratios, and there would be 
a correlation between the metallicity and the N/O ratio in the galaxies.

% Large-scale environment overview (voids, how they were discovered)
Large galaxy redshift surveys have shown that the large-scale structure of 
galaxies is similar to that of a three-dimensional cosmic web \citep{Bond96}, 
where voids (large, underdense regions that occupy approximately 60\% of space) 
separate galaxy clusters that are connected by thin filaments of galaxies.  
% Why we think the environment should influence N/O, especially in dwarf galaxies
These cosmic voids are an important environment for studying galaxy formation 
\citep[see][for a review]{vandeWeygaert11}, as the $\Lambda$CDM cosmology 
predicts void galaxies to have lower mass and be retarded in their star 
formation when compared to those in denser environments 
\citep[e.g.,][]{Gottlober03, Goldberg05, Cen11}.  Because dwarf galaxies are 
sensitive to many astrophysical effects, including cosmological reionization, 
internal feedback from supernovae and photoheating from star formation, external 
effects from tidal interactions and ram pressure stripping, small-scale details 
of dark matter halo assembly, and properties of dark matter, they should be the 
most sensitive to the effects of the void environment.

Previous work by \cite{Douglass17a} (hereafter Paper I) shows that there is no 
large-scale environmental dependence of the amount of oxygen in dwarf galaxies, 
in contrast to earlier studies by \cite{Pustilnik06}, \cite{Cooper08}, 
\cite{Deng11}, and \cite{Filho15}, for example.  One of the main arguments for 
the existence of an environmental dependence of the metallicity of galaxies 
centers around the idea that void galaxies are surrounded by pristine hydrogen 
that is unavailable to galaxies in denser regions.  By looking at just N/O, we 
remove the hydrogen dependence of the relative abundances.  Detecting a 
difference in the N/O ratio due to the large-scale environment would indicate 
that the cosmic environment has some influence on the nucleosynthesis of 
secondary elements.  In addition, if the environment does have some very minor 
effect on the metallicity of a galaxy, removing the hydrogen dependence could 
amplify this effect above the noise of the data.  Combined with the metallicity 
results in Paper I, we might be able to discern a large-scale environmental 
effect on the chemical evolution of galaxies.

% Why this paper is significant, new, and important (large data set - statistically relevant)
Large-scale sky surveys like the Sloan Digital Sky Survey 
\citep[SDSS;][]{Abazajian09} contain a large sample of dwarf galaxies, allowing 
us to analyze the dwarf galaxy population in the nearby universe with more 
statistical significance.  Over 1000 voids have been identified in SDSS DR7 
\citep{Pan12}, and SDSS provides spectroscopy to permit abundance estimates of 
those dwarf galaxies found in these voids.  Thus, we are able to estimate the 
N/O ratio as a function of large-scale environment for the largest sample of 
dwarf galaxies to date.

% Why are we using MPA-JHU emission line measurements?
We make use of the MPA-JHU catalog's reprocessed spectroscopic 
data\footnote{Available at http://www.mpa-garching.mpg.de/SDSS/DR7/} to study 
the N/O abundance ratio of a large collection of dwarf galaxies in SDSS DR7.  
Because our analysis depends on the weak [O{\sc iii}] $\lambda 4363$ auroral 
line, the MPA-JHU catalog's more detailed treatment of the stellar continuum 
permits the weaker emission lines to become more apparent.  As a result, using 
this catalog's flux measurements should improve the accuracy of our results.  We 
study the N/O abundance ratio of these dwarf galaxies as a function of 
large-scale environment to discern whether the large-scale environment has an 
effect on the relative abundance of heavier elements in dwarf galaxies.

% Outline of paper
Our paper is organized as follows.  Section 2 describes the method used to 
estimate the chemical abundances in galaxies.  We remind the reader of the 
source of our data in Section 3.  Section 4 includes the results of our analysis, 
and Section 5 is a discussion of the implications of our results on the 
large-scale environmental effects on galaxy evolution.  Finally, Section 6 
summarizes our conclusions and discusses future work.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%    THEORY
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Theory]{Estimation of gas-phase chemical abundances from optical spectroscopy}
\label{sec:Theory}

We study a galaxy's oxygen and nitrogen abundances because they are relatively 
abundant elements, they emit strong lines in the optical regime (including for 
several ionization states in oxygen), and a ratio of some of the oxygen lines 
provides a good estimate of the electron temperature \citep{Kewley02}.  What 
follows is a description of the theory and methods we employ to estimate the 
oxygen and nitrogen abundances in dwarf galaxies.

% ------------------------------------------------------------------------------
\subsection{[N{\sc ii}]}

The energy-level diagram for the various transitions of [N{\sc ii}] is very 
similar to that of [O{\sc iii}], since they have the same electron ground-state 
configuration ((1s)$^2$(2s)$^2$(2p)$^2$).  The similarities can be seen in Fig. 
\ref{fig:transitions_P2}.  Therefore, an estimate of the electron temperature can 
be made from the [N{\sc ii}] $\lambda 5755$ emission line.  However, this line 
is weaker than the [O{\sc iii}] $\lambda 4363$ auroral line (since there is less 
N than O in galaxies), so we use the [O{\sc iii}] auroral line for our 
temperature estimates, as in Paper I.  After obtaining a temperature and density 
estimate, we use the [N{\sc ii}] $\lambda \lambda 6548, 6584$ doublet to 
estimate the abundance of singly ionized nitrogen in a galaxy.

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{Images/Paper2/NIIOIII_energy_level_diagram-figure0}
    \caption[{[\ion{O}{3}] and [\ion{N}{2}] energy-level diagram}]{Energy-level 
    diagram for [O{\sc iii}] and [N{\sc ii}] $(2p^2)$ ions.  The most important 
    transitions are shown; all are in the visible spectrum.  These forbidden 
    transitions in both oxygen and nitrogen provide an estimate of the electron 
    temperature in the interstellar gas.  Because oxygen is more abundant, we 
    use the oxygen lines to estimate the temperature of the gas.}
    \label{fig:transitions_P2}
\end{figure}

% ------------------------------------------------------------------------------
\subsection{Direct $T_e$ method}

We use the same method to calculate the nitrogen abundance as in Paper I to 
estimate the oxygen abundance.  However, here we use the [N{\sc ii}] 
$\lambda \lambda 6548, 6584$ doublet instead of the [O{\sc ii}] $\lambda 3727$ 
and [O{\sc iii}] $\lambda \lambda 4959,5007$ doublets.  Because the temperature 
estimate depends on the auroral line [O{\sc iii}] $\lambda 4363$, this method is 
often difficult to employ.  As a result, it works best with low-redshift, 
low-metallicity galaxies.  The electron temperature is derived by solving the 
following system of equations:
\begin{equation}
	t_3 = \frac{1.432}{\log[(\lambda 4959 + \lambda 5007)/\lambda 4363] - \log C_T}
\end{equation}
where $t_3 = 10^{-4} T_e(\text{O}^{++})$ and
\begin{equation}
	C_T = (8.44 - 1.09t_3 + 0.5t_3^2 - 0.08t_3^3)\frac{1 + 0.0004x_3}{1 + 0.044x_3}
\end{equation}
where $x_3 = 10^{-4} n_e t_3^{-0.5}$.  The ionic abundances are then found with 
the equations
\begin{align}
    12 + \log \left( \frac{\text{O}^{++}}{\text{H}^+} \right) &= \log \frac{\lambda 4959 + \lambda 5007}{\text{H}\beta} + 6.200 + \frac{1.251}{t_3} - 0.55\log t_3 - 0.014t_3 \\
	12 + \log \left( \frac{\text{O}^+}{\text{H}^+} \right) &= \log \frac{\lambda 3727}{\text{H}\beta} + 5.961 + \frac{1.676}{t_2} - 0.40\log t_2 - 0.034t_2 + \log (1+1.35x_2) \\
	12 + \log \left( \frac{\text{N}^+}{\text{H}^+} \right) &= \log \frac{\lambda 6548 + \lambda 6584}{\text{H}\beta} + 6.234 + \frac{0.950}{t_2} - 0.42\log t_2 - 0.027t_2 + \log (1 + 0.116x_2)
\end{align}
where $t_2 = 10^{-4} T_e(\text{O}^+)$ and $x_2 = 10^{-4} n_e t_2^{-0.5}$.  We 
assume that $T_e(\text{N}^+) = T_e(\text{O}^+)$.

The signal-to-noise ratio of the SDSS spectra is too low to directly estimate 
the temperature of the gas in the low-ionization zone.  As a result, we use the 
relation $t_2 = 0.7t_3 + 0.3$ by \cite{Garnett92}.  This relation has been shown 
to overestimate this temperature \citep{Andrews13}.  Since the metal emission 
lines are the primary method of cooling for the gas, a high temperature 
corresponds to a low metallicity.  Therefore, an overestimate of the temperature 
results in an underestimated abundance.  As shown in Paper I, this only affects 
perhaps 15 of the dwarf galaxies in our sample and does not influence our 
conclusions.

The sum of the abundances of each of the element's ionization states is equal to 
the total abundance of any element, whether or not all ionization states are 
observed.  Most of oxygen exists as either singly or doubly ionized, so the 
total oxygen abundance is
\begin{equation}
	\frac{\text{O}}{\text{H}} = \frac{\text{O}^{++}}{\text{H}^+} + \frac{\text{O}^+}{\text{H}^+}
\end{equation}
Since we can only observe the nitrogen abundance in one of the main ionization 
states, we use an ionization correction factor (ICF) to account for the missing 
states.  For any element X, the total abundance is 
\begin{equation}\label{eqn:ICF}
    \frac{\text{X}}{\text{H}} = \sum_i ICF_i \frac{\text{X}^i}{\text{H}}
\end{equation}
For nitrogen, we employ the ICFs as defined in \cite{Izotov06}:
\begin{equation}\label{eqn:ICF_N}
    ICF(\text{N}^+) = \left\{ \begin{array}{ll}
    -0.825v + 0.718 + \frac{0.853}{v} & \mbox{low $Z$}\\
    -0.809v + 0.712 + \frac{0.852}{v} & \mbox{intermed $Z$}\\
    1.467v + 1.752 + \frac{0.688}{v} & \mbox{high $Z$}
    \end{array} \right.
\end{equation}
where $v = \text{O}^+ / (\text{O}^+ + \text{O}^{++})$.  The range for low $Z$ 
covers galaxies with $12 + \log \left( \text{O}/\text{H} \right) \leq 7.2$, 
while high $Z$ includes galaxies with 
$12 + \log \left( \text{O}/\text{H} \right) \geq 8.2$.  For galaxies with 
$7.2 < 12 + \log \left( \text{O}/\text{H} \right) < 7.6$, the values for the 
ICFs are a linear interpolation between the low-$Z$ and intermediate-$Z$ values, 
while the ICFs for galaxies with 
$7.6 < 12 + \log \left( \text{O}/\text{H} \right) < 8.2$ are a linear 
interpolation between the intermediate-$Z$ and high-$Z$ values.

The N/O ratio can be found from the O/H and N/H ratios:
\begin{equation}\label{eqn:NO}
    \log \left(\frac{\text{N}}{\text{O}}\right) = \left[ 12 + \log \left( \frac{\text{N}}{\text{H}} \right) \right] - \left[ 12 + \log \left( \frac{\text{O}}{\text{H}} \right) \right]
\end{equation}

%The N$^+$/O$^+$ ratio can then be found from the O$^+$/H and N$^+$/H ratios:
%\begin{equation}
%    \log \left(\frac{\text{N}^+}{\text{O}^+}\right) = \left[ 12 + \log \left( \frac{\text{N}^+}{\text{H}^+} \right) \right] - \left[ 12 + \log \left( \frac{\text{O}^+}{\text{H}^+} \right) \right]
%\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%    DATA
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Data]{SDSS data and galaxy selection}

The SDSS Data Release 7 \citep[DR7;][]{Abazajian09} uses drift scanning to map 
approximately one-quarter of the northern sky; it is a wide-field multiband 
imaging and spectroscopic survey.  A dedicated 2.5 m telescope at the Apache 
Point Observatory in New Mexico \citep{Fukugita96, Gunn98} takes the photometric 
data in the five-band SDSS system --- $u$, $g$, $r$, $i$, and $z$.  Galaxies 
selected for spectroscopic analysis must have a Petrosian $r$-band magnitude 
$m_r < 17.77$ \citep{Lupton01, Strauss02}.  Two double fiber-fed spectrographs 
and fiber plug plates take the spectra in an observed wavelength range of 
3800--9200 \AA with a resolution $\lambda / \Delta \lambda \sim 1800$ and a 
minimum fiber separation of 55" \citep{Blanton03}.  As in Paper I, we use 
the emission-line flux data from the MPA-JHU value-added catalog, which is based 
on the SDSS DR7 sample of galaxies.  Total star formation rates and total 
specific star formation rates are also from the MPA-JHU value-added catalog, 
following the technique discussed in \cite{Brinchmann04}.  The MPA-JHU catalog 
is also the source of the stellar mass estimates used, as calculated in 
\cite{Tremonti04}, following the method outlined in \cite{Kauffmann03}.  The 
KIAS value-added galaxy catalog \citep{Choi10} is our source of the absolute 
magnitudes and colors of the galaxies.

%-------------------------------------------------------------------------------
\subsection{Spectroscopic selection}\label{sec:SDSS_limits}

The following requirements are implemented on the SDSS DR7 main spectroscopic 
galaxy sample described above.  We use the same requirements for our sample as 
in Paper I; all galaxies must have
\begin{enumerate}
    \item{$M_r > -17$ (dwarf galaxies);}
    \item{a minimum $5\sigma$ detection of H$\beta$;}
    \item{a minimum $1\sigma$ detection of [\ion{O}{3}] $\lambda 4363$;}
    \item{a flux $>0$ for all other required lines;}
    \item{$T_e (\text{\ion{O}{3}}) < 3\times 10^4 \text{ K}$;}
    \item{a star-forming BPT classification by \cite{Brinchmann04}.}
\end{enumerate}
We also use the \texttt{oii\_flux} value from the MPA-JHU catalog in place of 
their [\ion{O}{2}] $\lambda \lambda 3726, 3729$ flux measurement since we are 
working at such low redshifts ($0.02 < z < 0.03$).  Detailed descriptions of 
these criteria can be found in Section 3.1 of Paper I.

%-------------------------------------------------------------------------------
\subsection{Void classification}

The large-scale environment of the galaxies was determined using the void 
catalog constructed by \cite{Pan12}, which is based on the galaxies in the SDSS 
DR7 catalog.  The VoidFinder algorithm of \cite{Hoyle02} removes all isolated 
galaxies with absolute magnitudes $M_r < -20$ (a galaxy is defined to be 
isolated if its third nearest neighbor is more than 7 $h^{-1}$ Mpc away).  
Placing a grid over the remaining galaxies, VoidFinder grows spheres in the 
centers of all grid cells that contain no galaxies.  The spheres expand until 
they encounter four galaxies on the surface.  To be considered part of a void, a 
sphere must have a minimum radius of 10 Mpc; two spheres that overlap by more 
than 10\% are considered part of the same void.  We refer the reader to 
\cite{Hoyle02} for a more detailed description of the VoidFinder algorithm.  
Using these voids, galaxies that live within any void sphere are classified as 
a void galaxy; those that are outside the spheres are considered wall galaxies.  
Due to the construction of the void spheres, we cannot identify any voids within 
10 Mpc of the edge of the survey.  As a result, the large-scale environment of 
any galaxy within this boundary is uncertain.

9519 of the $\sim$800,000 galaxies with spectra available in SDSS DR7 are dwarf 
galaxies ($M_r > -17$).  42 void dwarf galaxies, 89 wall dwarf galaxies, and 4 
dwarf galaxies with uncertain large-scale environments are left to analyze after 
applying the spectroscopic cuts (or 135 dwarf galaxies in total, 131 of which 
are used in the environmental study).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%    ANALYSIS & RESULTS
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Results]{Abundance analysis and results}

Our primary objective is to perform a relative measurement of the N/O ratio of 
dwarf galaxies to discern how the large-scale environment affects their chemical 
evolution.  As discussed in Paper I, multiple methods have been developed for 
metallicity calculations based on the quality of the spectra.  We use only the 
direct $T_e$ method for our abundance calculations, due to the limited galaxy 
types used in the calibration or theoretical development of other methods.

For reference, the solar metallicity $Z_{\odot} = 8.69\pm 0.05$ 
\citep{Asplund09}.

%-------------------------------------------------------------------------------
\subsection{Estimation of uncertainties and comparison of N/O and N$^+$/O$^+$}

% Uncertainties
We estimate uncertainties in the computed abundances using a Monte Carlo method.  
We calculate 100,000 abundance estimates using the measured line fluxes and 
scaled uncertainty estimates.  A new positive ``fake'' line flux is drawn from a 
normal distribution for each abundance estimate.  The standard deviation in 
the sets of 100,000 calculated abundance values is used for the error in the 
abundance calculation.  A more in-depth description of this process can be found 
in Paper I.

It has been common practice to assume that N/O $\cong$ N$^+$/O$^+$, thus 
eliminating the need for the ICF in Eqn. \ref{eqn:ICF}.  We find that this is a 
reasonable but slightly biased approximation, agreeing with the results of 
\cite{Nava06}.  A comparison of the N/O ratio and the N$^+$/O$^+$ ratio for our 
set of dwarf galaxies can be seen in Fig. \ref{fig:NO_NpOp}; galaxies with 
absolute magnitudes $M_r > -20$ are shown in gray for context.  A linear fit to 
all star-forming galaxies with magnitudes $M_r > -20$ has a slope of only 
$0.927\pm 0.0018$, with an rms error of 0.032 for the fit.  This comparison 
indicates that lower values of the N$^+$/O$^+$ ratio underestimate the N/O 
ratio, while higher values of N$^+$/O$^+$ overestimate the N/O ratio.  
Throughout this paper, we study the N/O ratio using ICF-corrected estimates of 
N/O (Eqns. \ref{eqn:ICF_N} and \ref{eqn:NO}).

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{Images/Paper2/1sig_I06_dwarf_0-20_SF_t3_logNpOp_logNO_fit}
    \caption[N/O versus N$^+$/O$^+$]{Comparison of the N/O and N$^+$/O$^+$ 
    abundance ratios for our dwarf galaxies.  Brighter galaxies ($M_r > -20$) 
    are shown in gray for context.  All our star-forming galaxies with 
    $M_r > -20$ roughly follow the approximation that N/O $\cong$ N$^+$/O$^+$, 
    which is often assumed in other studies of the abundance ratio of nitrogen 
    to oxygen.  In this paper, we will be using the abundance ratio N/O for our 
    analysis.}
    \label{fig:NO_NpOp}
\end{figure}

%-------------------------------------------------------------------------------
\subsection{Sources of systematic error}

There is a radial dependence of many physical properties of galaxies 
\citep{Bell00}.  Consequently, abundance estimates may depend on the locations 
of the spectroscopic fiber on the galaxy.  If all of the galaxy's light is not 
contained within the fiber of the spectrograph, the estimated abundances will 
not necessarily be representative of global abundance values.  For example, 
\cite{Bell00} show that the metallicity is not constant throughout a galaxy.  
Due to the spatially resolved spectra produced by MaNGA of SDSS-IV 
\citep{SDSS13}, a statistically significant measure of the radial dependence of 
a galaxy's metallicity should soon be possible \citep{Wilkinson15}.  In SDSS 
DR7, the fiber diameter is 3", corresponding to a physical diameter between 1.29 
and 1.93 kpc at redshifts $0.02 < z < 0.03$.  This covers a majority of most 
dwarf galaxies' luminous surfaces.  The fiber is almost always placed on the 
brightest spot of the galaxy, which is often the center of the galaxy for spiral 
and ellipticals.  Since the metallicity has been shown to decrease at large 
radius, these abundance values may be overestimates of the global abundances.  
Since many dwarf galaxies are irregular galaxies, the fiber is instead focused 
on a bright \ion{H}{2} region.  As a result, we are estimating the abundances of 
the gas from which stars recently formed.

We are implicitly limiting our sample of galaxies to only blue, star-forming 
dwarf galaxies as a result of our selection criteria outlined in Section 
\ref{sec:SDSS_limits}.  Consequently, this is not a representative sample of the 
full dwarf galaxy population.  In this study we are only able to discuss the 
large-scale environmental influence on blue, star-forming dwarf galaxies within 
a narrow redshift range.  It is impossible to use the direct $T_e$ method to 
measure the chemical abundances of red dwarf galaxies because the UV photons 
from young stars are needed to excite the interstellar gas.

%-------------------------------------------------------------------------------
\subsection{Galaxy abundances}

Abundances estimated using the direct $T_e$ method for our dwarf galaxy sample 
are listed in Table \ref{tab:Results_P2}, along with other important 
characteristics and identification for the galaxies (including their large-scale 
environment classification).

% Results table
\input{Tables/Paper2/results_table_short}

%-------------------------------------------------------------------------------
\subsubsection{Oxygen and nitrogen abundances}\label{sec:OH_NH}

Histograms of the resulting oxygen and nitrogen abundances are shown in Figs. 
\ref{fig:met1sig} and \ref{fig:N_1sig}, respectively.  Both figures show very 
little difference in the distribution of abundance values in dwarf galaxies 
between voids and walls.  A two-sample Kolmogorov-Smirnov (K-S) test quantifies 
this observation --- it produced a test statistic of 0.13 for oxygen and 0.11 
for nitrogen, corresponding to a probability of 67.1\% and 83.8\%, respectively, 
that a test statistic greater than or equal to this calculated test statistic 
will be measured if the void sample were drawn from the wall sample.  The 
cumulative distribution function (CDF) of these samples can be seen in the right 
panel of Figures \ref{fig:met1sig} and \ref{fig:N_1sig}.  The K-S test 
quantifies the visual impression in these figures that the distributions of 
oxygen and nitrogen abundances are similar for dwarf galaxies in voids and 
walls.

The average and median values of the dwarf galaxy abundances indicate very 
little large-scale environmental influence on the oxygen and nitrogen 
abundances.  The average oxygen abundance for void dwarf galaxies is 
$7.99\pm 0.049$ and the median is 8.04, while the average for wall dwarf 
galaxies is $7.93\pm 0.036$ with a median value of 8.01.  This implies that the 
wall dwarf galaxies have lower oxygen abundances by an average of 
$0.07\pm 0.060$ relative to the void dwarf galaxies; the shift in the median 
values is 0.03 for the dwarf galaxies, with wall dwarf galaxies having lower 
oxygen abundances than void dwarf galaxies.  There is a also a shift in the 
nitrogen abundances for the dwarf galaxies: void dwarf galaxies have an average 
nitrogen abundance of $6.74\pm 0.035$ and a median of 6.77, while the wall dwarf 
galaxies have an average nitrogen abundance of $6.72\pm 0.025$ and a median of 
6.75.  Again, wall dwarf galaxies have, on average, $0.02\pm 0.043$ lower 
nitrogen abundances than the void dwarf galaxies (the median shift for the 
nitrogen abundance of dwarf galaxies is 0.01, with wall galaxies lower than void 
dwarf galaxies).  These shifts are within the uncertainty, so they are not 
statistically significant --- if there is a large-scale environmental influence 
on the abundances of oxygen and nitrogen relative to hydrogen in dwarf galaxies, 
it is small.

% Dwarf galaxies
%\begin{figure*}
%    \centering
%    \includegraphics[width=0.49\textwidth]{Images/Paper1/1sig_dwarf_SF_t3_12logOH_hist}
%    \includegraphics[width=0.49\textwidth]{Images/Paper1/1sig_dwarf_SF_t3_12logOH_CDF}
%    \caption{Gas-phase oxygen abundances (relative to hydrogen) of void dwarf 
%    (red solid line) and wall dwarf (black dashed line) galaxies, taken from 
%    Fig. 4 in Paper I.  As we demonstrate in Paper I, the gas-phase oxygen 
%    abundances in dwarf galaxies do not depend on the large-scale environment.}
%    \label{fig:met1sig}
%\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[width=0.49\textwidth]{Images/Paper2/1sig_dwarf_SF_t3_12logNH_hist}
    \includegraphics[width=0.49\textwidth]{Images/Paper2/1sig_dwarf_SF_t3_12logNH_CDF}
    \caption[Nitrogen distribution of 135 dwarf galaxy sample]{Abundance of 
    nitrogen relative to hydrogen of void dwarf (red solid line) and wall dwarf 
    (black dashed line) galaxies.  A two-sample K-S test of the two data sets 
    results in an asymptotic $p$-value of 0.84, indicating an 84\% probability 
    that a test statistic greater than the observed value of 0.11 will be seen 
    if the void sample is drawn from the wall sample.  This is reflected 
    visually, as there appears to be very little difference between the two 
    populations, indicating that there is little large-scale environmental 
    influence on the nitrogen abundance of dwarf galaxies.}
    \label{fig:N_1sig}
\end{figure*}

%%%% Brighter star-forming galaxies %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
To see how our results of the environmental dependence of dwarf galaxies compare 
with somewhat brighter galaxies, we perform the same analysis on galaxies with 
absolute magnitudes $-17 > M_r > -20$.  The results of this analysis can be seen 
in Figs. \ref{fig:Z_bright} and \ref{fig:N_bright}.  As the dwarf galaxies have 
already shown, there is no obvious large-scale environmental dependence of the 
oxygen and nitrogen abundances of these brighter galaxies.  The results of a 
two-sample K-S test (listed in Table \ref{tab:stats}) mostly support this 
conclusion.  In the brightest magnitude bin (galaxies with $-19 > M_r > -20$), 
the K-S test returns a $p$-value of only 0.00062 for the oxygen abundances, 
indicating only a 0.062\% chance that there will be a test statistic greater 
than 0.07 if the void sample is drawn from the wall sample.  The oxygen 
abundances for void galaxies are higher than the wall galaxies by an average of 
$0.04\pm 0.017$ in this absolute magnitude bin, reinforcing the results of the 
K-S test that there is a large-scale environmental influence on the oxygen 
abundance in galaxies with magnitudes $-19 > M_r > -20$.  While the results of 
the K-S test are not as convincing for this magnitude range in the nitrogen 
abundances, there is still an average shift of $0.02\pm 0.011$ toward higher 
nitrogen abundances for void galaxies.  While only one magnitude bin shows a 
statistically significant shift between the two environments, all magnitude bins 
are shifted in the same direction.  This trend suggests that there may be a mild 
influence on the chemical evolution of galaxies due to their large-scale 
environment.

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{Images/Paper2/1sig_17-20_SF_t3_12logOH_stacked}
    \caption[Metallicity distribution of star-forming galaxies with 
    $-17 > M_r > -20$]{Gas-phase oxygen abundances relative to hydrogen of void 
    (red solid line) and wall (black dashed line) star-forming galaxies with 
    $-17 > M_r > -18$ (top), $-18 > M_r > -19$ (middle), and $-19 > M_r > -20$ 
    (bottom).  The results of a two-sample K-S test of the two data sets in each 
    absolute magnitude range can be found in Table \ref{tab:stats}.  These 
    results are reflected visually, as there appears to be very little 
    difference between the two populations (regardless of absolute magnitude), 
    indicating that there is little large-scale environmental influence on the 
    oxygen abundance of star-forming galaxies with absolute magnitudes 
    $-17 > M_r > -20$.}
    \label{fig:Z_bright}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{Images/Paper2/1sig_17-20_SF_t3_12logNH_stacked}
    \caption[Nitrogen distribution of star-forming galaxies with 
    $-17 > M_r > -20$]{Abundance of nitrogen relative to hydrogen of void (red 
    solid line) and wall (black dashed line) star-forming galaxies with 
    $-17 > M_r > -18$ (top), $-18 > M_r > -19$ (middle), and $-19 > M_r > -20$ 
    (bottom).  The results of a two-sample K-S test of the two data sets in each 
    absolute magnitude range can be found in Table \ref{tab:stats}.  These 
    results are reflected visually, as there appears to be very little 
    difference between the two populations (regardless of absolute magnitude), 
    indicating that there is little large-scale environmental influence on the 
    nitrogen abundance of star-forming galaxies with absolute magnitudes 
    $-17 > M_r > -20$.}
    \label{fig:N_bright}
\end{figure}

We note that there appears to be a shift in the oxygen and nitrogen abundances 
between the absolute magnitude bins in Figs. \ref{fig:Z_bright} and 
\ref{fig:N_bright} that is opposite to what is predicted by the mass-metallicity 
relation \citep{Tremonti04}.  This shift toward lower oxygen abundances as the 
galaxies increase in brightness is possibly due to the fact that the metallicity 
estimates are so dependent on the temperature-sensitive [\ion{O}{3}] 
$\lambda 4363$ auroral line.  As galaxies increase in metallicity, this line 
becomes weaker (as its strength is inversely proportional to the temperature).  
If the flux of this line is being underestimated, then the temperature is being 
overestimated, and therefore the oxygen and nitrogen abundances are being 
underestimated.  If we are seeing an underestimate of flux of the [\ion{O}{3}] 
$\lambda 4363$ emission line (and therefore an overestimate of the temperature 
in the region), then we should see a shift toward lower N/H values as the 
absolute magnitude is increased as well.  This pattern can be seen in Fig. 
\ref{fig:N_bright}.

%\begin{table}
%
%    \begin{tabu} in 0.75\textwidth {ccccccccc}
%        Absolute magnitude range & Environment & \# of galaxies & Average & Median & Average shift\footnote[1]{Wall -- Void (Positive shifts indicate that the wall galaxy average is greater than the void average; negative shifts indicate that the void galaxy average is greater than the wall average.)} & Median shift\footnote[1] & $p$-value & KS test statistic \\
%        \hline \\
%        \multirow{2}{*}{Dwarf galaxies} & Void & 42 & $6.74\pm 0.035$ & 6.77 & \multirow{2}{*}{$-0.02\pm 0.043$} & \multirow{2}{*}{0.8383} & \multirow{2}{*}{0.1129}\\
%         & Wall & 89 & $6.72\pm 0.025$ & 6.75 & & & \\
%        \multirow{2}{*}{$-17>M_r>-18$} & Void & 423 & $6.80\pm 0.011$ & 6.82 & \multirow{2}{*}{$0.00\pm 0.014$} & \multirow{2}{*}{0.7364} & \multirow{2}{*}{0.0401}\\
%         & Wall & 895 & $6.80\pm 0.008$ & 6.81 & & & \\
%        \multirow{2}{*}{$-18>M_r>-19$} & Void & 829 & $6.87\pm 0.009$ & 6.85 & \multirow{2}{*}{$0.01\pm 0.011$} & \multirow{2}{*}{0.0873} & \multirow{2}{*}{0.0538}\\
%         & Wall & 1498 & $6.89\pm 0.007$ & 6.87 & & & \\
%        \multirow{2}{*}{$-19>M_r>-20$} & Void & 798 & $6.97\pm 0.009$ & 6.94 & \multirow{2}{*}{$-0.02\pm 0.011$} & \multirow{2}{*}{0.2272} & \multirow{2}{*}{0.0455}\\
%         & Wall & 1490 & $6.95\pm 0.007$ & 6.93 & & & \\
%    \end{tabu}
%
%    \tablecomments{Statistics on the gas-phase nitrogen abundance in void and 
%    wall galaxies in each of the absolute magnitude ranges listed.  Combined 
%    with the histograms in Figs. \ref{fig:N_1sig} and \ref{fig:N_bright}, it is 
%    clear that there is no large-scale environmental dependence of the nitrogen 
%    abundance in galaxies.}
%
%    \label{tab:KStest_N}
%
%\end{table}

%-------------------------------------------------------------------------------
\subsubsection{Ratio of nitrogen to oxygen}

% Dwarf galaxies
In addition to studying the oxygen and nitrogen abundances relative to hydrogen, 
we also look at the ratio of nitrogen to oxygen.  The N/O abundance ratio 
suggests a slightly stronger environmental influence on the chemical evolution 
of dwarf galaxies than the oxygen and nitrogen abundances individually.  As can 
be seen in Fig. \ref{fig:NOratio}, there is a shift in the N/O ratio to lower 
values in the void dwarf galaxies than in the wall dwarf galaxies.  This 
difference is quantified in the K-S test --- the test returned a probability of 
11.1\% that a test statistic greater than or equal to 0.22 will be measured if 
the void sample was drawn from the wall sample.  The void dwarf galaxies have 
lower N/O ratios by an average of $0.05\pm 0.074$ than the wall dwarf galaxies; 
the difference in the median values of the N/O ratio in the void and wall dwarf 
galaxy samples is 0.07.  However, like the shifts seen in the oxygen and 
nitrogen abundances, the shift in the N/O ratio for dwarf galaxies is not 
statistically significant.

\begin{figure*}
    \centering
    \includegraphics[width=0.49\textwidth]{Images/Paper2/1sig_dwarf_SF_t3_logNO_hist}
    \includegraphics[width=0.49\textwidth]{Images/Paper2/1sig_dwarf_SF_t3_logNO_CDF}
    \caption[N/O distribution of 135 dwarf galaxy sample]{Ratio of nitrogen to 
    oxygen of void dwarf (red solid line) and wall dwarf (black dashed line) 
    galaxies.  A two-sample K-S test of the two data sets results in an 
    asymptotic $p$-value of 0.11, indicating an 11\% probability that a test 
    statistic greater than the observed value of 0.22 will be seen if the void 
    sample was drawn from the wall sample.  This is reflected visually, as the 
    void galaxies appear to have a lower value of N/O than the wall galaxies.  
    This is suggestive of a large-scale environmental influence on the relative 
    chemical abundances in dwarf galaxies.}
    \label{fig:NOratio}
\end{figure*}

%%%% Brighter star-forming galaxies %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We perform the same analysis with the N/O ratio on somewhat brighter galaxies, 
up through $M_r > -20$; the results of this analysis can be seen in Fig. 
\ref{fig:NO_bright} and in Table \ref{tab:stats}.  The shift toward lower N/O 
ratios for the void galaxies is small for all magnitude bins.  The direction of 
the shift between environments for the N/O ratio is consistent for all absolute 
magnitude bins: void galaxies have slightly lower N/O ratios than wall galaxies.  
This is only very weak evidence of a large-scale environmental influence on the 
relative abundances of elements in galaxies, but it is worth testing for in 
larger samples.

% 17-18
\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{Images/Paper2/1sig_17-20_SF_t3_logNO_stacked}
    \caption[N/O distribution of star-forming galaxies with $-17 > M_r > -20$]
    {Ratio of nitrogen to oxygen of void (red solid line) and wall (black dashed 
    line) star-forming galaxies with $-17 > M_r > -18$ (top), $-18 > M_r > -19$ 
    (middle), and $-19 > M_r > -20$ (bottom).  The results of a two-sample K-S 
    test of the two data sets in each absolute magnitude range can be found in 
    Table \ref{tab:stats}, in addition to other statistics of the samples.  Both 
    the histograms, CDFs, and statistics suggest a very slight difference 
    between the two populations, indicating a mild large-scale environmental 
    influence on the relative chemical abundances of star-forming galaxies with 
    absolute magnitudes $-17 > M_r > -20$.}
    \label{fig:NO_bright}
\end{figure}

%\begin{table}
%
%    \begin{tabu}{cccccccc}
%        Absolute magnitude range & Environment & \# of galaxies & Average & Median & Average shift\footnote[1]{Wall -- Void (Positive shifts indicate that the wall galaxy average is greater than the void average; negative shifts indicate that the void galaxy average is greater than the wall average.)} & $p$-value & KS test statistic \\
%        \hline \\
%        \multirow{2}{*}{Dwarf galaxies} & Void & 42 & $-1.25\pm 0.060$ & -1.28 & \multirow{2}{*}{$0.05\pm 0.074$} & \multirow{2}{*}{0.1116} & \multirow{2}{*}{0.2191}\\
%         & Wall & 89 & $-1.21\pm 0.044$ & -1.22 & & & \\
%        \multirow{2}{*}{$-17>M_r>-18$} & Void & 423 & $-1.08\pm 0.020$ & -1.13 & \multirow{2}{*}{$-0.00\pm 0.024$} & \multirow{2}{*}{0.2657} & \multirow{2}{*}{0.0588}\\
%         & Wall & 895 & $-1.08\pm 0.014$ & -1.09 & & & \\
%        \multirow{2}{*}{$-18>M_r>-19$} & Void & 829 & $-0.86\pm 0.015$ & -0.88 & \multirow{2}{*}{$0.02\pm 0.019$} & \multirow{2}{*}{0.0763} & \multirow{2}{*}{0.0550}\\
%         & Wall & 1498 & $-0.84\pm 0.012$ & -0.85 & & & \\
%        \multirow{2}{*}{$-19>M_r>-20$} & Void & 798 & $-0.62\pm 0.016$ & -0.62 & \multirow{2}{*}{$0.02\pm 0.020$} & \multirow{2}{*}{0.0715} & \multirow{2}{*}{0.0564}\\
%         & Wall & 1490 & $-0.60\pm 0.012$ & -0.60 & & & \\
%    \end{tabu}
%
%    \caption{Statistics of the relative abundance of nitrogen to oxygen in 
%    void and wall galaxies in each of the absolute magnitude ranges listed.  
%    Combined with the histograms in Figs. \ref{fig:NOratio} and 
%    \ref{fig:NO_bright}, these results suggest that there is a large-scale 
%    environmental dependence of the relative abundance of nitrogen to oxygen in 
%    dwarf galaxies.}
%
%    \label{tab:KStest_NO}
%
%\end{table}

Figure \ref{fig:NO_bright} indicates a shift toward higher values in the peak of 
the N/O distribution as the absolute magnitude of the galaxies increases.  There 
is a known positive correlation between the N/O ratio and the stellar mass of a 
galaxy, as discussed in Sec. \ref{sec:Mass_NO} below.  To test whether this 
relation is causing the shift seen in Figs. \ref{fig:NOratio} and 
\ref{fig:NO_bright}, we downsampled the wall galaxies in each magnitude bin to 
match the void sample.  The original shifts in the N/O ratio seen were still 
present after the downsampling; the observed shift in the N/O ratio is not due 
to any variations in the distribution of the stellar masses between the two 
environments.  In addition, if we are overestimating the temperatures in these 
galaxies as a result of an incorrect measurement of [\ion{O}{3}] $\lambda 4363$ 
(discussed above in Section \ref{sec:OH_NH}), that effect should cancel when we 
look at the ratio of nitrogen to oxygen.  This shift toward higher N/O values as 
a function of absolute magnitude indicates that brighter galaxies produce more 
nitrogen than fainter galaxies (relative to their oxygen abundance).  This 
result is consistent with the theory that nitrogen behaves as a secondary 
element in galaxies with high enough metallicity, if we assume a positive 
correlation between absolute magnitude and metallicity.

\begin{sidewaystable}
\centering

	\begin{tabu} to 0.75\textwidth {ccccccccc}
	    Abs. Mag. Range & Environment & \# of Galaxies & Average & Median & Average Shift\footnote[1]{Wall -- Void (positive shifts indicate that the wall values are greater than the void values; negative shifts indicate that the void values are greater than the wall values)} & Median Shift\footnote[1] & K-S Test Statistic & $p$-value \\
	    \hline
	    \hline
        % Oxygen %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \multicolumn{9}{c}{\OH}\\
        \hline
        \multirow{2}{*}{Dwarf galaxies} & Void & 42 & $7.99\pm 0.049$ & 8.04 & \multirow{2}{*}{$-0.07\pm 0.060$} & \multirow{2}{*}{-0.03} & \multirow{2}{*}{0.1322} & \multirow{2}{*}{0.6701}\\
         & Wall & 89 & $7.93\pm 0.036$ & 8.01 & & & & \\
        \multirow{2}{*}{$-17>M_r>-18$} & Void & 423 & $7.87\pm 0.016$ & 7.96 & \multirow{2}{*}{$0.01\pm 0.020$} & \multirow{2}{*}{-0.02} & \multirow{2}{*}{0.0455} & \multirow{2}{*}{0.5799}\\
         & Wall & 895 & $7.88\pm 0.012$ & 7.94 & & & & \\
        \multirow{2}{*}{$-18>M_r>-19$} & Void & 829 & $7.74\pm 0.013$ & 7.76 & \multirow{2}{*}{$-0.01\pm 0.016$} & \multirow{2}{*}{-0.04} & \multirow{2}{*}{0.0385} & \multirow{2}{*}{0.4000}\\
         & Wall & 1498 & $7.73\pm 0.009$ & 7.73 & & & & \\
        \multirow{2}{*}{$-19>M_r>-20$} & Void & 798 & $7.59\pm 0.013$ & 7.55 & \multirow{2}{*}{$-0.04\pm 0.017$} & \multirow{2}{*}{-0.05} & \multirow{2}{*}{0.0741} & \multirow{2}{*}{0.0062}\\
         & Wall & 1490 & $7.55\pm 0.010$ & 7.50 & & & & \\
        \hline
        % Nitrogen %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \multicolumn{9}{c}{\NH}\\
        \hline
        \multirow{2}{*}{Dwarf galaxies} & Void & 42 & $6.74\pm 0.035$ & 6.77 & \multirow{2}{*}{$-0.02\pm 0.043$} & \multirow{2}{*}{-0.01} & \multirow{2}{*}{0.1129} & \multirow{2}{*}{0.8383}\\
         & Wall & 89 & $6.72\pm 0.025$ & 6.75 & & & & \\
        \multirow{2}{*}{$-17>M_r>-18$} & Void & 423 & $6.80\pm 0.011$ & 6.82 & \multirow{2}{*}{$0.00\pm 0.014$} & \multirow{2}{*}{-0.01} & \multirow{2}{*}{0.0401} & \multirow{2}{*}{0.7364}\\
         & Wall & 895 & $6.80\pm 0.008$ & 6.81 & & & & \\
        \multirow{2}{*}{$-18>M_r>-19$} & Void & 829 & $6.87\pm 0.009$ & 6.85 & \multirow{2}{*}{$0.01\pm 0.011$} & \multirow{2}{*}{0.02} & \multirow{2}{*}{0.0538} & \multirow{2}{*}{0.0873}\\
         & Wall & 1498 & $6.89\pm 0.007$ & 6.87 & & & & \\
        \multirow{2}{*}{$-19>M_r>-20$} & Void & 798 & $6.97\pm 0.009$ & 6.94 & \multirow{2}{*}{$-0.02\pm 0.011$} & \multirow{2}{*}{-0.02} & \multirow{2}{*}{0.0455} & \multirow{2}{*}{0.2272}\\
         & Wall & 1490 & $6.95\pm 0.007$ & 6.93 & & & & \\
        \hline
        % N/O %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \multicolumn{9}{c}{\NO}\\
        \hline
        \multirow{2}{*}{Dwarf galaxies} & Void & 42 & $-1.25\pm 0.060$ & -1.28 & \multirow{2}{*}{$0.05\pm 0.074$} & \multirow{2}{*}{0.07} & \multirow{2}{*}{0.2191} & \multirow{2}{*}{0.1116}\\
         & Wall & 89 & $-1.21\pm 0.044$ & -1.22 & & & & \\
        \multirow{2}{*}{$-17>M_r>-18$} & Void & 423 & $-1.08\pm 0.020$ & -1.13 & \multirow{2}{*}{$-0.00\pm 0.024$} & \multirow{2}{*}{0.04} & \multirow{2}{*}{0.0588} & \multirow{2}{*}{0.2657}\\
         & Wall & 895 & $-1.08\pm 0.014$ & -1.09 & & & & \\
        \multirow{2}{*}{$-18>M_r>-19$} & Void & 829 & $-0.86\pm 0.015$ & -0.88 & \multirow{2}{*}{$0.02\pm 0.019$} & \multirow{2}{*}{0.03} & \multirow{2}{*}{0.0550} & \multirow{2}{*}{0.0763}\\
         & Wall & 1498 & $-0.84\pm 0.012$ & -0.85 & & & & \\
        \multirow{2}{*}{$-19>M_r>-20$} & Void & 798 & $-0.62\pm 0.016$ & -0.62 & \multirow{2}{*}{$0.02\pm 0.020$} & \multirow{2}{*}{0.02} & \multirow{2}{*}{0.0564} & \multirow{2}{*}{0.0715}\\
         & Wall & 1490 & $-0.60\pm 0.012$ & -0.60 & & & & \\
         \hline
	\end{tabu}

    \caption[Abundance statistics]{Statistics of the gas-phase oxygen, nitrogen, 
    and nitrogen relative to oxygen abundances in void and wall galaxies in each 
    of the absolute magnitude ranges listed.  Most of these results are not 
    statistically significant, as shown in Figs. 
    \ref{fig:met1sig}--\ref{fig:NO_bright}.  However, the shifts in chemical 
    abundances between the two environments are predominately in the same 
    direction for each of the magnitude bins, suggesting that there is some 
    influence on the chemical evolution of galaxies by the large-scale 
    environment.   Void galaxies have slightly higher oxygen and nitrogen 
    abundances than wall galaxies, but void galaxies have slightly lower N/O 
    ratios than wall galaxies.}

	\label{tab:stats}

\end{sidewaystable}

%-------------------------------------------------------------------------------
\subsection{N/O versus O/H}

Comparing the N/O ratio with the gas-phase oxygen abundance in a galaxy can help 
us understand the nucleosynthesis of nitrogen in galaxies.  When the metallicity 
of a galaxy is low, stars created from this gas do not have enough carbon to 
efficiently produce helium via the CNO cycle.  As a result, any nitrogen 
produced in these stars will behave as a primary element --- it will be produced 
in the same relative quantity as oxygen.  However, when the metallicity of a 
galaxy is high enough, stars are created with enough seed carbon to initiate the 
CNO cycle at an earlier stage in the star's life.  As a result, nitrogen will 
behave as a secondary element and will be produced in a larger quantity relative 
to the primary elements (like oxygen and carbon).  By studying the relation 
between N/O and the metallicity of a galaxy, we should be able to discern the 
critical metallicity at which nitrogen switches from a primary to a secondary 
element.

% Compare with results from Andrews13, Amorin10, VilaCostas93, Lee04, vanZee06, Molla06, Liang06, Pilyugin04, Nava06, Berg12, Thuan95, Henry00, Nicholls14b, PerezMontero09, Pilyugin02, Shields91, Contini02
Our results for N/O versus metallicity can be seen in Fig. \ref{fig:OvN}.  
Unlike many previous comparisons of N/O and metallicity 
\citep[for example,][]{VilaCostas93, Thuan95, Henry00, Pilyugin02, Lee04, 
Pilyugin04, Nava06, vanZee06a, PerezMontero09, Amorin10, Berg12}, we do not find 
a constant value for N/O as a function of O/H for dwarf galaxies (nor for any of 
the somewhat brighter galaxies).  \cite{Shields91}, \cite{Contini02}, and 
\cite{Nicholls14b} also find little or no evidence of a plateau in their study.  
Instead of a constant value for N/O as a function of O/H at low metallicities, 
we find a slight decrease in the N/O ratio as the metallicity increases; a 
linear fit to the dwarf galaxies reveals a slope of $-0.38\pm 0.078$.  This is 
close to the footnoted results of \cite{Andrews13}, who find a slope of $-0.21$ 
for their stellar-mass-binned galaxies with metallicities 
$12 + \log (\text{O}/\text{H}) < 8.5$.  The average value of \NO for the void 
dwarf galaxies is $-1.25\pm 0.060$ with a median value of $-1.28$, while the 
average value for the wall dwarf galaxies is $-1.21\pm 0.044$ with a median of 
$-1.22$.  As shown in Fig. \ref{fig:NOratio}, the void dwarf galaxies have 
slightly less nitrogen relative to oxygen than do dwarf galaxies in denser 
regions.  Both these median values are higher than that of \cite{Andrews13}, and 
these average values are higher than that of \cite{Izotov99} and \cite{Nava06}.

% Perhaps also show the dwarf galaxies colored by SFR for scatter?

\begin{figure}
    \includegraphics[width=0.5\textwidth]{Images/Paper2/1sig_I06_dwarf_0-20_SF_t3_Z12logOH_logNO}
    \caption[N/O versus metallicity of 135 dwarf galaxy sample]{N/O as a 
    function of O/H for star-forming void (red circles) and wall (black 
    triangles) dwarf galaxies.  Error bars have been omitted for clarity.  N/O 
    is expected to be constant for $12 + \log (\text{O}/\text{H}) \lesssim 8.5$, 
    as the metallicity of a galaxy's ISM is too low for stars to be created with 
    enough of the heavy elements to undergo the CNO cycle early enough in their 
    lifetimes.  As a result, nitrogen behaves as a primary element at galactic 
    metallicities less than approximately 8.5.  To place the dwarf galaxies in 
    the context of the general galaxy population, we also plot (gray stars) all 
    star-forming galaxies fainter than $M_r > -20$.}
    \label{fig:OvN}
\end{figure}

If a plateau in the O/H--N/O relation exists, then we should see a slope of 1 in 
the O/H--N/H relation.  When looking at N/H as a function of O/H in Fig. 
\ref{fig:OHvNH}, we see that there is a correlation between the nitrogen and 
oxygen abundances.  However, a best fit to the dwarf galaxies reveals a slope of 
only $0.62\pm 0.078$ --- the nitrogen abundance increases at a slower rate than 
the oxygen abundance.  This result matches the negative relationship between the 
metallicity and the N/O ratio seen in Fig. \ref{fig:OvN}.  If we examine only 
the low-metallicity ($12 + \log(\text{O}/\text{H}) < 7.6$) star-forming galaxies 
with $M_r > -20$, a linear fit produces a slope of $0.05\pm 0.019$ in Fig. 
\ref{fig:OHvNH} and a slope of $-0.94\pm 0.019$ in Fig. \ref{fig:OvN}.  This is 
in sharp contrast to the star-forming galaxies with $M_r > -20$ that have 
metallicities $12 + \log(\text{O}/\text{H}) > 7.6$, where their slope in Fig. 
\ref{fig:OHvNH} is $0.60\pm 0.022$ and $-0.39\pm 0.023$ in Fig. \ref{fig:OvN}.  
It appears that the nitrogen production is independent of the amount of oxygen 
produced in low-metallicity systems.  At normal metallicities 
($7.6 < 12 + \log(\text{O}/\text{H}) < 8.5$), there exists a positive 
relationship between the production of nitrogen and oxygen, although the ratio 
of N/O produced depends on the galaxy's metallicity.

There is no difference between void and wall galaxies in the relationship of 
oxygen and nitrogen production in the low-metallicity sample.  There is a slight 
difference in slopes between the void and wall galaxies with normal 
metallicities, where the void galaxies have a larger slope in the relationship 
between O/H and N/H and a smaller slope in the relationship between O/H and N/O.  
While statistically significant, the difference in the slopes between the two 
environments is not large enough to be physically relevant.  The significant 
scatter in both Figs. \ref{fig:OHvNH} and \ref{fig:OvN} indicates that the 
described relationships between the production of nitrogen and oxygen are only 
global trends in the nucleosynthesis of the galaxies.

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{Images/Paper2/1sig_I06_dwarf_0-20_SF_t3_Z12logOH_N12logNH}
    \caption[N/H versus metallicity for 135 dwarf galaxy sample]{N/H as a 
    function of O/H for star-forming void (red circles) and wall (black 
    triangles) dwarf galaxies.  Error bars have been omitted for clarity.  There 
    is a positive correlation between the two abundances.  With a best-fit slope 
    less than 1, we see that the synthesis of nitrogen in these galaxies is 
    primary.}
    \label{fig:OHvNH}
\end{figure}

%-------------------------------------------------------------------------------
%\subsection{Comparison to previously published abundance estimates}

% Amorin10 does not publish their N/O estimates

%-------------------------------------------------------------------------------
\subsection{Mass--N/O relation}\label{sec:Mass_NO}

Just as there is a well-known mass--metallicity relation for galaxies 
\citep[where the metallicity increases with stellar mass; see, 
e.g.,][]{Tremonti04}, there is also a mass--N/O relation.  We expect to see a 
primary N/O plateau in the mass--N/O relation, since galaxies with lower stellar 
masses have not yet produced enough heavy elements to synthesize more nitrogen 
than oxygen.  Beyond the low-mass limit, there should be a steady increase in 
the N/O ratio as a function of stellar mass, due to secondary nitrogen 
enrichment.  Our dwarf galaxies in Fig. \ref{fig:MNO} show a steady increase in 
N/O as a function of stellar mass; there is a hint of the beginnings of a 
plateau for $\log(M_*/M_{\odot}) \lesssim 8$.  The lack of a plateau here could 
be a result of our limited stellar mass range for the dwarf galaxies.  A linear 
fit to our dwarf galaxies reveals a slope of $0.6\pm 0.12$, which is much 
stronger than the slope of $0.30$ found by \cite{Andrews13}.

% Compare with results from Andrews13, Amorin10, PerezMontero09, PerezMontero13
From Fig. \ref{fig:MNO}, we conclude that the N/O plateau, if one exists, starts 
around $\log(M_*/M_{\odot}) \approx 8$.  This is at a much lower mass than that 
found by \cite{Andrews13} --- they claim the N/O plateau exists for galaxies 
with $\log(M_*/M_{\odot}) < 8.9$.  However, our relationship between stellar 
mass and N/O matches Fig. 3 of \cite{Amorin10}, as well as the results of 
\cite{PerezMontero09} and \cite{PerezMontero13}.  None of our data samples 
display an obvious N/O plateau above a stellar mass 
$\log(M_*/M_{\odot}) > 8$, indicative of primary nitrogen versus secondary 
nitrogen production in galaxies.  This could indicate that the switch from 
primary to secondary nitrogen production occurs at a much lower stellar mass 
than found by \cite{Andrews13}.  More low-mass galaxies are needed to extend 
this relation below $\log(M_*/M_{\odot}) < 8$.

\begin{figure}
    \includegraphics[width=0.5\textwidth]{Images/Paper2/MNO_1sig_I06_dwarf_0-20_SF_t3}
    \caption[Stellar mass versus N/O for 135 dwarf galaxy sample]{Mass--N/O 
    relation for star-forming void (red circles) and wall (black triangles) 
    dwarf galaxies.  Error bars have been omitted for clarity.  N/O is expected 
    to remain constant for low stellar masses and increase steadily for larger 
    masses, due to the mass-metallicity relation and the primary vs. secondary 
    synthesis of nitrogen.  To place the dwarf galaxies in the context of the 
    general galaxy population, we also plot (gray stars) the star-forming 
    galaxies with $M_r > -20$.}
    \label{fig:MNO}
\end{figure}

%-------------------------------------------------------------------------------
\subsection{Color--N/O relation}

% Compare to Fig. 9 of vanZee06a, Fig. 6 of Berg12
As \cite{vanZee06a} and \cite{Berg12} discuss, a time delay between the release 
of nitrogen and oxygen will result in a positive relationship between the N/O 
ratio and the color of a galaxy.  If oxygen is primarily produced in higher-mass 
stars (and since these stars die earlier than the intermediate-mass stars 
responsible for the synthesis of nitrogen), then, for a given star formation 
episode, the oxygen produced will be released on a shorter time scale than the 
nitrogen.  As a result, the amount of nitrogen relative to oxygen should 
increase as the hotter, more massive stars die and the galaxy becomes redder.  
This is exactly what we see in Fig. \ref{fig:color_NO}.  We use rest-frame 
colors $K$-corrected to a redshift of 0.1; they are corrected for galactic 
extinction and calculated with model magnitudes \citep{Choi10}.  
\cite{vanZee06a} and \cite{Berg12} also found an increase in the N/O ratio as a 
function of color.

\begin{figure*}
    \includegraphics[width=0.49\textwidth]{Images/Paper2/ur_NO_1sig_I06_dwarf_0-20_SF_t3}
    \includegraphics[width=0.49\textwidth]{Images/Paper2/gr_NO_1sig_I06_dwarf_0-20_SF_t3}
    \caption[Color versus N/O for 135 dwarf galaxy sample]{Color ($u-r$ and 
    $g-r$) vs. N/O ratio for star-forming void (red circles) and wall (black 
    triangles) dwarf galaxies.  Error bars have been omitted for clarity.  N/O 
    is expected to increase as galaxies become redder if there is a time delay 
    between the release of oxygen and nitrogen.  To place the dwarf galaxies in 
    context, we also plot the star-forming galaxies with $M_r > -20$ 
    (gray stars).}
    \label{fig:color_NO}
\end{figure*}

%-------------------------------------------------------------------------------
\subsection{(s)SFR--N/O relation}

We expect there to be a correlation between SFR or sSFR (per unit stellar mass) 
and the N/O ratio in galaxies as a result of the positive correlations between 
the SFR and stellar mass of a galaxy \citep{Brinchmann04} and the sSFR and the 
color of a galaxy (Fig. \ref{fig:color_sSFR}).  As shown in Fig. \ref{fig:MNO}, 
the N/O ratio increases with increasing stellar mass.  As a result, we expect 
there to be a positive correlation between the SFR and N/O ratio in our 
galaxies.  This can be seen in the sample of star-forming galaxies with 
$M_r > -20$ in the left panel of Fig. \ref{fig:SFR_NO}.  Due to the large 
scatter in this relation, the blue star-forming dwarf galaxies exhibit a 
negative correlation between their N/O ratios and their SFRs.  These SFR are 
aperture corrected to estimate the total SFR in the galaxy (not just within the 
SDSS fiber).

\begin{figure*}
    \includegraphics[width=0.49\textwidth]{Images/Paper2/u-r_sSFR_dwarf_0-20_SF_t3}
    \includegraphics[width=0.49\textwidth]{Images/Paper2/g-r_sSFR_dwarf_0-20_SF_t3}
    \caption[Color versus sSFR for 135 dwarf galaxy sample]{Color ($u-r$ and 
    $g-r$) vs. sSFR for star-forming void (red circles) and wall (black 
    triangles) dwarf galaxies.  It is obvious that there is a negative 
    correlation between the $\log (sSFR)$ and the color of a galaxy.  To place 
    the dwarf galaxies in context, we also show the star-forming galaxies with 
    $M_r > -20$ (gray stars).}
    \label{fig:color_sSFR}
\end{figure*}

The N/O ratio is expected to decrease as sSFR increases in galaxies, as is shown 
in the right panel of Fig. \ref{fig:SFR_NO}.  Bluer galaxies have higher sSFR.  
Fig. \ref{fig:color_NO} shows that there is a positive correlation between the 
color and the N/O ratio, such that bluer galaxies have lower N/O ratios.  As a 
result, we are not surprised to see that the N/O ratio decreases as the sSFR 
increases.
%Oxygen is produced in higher-mass stars 
%than nitrogen.  Since a star's lifetime is inversely proportional to its mass, 
%the stars that produce oxygen will die and release their heavy elements to the 
%ISM sooner than the stars responsible for producing nitrogen.  As a result, 
%after a recent star formation episode (when the sSFR is high), the amount of 
%oxygen will increase relative to nitrogen, decreasing the N/O ratio.  As the 
%sSFR of a galaxy declines, its N/O ratio will slowly increase as the nitrogen in 
%the intermediate-mass stars is released.

\begin{figure*}
    \includegraphics[width=0.49\textwidth]{Images/Paper2/SFR_NO_1sig_I06_dwarf_0-20_SF_t3}
    \includegraphics[width=0.49\textwidth]{Images/Paper2/sSFR_NO_1sig_I06_dwarf_0-20_SF_t3}
    \caption[(s)SFR versus N/O for 135 dwarf galaxy sample]{SFR--N/O and 
    sSFR--N/O relations for star-forming void (red circles) and wall (black 
    triangles) dwarf galaxies.  Error bars have been omitted for clarity.  Based 
    on the correlations between SFR and stellar mass and sSFR and color, we 
    expect the N/O ratio to increase with increasing SFR and decrease with sSFR.  
    To place the dwarf galaxies in context, we also show the star-forming 
    galaxies with $M_r > -20$ (gray stars).}
    \label{fig:SFR_NO}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%    DISCUSSION
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Discussion]{Large-scale environmental influence}\label{sec:environment}

The majority of the shifts in the gas-phase abundances of oxygen, nitrogen, and 
the N/O ratio seen in galaxies fainter than $L_*$ are small and statistically 
insignificant.  However, they occur in almost the same direction across all 
magnitude bins.  This trend suggests that the gas-phase abundances may be 
influenced by the galaxies' large-scale environments.  \cite{Shields91} find no 
offset in the N/O ratio between cluster and field galaxies, despite the 
difference in O/H they observe.  Similar to us, \cite{Contini02} and 
\cite{Pilyugin02} also find a statistically insignificant shift in the N/O ratio 
of cluster galaxies, although they find that these galaxies have lower N/O 
ratios than field spiral galaxies.  Based on Fig. \ref{fig:NOratio} and the 
statistics in Table \ref{tab:stats}, we find weak evidence that void dwarf 
galaxies have a smaller N/O ratio than dwarf galaxies in denser regions.  This 
means that void dwarf galaxies may have more oxygen than wall dwarf galaxies, 
and/or void dwarf galaxies could have less nitrogen than wall dwarf galaxies.  
Here we discuss these possibilities and explore their implications for the 
large-scale environmental impact on the formation and evolution of galaxies.

%If there was more oxygen in void dwarf galaxies than wall dwarf galaxies, then 
%we would expect to see this reflected in the oxygen abundance distributions.  
%However, as Fig. \ref{fig:met1sig} shows, this is not the case --- both void and 
%wall dwarf galaxies have equal distributions of oxygen abundance.  Therefore, to 
%have a difference in oxygen but to return the results seen in Fig. 
%\ref{fig:met1sig}, void dwarf galaxies must then also have more hydrogen than 
%wall dwarf galaxies.  This is definitely possible, as we expect that void 
%galaxies are more privy to an inflow of pristine hydrogen-rich gas than wall 
%galaxies.  However, explaining the excess oxygen in void galaxies is more 
%difficult.  Void dwarf galaxies might retain more of their metals than do wall 
%dwarf galaxies because of the absence of tidal forces, ram pressure stripping, 
%etc. in the void environment.
%
%On the other hand, the difference in Fig. \ref{fig:NOratio} could also be 
%explained by there being less nitrogen in void dwarf galaxies than wall dwarf 
%galaxies.  This would seem to match the theory more, since it is thought that 
%void galaxies should produce fewer metals.  However, this result is not 
%reflected in Fig. \ref{fig:N_1sig}, since the two populations are centered on 
%similar values of $12 + \log \left( \text{N}/\text{H} \right)$.

Table \ref{tab:stats} suggests a slight large-scale environmental dependence of 
the oxygen and nitrogen abundances (relative to hydrogen), where void galaxies 
have slightly more O/H and N/H than wall galaxies.  This small difference is 
not apparent when looking at Figs. \ref{fig:met1sig} and \ref{fig:N_1sig}.  
However, the N/O ratio amplifies this large-scale environmental effect so that a 
shift in the mean (or median) of the two populations can be seen in Fig. 
\ref{fig:NOratio}.  We hesitate to combine the results across all magnitude bins 
in an effort to improve their significance.  Instead, we look toward the future 
to analyze a larger sample of galaxies to increase the statistical significance 
of these results.

\subsection{Higher metallicities in void dwarf galaxies}

A slightly higher metallicity in void dwarf galaxies than wall dwarf galaxies 
may be evidence of a difference in the ratio of dark matter halo mass to stellar 
mass between the two environments.  Simulations by \cite{Jung14} and 
\cite{Tonnesen15} show that the dark matter halo masses of void central galaxies 
are larger than those of wall central galaxies for a given stellar mass.  Due to 
their environment, void dwarf galaxies are more likely to be in the center of 
their own dark matter halo.  Wall dwarf galaxies, on the other hand, are much 
more likely to be a satellite galaxy within a much larger dark matter halo; the 
simulation results mentioned above would not apply to these wall dwarf galaxies.  
However, because the wall dwarf galaxies studied here have sufficiently high 
sSFRs, they most likely live in a small-scale environment very similar to that 
of the void dwarf galaxies, as discussed in Paper I.  As a result, it is likely 
that (and should be tested to see whether) the wall dwarf galaxies in this study 
are actually central galaxies.

Applying the results of these simulations to our dwarf galaxy sample, if the 
ratio of dark matter halo mass to stellar mass is larger in void galaxies, the 
metals ejected from a void galaxy's ISM into its circumgalactic medium are more 
likely to fall back onto the ISM than in a wall galaxy with the same stellar 
mass, since the void galaxy's virial radius and potential well are larger.  As a 
result, two dwarf galaxies with the same stellar mass in these two different 
large-scale environments can have different metallicities --- void dwarf 
galaxies would have higher metallicities than wall dwarf galaxies, matching what 
we see in Table \ref{tab:stats}.

\subsection{Lower N/O ratios in void dwarf galaxies}

A difference in the N/O ratio between void dwarf galaxies and wall dwarf 
galaxies could be a result of the difference in the synthesis of nitrogen in 
galaxies within these two large-scale environments.  If void galaxies are 
retarded in their star formation (as simulations of the $\Lambda$CDM cosmology 
suggest), then cosmic downsizing would reduce the SFR at late times much more in 
wall galaxies than in void galaxies.  As a result, the minimum gas-phase 
metallicity required for the production of secondary nitrogen in walls would be 
achieved at an earlier time in the galaxy's lifetime than in a void galaxy.  
This would cause the N/O ratio in wall galaxies to be larger than that in voids.  
\cite{vanZee06a} suggest that a galaxy with a declining SFR (wall galaxies) will 
have a higher nitrogen-to-oxygen yield than a galaxy with a constant SFR (void 
galaxies).  This is due to more oxygen being released into the ISM as a result 
of the ongoing star formation in the void galaxies.  This explanation is 
supported by the color--N/O diagram in Fig. \ref{fig:color_NO}, which reveals 
that redder galaxies have higher N/O ratios.  The correlation between color and 
the N/O ratio found in \cite{vanZee06a}, \cite{Berg12}, and Fig. 
\ref{fig:color_NO} is a result of declining SFRs \citep{vanZee06a}.  Therefore, 
the shift in the N/O ratio we see between void and wall galaxies may be 
observational evidence of retarded star formation in void galaxies as a result 
of cosmic downsizing.
%If wall galaxies have a higher 
%N/H ratio than void galaxies, they could be producing nitrogen as a secondary 
%element more so than void dwarf galaxies.  This would cause the N/O ratio in 
%wall galaxies to be larger than that in voids.

Another explanation that would lead to a shift in the N/O ratio between 
environments is a difference in the ratio of intermediate- and high-mass stars 
produced in void and wall dwarf galaxies.  For there to be more oxygen relative 
to nitrogen in void dwarf galaxies, the percent of higher-mass stars produced in 
a star formation episode would be higher than that in wall dwarf galaxies.  This 
would indicate a varying IMF as a function of large-scale environment.  Previous 
studies have been inconclusive when testing for a varying IMF \citep[see][for 
example]{Kroupa01, Kroupa02, Hoversten08, Meurer09}.  It is beyond the scope of 
this paper to elaborate on this explanation.
%This is the opposite of the (extremely mild) offset between the two environments 
%that Ginny found.

%-------------------------------------------------------------------------------
\subsection{N/O ratio for extremely low metallicity galaxies}

While Paper I shows that there is not a special population of extremely low 
metallicity dwarf galaxies residing in voids, we want to look in particular at 
the N/O ratio of extremely low metallicity galaxies.  For the 21 dwarf galaxies 
with $12 + \log (\text{O}/\text{H}) < 7.6$ identified in Paper I, we see from 
Fig. \ref{fig:OHvNH} that their N/H ratios are also some of the lowest in the 
dwarf galaxy sample.  However, as shown in Fig. \ref{fig:OvN}, their N/O ratios 
cover the range of N/O ratio values of all the dwarf galaxies studied.  This is 
consistent with the expectation that nitrogen behaves as a primary element for 
galaxies with low and moderate metallicities.  Details of these 21 dwarf 
galaxies with extremely low metallicities are listed in Table \ref{tab:lowZ_P2}, 
including their gas-phase chemical abundances.

\input{Tables/Paper2/XMPtable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%    CONCLUSION
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

The nucleosynthesis of nitrogen is a vital component of the chemical evolution 
of galaxies in our universe.  We estimate the nitrogen abundance and N/O ratio 
of dwarf galaxies using the direct $T_e$ method and spectroscopic line flux 
measurements from the SDSS DR7 sample as reprocessed in the MPA-JHU catalog.  
The 135 galaxies analyzed suggest a slight large-scale environmental dependence 
of the N/O ratio, where void dwarf galaxies could have a lower N/O ratio than 
dwarf galaxies in denser environments.  Thus, the large-scale 
($\sim 10\text{ Mpc}$) environment might influence the chemical evolution of 
dwarf galaxies.

We find small, statistically insignificant shifts in the mean (or median) N/O 
ratio for galaxies between the void and denser regions across all blue, 
star-forming galaxies with $M_r > -20$.  These shifts are somewhat more 
significant, however, when we look at the entire sample of galaxies.  Each 
magnitude bin is shifted in the same direction, and are potentially very 
interesting, as they might indicate delayed star formation histories, more 
constant SFRs, and larger ratios of dark-matter-halo-mass to stellar mass in 
void galaxies, as discussed in Section \ref{sec:environment}.  A larger sample 
would help test these results.  We look to increase the sample and probe a 
larger magnitude (and mass) range of dwarf galaxies in Douglass \& Vogeley 
(2017, in preparation).

In addition, we look at the relationship between the N/O ratio and other 
physical characteristics of our dwarf galaxies.  In the relation between N/O and 
O/H, our galaxies all reside on the so-called ``nitrogen plateau,'' where the 
N/O ratio is predicted to be constant for low and intermediate metallicities.  
However, instead of a constant value for these galaxies, we find a negative 
correlation between the N/O and O/H ratios.  Our dwarf galaxies show a positive 
correlation between stellar mass and the N/O ratio.  These dwarf galaxies have 
some of the lowest N/O ratios for both their color and (s)SFR.  Beyond the 
suggestive large-scale environmental dependence of the N/O ratio, there is no 
clear large-scale environmental dependence in any of these relationships.

The N/O ratios of the extremely metal-poor dwarf galaxies are no different than 
those of the remaining dwarf galaxy sample, though their N/H abundance is also 
extremely low.  A more detailed study of these 21 extremely metal-poor dwarf 
galaxies is recommended to confirm their abundance values and discover any 
characteristics shared by the population.

Although SDSS provides spectroscopic observations for over 800,000 galaxies, 
only 135 are dwarf galaxies with emission-line fluxes necessary to estimate the 
gas-phase chemical abundances using the direct $T_e$ method.  The greatest 
limiting factor in this sample is the requirement of the [\ion{O}{2}] 
$\lambda 3727$ doublet in the abundance calculations.  We seek to develop a 
work-around for this emission line in Douglass \& Vogeley (2017, in preparation) 
to greatly increase our sample of dwarf galaxies with abundance estimates.  
These estimated ionic abundances can then be compared with environmental 
dependence of star formation and abundance predictions from high-resolution 
hydrodynamic simulations.

Further tests may refine our understanding of the environmental scale that is 
important for determining the chemical evolution of dwarf galaxies.  In 
particular, it will be important to examine whether the influence of relatively 
small-scale ($\sim$2 Mpc) environments is more significant to a dwarf galaxy's 
chemical evolution than the larger-scale environment investigated here.  In 
previous work, both \cite{Kreckel15} and \cite{Beygu17} find little evidence to 
support a significant large-scale environmental influence on the gas content, 
chemical content, or SFR of void galaxies.  Future work will expand on these 
studies with a larger sample and the possible influence they might have on the 
dwarf galaxies' chemical contents and SFRs.  \cite{Beygu17} also investigate any 
connection between a galaxy's physical properties and its location within a 
void.  We also look to study this possible connection with the increased sample 
size of dwarf galaxies in Douglass \& Vogeley (2017, in preparation).

### 2017-06-02 KellyDouglass/Thesis/Thesis_sections/Paper3.tex
Papers 1,2, small-scale results-conclusions

\chapter{Large-scale environmental dependence of chemical abundances in dwarf galaxies and implications for connecting star formation and halo mass}

### 2017-06-02 KellyDouglass/Thesis/Thesis_sections/smallScaleEnvironment.tex
Papers 1,2, small-scale results-conclusions

\chapter[Small-scale environment]{The influence of the small-scale environment on dwarf galaxy evolution}

This work was done in collaboration with Daniele Schneider for her senior thesis 
``The effects of small-scale environment on dwarf galaxies.''

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section[Introduction]{Introduction}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section[Theory]{Calculating distances}\label{sec:Theory_dist}

\subsection{Peculiar velocity}
% Finger of God

\subsection{Sky separation in \hMpc}

\subsection{Fractional virial radii}
% Virial radius calculation

\subsection{Absolute distance to nearest neighbor}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section[Data]{SDSS Data and galaxy selection}

% SDSS

% photometry from KIAS-VAGC
% sSFR from MPA-JHU (Brinchmann04)
% gas-phase chemical abundances from Douglass17c

\subsection{Various samples}

% Spectroscopic sample (those with chemical abundance estimates)
% Full SDSS dwarf galaxy sample

\subsection{Group catalog}

\cite{Berlind06}

\subsection{Finding the nearest neighbor}
% Absolute magnitude distribution of neighbors

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section[Results]{Distance analysis and results}

Our primary objective is to compare various physical characteristics of dwarf 
galaxies against their nearest neighbors or groups to discern how the 
small-scale environment affects their evolution.

\subsection{Parameter -- distance relations}\label{sec:Relations}

The relationships between various physical parameters and the distance to the 
nearest neighbor or group for our sample of star-forming dwarf galaxies are 
shown in Figs. \ref{fig:ur}--\ref{fig:NO}.  In each of the four plots within 
each figure, we bin the galaxies in distance-space and show the average 
parameter value in each bin, to see any overall trends in the data.  We also fit 
a linear line to the data; the output of these fits are in Table \ref{tab:fits}.  
Each of these four plots probes this distance relationship from a different 
angle.  The top left plots in Figs. \ref{fig:ur}--\ref{fig:NO} compare the 
target dwarf galaxy's parameter to the distance to its nearest neighbor, as 
defined by the the closest galaxy on the sky in \hMpc with a velocity difference 
less than 300 km/s.  The bottom left plots compare the target dwarf galaxy's 
parameter to the distance to its nearest neighbor, as defined by the closest 
galaxy on the sky in units of the virial radius of the neighbor galaxy with a 
velocity difference less than 300 km/s.  The nearest galaxy is not necessarily 
the same for these two distance measurements, as explained in Sec. 
\ref{sec:Theory_dist}.

We repeat this same analysis on the nearest groups to the target dwarf galaxy.  
The top right plots in Figs. \ref{fig:ur}--\ref{fig:NO} compare the target dwarf 
galaxy's parameter to the distance to the center of the nearest group, as 
defined as the closest group on the sky in \hMpc with a velocity difference less 
than 300 km/s.  The bottom right plots in Figs. \ref{fig:ur}--\ref{fig:NO} 
compare the target dwarf galaxy's parameter to the distance to the nearest group 
as defined by the closest group on the sky in units of the group's rms radius 
with a velocity difference of less than 300 km/s.  Groups are very rare in the 
void environment (by nature of the void environment), so the uncertainty in the 
binned values shown in these plots is much larger than in the galaxy neighbor 
plots.

These figures reveal influences from both the large-scale and small-scale 
environments, since we are identifying which galaxies reside in void regions and 
which do not.

\subsubsection{Color}

\begin{figure}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_ur_300}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_ur_300_group}
    \caption[$u-r$ versus distance to nearest neighbor and group]{Color ($u-r$) 
    versus distance to the nearest galaxy (on the left) and nearest group (on 
    the right).  The top panel shows the color as a function of the sky 
    separation in \hMpc between the target dwarf galaxy and the neighbor, while 
    the bottom panel shows the color as a function of the closest virial 
    neighbor.  Void galaxies are shown in red, while wall galaxies are shown in 
    black and unknown in green.  We have also included the average color for the 
    galaxies after binning by distance, to discern any finer behavior in the 
    relationships.  Linear fits to the void and wall galaxies are shown in 
    orange and blue, respectively.  It is clear that the void dwarf galaxies are 
    bluer than the wall dwarf galaxies.  The nearest galaxies appear to only 
    have some affect on the dwarf galaxy's color at separations less than 0.05 
    \hMpc, or 0.05$r_{vir}$.  The closest group appears to have some 
    affect on the target dwarf galaxy's color at distances less than 0.1 \hMpc 
    to the group's center; there appears to be no relationship between a dwarf 
    galaxy's color and its distance to the nearest group as represented by the 
    fraction of the group's radius.}
    \label{fig:ur}
\end{figure}

Because of the known morphology-density relation, we excepted to find that a 
dwarf galaxy's color became more blue as the distance to its nearest neighbor 
increased.  Fig. \ref{fig:ur} shows very little relationship between the 
distance and color, except at the smallest distance bin.  The linear fits 
quantify this observation --- the slopes are on the order of 10$^{-3}$.  
However, within a distance of 0.05 \hMpc or 0.05$r_{vir}$, dwarf galaxies tend 
to be bluer than at further distances from their nearest neighbor.  At distances 
less than 0.1 \hMpc from the center of the nearest groups, the dwarf galaxies 
are redder than average.  However, there does not appear to be any relationship 
between a dwarf galaxy's color and its distance to the center of the nearest 
group in units of the group's rms radius.  It has been well-established that 
void galaxies tend to be bluer than galaxies in denser environments 
\citep{Grogin99,Rojas04,Patiri06,vonBendaBeckmann08,Hoyle12}; this shift is 
apparent in Fig. \ref{fig:ur}, where the void dwarf galaxies are slightly bluer 
than the wall dwarf galaxies.

\subsubsection{sSFR}

\begin{figure}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_sSFR_300}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_sSFR_300_group}
    \caption[sSFR versus distance to nearest neighbor and group]{sSFR versus 
    distance to the nearest galaxy (on the left) and nearest group (on the 
    right).  The top panel shows the sSFR as a function of the sky separation in 
    \hMpc between the target dwarf galaxy and the neighbor, while the bottom 
    panel shows the sSFR as a function of the closest virial neighbor.  Void 
    galaxies are shown in red, while wall galaxies are shown in black and 
    unknown in green.  We have also included the average sSFR for the galaxies 
    after binning by distance, to discern any finer behavior in the 
    relationships.  Linear fits to the void and wall galaxies are shown in 
    orange and blue, respectively.  It is clear that the void dwarf galaxies 
    have higher sSFRs than the wall dwarf galaxies.  Only the neighbor galaxies 
    at separations less than 0.05 \hMpc or 0.05$r_{vir}$ appear to have some 
    affect on the dwarf galaxies' sSFR.  There appears to be no relationship 
    between a dwarf galaxy's sSFR and its distance to the nearest group.}
    \label{fig:sSFR}
\end{figure}

Following our prediction for the color-distance relations, we expect that the 
sSFR to increase with distance from the nearest neighbor.  We also see very 
little relationship between the distance and sSFR in Fig. \ref{fig:sSFR}, except 
in the smallest distance bin.  The linear fits quantify this observation --- the 
slopes are on the order of 10$^{-3}$.  Within a distance of 0.05 \hMpc or 
0.05$r_{vir}$, dwarf galaxies tend to have higher sSFRs than at further 
distances from their nearest neighbor.  There does not appear to be any 
relationship between a dwarf galaxy's sSFR and its distance to the center of the 
nearest group in either distance metric.  In these distance comparisons, there 
is a shift towards higher sSFRs in the void dwarf galaxies when compared to the 
wall dwarf galaxies, as has been observed many times before \citep{Rojas05,
vonBendaBeckmann08,Moorman15,Beygu16}.

\subsubsection{Metallicity}

\begin{figure}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_OH_300}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_OH_300_group}
    \caption[Metallicity versus distance to nearest neighbor and group]
    {Metallicity versus distance to the nearest galaxy (on the left) and nearest 
    group (on the right).  The top panel shows the metallicity as a function of 
    the sky separation in \hMpc between the target dwarf galaxy and the 
    neighbor, while the bottom panel shows the metallicity as a function of the 
    closest virial neighbor.  Void galaxies are shown in red, while wall 
    galaxies are shown in black and unknown in green.  We have also included the 
    average metallicity for the galaxies after binning by distance, to discern 
    any finer behavior in the relationships.  Linear fits to the void and wall 
    galaxies are shown in orange and blue, respectively.  It is clear that the 
    void dwarf galaxies have higher metallicities than the wall dwarf galaxies.  
    Only the neighbor galaxies at separations less than 0.05 \hMpc or 
    0.05$r_{vir}$ appear to have some affect on the dwarf galaxies' metallicity.  
    When measuring the distance to the nearest group in \hMpc, it appears that 
    the dwarf galaxies have lower metallicities at distances less than 0.1 \hMpc 
    from their nearest group.}
    \label{fig:OH}
\end{figure}

Based on our hypothesis that galaxies would be redder and have lower sSFRs at 
small distances to their nearest neighbors, we anticipated that the metallicity 
of the galaxies would decrease with increasing distance.  As before, we only see 
a relationship between the distance and metallicity in the smallest distance 
bin in Fig. \ref{fig:OH}.  The linear fits quantify this observation --- the 
slopes are on the order of 10$^{-2}$.  Within a distance of 0.05 \hMpc or 
0.05$r_{vir}$, dwarf galaxies tend to have higher metallicities than at further 
distances from their nearest neighbor.  At distances less than 0.1 \hMpc from 
the center of the nearest group, dwarf galaxies might have lower than average 
metallicities.  However, this could be an erroneous conclusion due to low-number 
statistics.  In these distance comparisons, there is a shift towards higher 
metallicities in the void dwarf galaxies when compared to the wall dwarf 
galaxies, as has been observed by \cite{Douglass17b} and Douglass \& Vogeley 
(2017, in prep).

\subsubsection{Nitrogen abundance}

\begin{figure}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_NH_300}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_NH_300_group}
    \caption[N/H versus distance to nearest neighbor and group]{Gas-phase 
    nitrogen abundance versus distance to the nearest galaxy (on the left) and 
    nearest group (on the right).  The top panel shows N/H as a function of the 
    sky separation in \hMpc between the target dwarf galaxy and the neighbor, 
    while the bottom panel shows N/H as a function of the closest virial 
    neighbor.  Void galaxies are shown in red, while wall galaxies are shown in 
    black and unknown in green.  We have also included the average nitrogen 
    abundance for the galaxies after binning by distance, to discern any finer 
    behavior in the relationships.  Linear fits to the void and wall galaxies 
    are shown in orange and blue, respectively.  There is very little difference 
    in N/H between the two large-scale environments.  Only the neighbor galaxies 
    at separations less than 0.05$r_{vir}$ appear to have some affect on the 
    dwarf galaxies' nitrogen abundance.  There does not appear to be any 
    relationship between the dwarf galaxies' nitrogen abundance and the distance 
    to their nearest group.}
    \label{fig:NH}
\end{figure}

It was expected that the gas-phase nitrogen abundance would follow the same 
trend as the metallicity, to decrease with increasing distance.  As observed 
with the other parameters, Fig. \ref{fig:NH} shows very little relationship 
between the distance and N/H, except in the smallest distance bin for the 
closest virial neighbor.  The linear fits quantify this observation --- the 
slopes are on the order of 10$^{-2}$.  Within a distance of 0.05$r_{vir}$, dwarf 
galaxies tend to have higher nitrogen abundances than at distances further from 
their nearest neighbor.  There does not seem to be any relationship between the 
nitrogen abundance of the star-forming dwarf galaxies and distance to the center 
of the nearest group.  Unlike the shifts seen with the other parameters and what 
is observed in \cite{Douglass17b} and Douglass \& Vogeley (2017, in prep), we 
see no significant difference in the nitrogen abundance resulting from the 
large-scale environment.

\subsubsection{N/O ratio}

\begin{figure}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_NO_300}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_NO_300_group}
    \caption[N/O versus distance to nearest neighbor and group]{N/O ratio versus 
    distance to the nearest galaxy (on the left) and nearest group (on the 
    right).  The top panel shows the N/O ratio as a function of the sky 
    separation in \hMpc between the target dwarf galaxy and the neighbor, while 
    the bottom panel shows N/O as a function of the closest virial neighbor.  
    Void galaxies are shown in red, while wall galaxies are shown in black and 
    unknown in green.  We have also included the average nitrogen abundance for 
    the galaxies after binning by distance, to discern any finer behavior in the 
    relationships.  Linear fits to the void and wall galaxies are shown in 
    orange and blue, respectively.  The void dwarf galaxies have lower N/O 
    ratios than the wall dwarf galaxies, but there is no distinct relationship 
    between the distance to the nearest neighbor and the N/O ratio.  The N/O 
    ratio might be higher in dwarf galaxies within 0.05 \hMpc of the center of 
    the closest group.}
    \label{fig:NO}
\end{figure}

We do not expect any influence on the relative synthesis of oxygen and nitrogen 
from the proximity to a nearest neighbor.  Unlike the other parameters studied, 
Fig. \ref{fig:NO} shows that the N/O ratio does not have any relationship with 
the distance to a nearest neighbor at any separation.  This is reflected in the 
linear fits to the data --- the slopes are on the order of 10$^{-2}$ and 
smaller.  When looking at the relationship between the N/O ratio and the 
distance to the nearest group, though, the N/O ratio might be higher than 
average in galaxies within 0.1 \hMpc of the group's center.  The shift towards 
lower N/O ratios in star-forming void dwarf galaxies is readily apparent, as 
\cite{Douglass17b} and Douglass \& Vogeley (2017, in prep) find.

\subsection{Linear fit parameters}

\begin{table}
    \begin{tabular}{lcccc}
        Property & Slope (wall) & Slope (void) & Intercept (wall) & Intercept (void)\\
        \hline
        \hline
        \multicolumn{5}{c}{Nearest galaxy by distance}\\
        \hline
        $u-r$ & $1.25\pm 1.17\times 10^{-3}$ & $-9.14\pm 0.56\times 10^{-3}$ & $1.15\pm 0.00076$ & $1.09\pm0.00049$\\
        sSFR & $2.07\pm 0.18\times 10^{-2}$ & $-0.16\pm 0.08\times 10^{-3}$ & $-9.45\pm 0.001$ & $-9.34\pm 0.0007$\\
        \OH & $5.35\pm 0.17\times 10^{-2}$ & $0.33\pm 0.08\times 10^{-2}$ & $7.75\pm 0.0011$ & $7.86\pm 0.0007$\\
        \NH & $1.64\pm 0.11\times 10^{-2}$ & $0.62\pm 0.06\times 10^{-2}$ & $6.53\pm 0.0007$ & $6.52\pm 0.0006$\\
        \NO & $-3.70\pm 0.13\times 10^{-2}$ & $0.29\pm 0.07\times 10^{-2}$ & $-1.23\pm 0.0009$ & $-1.35\pm 0.0006$\\
        \hline
        \multicolumn{5}{c}{Nearest galaxy by fraction of virial radius}\\
        \hline
        $u-r$ & $-3.81\pm 0.04\times 10^{-3}$ & $-0.46\pm 0.01\times 10^{-3}$ & $1.16\pm 0.00014$ & $1.09\pm0.00008$\\
        sSFR & $5.96\pm 0.06\times 10^{-3}$ & $-0.41\pm 0.02\times 10^{-3}$ & $-9.45\pm 0.0002$ & $-9.33\pm 0.0001$\\
        \OH & $1.41\pm 0.005\times 10^{-2}$ & $0.12\pm 0.08\times 10^{-2}$ & $7.74\pm 0.0002$ & $7.86\pm 0.0001$\\
        \NH & $1.82\pm 0.11\times 10^{-3}$ & $-1.14\pm 0.002\times 10^{-3}$ & $6.53\pm 0.0001$ & $6.52\pm 0.0001$\\
        \NO & $-1.22\pm 0.004\times 10^{-2}$ & $-0.41\pm 0.02\times 10^{-3}$ & $-1.21\pm 0.0002$ & $-1.33\pm 0.0001$\\
        \hline
        \multicolumn{5}{c}{Nearest group by distance}\\
        \hline
        $u-r$ & $-2.53\pm 0.01\times 10^{-3}$ & $1.34\pm 0.01\times 10^{-3}$ & $1.16\pm 0.00008$ & $1.08\pm0.0001$\\
        sSFR & $7.77\pm 0.02\times 10^{-3}$ & $-1.68\pm 0.02\times 10^{-3}$ & $-9.48\pm 0.001$ & $-9.33\pm 0.0001$\\
        \OH & $3.65\pm 0.16\times 10^{-4}$ & $2.06\pm 0.19\times 10^{-4}$ & $7.77\pm 0.0001$ & $7.86\pm 0.0001$\\
        \NH & $4.84\pm 0.01\times 10^{-3}$ & $6.30\pm 0.01\times 10^{-3}$ & $6.51\pm 0.00008$ & $6.49\pm 0.0001$\\
        \NO & $4.47\pm 0.01\times 10^{-3}$ & $6.09\pm 0.01\times 10^{-3}$ & $-1.26\pm 0.0001$ & $-1.38\pm 0.0001$\\
        \hline
        \multicolumn{5}{c}{Nearest group by fraction of group radius}\\
        \hline
        $u-r$ & $-1.00\pm 0.002\times 10^{-3}$ & $0.90\pm 0.002\times 10^{-3}$ & $1.16\pm 0.00003$ & $1.07\pm0.00003$\\
        sSFR & $2.70\pm 0.002\times 10^{-3}$ & $-1.71\pm 0.002\times 10^{-3}$ & $-9.48\pm 0.00005$ & $-9.31\pm 0.00005$\\
        \OH & $8.81\pm 0.02\times 10^{-4}$ & $-8.74\pm 0.19\times 10^{-4}$ & $7.76\pm 0.00005$ & $7.88\pm 0.00005$\\
        \NH & $2.31\pm 0.001\times 10^{-3}$ & $2.47\pm 0.001\times 10^{-3}$ & $6.49\pm 0.00003$ & $6.47\pm 0.00004$\\
        \NO & $1.43\pm 0.002\times 10^{-3}$ & $3.35\pm 0.002\times 10^{-3}$ & $-1.26\pm 0.00005$ & $-1.40\pm 0.00005$
    \end{tabular}
    \caption[Fit parameters of properties versus distances]{Linear fit 
    parameters to various properties of the target dwarf galaxies by their 
    distances to the nearest galaxy in units of \hMpc, the nearest galaxy in 
    units of the neighbor's virial radius, the center of the nearest group in 
    units of \hMpc, and the nearest group in units of the group's rms radius; 
    all objects must be within 300 km/s of the target galaxy.  The slopes are 
    all negligible, quantifying the observations made that the proximity to a 
    galaxy or group has little influence on a dwarf galaxy's evolution.}
    \label{tab:fits}
\end{table}

To quantify the results shown in Figs. \ref{fig:ur}--\ref{fig:NO}, we calculate 
the parameters for the best fit linear line.  Any slope of significant magnitude 
shows an overall correlation between a given physical parameter and the galaxy's 
distance to its nearest neighbor or group.  The results of this analysis are 
listed in Table \ref{tab:fits}.  These slopes reflect the observations described 
in Section \ref{sec:Relations}: there is no correlation between the distance to 
the nearest neighbor and a galaxy's color, sSFR, or gas-phase chemical 
abundances.  This analysis does not capture any variations within the range of 
distances for all dwarf galaxies included in this study.

\subsection{Selection effects}

% Peculiar velocity
\begin{figure}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_ur_150}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_ur_600}
    \caption[Sensitivity to peculiar velocity maximum]{Color versus distance to 
    nearest galaxy (in units of \hMpc on top and virial radii on bottom), with a 
    maximum allowed peculiar velocity of 150 km/s in the left panel and 600 km/s 
    in the right panel.  Void galaxies are shown in red, wall in black, and 
    unknown in green.  The galaxies are binned by distance to tease out any 
    trends at smaller distance scales; linear fits to the void and wall galaxies 
    are shown in orange and blue, respectively.  When compared with the two 
    plots in the left panel of Fig. \ref{fig:ur}, we see that there is no 
    significant influence on our results from the choice of maximum peculiar 
    velocity allowed.}
    \label{fig:ur_vpeculiar}
\end{figure}

We test two of our input parameters to understand how sensitive our results are 
to any initial conditions.  The first parameter we discuss is the sensitivity of 
our results on the maximum peculiar velocity to define a match.  Throughout our 
analysis, we use 300 km/s as the maximum velocity separation allowed between the 
target galaxy and its nearest neighbor or group.  We look at how this affects our 
results by repeating the analysis with maximum velocities of 150 km/s and 600 
km/s.  The results of this comparison on the color of the galaxies can be seen in 
Fig. \ref{fig:ur_vpeculiar}.  The nearest neighbors in the left-hand panel are 
restricted to a maximum peculiar velocity of 150 km/s, while those in the right 
panel are restricted to 600 km/s.  When compared to each other and to the 
left-hand panel of Fig. \ref{fig:ur}, it is clear that our choice of maximum 
peculiar velocity has no affect on the results of the study.

% Spectroscopic sample v. complete sample
\begin{figure}
    \includegraphics[width=0.5\textwidth]{Images/smallScaleEnvironment/ALLdwarf_ur_300}
    \caption[Color versus distance of full SDSS dwarf population]{Color versus 
    distance to the nearest galaxy (in units of \hMpc on top and virial radii on 
    the bottom) for the entire dwarf galaxy population in SDSS DR7.  When 
    compared to the left-hand panel of Fig. \ref{fig:ur}, we see that there is 
    no difference in the results of the analysis by studying only star-forming 
    galaxies with sufficient detection of the various emission lines necessary 
    to estimate the gas-phase chemical abundances.}
    \label{fig:ur_allDwarf}
\end{figure}

We also test the sensitivity of our results to the population of galaxies being 
studied.  Because we want to look at the relationship between distance and the 
gas-phase chemical abundances of the dwarf galaxies, our sample is limited to 
star-forming dwarf galaxies with detected emission lines necessary for 
estimation of the chemical abundances with the Direct $T_e$ method 
\citep[see][for more details]{Douglass17a}.  We perform the same distance 
analysis on all dwarf galaxies detected in SDSS DR7 with respect to their 
color, to understand how our results depend on our sample.  When we compare Fig. 
\ref{fig:ur_allDwarf} with the left-hand panel of Fig. \ref{fig:ur}, we see that 
there is no difference in the correlation between color and distance to the 
nearest neighbor.  It is clear that our selection bias to star-forming dwarf 
galaxies does not influence any trends we observe in our analysis.

\subsection{Including redshift in the distance}
% Evidence of mergers

\begin{figure}
    \includegraphics[width=0.5\textwidth]{Images/smallScaleEnvironment/dwarf_ur_xyz}
    \caption[Color versus distance calculated with redshift]{Color versus 
    distance to the nearest galaxy (in units of \hMpc on top and virial radii on 
    the bottom) for the star-forming dwarf galaxies.  The redshift is included 
    when calculating the distance to the nearest neighbor.  While there is still 
    no correlation between distance and color, we do note that there is a gap in 
    the distribution of galaxies around a distance of 0.05 \hMpc or 0.5$r_{vir}$ 
    from the nearest neighbor.}
    \label{fig:ur_xyz}
\end{figure}

Realizing that the peculiar velocity, which is included in a galaxy's redshift, 
is not insignificant at the smaller scales, we have been careful to avoid 
calculating the distance between objects with the redshift.  However, we are 
interested to see how the inclusion of redshift in the distance calculations 
affects the results of our analysis.  Therefore, we repeat the same analysis on 
the relationship between color and distance, but this time we include redshift 
as a third component in the distance calculations.  Consequently, we no longer 
limit our sample by a peculiar velocity separation.  Fig. \ref{fig:ur_xyz} shows 
the relationship between these distances and the color of the star-forming dwarf 
galaxies.  When compared to Fig. \ref{fig:ur}, we see that there is no change in 
the correlation between distance and color for the galaxies.

We note the existence of a gap in the distribution of galaxies around a distance 
of 0.05 \hMpc or 0.5$r_{vir}$ from the nearest neighbor that is not present in 
Fig. \ref{fig:ur}.  When we incorporate the redshift into the distance 
calculations, the resulting distance between galaxies which have small sky 
separations but larger redshift separations is much larger than those with 
larger sky separations and little redshift separation.  As a result, galaxies 
which were originally close to the color axis in Fig. \ref{fig:ur} will be 
moved to much larger distances, while the locations of those which were 
originally further from the color axis will change much less.  The dwarf 
galaxies which remain close to the color axis in Fig. \ref{fig:ur_xyz} must, 
therefore, have small sky separation and almost no difference in their peculiar 
velocities.  We conclude that these represent merging systems, which visual 
inspection will help to confirm.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section[Discussion]{Discussion}

We see almost no relationship between a dwarf galaxy's color, sSFR, or gas-phase 
chemical abundance and its distance to the nearest galaxy or group, implying 
that the small-scale environment does not significantly influence a dwarf 
galaxy's evolution.  This is in contrast to the large-scale environment, which 
we have seen to influence the formation and evolution of dwarf galaxies.

Only those galaxies within 0.05 \hMpc and 0.05$r_{vir}$ of a nearest neighbor, 
or those within 0.1 \hMpc of the nearest group appear to deviate from the 
average galaxy values.  The galaxies within this proximity of their nearest 
neighbor tend to be bluer, have a higher sSFR, and have higher oxygen and 
nitrogen abundances.  Based on the shift in the distribution of galaxies in Fig. 
\ref{fig:ur_xyz}, these galaxies might be merging or strongly interacting with 
their nearest neighbor.  This would then provide evidence that galaxy 
interactions result in a burst of star formation, which would increase the 
gas-phase chemical abundances of the dwarf galaxies.  Because merging galaxies 
share the same dark matter halo, it appears that the sharing of a dark matter 
halo has more influence on the evolution of a galaxy than the distance to its 
nearest neighbor.

Dwarf galaxies within 0.1 \hMpc of the center of the nearest group are redder, 
have lower oxygen abundances, and have higher N/O ratios than average.  Being so 
close to the center of a group prevents more recent episodes of star formation.  
Due to their proximity to the group center, it is also likely that these dwarf 
galaxies are not able to retain as much of their heavier elements as for a more 
isolated galaxy, reducing their gas-phase oxygen abundance (and therefore 
increasing their N/O ratio).

\subsection{Comparison to literature results}

The influence on the gas-phase oxygen abundance within 0.05 \hMpc and 
0.05$r_{vir}$ agrees with the results of \cite{Shields91,Pustilnik06,Cooper08,
Ellison09,Pustilnik11a,Pustilnik14}, and \cite{SanchezAlmeida16}, which all find 
that galaxies with higher metallicities preferentially reside in denser regions.  
Work by \cite{Rupke08} finds that interacting galaxies have suppressed 
metallicities due to interaction- or merger-induced gas flows into the galaxy 
centers.

A study combining the effects of interactions and the large-scale environment is 
explained in \cite{Park09}.  They find two characteristic distances within which 
the behavior of the target galaxy changes: 0.05$r_{vir}$ and $r_{vir}$ of the 
neighboring galaxy.  Our results seem to confirm the significance of distances 
out to 0.05$r_{vir}$, while we see no significant change around the virial 
radius of the neighboring galaxy.  While they only look at galaxies with 
$M_r < -19$ and limit the neighbors to be at least half a magnitude brighter 
than the target, \cite{Park09} find that the morphology and luminosity play a 
significant role in these relationships.  Of particular note is their 
observation that star formation increases in late type galaxies when their 
nearest neighbor is also of late type.  This is the same behavior we see in our 
sample of dwarf galaxies at distances less than 0.05$r_{vir}$.  With all our 
target galaxies actively forming stars, and more than half of their nearest 
neighbors also dwarf galaxies, it is most likely that our galaxy pairs are also 
of the late-late type.  Based on the results of \cite{Park09}, the deviations we 
see for those galaxies with nearest neighbors within 0.05 \hMpc and 
0.05$r_{vir}$ warrant further study.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section[Conclusion]{Conclusion}

Using the star-forming dwarf galaxies in the SDSS DR7 sample with gas-phase 
chemical abundances from Douglass \& Vogeley (2017, in prep), we investigate the 
influence of the small-scale environment on the evolution of dwarf galaxies.  
From the $\sim$2000 galaxies in the sample, there only appears to be an effect 
from a neighboring galaxy within 0.05 \hMpc or 0.05$r_{vir}$.  The proximity of 
a group seems to only affect the target dwarf galaxy if it is within 0.1 \hMpc.  
Thus, the small-scale ($\sim 1$ \hMpc) environment does not appear to strongly 
influence the evolution of dwarf galaxies.

We examine the relationship between distance to the nearest neighbor or group 
and the target galaxy's color, sSFR, and gas-phase chemical abundances.  We find 
that, for those galaxies with a neighbor within 0.05 \hMpc or 0.05$r_{vir}$, the 
dwarf galaxies are bluer, have a higher sSFR, and have higher oxygen and 
nitrogen abundances than average.  In contrast, dwarf galaxies within 0.1 \hMpc 
of the center of the closest group are redder, have lower oxygen abundances, and 
have higher N/O ratios than average.  These results do not depend on the maximum 
peculiar velocity difference or on the sample (star-forming versus all 
galaxies).

When we incorporate the redshift into the distance calculations, we find that 
those galaxies within 0.05$r_{vir}$ are most likely mergers or strongly 
interacting with their nearest neighbor.  This matches the results of 
\cite{Park09}, who find that late-late type galaxy pairs within 0.05$r_{vir}$ 
are bluer and have higher star formation rates.  These merging galaxies likely 
share the same dark matter halo, indicating that the dark matter halo is more 
influential on a galaxy's evolution than its distance to the nearest neighbor.

### 2017-06-02 KellyDouglass/Thesis/preamble.tex
Papers 1,2, small-scale results-conclusions

\begin{preamble}

\iffinal{}{\newpage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Dedications
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{DUTdedications}
\begin{center}
Dedications
\end{center}
\end{DUTdedications}

\iffinal{}{\newpage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Acknowledgements
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{acknowledgments}

I would like to thank Crystal Moorman for her help and support throughout this 
work.  I would also like to acknowledge Renyue Cen for his help in the 
interpretation of these results.  Finally, I would like to thank the referees 
(including Burcu Beygu) for their detailed comments and critique of my work.

Support for this work was provided by NSF grant AST--1410525.

Funding for the SDSS and SDSS-II has been provided by the Alfred P. Sloan 
Foundation, the Participating Institutions, the National Science Foundation, the 
U.S. Department of Energy, the National Aeronautics and Space Administration, 
the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education 
Funding Council for England.  The SDSS Web Site is \emph{http://www.sdss.org/}.

The SDSS is managed by the Astrophysical Research Consortium for the 
Participating Institutions.  The Participating Institutions are the American 
Museum of Natural History, Astrophysical Institute Potsdam, University of Basil, 
University of Cambridge, Case Western Reserve University, University of Chicago, 
Drexel University, Fermilab, the Institute for Advanced Study, the Japan 
Participation Group, Johns Hopkins University, the Joint Institute for Nuclear 
Astrophysics, the Kavli Institute for Particle Astrophysics and Cosmology, the 
Korean Scientist Group, the Chinese Academy of Sciences (LAMOST), Los Alamos 
National Laboratory, the Max-Planck-Institute for Astronomy (MPIA), the 
Max-Planck-Institute for Astrophysics (MPA), New Mexico State University, Ohio 
State University, University of Pittsburgh, University of Portsmouth, Princeton 
University, the United States Naval Observatory, and the University of 
Washington.

\end{acknowledgments}

\iffinal{}{\newpage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Table of Contents
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\tableofcontents

\iffinal{}{\newpage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% List of Tables
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\listoftables

\iffinal{}{\newpage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% List of Figures
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\listoffigures

\iffinal{}{\newpage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}

% Paper 1
We study how the cosmic environment affects galaxy evolution in the Universe by 
comparing the metallicities of dwarf galaxies in voids with dwarf galaxies in 
more dense regions.  Ratios of the fluxes of emission lines, particularly those 
of the forbidden [\ion{O}{3}] and [\ion{S}{2}] transitions, provide estimates of 
a region's electron temperature and number density.  From these two quantities 
and the emission line fluxes [\ion{O}{2}] $\lambda 3727$, [\ion{O}{3}] 
$\lambda 4363$, and [\ion{O}{3}] $\lambda \lambda 4959,5007$, we estimate the 
abundance of oxygen with the Direct $T_e$ method.  We estimate the metallicity 
of 42 blue, star-forming void dwarf galaxies and 89 blue, star-forming dwarf 
galaxies in more dense regions using spectroscopic observations from the Sloan 
Digital Sky Survey Data Release 7, as re-processed in the MPA-JHU value-added 
catalog.  We find very little difference between the two sets of galaxies, 
indicating little influence from the large-scale environment on their chemical 
evolution.  Of particular interest are a number of extremely metal-poor dwarf 
galaxies that are less prevalent in voids than in the denser regions.

% Paper 2
We examine how the cosmic environment affects the chemical evolution of galaxies 
in the universe by comparing the N/O ratio of dwarf galaxies in voids with 
dwarf galaxies in denser regions.  Ratios of the forbidden [\ion{O}{3}] and 
[\ion{S}{2}] transitions provide estimates of a region's electron temperature 
and number density.  We estimate the abundances of oxygen and nitrogen using 
these temperature and density estimates and the emission-line fluxes 
[\ion{O}{2}] $\lambda 3727$, [\ion{O}{3}] $\lambda \lambda 4959, 5007$, and 
[\ion{N}{2}] $\lambda \lambda 6548, 6584$ with the direct $T_e$ method.  Using 
spectroscopic observations from the Sloan Digital Sky Survey Data Release 7, we 
are able to estimate the N/O ratio in 42 void dwarf galaxies and 89 dwarf 
galaxies in denser regions.  The N/O ratio for void dwarfs ($M_r > -17$) is 
slightly lower ($\sim 12\%$) than for dwarf galaxies in denser regions.   We 
also estimate the nitrogen and oxygen abundances of 2050 void galaxies and 3883 
galaxies in denser regions with $M_r > -20$.  These somewhat brighter galaxies 
(but still fainter than $L_*$) also display similar minor shifts in the N/O 
ratio.  The shifts in the average and median element abundance values in all 
absolute magnitude bins studied are in the same direction, suggesting that the 
large-scale environment may influence the chemical evolution of galaxies.  We 
discuss possible causes of such a large-scale environmental dependence of the 
chemical evolution of galaxies, including retarded star formation and a higher 
ratio of dark matter halo mass to stellar mass in void galaxies.

% Paper 3

% Small-scale enivronment

% GV

\end{abstract}

\iffinal{}{\newpage}

\end{preamble}

### 2017-06-05 KellyDouglass/Thesis/Thesis_sections/GV.tex
GV chapter

@@
 
-\section[Data]{SDSS and GALEX data}
+\section[Theory]{Calculating the color of a galaxy}
 
-\subsection{Optical data --- SDSS}
-%  - KIAS-VAGC (morphological classification)
-% Should we use NSA for abs. mag. instead?
-SDSS \citep{Abazajian09} (absolute magnitudes courtesy of the MPA-JHU 
-catalog\footnote{http://www.mpa-garching.mpg.de/SDSS/DR7/})
-
-The KIAS Value-Added Galaxy Catalog 
-\citep[KIAS-VAGC]{Choi10} attempted to calculate a morphological class and type 
-for all galaxies in SDSS DR7 based on the color $u-r$, color gradient 
-$\Delta (g-r)$, and inverse concentration index.
-
-\subsection{UV data --- GALEX}
-\citep{Martin05}
+A galaxy's color is the ratio of the flux emitted by the galaxy in two different 
+bands.  The stellar population of a galaxy will determine its color --- redder 
+galaxies contain much older, cooler stars, while the spectrum of a bluer galaxy 
+is produced by light from much younger, hotter stars.  A galaxy's color is 
+independent of its redshift, so only photometry is needed to calculate the 
+ratio.  While the KIAS-VAGC catalog (described below in Section \ref{sec:SDSS}) 
+provides the $u-r$ color for all galaxies in SDSS, we make use of the Petrosian 
+fluxes in the NSA (described in Section \ref{sec:GALEX}) to calculate the 
+UV--optical color.  The NUV$-r$ color is calculated by
+\begin{equation}
+    \text{NUV}-r = -2.5\log \left( \frac{f_{NUV}}{f_r} \right)
+\end{equation}
+where $f_{NUV}$ is the Petrosian flux in the NUV-band of GALEX, and $f_r$ is the 
+Petrosian flux in the $r$-band of SDSS.
 
@@
 
-\section[Results]{Results}
+\section[Data]{SDSS and GALEX data}
 
-Combining the results of GALEX with the optical photometry of SDSS, we construct 
-a NUV$-r$ CMD.  Probing light from even younger stars in the galaxies, GALEX is 
-able to increase the separation of the blue sequence and red cloud populations 
-of the optical CMD, revealing a third, smaller population of galaxies 
-\citep{Wyder07}.
+We use the photometric data from SDSS (optical) and GALEX (ultraviolet) as 
+cross-matched in the NSA.
+
+\subsection{Optical data --- SDSS}\label{sec:SDSS}
+% Should we use NSA for abs. mag. instead? - yes, but not for the thesis
+
+The SDSS Data Release 7 \citep[DR7]{Abazajian09} is a wide-field multi-band 
+imaging and spectroscopic survey.  It uses drift scanning to map approximately 
+one-quarter of the northern sky.  A dedicated 2.5-meter telescope at the Apache 
+Point Observatory in New Mexico takes photometric data in the five-band SDSS 
+system --- $u$, $g$, $r$, $i$, and $z$ \citep{Fukugita96,Gunn98}.  Galaxies with 
+a Petrosian $r$-band apparent magnitude $m_r < 17.77$ are selected for 
+spectroscopic analysis \citep{Lupton01,Strauss02}.  Gas-phase chemical 
+abundances are calculated via the Direct $T_e$ method using emission-line fluxes 
+measured by the MPA-JHU catalog\footnote{Available at 
+\url{http://www.mpa-garching.mpg.de/SDSS/DR7}} and published in Douglass \& 
+Vogeley (2017, in prep).  The large-scale environment of the galaxies is based 
+on the void catalog compiled by \cite{Pan12}.  This void catalog is constructed 
+from SDSS DR7 using the VoidFinder algorithm of \cite{Hoyle02}.  Galaxies which 
+are located within the identified voids are labeled as void galaxies; those 
+which do not reside in a void are designated as wall galaxies.  Because the 
+minimum diameter of a void is defined as 10 \hMpc , the large-scale environment 
+of galaxies within 5 \hMpc of the edge of the SDSS DR7 footprint cannot be 
+described, so their environment is labeled as unknown.
+
+% KIAS-VAGC (morphological classification)
+The Korea Institute for Advanced Study Value-Added Galaxy Catalog 
+\citep[KIAS-VAGC]{Choi10} contains galaxies from the SDSS DR7 main sky survey 
+based on the New York University Value-Added Galaxy Catalog Data Release 7 
+\citep[NYU-VAGC]{Blanton05}.  It provides a morphological class and type 
+following the automated morphology classification scheme of \cite{Park05}, using 
+the color $u-r$, color gradient $\Delta (g-r)$, and inverse concentration index.  
+We use the absolute magnitudes as listed in the KIAS-VAGC.
+
+\subsection{UV data --- GALEX}\label{sec:GALEX}
+The Galaxy Evolution Explorer \citep[GALEX]{Martin05} is an orbiting space 
+telescope conducting an extra-galactic ultraviolet all-sky survey.  The 
+instrument allows imaging and spectroscopic observations in two ultraviolet 
+bands --- Far UV (FUV, 1350--1780\AA) and Near UV (NUV, 1770--2730\AA) 
+\citep{Morrissey07}.  The NUV-$r$ colors used in this study are calculated from 
+the azimuthally-averaged SDSS-style Petrosian fluxes provided in the NASA-Sloan 
+Atlas version 0.1.2 \citep[NSA]{Blanton11}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section[Results]{Classification of galaxies in the color-magnitude diagram}
 
@@
 
-Preliminary analysis of mine reveals a population of galaxies that lie in the 
-Green Valley on the NUV$-r$ color-magnitude diagram, identified independent of 
-their location on the diagram.  I find that, rather than being 
-classified based on arbitrary limits placed on the NUV$-r$ values, the galaxies 
-can be easily separated into three distinct populations based on the galaxies' 
-morphological types as calculated in the KIAS-VAGC; this can be seen in Fig. 
-\ref{fig:NUVr_CMD}.  Defined by the $u-r$ color and the color gradient 
-$\Delta (g-i)$, it is novel that an estimate of the morphological type of the 
-galaxies is an adequate classification for the three populations of the NUV$-r$ 
-CMD.  In addition, Fig. \ref{fig:NUVr_hist} shows a histogram of the galaxies 
-which overlap in both GALEX and SDSS, separated by their morphological 
-classification from the KIAS-VAGC.  It shows that the three populations are well 
-fit by three Gaussians --- the new population in the middle is the transient 
-galaxy population originally ``missing'' from the optical CMD.
+Combining the results of GALEX with the optical photometry of SDSS, we construct 
+a NUV$-r$ CMD.  Probing light from even younger stars in the galaxies, GALEX is 
+able to increase the separation of the blue sequence and red cloud populations 
+of the optical CMD, revealing a third, smaller population of galaxies 
+\citep{Wyder07}.
 
@@
 
-\subsection{Large-scale environmental dependence of dwarf galaxy evolution}
+This analysis reveals a population of galaxies that lie in the Green Valley on 
+the NUV$-r$ color-magnitude diagram, identified independent of their location on 
+the diagram.  Rather than being classified based on arbitrary limits placed on 
+the NUV$-r$ values \citep[as done by][]{Schawinski14,Salim14a}, the galaxies can 
+be easily separated into three distinct populations based on the galaxies' 
+morphological types as calculated in the KIAS-VAGC; this can be seen in Fig. 
+\ref{fig:NUVr_CMD}.  Defined by the $u-r$ color and the color gradient 
+$\Delta (g-i)$, it is novel that an estimate of the morphological type of the 
+galaxies is an adequate classification for the three populations of the NUV$-r$ 
+CMD.  In addition, Fig. \ref{fig:NUVr_hist} shows a histogram of the galaxies 
+which overlap in both GALEX and SDSS, separated by their morphological 
+classification from the KIAS-VAGC.  It shows that the three populations are well 
+fit by three Gaussians --- the new population in the middle is the transient 
+galaxy population originally ``missing'' from the optical CMD.
+
+% classical classification of morphology v. aimc (aimc appaers to be a good indication of the transition in galaxy evolution
+The morphological classification that we use to isolate the green valley 
+population is relatively unique in that it is analytic; morphological 
+classification attempts are often completed in a more subjective manner 
+\citep[such as the GalaxyZoo,][]{Lintott11}.  In particular, the 
+morphological type provided in KIAS-VAGC is a combination of the color $u-r$ and 
+the color gradient $\Delta (g-i)$.  Both these quantities are independent of the 
+NUV$-r$ CMD, which is part of the novelty behind why this measure separates the 
+galaxies into the three evolutionary stages of the CMD so well.
+
+\subsection{Properties of the Green Valley Galaxies}
+
+\subsubsection{Stellar mass}
+
+\begin{figure}
+    \includegraphics[width=0.65\textwidth]{Images/GV/Mstar_hist}
+    \caption[Stellar mass distribution by morphological type]{The distribution 
+    of stellar mass for all galaxies in SDSS DR7, separated by their 
+    morphological type.  The galaxies in the green valley have stellar masses 
+    comparable to those in the red cloud.  The stellar masses of those galaxies 
+    in the blue sequence range from the lowest mass objects up through the 
+    stellar masses of the green valley galaxies.}
+    \label{fig:M_hist}
+\end{figure}
+
+If the green valley galaxies represent those galaxies transitioning between the 
+blue sequence and red cloud, then their stellar masses should overlap the masses 
+in both these populations.  The distribution of the stellar masses for the 
+galaxies in SDSS DR7 is shown in Fig. \ref{fig:M_hist}.  We can see that the 
+galaxies in the green valley have stellar masses comparable to those in the red 
+cloud.  The stellar masses of those galaxies in the blue sequence range from the 
+lowest mass objects up through the stellar masses of the green valley galaxies.  
+The distribution of stellar masses of galaxies in the blue sequence should be 
+much broader than the range of masses seen in the red cloud galaxies, since 
+those in the blue sequence are forming stars and slowly building up their mass.  
+Galaxies in the red cloud are fairly stagnant in their star formation, so the 
+range of stellar masses of these galaxies will be more narrow than that of the 
+blue sequence.  If the green valley galaxies are transitioning between the two 
+populations due to a quenching of star formation or a sudden burst of star 
+formation, then we would expect their mass range to cover the high-mass end of 
+the blue sequence and most of the red cloud.  Indeed, this is what we see in 
+Fig. \ref{fig:M_hist}.
+
+\subsubsection{Star formation rates}
+
+\begin{figure}
+    \includegraphics[width=0.49\textwidth]{Images/GV/SFR_hist}
+    \includegraphics[width=0.49\textwidth]{Images/GV/sSFR_hist}
+    \caption[(s)SFR distribution by morphological type]{The distribution of SFR 
+    (left panel) and sSFR (right panel) for all galaxies in SDSS DR7, separated 
+    by their morphological type.  The green valley galaxies occupy the 
+    intermediate SFRs, while galaxies in the red cloud have low SFRs and 
+    galaxies in the blue sequence have higher SFRs.  The same ranges exist for 
+    the sSFRs, although the green valley galaxies extend well into the range of 
+    sSFRs occupied by the galaxies in the red cloud.}
+    \label{fig:SFR_hist}
+\end{figure}
+
+Again, if green valley galaxies are transitioning between the blue sequence and 
+red cloud, then they should have intermediate (s)SFRs.  The distribution of SFR 
+and sSFR for the galaxies in SDSS DR7 are shown in Fig. \ref{fig:SFR_hist}, with 
+the galaxies separated by their morphological types.  We see that the 
+distribution of SFRs for galaxies in the green valley peaks around 
+$\log(\text{SFR}) \sim -0.5$, in between the ranges occupied by the red cloud 
+and blue sequence galaxies.  A similar distribution is shown for the sSFRs, 
+although the green valley galaxies extend well into the range of sSFRs occupied 
+by the galaxies in the red cloud.  \cite{Salim14a} describes transitional 
+galaxies (those in the green valley) to have lower sSFRs than galaxies in the 
+blue sequence, specifically $-11.8 < \log(\text{sSFR}) < -10.8$.  While our 
+results do indicate that the green valley galaxies have lower sSFRs than those 
+in the blue sequence, we find that their sSFRs extend well into the red cloud 
+range, or to $\log(\text{sSFR}) \sim -12$.
+
+\subsubsection{Gas-phase chemical abundances}
+
+% Histogram of metallicity for red, blue, green galaxies
+\begin{figure}
+    \includegraphics[width=0.49\textwidth]{Images/GV/Z12logOH_I06relations_t3}
+    \includegraphics[width=0.49\textwidth]{Images/GV/N12logNH_I06relations_t3}
+    \includegraphics[width=0.49\textwidth]{Images/GV/logNO_I06relations_t3}
+    \caption[Distribution of gas-phase chemical abundances in cross-matched SDSS 
+    DR7 -- GALEX galaxies]{Histograms of the oxygen abundance (top left), 
+    nitrogen abundance (top right), and N/O ratio (bottom center) of the 
+    cross-matched SDSS DR7 -- GALEX galaxies, separated into their locations on 
+    the NUV$-r$ color-magnitude diagram according to the morphological type 
+    listed in the KIAS-VAGC.  It is readily apparent that the green valley 
+    galaxies have higher nitrogen abundances than those in the blue sequence 
+    (and some of the red cloud).  This, therefore, corresponds to them having 
+    high N/O ratios.}
+    \label{fig:Z_hist}
+\end{figure}
 
@@
 integrated star formation histories, which can provide insight into the 
-enrichment of the ISM and CGM.  Dwarf galaxies ($M_r > -17$) have a 
-slightly different evolutionary history than galaxies of large stellar masses, 
-especially when looking at environmental factors.  The lower stellar masses of 
-these galaxies makes them more susceptible to damage from galactic interactions 
-and supernovae feedback, since they have smaller gravitational potential wells.  
-My current work involves studying the large-scale environmental dependence of 
-the chemical evolution of dwarf galaxies \citep{Douglass17a,Douglass17b}.  I estimate gas-phase 
-metallicities (the oxygen abundance of a galaxy relative to hydrogen) with the 
-Direct $T_e$ method, known for its accuracy and unbiased results.  This method 
-``directly'' estimates the temperature of the electrons in an H{\sc ii} 
-region from a ratio of the [O{\sc iii}] $\lambda$4363 aural line and the 
-[O{\sc iii}] $\lambda \lambda$4959,5007 doublet \citep[as discussed in][this ratio 
-is sensitive to the temperature of the ionized gas in an H{\sc ii} 
-region]{Osterbrock89,Douglass17a}; with the temperature and density, abundance estimates can 
-be made based on emission line ratios from the galaxy.  It can be very difficult 
-to use, however, as it relies on a relatively strong detection of the weak [O 
-{\sc iii}] $\lambda 4363$ auroral line --- the uncertainty in the measured flux 
-of this emission line is the greatest source of error when using this method to 
-estimate the chemical abundances.  Consequently, it is used most often on blue, 
-star-forming galaxies.  A detailed description of the Direct $T_e$ method can be 
-found in \cite{Douglass17a}.  We use a BPT diagram \citep{Baldwin81} to determine if a 
-galaxy is star-forming or has traces of an AGN in its spectrum.  BPT diagrams 
-measure the hardness of a galaxy's spectrum based on the relationship between 
-ratios of some of the galaxy's emission lines.  Our star-forming classification 
-is a result of the work done by \cite{Brinchmann04}.
+enrichment of the ISM and CGM.  A few of the galaxies for which Douglass \& 
+Vogeley (2017, in prep) are able to estimate metallicities reside in the green 
+valley.  When compared with the metallicities of galaxies in the blue sequence 
+and red cloud, Fig. \ref{fig:Z_hist} shows that the green valley galaxies have 
+higher nitrogen abundances than star-forming galaxies in the blue sequence (and 
+some of the red cloud).  With oxygen abundances that fall within the same range 
+as the other two galaxy populations, this shift causes the N/O ratio to be much 
+higher in green valley galaxies than in the blue sequence.
 
-A few of the galaxies for which I am able to estimate metallicities reside in 
-the green valley.  When compared with the metallicities of galaxies in the blue 
-sequence and red cloud, Fig. \ref{fig:Z_hist} shows that the star-forming green 
-valley galaxies have much lower oxygen abundances than star-forming galaxies in 
-the blue sequence and red cloud.  With nitrogen abundances that fall within the 
-same range as the other two galaxy populations, this shift causes the N/O ratio 
-to be much higher in green valley galaxies than in the others.
-
-% Histogram of metallicity for red, blue, green galaxies
-\begin{figure}
-    \includegraphics[width=0.49\textwidth]{Images/GV/Z12logOH_I06relations_SF_t3}
-    \includegraphics[width=0.49\textwidth]{Images/GV/N12logNH_I06relations_SF_t3}
-    \includegraphics[width=0.49\textwidth]{Images/GV/logNO_I06relations_SF_t3}
-    \caption[Distribution of gas-phase chemical abundances in cross-matched SDSS 
-    DR7 -- GALEX galaxies]{Histograms of the oxygen abundance (top left), 
-    nitrogen abundance (top right), and N/O ratio (bottom center) of the 
-    cross-matched SDSS DR7 -- GALEX galaxies (both dwarf galaxies and brighter 
-    systems), separated into their locations on the NUV$-r$ color-magnitude 
-    diagram according to the morphological type listed in the KIAS-VAGC.  It is 
-    readily apparent that the green valley galaxies have much lower oxygen 
-    abundances than those in the blue sequence or red cloud.  This, therefore, 
-    corresponds to them having the highest N/O values of the three categories.}
-    \label{fig:Z_hist}
-\end{figure}
-
-When we separate the galaxies in each of the three populations by their 
-large-scale environment, we discover a variation in these populations as a 
-function of luminosity.  Galaxies are divided into one of two categories for 
-their large-scale environment: voids or walls (more dense regions) based on the 
-void catalog compiled by \cite{Pan12}.  This void catalog is constructed from 
-SDSS DR7 using the VoidFinder algorithm of \cite{Hoyle02}.  As we see in Fig. 
-\ref{fig:Mr_bin}, the fraction of galaxies in the green valley depends on the 
-large-scale environment, even at fixed stellar mass or luminosity.  A larger 
-fraction of wall dwarf galaxies are found in the green valley than for void 
-dwarf galaxies.
+\subsubsection{Large-scale environment}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section[Discussion]{Discussion}
-
-\subsection{Morphological classification and gas content indicators}
-
-% classical classification of morphology v. aimc (aimc appaers to be a good indication of the transition in galaxy evolution
-% Are there other markers in the gas content of these galaxies?
-
-The morphological classification that we use to isolate the green valley 
-population is relatively unique in that it is analytic; morphological 
-classification attempts are often completed in a more subjective manner 
-\citep[such as the GalaxyZoo,][]{Lintott11}.  In particular, the 
-morphological type provided in KIAS-VAGC is a combination of the color $u-r$ and 
-the color gradient $\Delta (g-i)$.  Both these quantities are independent of the 
-NUV$-r$ CMD, which is part of the novelty behind why this measure separates the 
-galaxies into the three evolutionary stages of the CMD so well.
-
-%I also plan to search for other markers in the gas content of the galaxies in 
-%the green valley.  
-If a galaxy's star formation is quenched due to a loss of 
-cold gas, then its H{\sc i} content will be lower than other galaxies of a 
-similar stellar mass and large-scale environment.  If it is quenched due to a 
-high gas temperature (from AGN or supernovae feedback), then the temperature of 
-the gas will be higher than others of a similar size.  These factors will also 
-help to determine when and why a galaxy transitions from star-forming to 
-quiescent (and maybe back to star-forming).
-
-\subsection{Testing for evidence of AGN feedback}
-
-During my estimation of the chemical content of galaxies with $M_r > -20$, I 
-note that the oxygen abundances of galaxies classified as AGN by their 
-emission line ratios in the BPT diagrams exhibit extremely low oxygen abundances 
-(but normal nitrogen abundance values) when compared to star-forming galaxies of 
-a similar stellar mass and large-scale environment.  The same abundance 
-signature is seen in the the oxygen and nitrogen abundance results seen in Fig. 
-\ref{fig:Z_hist} of the green valley galaxies.  This might indicate a 
-link between some dwarf green valley galaxies and a host AGN.  This 
-would support other studies of the transition of galaxies from the blue sequence 
-to the red cloud, which attribute the quenching of star formation to accretion 
-of a central black hole.
-
-I expect to find a large-scale environmental effect on the star formation 
-quenching mechanism in addition to the AGN effects.  Giving us feedback on the 
-role of the environment in a galaxy's evolution, these results will have great 
-impact on the input parameters of large hydrodynamic simulations.  This project 
-will serve as an example of the possible science that will be able to be done 
-with the future James Webb Space Telescope.
+When we separate the galaxies in each of the three populations by their 
+large-scale environment, we discover a variation in these populations as a 
+function of luminosity.  As we see in Fig. \ref{fig:Mr_bin}, the fraction of 
+galaxies in the green valley depends on the large-scale environment, even at 
+fixed stellar mass or luminosity.  A larger fraction of faint wall galaxies are 
+found in the green valley than for faint void galaxies.
 
@@
 
-\section[Conclusion]{Conclusion}
+\section[Discussion]{Understanding green valley galaxies}
+
+Galaxies in the green valley are described to be in a transitional period of the 
+galaxy's life cycle, where they are being quenched in their star formation or 
+are beginning to form stars after being quiescent.  Here, we are able to 
+quantitatively define galaxies in the green valley of the UV-optical CMD.  We 
+find them to be of comparable stellar mass to galaxies in the red cloud, have 
+intermediate SFRs and intermediate-to-low sSFRs, and have higher gas-phase 
+nitrogen abundances and N/O ratios than galaxies in the blue sequence.
+
+The stellar mass range of galaxies in the green valley in Fig. \ref{fig:M_hist} 
+shows us that these galaxies have completed most of their star formation.  They 
+have acquired enough stars to have converted most of their gas into heavier 
+elements.  Combined with the intermediate SFRs and intermediate-to-low sSFRs 
+seen in Fig. \ref{fig:SFR_hist}, this tells us that these galaxies are no longer 
+forming stars at a high rate.  This is most likely due to an extinction of 
+available cool gas from which to form stars.  These galaxies are reaching a 
+natural point in their evolution where they transition from an active star 
+formation period to a quieter, more quiescent lifestyle.
+
+As explained in \cite{Douglass17b}, nitrogen is thought to be produced in both a 
+primary and secondary stage, depending on the presence of other heavy elements.  
+The fact that the galaxies in the green valley have higher nitrogen abundances 
+compared to those in the blue sequence indicate that they are building up a 
+surplus of nitrogen, most likely due to the presence of heavier elements at the 
+later star formation episodes.  The surplus of heavier elements allows the CNO 
+cycle to commence earlier in the stars' lifetimes, producing nitrogen at a 
+higher rate than oxygen.  It is also possible that the higher nitrogen 
+abundances are a sign that the galaxies' intermediate mass stars (those 
+primarily responsible for nitrogen synthesis) have expired.  This surplus of 
+nitrogen results in the high N/O ratios seen for the green valley galaxies in 
+Fig. \ref{fig:Z_hist}.
+
+Fig. \ref{fig:Mr_bin} shows that a higher fraction of faint wall galaxies are in 
+the green valley than faint void galaxies.  This would indicate that void 
+galaxies are slightly behind wall galaxies in their evolution, matching 
+predictions based on the $\Lambda$CDM cosmology.  These results also coincide 
+with the observations of \cite{Douglass17b} and Douglass \& Vogeley (2017, in 
+prep).  They find that, for dwarf galaxies ($M_r > -17$), those which exist in 
+voids may have commenced their star formation at a later time and have not 
+experienced the same cosmic downsizing as dwarf galaxies residing in denser 
+regions.  The higher fraction of wall dwarf galaxies in the green valley might 
+also point to an environmental influence on the reason for transitioning through 
+the green valley, such as ram pressure stripping, which would occur much less 
+frequently in the void environment.  However, the existence of void galaxies in 
+the green valley indicate that galaxy interactions cannot be the only quenching 
+mechanism.
+
+\subsection{Gas content indicators}
+
+% Are there other markers in the gas content of these galaxies? 
+If a galaxy's star formation is quenched due to a loss of cold gas, then its 
+H{\sc i} content will be lower than other galaxies of a similar stellar mass and 
+large-scale environment.  \cite{Schawinski14} finds that 48\% of the late-type 
+galaxies they define to be in the green valley have \ion{H}{1} detections in the 
+ALFALFA survey, consistent with a high probability of gas resevoir retention.  
+Likewise, \cite{Catinella12} shows that the gas fraction ($M_{\ion{H}{1}}/M_*$) 
+correlates with the NUV$-r$ color, suggesting that the transition of galaxies 
+into the green valley is not due to an abrupt change in the galaxy's neutral gas 
+supply.  If it is quenched due to a high gas temperature (from AGN or supernovae 
+feedback), then the temperature of the gas will be higher than others of a 
+similar size.  These factors will also help to determine when and why a galaxy 
+transitions from star-forming to quiescent (and maybe back to star-forming).
+
+\subsection{Evidence of AGN feedback}
+
+During my estimation of the chemical content of galaxies with $M_r > -20$, I 
+note that the oxygen abundances of galaxies classified as AGN by their 
+emission line ratios in the BPT diagrams exhibit higher nitrogen abundances 
+(but normal oxygen abundance values) when compared to star-forming galaxies of 
+a similar stellar mass and large-scale environment.  The same abundance 
+signature is seen in the the oxygen and nitrogen abundance results seen in Fig. 
+\ref{fig:Z_hist} of the green valley galaxies.  This might indicate a 
+link between green valley galaxies and a host AGN.  This would support other 
+studies of the transition of galaxies from the blue sequence to the red cloud, 
+which attribute the quenching of star formation to accretion of a central black 
+hole \citep[e.g.,][]{Croton06,Stasinska08}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section[Conclusions]{Conclusions}
+
+We can define galaxies which are transitioning through the green valley of the 
+color-magnitude diagram by combining the galaxy's color, color gradient, and 
+inverse concentration index.  Galaxies with a magnitude less than 25 for the 
+morphological type as calculated in the KIAS-VAGC exist in the green valley 
+portion of the UV-optical color magnitude diagram.  Galaxies defined as early 
+types (morphological type values equal to 1 or 2) are in the red cloud, while 
+those with morphological type values greater than 25 are in the blue sequence.  
+With this quantitative definition for galaxies transitioning through the green 
+valley, we can begin to understand the properties of green valley galaxies and 
+the evolution of galaxies.
+
+Based on our analysis, green valley galaxies have stellar masses comparable to 
+those in the red cloud.  They have intermediate SFRs, and low-to-intermediate 
+sSFRs.  Green valley galaxies also have high gas-phase nitrogen abundances (N/H), 
+resulting in high N/O ratios.  While their SFRs show that something has quenched 
+their star formation, their stellar masses inform us that this is not due to any 
+premature quenching mechanism.  The high nitrogen abundances in the green valley 
+galaxies indicates that the galaxies are either no longer forming stars (since 
+nitrogen is produced in lower mass stars than oxygen), or that the galaxies were 
+able to produce both primary and secondary nitrogen (heavy elements were present 
+during the last few star formation episodes to permit the CNO cycle to commence 
+earlier).  This chemical abundance pattern (normal oxygen, high nitrogen, and 
+high N/O ratio) is also seen in galaxies classified as AGN, indicating that the 
+galaxies in the green valley have an AGN.
+
+There is a higher fraction of faint wall galaxies in the green valley than in 
+the void regions.  In conjunction with the conclusions of \cite{Douglass17b} and 
+Douglass \& Vogeley (2017, in prep), this indicates that void dwarf galaxies are 
+less evolved than dwarf galaxies in denser environments.  It would be beneficial 
+to investigate the small-scale ($\sim 1$ \hMpc) environment of galaxies in the 
+green valley, to determine if any interactions are responsible for the 
+transitional state.

### 2017-06-05 KellyDouglass/Thesis/Thesis_sections/Conclusion.tex
Small-scale theory, data

\chapter{Conclusions}

\section{Suggestions for future work}

### 2017-06-05 KellyDouglass/Thesis/Thesis_sections/smallScaleEnvironment.tex
GV chapter
Small-scale theory, data

@@
 
+Morphology-density relation \cite{Dressler80}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+We employ two different spatial metrics to determine the best way to locate a 
+galaxy's nearest neighbor.  Within a relative velocity 
+$v_{rel} < 300\text{ km/s}$, we use the physically closest (in units of \hMpc) 
+and the neighbor with the smallest fraction of its virial radius; both these 
+methods are described below in further detail.  The two methods result in 
+different neighboring galaxies for 40\% of our dwarf galaxy sample.
+
 \subsection{Peculiar velocity}
@@
 
+A galaxy's redshift is composed of both the expansion of the universe and the 
+galaxy's peculiar velocity (its motion relative to its surrounding galaxies and 
+environment).  Known as the ``Finger of God'' effect, the peculiar velocity 
+causes galaxy groups and clusters to appear extended along the line of sight 
+when using redshift as a distance measurement.  When we calculate distances on 
+large scales, the peculiar velocity is negligible.  However, when we study the 
+distance between two objects in the universe on a small scale (within a few 
+\hMpc), the peculiar velocity dominates.  The relative velocity $v_{rel}$ 
+between galaxies $a$ and $b$ is defined as
+\begin{equation}
+    v_{rel} = |z_a - z_b|c
+\end{equation}
+where $z$ is the redshift.  We require all 
+neighbors to have a maximum relative velocity $v_{rel} < 300\text{ km/s}$.  We 
+show in Sec. \ref{sec:selection_effects} that our results are insensitive to 
+this value.
+
 \subsection{Sky separation in \hMpc}
+
+The projected distance between two galaxies is found by projecting the two 
+galaxies onto a sphere of radius $\bar{r}$, where $\bar{r}$ is the average 
+distance from Earth of the two galaxies.  This assumes that two galaxies which 
+are gravitationally bound are in a system where the relative velocity between us 
+and it is 0 and that $\bar{r}$ is the distance to the center of the system.  The 
+distance to the system is calculated as
+\begin{equation}
+    \bar{r} = \frac{\bar{z}c}{H_0}
+\end{equation}
+where $\bar{z}$ is the average redshift of the two galaxies, $c$ is the speed of 
+light, and $H_0$ is the Hubble constant.  Each galaxy's right ascension (RA) and 
+declination (dec.) are converted to Cartesian coordinates to find their sky 
+separation.
 
@@
 
+From \cite{Hwang10}, we calculate the virial radius of a galaxy to be
+\begin{equation}\label{eqn:r_vir}
+    r_{vir} = (3L\gamma/4\pi/200\rho_c)^{1/3}
+\end{equation}
+where $L$ is the galaxy's luminosity, $\gamma$ is the mass-to-light ratio, and 
+$\rho_c$ is the critical density of the universe.  The critical density is the 
+density at which evenly distributed gas would collapse to form a galaxy.  The 
+mass-to-light ratio depends on the galaxy's morphology type, where 
+$\gamma_{early} = 2\gamma_{late}$.  \cite{Hwang10} defines 
+$200\rho_c = 740\bar{\rho}$, where 
+$\bar{\rho} = (0.0223\pm 0.0005)(\gamma_{late}L_{-20})(\text{\hMpc})^3$.  We can 
+then rewrite Eqn. \ref{eqn:r_vir} as
+\begin{equation}
+    r_{vir} = \left( \frac{3}{4\times 740\times 0.0223\pi} \frac{\gamma}{\gamma_{late}} \frac{L}{L_{-20}} \right)^{1/3}
+\end{equation}
+where $L_{-20}$ is the luminosity of a galaxy with $M_r = -20$.  We can then use 
+the virial radius to scale the distance between two galaxies as a fraction of 
+the neighbor's virial radius.
+
+Rather than using a measure of the virial radius for the group analysis, we 
+scale the distance as a fraction of the group's rms radius.
+
 \subsection{Absolute distance to nearest neighbor}
+% Including redshift
+
+We can also calculate the distance between two galaxies by ignoring the effects 
+of their relative velocities.
 
@@
 % SDSS
+The Sloan Digital Sky Survey Data Release 7 \citep[SDSS DR7;][]{Abazajian09} is 
+a wide-field multiband imaging and spectroscopic survey which maps approximately 
+one-quarter of the northern sky using a drift scanning technique.  Photometric 
+data in the five-band SDSS system --- $u$, $g$, $r$, $i$, and $z$ --- is taken 
+on a dedicated 2.5m telescope at the Apache Point Observatory in New Mexico 
+\citep{Fukugita96,Gunn98}.  Galaxies with Petrosian $r$-band magnitudes 
+$m_r < 17.77$ are selected for follow-up spectroscopic analysis \citep{Lupton01,
+Strauss02}.  The galaxy colors are taken from the Korean Institute for Advanced 
+Study Value-Added Galaxy Catalog \citep[KIAS-VAGC;][]{Choi10}, which contains 
+galaxies from the SDSS DR7 main sky survey based on the New York University 
+Value-Added Galaxy Catalog Data Release 7 \citep[NYU-VAGC;][]{Blanton05}.  Total 
+star formation rates (SFR) and total specific star formation rates (sSFR) are 
+from the MPA-JHU value-added catalog\footnote{Available at 
+\url{http://www.mpa-garching.mpg.de/SDSS/DR7/}}, calculated using the technique 
+described in \cite{Brinchmann04}.  The gas-phase chemical abundances used are 
+from Douglass \& Vogeley (2017, in prep.), which are calculated using the Direct 
+$T_e$ method.  The galaxies' large-scale environments are based on the void 
+catalog compiled by \cite{Pan12}, which is constructed from SDSS DR7 using the 
+VoidFinder algorithm of \cite{Hoyle02}.  Galaxies which are located within 
+identified voids are labeled as void galaxies, and those which do not fall 
+within a void are designated as a wall galaxy.  The large-scale environment 
+within 5 \hMpc of the edge of the main SDSS DR7 footprint cannot be described 
+using the VoidFinder algorithm because the minimum diameter of a void is 10 
+\hMpc.  Therefore, the large-scale environment for galaxies within 5 \hMpc of 
+the edge of the main footprint in SDSS DR7 is designated as unknown.
 
@@
 
+Two galaxy samples are used in this analysis.  The largest one contains the 
+11,845 dwarf galaxies spectroscopically observed in SDSS DR7.  The second sample 
+contains those star-forming dwarf galaxies from the first set which have 
+gas-phase chemical abundances in Douglass \& Vogeley (2017, in prep.), totaling 
+2506 dwarf galaxies.  While this subset of galaxies contains only star-forming 
+galaxies and is not representative of all dwarf galaxies, we show in Section 
+\ref{sec:selection_effects} that this does not affect our results.
+
 \subsection{Group catalog}
 
-\cite{Berlind06}
-
-\subsection{Finding the nearest neighbor}
-% Absolute magnitude distribution of neighbors
+In addition to comparing the target galaxies to their nearest neighbor, we also 
+look at the relationship between the dwarf galaxies' properties and their 
+proximity to the nearest galaxy group.  We use the Mr18 Berlind group catalog 
+\cite{Berlind06} as our source of groups, which is built on the galaxies in the 
+NYU-VAGC. The catalog identifies groups using a friends-of-friends algorithm 
+\citep{Huchra82} to connect galaxies with $M_r < -18$.
 
@@
 
-\subsection{Selection effects}
+\subsection{Selection effects}\label{sec:selection_effects}
 
@@
 galaxies does not influence any trends we observe in our analysis.
+
+% Absolute magnitude distribution of nearest neighbors
+\begin{figure}
+    \includegraphics[width=\textwidth]{Images/smallScaleEnvironment/Mr_distribution}
+    \caption[Distribution of absolute magnitudes of nearest neighbors]{The 
+    distributions in absolute magnitude (left panel) and absolute magnitude 
+    relative to the target galaxy (right panel) of the nearest neighbor 
+    galaxies.  The top row includes those nearest neighbors in units of \hMpc, 
+    and the bottom row consists of the nearest neighbors in units of the 
+    neighbor's virial radius.  Comparing the two plots in the right panel, we 
+    see that the closest galaxy to the target dwarf galaxies is often of equal 
+    or fainter magnitude than the target galaxy.  Alternatively, using the 
+    virial radius of the neighbor galaxy as a measure of distance often finds a 
+    brighter galaxy than the target galaxy, as the bottom right plot shows.}
+    \label{fig:Mr_dist}
+\end{figure}
+
+For about 41\% of our dwarf galaxy sample, the two different metrics by which to 
+define the nearest neighbor (minimum in units of \hMpc or virial radius of the 
+nearest neighbor) return different neighboring galaxies.  Fig. \ref{fig:Mr_dist} 
+compares the absolute magnitude distributions of these two nearest neighbor 
+populations.  The left panel shows the distribution of the absolute magnitudes 
+of the nearest neighbor galaxies, while the right panel shows the distribution 
+in absolute magnitude of the nearest neighbor galaxy relative to its target 
+galaxy.  The top row includes those nearest neighbors in units of \hMpc, and the 
+bottom row consists of the nearest neighbors in units of the neighbor's virial 
+radius.  Comparing the two plots in the right panel, we see that the closest 
+galaxy to the target dwarf galaxy is often of equal or fainter magnitude than 
+the target galaxy.  Alternatively, using the virial radius of the neighbor 
+galaxy as a measure of the distance often finds a brighter galaxy than the 
+target galaxy, as the bottom right plot in Fig. \ref{fig:Mr_dist} shows.  By 
+using these two different distance metrics, we are able to probe the 
+relationship between a dwarf galaxy and its nearest neighbor and nearest dark 
+matter halo.
 
@@
 
-\section[Conclusion]{Conclusion}
+\section[Conclusions]{Conclusions}
 
@@
 influential on a galaxy's evolution than its distance to the nearest neighbor.
+
+Further analysis of this study should include comparing the properties of the 
+target galaxies with the nearest neighbors' properties as a function of 
+distance (``galactic conformity'').  The gas-phase chemical abundances between a 
+galaxy and its nearest neighbor could be strongly correlated.

### 2017-06-06 KellyDouglass/Thesis/Thesis_sections/GV.tex
Small-scale intro, GV edits

@@
-\chapter[Green valley galaxies]{Green valley galaxies}
+\chapter[Green valley galaxies]{Identifying green valley galaxies}
 
@@
 cooling, thereby quenching star formation.  In addition to internal mechanisms, 
-galaxies will often experience interactions in more dense regions.  Depending on 
-the properties of the galaxies involved (mass, speed, etc.), these interactions 
-can either strip gas from the galaxy (removing a primary source of fuel for 
-future star formation), or they can trigger a burst of star formation.
+galaxies will often experience interactions in denser environmental regions.  
+Depending on the properties of the galaxies involved (mass, speed, etc.), these 
+interactions can either strip gas from the galaxy (removing a primary source of 
+fuel for future star formation), or they can trigger a burst of star formation.
 
@@
 The SDSS Data Release 7 \citep[DR7]{Abazajian09} is a wide-field multi-band 
-imaging and spectroscopic survey.  It uses drift scanning to map approximately 
+imaging and spectroscopic survey that uses drift scanning to map approximately 
 one-quarter of the northern sky.  A dedicated 2.5-meter telescope at the Apache 
@@
 lowest mass objects up through the stellar masses of the green valley galaxies.  
-The distribution of stellar masses of galaxies in the blue sequence should be 
-much broader than the range of masses seen in the red cloud galaxies, since 
-those in the blue sequence are forming stars and slowly building up their mass.  
-Galaxies in the red cloud are fairly stagnant in their star formation, so the 
-range of stellar masses of these galaxies will be more narrow than that of the 
-blue sequence.  If the green valley galaxies are transitioning between the two 
+The distribution of stellar masses of blue sequence galaxies should be much 
+broader than the range of masses seen in the red cloud galaxies, since those in 
+the blue sequence are slowly building up their stellar mass by forming stars 
+from both their gas reservoirs and cool gas falling onto the galaxy.  Galaxies 
+in the red cloud are fairly stagnant in their star formation, so the range of 
+stellar masses of these galaxies will be more narrow than that of the blue 
+sequence.  If the green valley galaxies are transitioning between the two 
 populations due to a quenching of star formation or a sudden burst of star 
 formation, then we would expect their mass range to cover the high-mass end of 
-the blue sequence and most of the red cloud.  Indeed, this is what we see in 
-Fig. \ref{fig:M_hist}.
+the blue sequence and most of the red cloud.  These expectations are met in Fig. 
+\ref{fig:M_hist}.
 
@@
 
-Again, if green valley galaxies are transitioning between the blue sequence and 
-red cloud, then they should have intermediate (s)SFRs.  The distribution of SFR 
-and sSFR for the galaxies in SDSS DR7 are shown in Fig. \ref{fig:SFR_hist}, with 
-the galaxies separated by their morphological types.  We see that the 
-distribution of SFRs for galaxies in the green valley peaks around 
+If green valley galaxies are transitioning between the blue sequence and red 
+cloud, then they should have intermediate (s)SFRs.  The distribution of SFR and 
+sSFR for the galaxies in SDSS DR7 are shown in Fig. \ref{fig:SFR_hist}, with the 
+galaxies separated by their morphological types.  We see that the distribution 
+of SFRs for galaxies in the green valley peaks around 
 $\log(\text{SFR}) \sim -0.5$, in between the ranges occupied by the red cloud 
@@
 blue sequence, specifically $-11.8 < \log(\text{sSFR}) < -10.8$.  While our 
-results do indicate that the green valley galaxies have lower sSFRs than those 
-in the blue sequence, we find that their sSFRs extend well into the red cloud 
-range, or to $\log(\text{sSFR}) \sim -12$.
+results do indicate that green valley galaxies have lower sSFRs than those in 
+the blue sequence, we find that their range of sSFR is almost double the width 
+of that described in \cite{Salim14a}.  The green valley galaxies have a sSFR 
+within the range $-12 \lesssim \log(\text{sSFR}) \lesssim -10$.
 
@@
 
-The stellar mass range of galaxies in the green valley in Fig. \ref{fig:M_hist} 
-shows us that these galaxies have completed most of their star formation.  They 
-have acquired enough stars to have converted most of their gas into heavier 
-elements.  Combined with the intermediate SFRs and intermediate-to-low sSFRs 
-seen in Fig. \ref{fig:SFR_hist}, this tells us that these galaxies are no longer 
-forming stars at a high rate.  This is most likely due to an extinction of 
-available cool gas from which to form stars.  These galaxies are reaching a 
-natural point in their evolution where they transition from an active star 
-formation period to a quieter, more quiescent lifestyle.
+The range of stellar masses in galaxies from the green valley in Fig. 
+\ref{fig:M_hist} shows us that these galaxies have completed most of their star 
+formation.  They have acquired enough stars to have converted much of their gas 
+into heavier elements.  Combined with the intermediate SFRs and 
+intermediate-to-low sSFRs seen in Fig. \ref{fig:SFR_hist}, this tells us that 
+these galaxies are no longer forming stars at a high rate.  This is most likely 
+due to an extinction of available cool gas from which to form stars.  These 
+galaxies are reaching a natural point in their evolution where they transition 
+from an active star formation period to a quieter, more quiescent lifestyle.
 
@@
 
-Fig. \ref{fig:Mr_bin} shows that a higher fraction of faint wall galaxies are in 
-the green valley than faint void galaxies.  This would indicate that void 
-galaxies are slightly behind wall galaxies in their evolution, matching 
-predictions based on the $\Lambda$CDM cosmology.  These results also coincide 
-with the observations of \cite{Douglass17b} and Douglass \& Vogeley (2017, in 
-prep).  They find that, for dwarf galaxies ($M_r > -17$), those which exist in 
-voids may have commenced their star formation at a later time and have not 
-experienced the same cosmic downsizing as dwarf galaxies residing in denser 
-regions.  The higher fraction of wall dwarf galaxies in the green valley might 
-also point to an environmental influence on the reason for transitioning through 
-the green valley, such as ram pressure stripping, which would occur much less 
-frequently in the void environment.  However, the existence of void galaxies in 
-the green valley indicate that galaxy interactions cannot be the only quenching 
-mechanism.
+Fig. \ref{fig:Mr_bin} shows a higher fraction of faint wall galaxies than faint 
+void galaxies are in the green valley.  This would indicate that void galaxies 
+are slightly behind wall galaxies in their evolution, matching predictions based 
+on the $\Lambda$CDM cosmology.  These results also coincide with the 
+observations of \cite{Douglass17b} and Douglass \& Vogeley (2017, in prep).  
+They find that, for dwarf galaxies ($M_r > -17$), those which exist in voids may 
+have commenced their star formation at a later time and have not experienced the 
+same cosmic downsizing as dwarf galaxies residing in denser regions.  The higher 
+fraction of wall dwarf galaxies in the green valley might also point to an 
+environmental influence on the reason for transitioning through the green 
+valley, such as ram pressure stripping, which would occur much less frequently 
+in the void environment.  However, the existence of void galaxies in the green 
+valley indicate that galaxy interactions cannot be the only star formation 
+quenching mechanism.
 
@@
 During my estimation of the chemical content of galaxies with $M_r > -20$, I 
-note that the oxygen abundances of galaxies classified as AGN by their 
-emission line ratios in the BPT diagrams exhibit higher nitrogen abundances 
-(but normal oxygen abundance values) when compared to star-forming galaxies of 
-a similar stellar mass and large-scale environment.  The same abundance 
-signature is seen in the the oxygen and nitrogen abundance results seen in Fig. 
+note that the oxygen abundances of galaxies classified as having an AGN by their 
+emission line ratios in the BPT diagrams exhibit higher nitrogen abundances and 
+normal oxygen abundance values when compared to star-forming galaxies of a 
+similar stellar mass and large-scale environment.  The same abundance signature 
+is seen in the the oxygen and nitrogen abundance results seen in Fig. 
 \ref{fig:Z_hist} of the green valley galaxies.  This might indicate a 
@@
 premature quenching mechanism.  The high nitrogen abundances in the green valley 
-galaxies indicates that the galaxies are either no longer forming stars (since 
+galaxies indicate that the galaxies are either no longer forming stars (since 
 nitrogen is produced in lower mass stars than oxygen), or that the galaxies were 
@@
 
-There is a higher fraction of faint wall galaxies in the green valley than in 
-the void regions.  In conjunction with the conclusions of \cite{Douglass17b} and 
+There is a higher fraction of faint wall galaxies than faint void galaxies in 
+the green valley.  In conjunction with the conclusions of \cite{Douglass17b} and 
 Douglass \& Vogeley (2017, in prep), this indicates that void dwarf galaxies are 

### 2017-06-06 KellyDouglass/Thesis/Thesis_sections/smallScaleEnvironment.tex
Small scale theory update
Small-scale intro, GV edits

@@
 
-Morphology-density relation \cite{Dressler80}
+% Large-scale environment influence
+Large galaxy redshift surveys have shown that the large-scale structure of the 
+distribution of galaxies in the universe is similar to that of a 
+three-dimensional cosmic web \citep{Bond96}, where galaxy clusters are connected 
+by thin filaments of galaxies and are separated by voids (large, underdense 
+regions that occupy close to 60\% of space).  Over the last few decades, the 
+Sloan Digital Sky Survey \citep{Abazajian09,Ahn12} have propelled the research 
+into the influence of the large-scale environment on the formation and evolution 
+of galaxies.
+
+Because gravitational clustering within a void proceeds as if in a very 
+low-density universe, cosmic voids are an important environment for studying 
+galaxy formation \citep[see][for a review]{vandeWeygaert11}.  The $\Lambda$CDM 
+cosmology predicts that galaxies which formed in voids to have lower masses and 
+be retarded in their star formation when compared to those in more dense 
+environments \citep{Gottlober03,Goldberg05,Cen11}.  The effects of the void 
+environment should be most obvious in dwarf galaxies due to their minimal 
+gravitational potential.  As a result, they are more sensitive to astrophysical 
+effects such as cosmological reionization, internal feedback from supernova and 
+photoheating from star formation, small-scale details of dark matter halo 
+assembly, and the properties of dark matter.
+
+Observations have shown that the properties of dwarf galaxies vary dramatically 
+with the environment \citep[e.g.,][]{Ann08,Geha12}.  Void galaxies have been 
+found to have lower stellar mass \citep{Hoyle05,Croton05,Moorman15}, be bluer 
+and of a later type \citep{Grogin00,Rojas04,Patiri06,Park07,vonBendaBeckmann08,
+Hoyle12}, have higher star formation rates \citep{Rojas05,Moorman15,Beygu16}, 
+and be more gas rich \citep{Kreckel12,Moorman16,Jones16} than galaxies in denser 
+regions.
+
+% Small-scale environment - what has been done so far?
+In conjunction with the large-scale environment, the small-scale environment 
+($\sim 1$ \hMpc) has also been found to influence a galaxy's evolution.  There 
+exits a well-established morphology-density relation \cite{Dressler80}, where 
+the fraction of late-type galaxies is inversely proportional to the local 
+density.  \cite{Ellison09} determined that a galaxy's local environment 
+influences a galaxy's evolution more than its large-scale environment.  
+Likewise, \cite{Rupke08} concluded that interacting galaxies have suppressed 
+metallicities, because interactions induce flows of hydrogen.  \cite{Park09} 
+found that, for galaxies with $M_r < -19$, galaxy interactions out to the virial 
+radius of the nearest neighbor influence the evolution of the target galaxy.  
+They determine that the large-scale environment has a minimal effect on the 
+evolution of a galaxy once the luminosity and morphology are taken into account.
+
+We want to understand if the small-scale environment is more influential in a 
+galaxy's evolution than its large-scale environment.  Additionally, within the 
+small-scale environment, are tidal influences (due to the nearest neighbor 
+galaxy) or gravitational potentials (from the nearest galaxy group) more 
+influential in a galaxy's evolution?  A group consists of multiple galaxies that 
+share the same dark matter halo.  A group member will gravitationally interact 
+with all other group members, not just its nearest neighbor.  And a galaxy near 
+a group, but not within it, may also experience strong tidal effects from the 
+group similar to (but stronger than) those from a neighboring galaxy.
 
@@
 We can also calculate the distance between two galaxies by ignoring the effects 
-of their relative velocities.
+of their relative velocities.  Instead of projecting both galaxies onto a sphere 
+with radius $\bar{r}$, we instead project each onto its own sphere of radius 
+\begin{equation}
+    r = \frac{cz}{H_0}
+\end{equation}
+We then convert to Cartesian coordinates and use the three-dimensional 
+Pythagorean theorem to calculate the distance between the two galaxies.
 

### 2017-06-06 KellyDouglass/Thesis/DirectMethodPhysics.tex
BPT distribution of abundances, Appendix section on physics of transitions added

\chapter{The physics of the Direct $T_e$ method}

UV photons from young stars in an \ion{H}{2} region keep the interstellar gas 
partially ionized.  In an \ion{H}{2} region, a photon with an energy 
$E_\gamma \gtrsim 13.6\text{ eV}$ ionizes a hydrogen atom, producing an H$^+$ 
ion and an electron with some kinetic energy 
$K_{e^-} = E_\gamma - 13.6\text{ eV}$.  As the free electron moves around in the 
gas, it loses some of its kinetic energy as it collisionally excites other ions 
in the gas.  Because we are in a Str\"{o}mgren sphere (an ionized region or an 
\ion{H}{2} region), the cross-section for this electron scattering is much 
larger than the photoionization cross section, so the free electrons will 
thermalize quickly \citep{DeRobertis87}.  Eventually, the free electron 
recombines with an H$^+$ ion, forming atomic hydrogen again.  The ions that were 
collisionally excited by the electron before its recombination eventually 
de-excite via forbidden transitions, emitting radiation that escapes the 
\ion{H}{2} region.

In equilibrium, the total energy input into the gas via radiation from the star 
(that ionizes the hydrogen), $E_{photoionization}$, must be equal to the energy 
required to recombine the electron and the H$^+$ ion, $E_{recombination}$, and 
the energy radiated away from the \ion{H}{2} region by the forbidden 
transitions, $E_{radiation}$.  So
\begin{equation}
    E_{photoionization} = E_{recombination} + E_{radiation}
\end{equation}
For radiative de-excitation to dominate over collisional de-excitation, the 
electron density $n_e \ll 10^{8-10}\text{ cm}^{-3}$ \citep{DeRobertis87}.  
Typical \ion{H}{2} regions have an electron density 
$n_e \approx 100\text{ cm}^{-3}$, so radiative de-excitation dominates; this is 
why we observe forbidden transitions in outer space but not here on Earth.

\section{Temperatures from the forbidden emission lines}

%%%%%%%% All from DeRobertis87
%Of the ions that dominate radiative cooling (O$^+$, N$^+$, etc.), most have 
%either p$^2$, p$^3$, or p$^4$ ground-state electron configurations with five 
%energy levels $\leq 5\text{ eV}$ above the ground state.  For each excitation 
%level $i$, \cite{DeRobertis87} shows that the equations of statistical 
%equilibrium are
%\begin{equation}
%    \sum_{j \neq i} n_j n_e q_{ij} + \sum_{j > i} n_j A_{ji} = \sum_{j \neq i} n_i n_e q_{ij} + \sum_{j < i} n_i A_{ij}
%\end{equation}
%where $n_j$ is the fraction of the ion in level $j$, $q_{ij}$ is the electron 
%(de)excitation rate coefficient (in units of cm$^{-3}$s$^{-1}$), and $A_{ij}$ is 
%the radiate transition probability with units of s$^{-1}$.  From left to right, 
%these terms describe the collisional transitions to $i$, the radiative 
%transitions down to $i$, the collisional transitions from $i$, and the radiative 
%transitions down from $i$.  For a given ion X$^i$ with a number density 
%$N(\text{X}^i)$, the relative populations must must sum to unity:
%\begin{equation}
%    \sum_j \frac{n_j}{N(\text{X}^i} = 1
%\end{equation}
%
%$A_{ij}$ are independent of temperature and inversely proportional to the 
%lifetime of the upper level.  Conversely, the coefficients $q_{ij}$ depend on 
%temperature since they are a measure of how likely collisions will occur.  These 
%can be calculated as
%\begin{equation}
%    q_{ij} = \frac{8.629\times 10^{-6}}{T_e^{1/2}} \frac{\Omega (i,j)}{\omega_i}
%\end{equation}
%where $T_e$ is the electron temperature, $\omega_i$ is the statistical weight of 
%level $i$, and $\Omega (i,j)$ is the average collisional strength.  While 
%$\Omega$ is dimensionless, it does depend on the temperature 
%\cite{DeRobertis87}.  The excitation rate $q_{ij}$ is related to the 
%de-excitation rate $q_{ji$ by
%\begin{equation}
%    q_{ji} = \frac{\omega_i}{\omega_j} q_{ij} \exp{-\Chi_{ij}/kT}
%\end{equation}
%where $\Chi_{ij}$ is the excitation energy difference between levels $i$ and 
%$j$.

%%%%%%% From Osterbrock89

%In a pure hydrogen nebula, \cite{Osterbrock89} shows us that the photoionization 
%energy input (per unit volume per unit time) is equal to 
%\begin{equation}
%    G(H) = n_e n_p \alpha_A (H^0, T) \frac{3}{2} kT_i
%\end{equation}
%where $n_e$ is the number density of electrons, $n_p$ is the number density of 
%protons, $\alpha_A$ is the recombination coefficient summed over all energy 
%levels, and $T_i$ is the photoelectron's initial temperature.  Assuming a 
%blackbody spectrum, $T_i \approx T_*$ for $kT_* < h\nu_0$.  The gain $G(H)$ 
%depends on the form of the ionizing radiation field, not its strength.  The rate 
%of creation of the photoelectrons depends on the strength of the radiation 
%field, or the recombination rate.
%
%Likewise, \cite{Osterbrock89} shows that the rate of energy lost through 
%recombination per unit volume is equal to
%\begin{equation}
%    L_R (H) = n_e n_p kT \beta_A (H^0, T)
%\end{equation}
%where $\beta_A$ is the effective recombination coefficient for recombination 
%energy loss.

Expanding the description in Sec. \ref{sec:O3}, we can define the ratio of the 
emission line strengths for [\ion{O}{3}] $\lambda$4363 and [\ion{O}{3}] 
$\lambda \lambda$4959,5007 as
\begin{equation}
    \frac{j_{4959} + j_{5007}}{j_{4363}} = \frac{\Omega(^3\text{P}, ^1\text{D})}{\Omega(^3\text{P}, ^1\text{S})} \left[ \frac{A_{^1\text{S}, ^1\text{D}} + A_{^1\text{S}, ^3\text{P}}}{A_{^1\text{S}, ^1\text{D}}} \right] \frac{\bar{\nu}(^3\text{P}, ^1\text{D})}{\nu(^1\text{D}, ^1\text{S})} e^{\Delta E/kT}
\end{equation}
where $j_\lambda$ is the emissivity of the emission line, $\Omega (i,j)$ is the 
collision strength between levels $i$ and $j$, $A_{i,j}$ is the radiative 
transition probability between an upper level $i$ and a lower level $j$, $\nu$ 
is the frequency of the transition, $\Delta E$ is the energy difference between 
the $^1$D$_2$ and $^1$S$_0$ levels, and $T$ is the electron temperature 
\cite{Osterbrock89}.  The transition probabilities $A_{i,j}$ do not depend on 
the temperature, but the collision strength $\Omega (i,j)$ is 
temperature-dependent.  We can define
\begin{equation}
    \bar{\nu}(^3\text{P}, ^1\text{D}) = \frac{A_{^1\text{D}_2, ^3\text{P}_2} \nu (5007) + A_{^1\text{D}_2, ^3\text{P}_1} \nu (4959)}{A_{^1\text{D}_2, ^3\text{P}_2} + A_{^1\text{D}_2, ^3\text{P}_1}}
\end{equation}
Inserting numerical values for the collision strengths and transition 
probabilities from \cite{Osterbrock89}, the ratio becomes
\begin{equation}
    \frac{j_{4959} + j_{5007}}{j_{4363}} = \frac{7.73 \exp[(3.29\times 10^4)/T]}{1 + 4.5\times 10^{-4} (N_e/T^{1/2})}
\end{equation}
By measuring the flux of these emission lines, we can then solve for the 
temperature of the gas.

%\section{[\ion{O}{3}]}
%
%There are three significant emission lines for doubly-ionized oxygen.  The 
%relative excitation rates to the $^1$S and $^1$D energy levels depend very 
%strongly on the electron temperature, $T_e$; therefore, the relative strengths 
%of these emitted lines can be used to measure the electron temperature 
%\citep{Osterbrock89}.  In the low-density limit $(n_e < 10^5 \text{ cm}^{-3})$, 
%most excitations to the $^1$D level result in an emission of a photon with a 
%wavelength of either $5007\text{\AA}$ or $4959\text{\AA}$, as shown in Fig. 
%\ref{fig:transitions_P1}.  Most excitations up to $^1$S produce a photon of 
%wavelength $4363\text{\AA}$, followed by a photon of either of the two previous 
%wavelengths (since the electron is now in the $^1$D level).
%
%At higher densities, collisional de-excitation begins to influence these 
%emission rates \citep{Osterbrock89}.  Because the $^1$D level has a longer 
%lifetime than the $^1$S state, it is collisionally de-excited at lower electron 
%densities.  This weakens the $\lambda 4959$ and $\lambda 5007$ emission lines.  
%At the same time, the additional collisional excitations of the $^1$D state 
%permitted by the higher electron densities strengthen the $\lambda 4363$ 
%emission line.
%
%[\ion{O}{3}] $\lambda 4363$ is a temperature-sensitive forbidden transition line 
%of doubly-ionized oxygen that is the preferred line to use when measuring the 
%metallicity of galaxies.  Since the most effective cooling channel in \ion{H}{2} 
%regions is oxygen line emission, lower metallicity regions have higher 
%temperatures \citep{Saintonge07}.  Collisional excitations up to this energy 
%level are more common at higher temperatures, since there are more electrons 
%with the kinetic energy required to excite the O$^{++}$ ion to this energy 
%level.  As a result, the line strength of [\ion{O}{3}] $\lambda 4363$ correlates 
%with the region's temperature and is therefore anticorrelated with the 
%metallicity of the galaxy.

%\section{[\ion{N}{2}]}
%
%The energy-level diagram for the various transitions of [\ion{N}{2}] is very 
%similar to that of [\ion{O}{3}], since they have the same electron ground-state 
%configuration ((1s)$^2$(2s)$^2$(2p)$^2$).  The similarities can be seen in Fig. 
%\ref{fig:transitions_P2}.  Therefore, an estimate of the electron temperature can 
%be made from the [\ion{N}{2}] $\lambda 5755$ emission line.  However, this line 
%is weaker than the [\ion{O}{3}] $\lambda 4363$ auroral line (since there is less 
%N than O in galaxies), so we use the [\ion{O}{3}] auroral line for our 
%temperature estimates, as in Paper I.  After obtaining a temperature and density 
%estimate, we use the [\ion{N}{2}] $\lambda \lambda 6548, 6584$ doublet to 
%estimate the abundance of singly ionized nitrogen in a galaxy.

\section{[\ion{S}{2}]}

Similar to the sensitivity of the doubly-ionized oxygen ion transitions to the 
electron temperature of the surrounding gas, the transitions for singly-ionized 
sulfur are sensitive to electron number density.  The relative excitation rates 
depend only on the ratio of the collision strengths when two emission lines 
(from the same ion) with nearly identical excitation energies are compared 
\citep{Osterbrock89}.  If the two levels have different transition probabilities 
and/or different collisional de-excitation rates, their ratio depends on the 
density.

The relative excitation rates of the two lines shown in Fig. 
\ref{fig:transitions_P1} are proportional to their statistical weights; thus, the 
ratio of the line intensities is a constant in the low-density limit 
\citep{Osterbrock89}.  In the high-density regime, this ratio is best accurately 
described by a Boltzmann population ratio.  There is a critical density for the 
energy levels which describes the turning point between these two extremes.

### 2017-06-06 KellyDouglass/Thesis/Thesis_sections/GV.tex
BPT distribution of abundances, Appendix section on physics of transitions added

@@
 
-During my estimation of the chemical content of galaxies with $M_r > -20$, I 
-note that the oxygen abundances of galaxies classified as having an AGN by their 
-emission line ratios in the BPT diagrams exhibit higher nitrogen abundances and 
-normal oxygen abundance values when compared to star-forming galaxies of a 
-similar stellar mass and large-scale environment.  The same abundance signature 
-is seen in the the oxygen and nitrogen abundance results seen in Fig. 
-\ref{fig:Z_hist} of the green valley galaxies.  This might indicate a 
-link between green valley galaxies and a host AGN.  This would support other 
-studies of the transition of galaxies from the blue sequence to the red cloud, 
-which attribute the quenching of star formation to accretion of a central black 
-hole \citep[e.g.,][]{Croton06,Stasinska08}.
+\begin{figure}
+    \includegraphics[width=0.49\textwidth]{Images/GV/1sig_all_BPT_t3_12logOHrelations_dust_hist}
+    \includegraphics[width=0.49\textwidth]{Images/GV/1sig_all_BPT_t3_12logNHrelations_dust_hist}
+    \includegraphics[width=0.49\textwidth]{Images/GV/1sig_all_BPT_t3_logNOrelations_dust_hist}
+    \caption[Gas-phase chemical abundance distributions for star-forming, 
+    composite, and AGN galaxies]{Distribution of the gas-phase oxygen abundance 
+    (O/H, top left), nitrogen abundance (N/H, top right), and N/O ratio (bottom 
+    center) of the SDSS DR7 galaxies with detectable emission lines for 
+    abundance calculations with the Direct $T_e$ method.  Star-forming galaxies 
+    are shown with a solid cyan line, while composite galaxies are a dashed 
+    orange line and galaxies with an AGN are represented as a dotted magenta 
+    line.  Composite galaxies have lower oxygen abundances than both 
+    star-forming galaxies and those with an AGN.  The nitrogen abundance range 
+    is different for each of the three classes, with star-forming galaxies 
+    having the lowest nitrogen abundances, AGN having the highest, and 
+    composite galaxies in the middle.  Therefore, star-forming galaxies have 
+    N/O ratios $< 0$, while composite galaxies and galaxies with an AGN have 
+    N/O ratios between -1 and 0.5.}
+    \label{fig:BPT_abund}
+\end{figure}
+
+To understand the gas-phase chemical abundances of the green valley galaxies, we 
+compare Fig. \ref{fig:Z_hist} with the distribution of the gas-phase chemical 
+abundances of star-forming and composite galaxies and galaxies with an AGN shown 
+in Fig. \ref{fig:BPT_abund}.  We see that the galaxies with an AGN have the most 
+similar distributions in the three abundance ratios as the green valley 
+galaxies: both groups have similar oxygen abundances (O/H) and higher nitrogen 
+abundances (N/H) and N/O ratios than the star-forming galaxies.  This might 
+indicate a link between green valley galaxies and a host AGN.  The presence of 
+an AGN in green valley galaxies would support other studies of the transition of 
+galaxies from the blue sequence to the red cloud, which attribute the quenching 
+of star formation to accretion of a central black hole \citep[e.g.,][]{Croton06,
+Stasinska08}.
 

### 2017-06-06 KellyDouglass/Thesis/Thesis_sections/Paper1.tex
BPT distribution of abundances, Appendix section on physics of transitions added

@@
 % Oxygen
-\subsection{[O{\sc iii}]}\label{sec:O3}
+\subsection{[\ion{O}{3}]}\label{sec:O3}
 
@@
 %-------------------------------------------------------------------------------
-\subsection{[O{\sc ii}]}
+\subsection{[\ion{O}{2}]}
+
 A less temperature-sensitive line than [O{\sc iii}] $\lambda 4363$, the 
@@
 % Sulfur
-\subsection{[S{\sc ii}]}
+\subsection{[\ion{S}{2}]}
+
 Just as we are able to measure the electron temperature from [O{\sc iii}] 
@@
 \subsection{Direct $T_e$ method}
+
 We use the method published by \cite{Izotov06}, which is based on the 
@@
     \begin{tabular}{cccc}
-        \hline \\
+        \hline
          & $Z < 7.6$ & $7.6 \leq Z < 8.2$ & $Z \geq 8.2$\\
-        \hline \\
-        \hline \\
+        \hline
+        \hline
         \multicolumn{4}{c}{$1 \sigma$ restriction on [O{\sc iii}] $\lambda 4363$}\\
-        \hline \\
+        \hline
         Void & 9.52\% (4)   & 66.67\% (28) & 23.81\% (10)\\
         Wall & 19.10\% (17) & 59.55\% (53) & 21.35\% (19)\\
-        \hline \\
+        \hline
         \multicolumn{4}{c}{No restriction on [O{\sc iii}] $\lambda 4363$}\\
-        \hline \\
+        \hline
         Void & 13.33\% (16) & 45.83\% (55)  & 40.83\% (49)\\

### 2017-06-06 KellyDouglass/Thesis/Thesis_sections/Paper2.tex
BPT distribution of abundances, Appendix section on physics of transitions added

@@
 % ------------------------------------------------------------------------------
-\subsection{[N{\sc ii}]}
-
-The energy-level diagram for the various transitions of [N{\sc ii}] is very 
-similar to that of [O{\sc iii}], since they have the same electron ground-state 
+\subsection{[\ion{N}{2}]}
+
+The energy-level diagram for the various transitions of [\ion{N}{2}] is very 
+similar to that of [\ion{O}{3}], since they have the same electron ground-state 
 configuration ((1s)$^2$(2s)$^2$(2p)$^2$).  The similarities can be seen in Fig. 
 \ref{fig:transitions_P2}.  Therefore, an estimate of the electron temperature can 
-be made from the [N{\sc ii}] $\lambda 5755$ emission line.  However, this line 
-is weaker than the [O{\sc iii}] $\lambda 4363$ auroral line (since there is less 
-N than O in galaxies), so we use the [O{\sc iii}] auroral line for our 
+be made from the [\ion{N}{2}] $\lambda 5755$ emission line.  However, this line 
+is weaker than the [\ion{O}{3}] $\lambda 4363$ auroral line (since there is less 
+N than O in galaxies), so we use the [\ion{O}{3}] auroral line for our 
 temperature estimates, as in Paper I.  After obtaining a temperature and density 
-estimate, we use the [N{\sc ii}] $\lambda \lambda 6548, 6584$ doublet to 
+estimate, we use the [\ion{N}{2}] $\lambda \lambda 6548, 6584$ doublet to 
 estimate the abundance of singly ionized nitrogen in a galaxy.
@@
     \caption[{[\ion{O}{3}] and [\ion{N}{2}] energy-level diagram}]{Energy-level 
-    diagram for [O{\sc iii}] and [N{\sc ii}] $(2p^2)$ ions.  The most important 
+    diagram for [\ion{O}{3}] and [\ion{N}{2}] $(2p^2)$ ions.  The most important 
     transitions are shown; all are in the visible spectrum.  These forbidden 
@@
 We use the same method to calculate the nitrogen abundance as in Paper I to 
-estimate the oxygen abundance.  However, here we use the [N{\sc ii}] 
-$\lambda \lambda 6548, 6584$ doublet instead of the [O{\sc ii}] $\lambda 3727$ 
-and [O{\sc iii}] $\lambda \lambda 4959,5007$ doublets.  Because the temperature 
-estimate depends on the auroral line [O{\sc iii}] $\lambda 4363$, this method is 
+estimate the oxygen abundance.  However, here we use the [\ion{N}{2}] 
+$\lambda \lambda 6548, 6584$ doublet instead of the [\ion{O}{2}] $\lambda 3727$ 
+and [\ion{O}{3}] $\lambda \lambda 4959,5007$ doublets.  Because the temperature 
+estimate depends on the auroral line [\ion{O}{3}] $\lambda 4363$, this method is 
 often difficult to employ.  As a result, it works best with low-redshift, 

### 2017-06-07 KellyDouglass/Thesis/simulations.tex
Added simulations appendix section

\chapter[Simulations]{Simulations of dwarf galaxy formation and evolution}

Numerous simulations have been performed over the years in an attempt to 
understand the formation and evolution of our universe.  As observers, it is 
important to connect our observations with the theory in order to grow our ideas 
about the universe.

\section{General dwarf galaxy formation and evolution}

% Hierarchical formation of halos
It is impossible to directly observe the formation of a galaxy.  Based on 
detected merging galaxies, the astronomical community has surmised the galaxies 
have increased their mass largely due to the merging of smaller galaxies.  
\cite{deRossi07} performed $\Lambda$CDM simulations of hierarchical galaxy 
formation.  They find that the growth of systems by aggregation is responsible 
for the mass-metallicity relation.  Less massive systems tend to increase their 
stellar mass by either gas-rich mergers or secular evolution, resulting in a 
stronger correlation between stellar mass and metallicity.  Evidence of this is 
seen in the mass-metallicity relation of \cite{Tremonti04}, where there is 
little relationship between stellar mass and the metallicity for massive 
systems, but at intermediate and lower masses the correlation is strong between 
the two quantities.

% ISM - inflows and outflows
The inflow and outflow of gas in galaxies are aspects of galaxy evolution that 
are not yet well understood.  This is especially important when studying dwarf 
galaxies, since their gravitational potential wells are potentially small enough 
to be strongly influenced by star formation and/or supernovae.  Simulations by 
\cite{Marcolini04} find that when ram pressure from the intergalactic medium 
(IGM) is comparable to the thermal pressure of the central interstellar medium 
(ISM), stripping and superwind influence each other and increase the gas removal 
rate.  They find that the amount of metal-rich ejecta is sensitive to the ram 
pressure.  
% supernova
Simulations by \cite{Power14} and \cite{Melioli15} show that supernovae contain 
sufficient energy to unbind the gas in a low mass halo.  \cite{Hu16} show that 
supernova-driven galactic outflows push metal-rich gas into the halo.  A small 
fraction of the gas eventually escapes the halo, while most falls back onto the 
disc.  This results in the halo metallicity being about 20\% higher than the 
disc metallicity.  Likewise, \cite{Muratov17} find that almost all metals 
produced in a Type II supernova are ejected from the galaxy.
% star formation
Unlike the supernovae, \cite{Melioli15} finds that the ISM material does not 
have a strong likelihood of being expelled from a galaxy due to star formation.  
In contrast, \cite{Muratov15} finds that a large portion of material is ejected 
in galactic outflows after a bust of star formation, which collects in the 
circumgalactic medium (CGM) and is sometimes recycled in later star formation 
episodes.  In galaxies with $M_h < 10^{12} M_\odot$, a fraction of material is 
lost to the IGM.

% Metallicity
In numerical simulations to study the properties of the ISM in an isolated, 
star-forming galaxy, \cite{Hu16} finds that stellar feedback slowly increases 
the disc metallicity.  The majority of outflows are enriched winds, which 
reduces the metallicity of the ISM.  \cite{Muratov17} finds that outflows to the 
CGM generated in dwarf galaxies at low redshifts are dominated by metal-poor 
gas.  Galaxies retain most of the metals they produce, though a large fraction 
is in the CGM.  By combining our observations with the results of these 
simulations, we can begin to understand how star formation and supernovae 
influence a dwarf galaxy's gas content.

\section{Environmental differences}

Unlike the simulations described above, simulations which investigate the 
influence of the large-scale environment on the formation and evolution of 
galaxies have presented a more uniform picture.  Simulations by \cite{Jung14,
Xie14} and \cite{Tonnesen15} show that dark matter halos assembled later in 
underdense regions for a given halo mass.  For central galaxies, \cite{Jung14} 
and \cite{Tonnesen15} find that the ratio of stellar mass to halo mass is larger 
in overdense regions because star formation rates were higher in these denser 
regions.

\cite{Cen11} studied cosmic downsizing with high-resolution large-scale 
hydrodynamic galaxy formation simulations based on the $\Lambda$CDM cosmology.  
He finds that cosmic downsizing is part of a trend where the sSFR is a function 
of halo mass such that lower-mass galaxies have higher sSFRs.  The formation of 
large halos (groups and clusters) and the large-scale structure causes cosmic 
gas to heat beyond a critical temperature at which the gas's entropy is too high 
to cool to continue feeding the galaxies and their star formation.  As the 
surrounding gas in the dense regions becomes heated beyond the critical limit, 
the sSFR of the affected galaxies decreases and the galaxies transition from the 
blue sequence to the red cloud.  In the void environment, this heating does not 
occur, and so galaxies in the voids maintain a high sSFR in the present epoch.  
While this is the overall trend, there still exists some galaxies at $z=0$ which 
have a high sSFR but reside in the more dense environments.

### 2017-06-08 KellyDouglass/Thesis/Thesis_sections/smallScaleEnvironment.tex
Updated smallScaleEnvironment chapter with Steve's comments

@@
 regions that occupy close to 60\% of space).  Over the last few decades, the 
-Sloan Digital Sky Survey \citep{Abazajian09,Ahn12} have propelled the research 
+Sloan Digital Sky Survey \citep{Abazajian09,Ahn12} has accelerated the research 
 into the influence of the large-scale environment on the formation and evolution 
@@
 galaxy formation \citep[see][for a review]{vandeWeygaert11}.  The $\Lambda$CDM 
-cosmology predicts that galaxies which formed in voids to have lower masses and 
-be retarded in their star formation when compared to those in more dense 
+cosmology predicts that galaxies formed in voids have lower masses and are 
+retarded in their star formation when compared to those in more dense 
 environments \citep{Gottlober03,Goldberg05,Cen11}.  The effects of the void 
@@
 gravitational potential.  As a result, they are more sensitive to astrophysical 
-effects such as cosmological reionization, internal feedback from supernova and 
+effects such as cosmological reionization, internal feedback from supernovae and 
 photoheating from star formation, small-scale details of dark matter halo 
@@
 In conjunction with the large-scale environment, the small-scale environment 
-($\sim 1$ \hMpc) has also been found to influence a galaxy's evolution.  There 
-exits a well-established morphology-density relation \cite{Dressler80}, where 
+($\sim 1$ \hMpc) has also been found to influence a galaxy's evolution.  A 
+well-established morphology-density relation exists \citep{Dressler80}, where 
 the fraction of late-type galaxies is inversely proportional to the local 
@@
 We want to understand if the small-scale environment is more influential in a 
-galaxy's evolution than its large-scale environment.  Additionally, within the 
-small-scale environment, are tidal influences (due to the nearest neighbor 
-galaxy) or gravitational potentials (from the nearest galaxy group) more 
-influential in a galaxy's evolution?  A group consists of multiple galaxies that 
-share the same dark matter halo.  A group member will gravitationally interact 
-with all other group members, not just its nearest neighbor.  And a galaxy near 
-a group, but not within it, may also experience strong tidal effects from the 
-group similar to (but stronger than) those from a neighboring galaxy.
+galaxy's evolution than its large-scale environment.  One important question 
+within the small-scale environment asks if tidal influences due to the nearest 
+neighbor galaxy or gravitational potentials from the nearest galaxy group are 
+more influential in a galaxy's evolution.  A group consists of multiple galaxies 
+that share the same dark matter halo.  A group member will interact 
+gravitationally with all other group members, not just its nearest neighbor.  
+And a galaxy near a group, but not within it, may also experience strong tidal 
+effects from the group similar to and stronger than those from a neighboring 
+galaxy.
 
@@
 galaxy's nearest neighbor.  Within a relative velocity 
-$v_{rel} < 300\text{ km/s}$, we use the physically closest (in units of \hMpc) 
-and the neighbor with the smallest fraction of its virial radius; both these 
-methods are described below in further detail.  The two methods result in 
-different neighboring galaxies for 40\% of our dwarf galaxy sample.
+$v_{rel} < 300\text{ km/s}$, we use either the physically closest galaxy in 
+units of \hMpc or the galaxy within the smallest fraction of its virial radius; 
+both these methods are described below in further detail.  The two methods 
+result in different neighboring galaxies for about 40\% of our dwarf galaxy 
+sample.
 
@@
 Rather than using a measure of the virial radius for the group analysis, we 
-scale the distance as a fraction of the group's rms radius.
+scale the distance as a fraction of the group's root mean square (rms) radius.
 
@@
 Each of these four plots probes this distance relationship from a different 
-angle.  The top left plots in Figs. \ref{fig:ur}--\ref{fig:NO} compare the 
-target dwarf galaxy's parameter to the distance to its nearest neighbor, as 
-defined by the the closest galaxy on the sky in \hMpc with a velocity difference 
-less than 300 km/s.  The bottom left plots compare the target dwarf galaxy's 
-parameter to the distance to its nearest neighbor, as defined by the closest 
-galaxy on the sky in units of the virial radius of the neighbor galaxy with a 
-velocity difference less than 300 km/s.  The nearest galaxy is not necessarily 
-the same for these two distance measurements, as explained in Sec. 
-\ref{sec:Theory_dist}.
+angle.  The top left plots in Figs. \ref{fig:ur}--\ref{fig:NO} relate the target 
+dwarf galaxy's parameter to the distance to its nearest neighbor, as defined by 
+the the closest galaxy on the sky in \hMpc with a velocity difference less than 
+300 km/s.  The bottom left plots relate the target dwarf galaxy's parameter to 
+the distance to its nearest neighbor, as defined by the closest galaxy on the 
+sky in units of the virial radius of the neighbor galaxy with a velocity 
+difference less than 300 km/s.  The nearest galaxy is not necessarily the same 
+for these two distance measurements, as explained in Sec. \ref{sec:Theory_dist}.
 
 We repeat this same analysis on the nearest groups to the target dwarf galaxy.  
-The top right plots in Figs. \ref{fig:ur}--\ref{fig:NO} compare the target dwarf 
+The top right plots in Figs. \ref{fig:ur}--\ref{fig:NO} relate the target dwarf 
 galaxy's parameter to the distance to the center of the nearest group, as 
-defined as the closest group on the sky in \hMpc with a velocity difference less 
+defined as the closest group in the sky in \hMpc with a velocity difference less 
 than 300 km/s.  The bottom right plots in Figs. \ref{fig:ur}--\ref{fig:NO} 
-compare the target dwarf galaxy's parameter to the distance to the nearest group 
+relate the target dwarf galaxy's parameter to the distance to the nearest group 
 as defined by the closest group on the sky in units of the group's rms radius 
@@
 
-Because of the known morphology-density relation, we excepted to find that a 
-dwarf galaxy's color became more blue as the distance to its nearest neighbor 
+Because of the known morphology-density relation, we expect to find that a dwarf 
+galaxy's color became more blue as the distance to its nearest neighbor 
 increased.  Fig. \ref{fig:ur} shows very little relationship between the 
@@
 
-We test two of our input parameters to understand how sensitive our results are 
-to any initial conditions.  The first parameter we discuss is the sensitivity of 
-our results on the maximum peculiar velocity to define a match.  Throughout our 
-analysis, we use 300 km/s as the maximum velocity separation allowed between the 
-target galaxy and its nearest neighbor or group.  We look at how this affects our 
-results by repeating the analysis with maximum velocities of 150 km/s and 600 
-km/s.  The results of this comparison on the color of the galaxies can be seen in 
-Fig. \ref{fig:ur_vpeculiar}.  The nearest neighbors in the left-hand panel are 
+We test two components of our nearest neighbor criteria to understand how 
+sensitive our results are to any initial conditions.  The first parameter we 
+discuss is the sensitivity of our results on the maximum peculiar velocity to 
+define a match.  Throughout our analysis, we use 300 km/s as the maximum 
+velocity separation allowed between the target galaxy and its nearest neighbor 
+or group.  We look at how this affects our results by repeating the analysis 
+with maximum velocities of 150 km/s and 600 km/s.  The results of this 
+comparison on the color of the galaxies can be seen in Fig. 
+\ref{fig:ur_vpeculiar}.  The nearest neighbors in the left-hand panel are 
 restricted to a maximum peculiar velocity of 150 km/s, while those in the right 
@@
 therefore, have small sky separation and almost no difference in their peculiar 
-velocities.  We conclude that these represent merging systems, which visual 
-inspection will help to confirm.
+velocities.  We surmise that these represent merging systems, which future 
+visual inspection will help to confirm.
 
@@
 
-We see almost no relationship between a dwarf galaxy's color, sSFR, or gas-phase 
-chemical abundance and its distance to the nearest galaxy or group, implying 
-that the small-scale environment does not significantly influence a dwarf 
-galaxy's evolution.  This is in contrast to the large-scale environment, which 
-we have seen to influence the formation and evolution of dwarf galaxies.
+We see no relationship between a dwarf galaxy's color, sSFR, or gas-phase 
+chemical abundances and its distance to the nearest galaxy or group beyond the 
+target galaxy's immediate vicinity, implying that the small-scale environment 
+does not significantly influence a dwarf galaxy's evolution.  This is in 
+contrast to the large-scale environment, which we have seen to influence the 
+formation and evolution of dwarf galaxies.
 
@@
 or those within 0.1 \hMpc of the nearest group appear to deviate from the 
-average galaxy values.  The galaxies within this proximity of their nearest 
-neighbor tend to be bluer, have a higher sSFR, and have higher oxygen and 
-nitrogen abundances.  Based on the shift in the distribution of galaxies in Fig. 
-\ref{fig:ur_xyz}, these galaxies might be merging or strongly interacting with 
-their nearest neighbor.  This would then provide evidence that galaxy 
-interactions result in a burst of star formation, which would increase the 
+average galaxy values.  The target galaxies within this proximity of their 
+nearest neighbor tend to be bluer, have a higher sSFR, and have higher oxygen 
+and nitrogen abundances.  Based on the shift in the distribution of galaxies 
+seen in Fig. \ref{fig:ur_xyz}, these galaxies might be merging or strongly 
+interacting with their nearest neighbor.  If so, this provides evidence that 
+galaxy interactions result in a burst of star formation that increases the 
 gas-phase chemical abundances of the dwarf galaxies.  Because merging galaxies 
@@
 
-Dwarf galaxies within 0.1 \hMpc of the center of the nearest group are redder, 
-have lower oxygen abundances, and have higher N/O ratios than average.  Being so 
-close to the center of a group prevents more recent episodes of star formation.  
-Due to their proximity to the group center, it is also likely that these dwarf 
-galaxies are not able to retain as much of their heavier elements as for a more 
-isolated galaxy, reducing their gas-phase oxygen abundance (and therefore 
-increasing their N/O ratio).
+In contrast, dwarf galaxies within 0.1 \hMpc of the center of the nearest group 
+are redder, have lower oxygen abundances (O/H), and have higher N/O ratios than 
+average.  Being so close to the center of a group seems to prevent more recent 
+episodes of star formation.  Due to their proximity to the group center, it is 
+also likely that these dwarf galaxies are not able to retain as much of their 
+heavy elements as a more isolated galaxy, thereby reducing their gas-phase 
+oxygen abundance (and increasing their N/O ratio).
 

### 2017-06-08 KellyDouglass/Thesis/Thesis_sections/Conclusion.tex
Wrote conclusion chapter

@@
-\chapter{Conclusions}
+\chapter[Conclusion]{Conclusions and suggestions for future work}
 
-\section{Suggestions for future work}
+% Papers 1-3
+\section[Chemical abundances]{Large-scale environmental influence on the gas-phase chemical abundances in dwarf galaxies}
+We find that the large-scale environment influences the chemical evolution of 
+dwarf galaxies by estimating the gas-phase oxygen (O/H) and nitrogen (N/H) 
+abundances and the N/O ratio of star-forming dwarf galaxies in SDSS DR7 using 
+the Direct $T_e$ method and spectroscopic line flux measurements as reprocessed 
+in the MPA-JHU catalog \citep[Douglass \& Vogeley 2017, in prep]{Douglass17a,
+Douglass17b}.  Due to the minimum redshift limit for detecting the [\ion{O}{2}] 
+$\lambda$3727 emission line in SDSS DR7 spectra, only 135 dwarf galaxies are 
+available for analysis with the Direct $T_e$ method.  With this sample, we 
+initially see no difference in the metallicity (O/H) between dwarf galaxies in 
+voids and in denser regions.  However, upon closer inspection, we find minor 
+shifts in the distributions of gas-phase chemical abundances for void dwarf 
+galaxies when compared to star-forming dwarf galaxies in denser regions: 
+star-forming dwarf galaxies have higher oxygen abundances (O/H), lower nitrogen 
+abundances (N/H), and lower N/O ratios.
+
+By deriving a relation between the doubly-ionized oxygen and total oxygen 
+abundance in star-forming galaxies, we can expand our sample to consist of 1920 
+star-forming galaxies by removing the dependence on the [\ion{O}{2}] 
+$\lambda$3727 doublet.  This larger sample exhibits the same shifts in the 
+gas-phase chemical abundances as the smaller, 135 star-forming dwarf galaxy 
+sample, but with a much higher statistical significance.  We find that 
+star-forming void dwarf galaxies have, on average, 7\% higher oxygen abundances, 
+10\% lower nitrogen abundances, and 17\% lower N/O ratios than star-forming 
+dwarf galaxies in denser regions.  The large-scale ($\sim 10$ \hMpc) environment 
+influences the chemical evolution of star-forming dwarf galaxies.
+
+In addition to studying the large-scale environmental influence on the 
+distribution of gas-phase chemical abundances in star-forming dwarf galaxies, we 
+also investigate if and how the large-scale environment affects relationships 
+between the chemical abundances and various other physical parameters of the 
+galaxies.  We find that all of our galaxies reside on the ``nitrogen plateau'' 
+in the relationship between N/O and O/H, where the N/O ratio is predicted to be 
+independent of metallicities \OH $< 8.5$.  However, instead of a constant value 
+for the N/O ratio, we instead find that the N/O ratio decreases with increasing 
+metallicity.  This is contrary to what we see in the N/O-$M_*$ relationship, 
+where we find that some of the star-forming dwarf galaxies have a constant value 
+of N/O for a range of masses while the remainder exhibit a positive relationship 
+between the stellar mass and N/O ratio.  We make note of a different critical 
+mass in the N/O-$M_*$ relationship in the two environments, where the void dwarf 
+galaxies begin to show evidence of secondary nitrogen synthesis at a stellar 
+mass $\sim 0.4\text{ dex}$ lower than for the galaxies in denser regions.  Most 
+of our star-forming dwarf galaxies follow the established mass-metallicity 
+relation \citep[e.g.,][]{Tremonti04}.
+
+No relationship is observed between the metallicity and \ion{H}{1} mass in our 
+sample of star-forming dwarf galaxies, but we do find that the N/O ratio 
+decreases with increasing \ion{H}{1} mass for a given stellar mass.  The 
+star-forming dwarf galaxies also exhibit an increase in the metallicity and 
+N/O ratio with increasing color (both $u-r$ and $g-r$).  We see very little 
+correlation with SFR for either metallicity or the N/O ratio in dwarf galaxies, 
+but the metallicity and N/O ratio decrease with increasing sSFR.  Beyond the 
+large-scale environmental influence on the distributions of the gas-phase 
+chemical abundances and the critical mass in the N/O-$M_*$ relationship, we do 
+not observe any significant differences between the star-forming void and wall 
+dwarf galaxies in any of these relationships.
+
+We surmise that the differences in the distributions of metallicity and the N/O 
+ratio seen in the sample of star-forming dwarf galaxies are due to a large-scale 
+environmental influence on their star formation history and evolution.  The 
+shift in the gas-phase oxygen abundance distribution could be observational 
+evidence for delayed star formation in void galaxies when compared to those in 
+denser regions.  This would result in a smaller ratio of stellar mass to dark 
+matter halo mass in void galaxies than in dwarf galaxies in denser regions, as 
+predicted in simulations by \cite{Jung14} and \cite{Tonnesen15}.  If the void 
+galaxies are retaining more oxygen as a result of their deeper potential wells, 
+then they would be able to commence secondary nitrogen synthesis earlier, as 
+seen in the N/O-$M_*$ relation in Fig. \ref{fig:M_NO}.  In addition, the shift 
+towards lower N/O ratios in the star-forming dwarf galaxies might be evidence 
+that cosmological downsizing is environmentally dependent as predicted by 
+\cite{Cen11}.  Our results provide evidence for delayed, ongoing star formation 
+in void dwarf galaxies whose dark matter halos ceased coalescing earlier than 
+for dwarf galaxies in denser regions.
+
+It has been hypothesized that a special population of extremely metal-poor 
+galaxies exist in void regions.  We find no evidence for a special population of 
+extremely metal-poor star-forming dwarf galaxies in the voids, as we note an 
+equal fraction of low metallicity dwarf galaxies in both the void and denser 
+regions.  Due to their low gas-phase oxygen abundances, these 287 dwarf galaxies 
+have some of the larger N/O ratios of the star-forming dwarf galaxies sample 
+studied.  While the metallicities of these galaxies cause them to stand out in 
+the relationships between metallicity and other physical quantities (stellar 
+mass, color, (s)SFR), they are not unusual when studying the relationships 
+between the N/O ratio and these other quantities.
+
+% Small-scale environment
+\section[Small-scale environment]{Small-scale environmental influence on dwarf galaxy evolution}
+In addition to the influence of the large-scale environment on the evolution of 
+dwarf galaxies, we also study the effects of the small-scale environment on dwarf 
+galaxies.  We find that only the presence of a neighboring galaxy within 0.05 
+\hMpc or 0.05$r_{vir}$, or the presence of a group within 0.1 \hMpc influences a 
+dwarf galaxy's evolution.  Dwarf galaxies with a nearest neighbor galaxy within 
+0.05 \hMpc or 0.05$r_{vir}$ are bluer, have a higher sSFR, and have higher 
+oxygen and nitrogen abundances than average.  In contrast, dwarf galaxies within 
+0.1 \hMpc of the center of the closest group are redder, have lower oxygen 
+abundances, and have higher N/O ratios than average.  These results are 
+independent of the maximum relative velocity required to define a nearest 
+neighbor and the sample (star-forming versus all dwarf galaxies).
+
+When we incorporate the redshift into the distance calculations, we find that 
+the galaxies within 0.05$r_{vir}$ are most likely strongly interacting or 
+merging with their nearest neighbor.  This matches the results of \cite{Park09}, 
+who find that late-late type galaxy pairs within 0.05$r_{vir}$ are bluer and 
+have higher SFRs.  These merging galaxies likely share the same dark matter 
+halo, indicating that the dark matter halo is more influential on a galaxy's 
+evolution than the galaxy's distance to the nearest neighbor.
+
+% GV galaxies
+\section[GV galaxies]{Properties of green valley galaxies}
+Finally, we also investigate the properties of galaxies residing in the green 
+valley of the color-magnitude diagram (CMD), in an effort to understand the role 
+of the environment on a galaxy's evolution through the color-magnitude diagram.  
+We discover that we can define galaxies which are transitioning through the 
+green valley of the CMD by combining the galaxy's color, color gradient, and 
+inverse concentration index.  Galaxies with a magnitude less than 25 for the 
+morphological type as calculated in the KIAS-VAGC exist in the green valley 
+portion of the UV-optical CMD.  Galaxies defined as early types (morphological 
+type values equal to 1 or 2) are in the red cloud, while those with 
+morphological type values greater than 25 are in the blue sequence.  With this 
+quantitative definition for galaxies transitioning through the green valley, we 
+can begin to understand the properties of green valley galaxies and their 
+evolution.
+
+Based on our analysis, green valley galaxies have stellar masses comparable to 
+galaxies in the red cloud.  They have intermediate SFRs and low-to-intermediate 
+sSFRs.  Green valley galaxies also have high gas-phase nitrogen abundances 
+(N/H), resulting in high N/O ratios.  While their SFRs show that their star 
+formation has been quenched, their stellar masses inform us that this is not due 
+to any premature quenching mechanism.  The high nitrogen abundances in the green 
+valley galaxies indicate that the galaxies are either no longer forming stars 
+(since nitrogen is produced in lower mass stars than oxygen), or that the 
+galaxies were able to synthesize both primary and secondary nitrogen (heavy 
+elements were present during the last few star formation episodes to permit the 
+CNO cycle to commence earlier).  This chemical abundance pattern of normal 
+oxygen (O/H), high nitrogen (N/H), and high N/O ratio is also seen in galaxies 
+classified as AGN, indicating that galaxies in the green valley have an AGN.
+
+There is a higher fraction of faint galaxies from denser regions than faint void 
+galaxies in the green valley.  Combined with the previous results about the 
+large-scale environmental influence on the gas-phase chemical abundances, this 
+indicates that void dwarf galaxies are less evolved than dwarf galaxies in 
+denser environments.
+
+\section[Future work]{Suggestions for future work}
+
+% Metallicity
+%  - gradients
+%  - chemical abundances of composite, AGN galaxies
+%  - SHELS?
+
+% GV galaxies
+%  - understand aimc calculation
+%  - metallicity gradients
+%  - small-scale environment
+
+A critical problem in galaxy formation is understanding how galaxies transition 
+from the blue sequence to the red cloud in the optical color-magnitude diagram.  
+Star formation is thought to be quenching in galaxies moving through the green 
+valley, but the relevant baryonic processes (gas cooling, feedback, etc.) are 
+very complex and heavily independent.  The enrichment of the interstellar medium 
+(ISM) and circumgalactic medium (CGM) of a galaxy involves many complicated 
+processes, the interplay of which is not yet well understood.  Investigating the 
+star formation history and chemical evolution of galaxies in the green valley 
+should provide clues of the movement of a galaxy through the color-magnitude 
+diagram.
+
+With the advent of 2-dimensional spectroscopic data from SDSS MaNGA \citep{MaNGA,
+SDSS13}, it is possible to examine how the ISM and CGM are enriched over time.  
+MaNGA is the first large-scale survey using integral-field spectroscopy, which 
+would permit the study of spatially-resolved physical properties of galaxies 
+across many different environments, morphologies, and stages of evolution.  In 
+particular, it would be instructive to study the gradients of the gas-phase 
+chemical abundances of galaxies in order to better understand their evolution 
+through the CMD and also the influence of the environment in both large and 
+small scales on the chemical evolution of these galaxies.
+
+A better knowledge of the chemical abundances of galaxies with an AGN is also 
+crucial to understanding the evolution of galaxies.  Understanding how the 
+presence of an AGN affects a galaxy's evolution is currently limited --- most 
+research at the moment is concentrated on the physics within an AGN.  Many 
+simulations have been done to test different theories about the role of an AGN 
+in a galaxy, and observations are now needed to test the results of the 
+simulations.
+
+% Small-scale environment
+%  - relative parameter values as a function of distance
+%  - visual inspection of mergers
+
+The work done here on the small-scale environment is only the beginning of what 
+can be done in this subject area.  In addition to studying the relationship 
+between a galaxy's physical parameters and its distance to the nearest neighbor, 
+it is also important to look at the ratio of the galaxy's parameters to its 
+neighbor's and the distance to the nearest neighbor --- ``galactic 
+conformity.''  These comparisons should include a morphological comparison, 
+similar to the analysis done by \cite{Park09}.  We also find evidence of 
+possible mergers when studying the influence of the small-scale environment.  
+Visual inspection of these dwarf galaxies is imperative to confirming this 
+conclusion.

### 2017-06-09 KellyDouglass/Thesis/Thesis_sections/Introduction.tex
Beginning of intro written

\chapter{Introduction}

% Description of large-scale structure in our universe
%  - What has been observed?
%  - What has been simulated?

\begin{figure}
    \includegraphics[width=0.65\textwidth]{Images/Intro/sdss}
    \caption[SDSS galaxy map]{A slice through the SDSS galaxy distribution; each 
    point on this plot is a galaxy.  Large sky surveys such as SDSS have 
    revealed a non-uniform distribution of galaxies throughout the universe.  
    Dubbed the cosmic web, galaxies clump together in clusters and along 
    filaments, leaving giant gaps between them (similar to a sponge).}
    \label{fig:SDSS_map}
\end{figure}

\begin{figure}
%    \includegraphics[width=0.9\textwidth]{Images/Intro/Millenium_simulation}
    \caption[Dark matter simulation]{Snapshots of a portion of the Millenium 
    Simulation showing the dark matter distribution at different points in time 
    from 0.21 Gyr after the Big Bang to the present.  Small perturbations in the 
    initial distribution of dark matter are amplified as the universe expands.  
    Gravity causes the slightly overdense regions to contract while 
    simultaneously causing the underdense regions to expand.}
    \label{fig:DMsim}
\end{figure}

Large sky surveys \citep[such as the Sloan Digital Sky Survey --- 
SDSS][]{York00} have revealed a non-uniform distribution of galaxies throughout 
the universe.  Taking on a shape similar to that of a three-dimensional cosmic 
web \citep{Bond96} or a sponge, galaxies clump together in clusters and along 
filaments, leaving void regions between them.  Evidence of this distribution can 
be seen in Fig. \ref{fig:SDSS_map} for galaxies in the SDSS Data Release 7 
\citep[SDSS DR7][]{Abazajian09}.  Based on these observations, dark matter 
simulations have been constructed which successfully reproduce the same 
large-scale structure.  If we start with a mostly uniform distribution of dark 
matter at the Big Bang, Fig. \ref{fig:DMsim} outlines the evolution of that dark 
matter up to present day.  These snapshots from the Millenium Simulation project 
\citep{Springel05} show that small perturbations in the initial distribution of 
dark matter are amplified as the universe expands.  Gravity causes the slightly 
overdense regions to collapse while simultaneously causing the underdense 
regions to expand.  Due to dark matter's strong gravitational interaction, we 
believe that the baryonic mattter (that which interacts electromagnetically) 
will trace the dark matter distribution, resulting in the galaxy distribution we 
observe today.

% Void galaxies
\begin{figure}
%    \includegraphics[width=0.9\textwidth]{Images/Intro/void_slice}
    \caption[Sky map highlighting voids and void galaxies]{A 10 \hMpc slice of 
    SDSS DR7 \citep[Fig. 1]{Moorman14} with void regions highlighted in blue 
    circles.  Void galaxies are shown as red points while wall galaxies are 
    black.  Existing in the cosmological voids (space between the galactic 
    filaments), void galaxies are though to demonstrate the fundamental 
    characteristics of galactic evolution.}
\end{figure}

The galaxies within the underdense void environments are named ``void 
galaxies.''  Existing in the cosmological voids, void galaxies are thought to 
demonstrate the fundamental characteristics of galactic evolution.  Cosmic voids 
are an important environment for studying galaxy formation \citep[see][for a 
review]{vandeWeygaert11}.  Gravitational clustering proceeds as if in a very low 
density universe, where the amassment of gravitationally bound dark matter halos 
ends relatively early and there is little subsequent interaction between the 
galaxies due to the lower density and the faster local Hubble expansion.  
Therefore, $\Lambda$CDM cosmology predicts that galaxies formed in voids should 
have lower mass and be retarded in their star formation when compared to those 
in denser regions \cite[e.g.,][]{Gottlober03,Goldberg05,Cen11}.  
\cite{Goldberg04} show that a void region that is only 10\% of the mean density 
of the universe with $\Omega_{matter} = 0.3$, $h = 0.7$ dynamically evolves as 
if $\Omega_{matter} = 0.02$, $\Omega_\Lambda = 0.48$, and $h = 0.84$.  
Additionally, hydrodynamical cosmological simulations by \cite{Cen11} show that 
the gas in voids remains below the critical entropy threshold, allowing void 
galaxies to continue to form stars.  Void galaxies evolve in a relatively 
pristine environment where interactions are rare and star formation proceeds up 
to the present epoch because void galaxies are able to retain their gas.  This 
contrasts the denser environments, where the chemical composition and evolution 
of galaxies are drastically altered due to mergers and tidal stripping and/or 
ram-pressure stripping.

% What do we already know about the environmental influence?

% Dwarf galaxies

\begin{figure}
    \includegraphics[width=0.65\textwidth]{Images/Intro/1sig_13-23_SDSS_Mr_hist_count_fill}
    \caption[Absolute magnitude distribution of galaxies in SDSS DR7]{Absolute 
    magnitude ($M_r$) distribution of galaxies in SDSS DR7, separated into void 
    and wall environments.  Dwarf galaxies are defined as galaxies with absolute 
    magnitudes fainter than -17 ($M_r > -17$).  For reference, the Milky Way has 
    an absolute magnitude $M_r \approx -20$.}
\end{figure}

% Galaxy structure

% Metallicity
%  - How are elements synthesized in stars?
%  - What does the light look like when it reaches us?  When we look at an emission spectrum, what are we studying?
%  - What are forbidden transitions and why are they important?
%  - How do we get the temperature from the emission line ratio?  (Summary - refer to appendix for more details)
%  - What is the metallicity?  O/H - Why oxygen?  and once we estimate the abundances of each ion, we add them together to get the total abundance for that element

\begin{figure}
    \includegraphics[width=0.9\textwidth]{Images/Intro/Kirchoff}
    \caption[Kirchoff's laws of spectroscopy]{Three different viewpoints of the 
    light emitted from a star and/or a cool cloud of gas, representing 
    Kirchoff's laws of spectroscopy.  A star emits light across all wavelengths, 
    so the resulting spectrum is known as a continuous spectrum.  Star's light 
    that has passed through a cloud of cool gas before being observed is an 
    absorption spectrum, where the elements in the cloud have absorbed some of 
    the light at specific wavelengths (corresponding to the particular elements 
    present in the gas).  If observed off the line-of-sight of the star, the 
    light emitted from the cloud of cooler gas is named an emission spectrum, 
    where the gas is re-radiating the light it absorbed from the star.}
\end{figure}

\begin{figure}
%    \includegraphics[width=0.9\textwidth]{Images/Intro/spectrum}
    \caption[Sample (void) dwarf galaxy spectrum]{Example SDSS DR7 spectrum --- 
    this is a void dwarf galaxy whose gas-phase chemical abundances are slightly 
    above average.  The [\ion{O}{3}] $\lambda$4363 auroral line is circled in 
    red, while the [\ion{O}{3}] $\lambda \lambda$4959,5007 doublet is circled in 
    yellow.}
\end{figure}

% Outline of Thesis
% Pose the problem - how does the large-scale environment affect galaxy evolution?
We want to understand how dark matter affects the evolution of a galaxy, and 
what influence it has on a galaxy's star formation.  To do this, we compare the 
properties of galaxies living in voids with galaxies in denser regions in an 
effort to understand how the properties of the gas and the history of star 
formation in a galaxy depend on the environment.  We then try to infer what 
these results tell us about the dark matter structure and history of the galaxy.

### 2017-06-09 KellyDouglass/Thesis/Thesis_sections/Paper1.tex
Beginning of intro written

@@
 
-This paper is published in the \emph{Astrophysical Journal}, 2017 (Vol. 834, 
-pages 186--198).
+This chapter is published in the \emph{Astrophysical Journal}, 2017 (Vol. 834, 
+pages 186--198) by Kelly A. Douglass \& Michael S. Vogeley; it will be 
+referenced as Douglass \& Vogeley (2017a).
+
+\begin{chapabstract}
+We study how the cosmic environment affects galaxy evolution in the Universe by 
+comparing the metallicities of dwarf galaxies in voids with dwarf galaxies in 
+more dense regions.  Ratios of the fluxes of emission lines, particularly those 
+of the forbidden [\ion{O}{3}] and [\ion{S}{2}] transitions, provide estimates of 
+a region's electron temperature and number density.  From these two quantities 
+and the emission line fluxes [\ion{O}{2}] $\lambda 3727$, [\ion{O}{3}] 
+$\lambda 4363$, and [\ion{O}{3}] $\lambda \lambda 4959,5007$, we estimate the 
+abundance of oxygen with the Direct $T_e$ method.  We estimate the metallicity 
+of 42 blue, star-forming void dwarf galaxies and 89 blue, star-forming dwarf 
+galaxies in more dense regions using spectroscopic observations from the Sloan 
+Digital Sky Survey Data Release 7, as re-processed in the MPA-JHU value-added 
+catalog.  We find very little difference between the two sets of galaxies, 
+indicating little influence from the large-scale environment on their chemical 
+evolution.  Of particular interest are a number of extremely metal-poor dwarf 
+galaxies that are less prevalent in voids than in the denser regions.
+\end{chapabstract}
 

### 2017-06-09 KellyDouglass/Thesis/Thesis_sections/Paper2.tex
Beginning of intro written

@@
 
-This paper is published in the \emph{Astrophysical Journal}, 2017 (Vol. 837, 
-pages 42--55).
+This chapter is published in the \emph{Astrophysical Journal}, 2017 (Vol. 837, 
+pages 42--55) by Kelly A. Douglass \& Michael S. Vogeley; it will be referenced 
+as Douglass \& Vogeley (2017b).
+
+\begin{chapabstract}
+We examine how the cosmic environment affects the chemical evolution of galaxies 
+in the universe by comparing the N/O ratio of dwarf galaxies in voids with 
+dwarf galaxies in denser regions.  Ratios of the forbidden [\ion{O}{3}] and 
+[\ion{S}{2}] transitions provide estimates of a region's electron temperature 
+and number density.  We estimate the abundances of oxygen and nitrogen using 
+these temperature and density estimates and the emission-line fluxes 
+[\ion{O}{2}] $\lambda 3727$, [\ion{O}{3}] $\lambda \lambda 4959, 5007$, and 
+[\ion{N}{2}] $\lambda \lambda 6548, 6584$ with the direct $T_e$ method.  Using 
+spectroscopic observations from the Sloan Digital Sky Survey Data Release 7, we 
+are able to estimate the N/O ratio in 42 void dwarf galaxies and 89 dwarf 
+galaxies in denser regions.  The N/O ratio for void dwarfs ($M_r > -17$) is 
+slightly lower ($\sim 12\%$) than for dwarf galaxies in denser regions.   We 
+also estimate the nitrogen and oxygen abundances of 2050 void galaxies and 3883 
+galaxies in denser regions with $M_r > -20$.  These somewhat brighter galaxies 
+(but still fainter than $L_*$) also display similar minor shifts in the N/O 
+ratio.  The shifts in the average and median element abundance values in all 
+absolute magnitude bins studied are in the same direction, suggesting that the 
+large-scale environment may influence the chemical evolution of galaxies.  We 
+discuss possible causes of such a large-scale environmental dependence of the 
+chemical evolution of galaxies, including retarded star formation and a higher 
+ratio of dark matter halo mass to stellar mass in void galaxies.
+\end{chapabstract}
 

### 2017-06-09 KellyDouglass/Thesis/preamble.tex
Beginning of intro written

@@
 
-I would like to thank Crystal Moorman for her help and support throughout this 
-work.  I would also like to acknowledge Renyue Cen for his help in the 
-interpretation of these results.  Finally, I would like to thank the referees 
-(including Burcu Beygu) for their detailed comments and critique of my work.
+% Advisor
 
-Support for this work was provided by NSF grant AST--1410525.
+% Thesis committee and collaborators (Renyue, Daniele, Jinfu, Brean, Salvatore)
+I would like to thank our collaborator Renyue Cen for his help in the 
+interpretation of these results.  I would also like to acknowledge Crystal 
+Moorman for her help and support throughout this work.  Finally, I would like to 
+thank the referees (including Burcu Beygu) for their detailed comments and 
+critique of my work.
 
-Funding for the SDSS and SDSS-II has been provided by the Alfred P. Sloan 
-Foundation, the Participating Institutions, the National Science Foundation, the 
-U.S. Department of Energy, the National Aeronautics and Space Administration, 
-the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education 
-Funding Council for England.  The SDSS Web Site is \emph{http://www.sdss.org/}.
+% Grad students & PLBD
 
-The SDSS is managed by the Astrophysical Research Consortium for the 
-Participating Institutions.  The Participating Institutions are the American 
-Museum of Natural History, Astrophysical Institute Potsdam, University of Basil, 
-University of Cambridge, Case Western Reserve University, University of Chicago, 
-Drexel University, Fermilab, the Institute for Advanced Study, the Japan 
-Participation Group, Johns Hopkins University, the Joint Institute for Nuclear 
-Astrophysics, the Kavli Institute for Particle Astrophysics and Cosmology, the 
-Korean Scientist Group, the Chinese Academy of Sciences (LAMOST), Los Alamos 
-National Laboratory, the Max-Planck-Institute for Astronomy (MPIA), the 
-Max-Planck-Institute for Astrophysics (MPA), New Mexico State University, Ohio 
-State University, University of Pittsburgh, University of Portsmouth, Princeton 
-University, the United States Naval Observatory, and the University of 
-Washington.
+% Family
+
+% Steve
+
+%Support for this work was provided by NSF grant AST--1410525.
+%
+%Funding for the SDSS and SDSS-II has been provided by the Alfred P. Sloan 
+%Foundation, the Participating Institutions, the National Science Foundation, the 
+%U.S. Department of Energy, the National Aeronautics and Space Administration, 
+%the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education 
+%Funding Council for England.  The SDSS Web Site is \emph{http://www.sdss.org/}.
+%
+%The SDSS is managed by the Astrophysical Research Consortium for the 
+%Participating Institutions.  The Participating Institutions are the American 
+%Museum of Natural History, Astrophysical Institute Potsdam, University of Basil, 
+%University of Cambridge, Case Western Reserve University, University of Chicago, 
+%Drexel University, Fermilab, the Institute for Advanced Study, the Japan 
+%Participation Group, Johns Hopkins University, the Joint Institute for Nuclear 
+%Astrophysics, the Kavli Institute for Particle Astrophysics and Cosmology, the 
+%Korean Scientist Group, the Chinese Academy of Sciences (LAMOST), Los Alamos 
+%National Laboratory, the Max-Planck-Institute for Astronomy (MPIA), the 
+%Max-Planck-Institute for Astrophysics (MPA), New Mexico State University, Ohio 
+%State University, University of Pittsburgh, University of Portsmouth, Princeton 
+%University, the United States Naval Observatory, and the University of 
+%Washington.
 
@@
 
-% Paper 1
-We study how the cosmic environment affects galaxy evolution in the Universe by 
-comparing the metallicities of dwarf galaxies in voids with dwarf galaxies in 
-more dense regions.  Ratios of the fluxes of emission lines, particularly those 
-of the forbidden [\ion{O}{3}] and [\ion{S}{2}] transitions, provide estimates of 
-a region's electron temperature and number density.  From these two quantities 
-and the emission line fluxes [\ion{O}{2}] $\lambda 3727$, [\ion{O}{3}] 
-$\lambda 4363$, and [\ion{O}{3}] $\lambda \lambda 4959,5007$, we estimate the 
-abundance of oxygen with the Direct $T_e$ method.  We estimate the metallicity 
-of 42 blue, star-forming void dwarf galaxies and 89 blue, star-forming dwarf 
-galaxies in more dense regions using spectroscopic observations from the Sloan 
-Digital Sky Survey Data Release 7, as re-processed in the MPA-JHU value-added 
-catalog.  We find very little difference between the two sets of galaxies, 
-indicating little influence from the large-scale environment on their chemical 
-evolution.  Of particular interest are a number of extremely metal-poor dwarf 
-galaxies that are less prevalent in voids than in the denser regions.
-
-% Paper 2
-We examine how the cosmic environment affects the chemical evolution of galaxies 
-in the universe by comparing the N/O ratio of dwarf galaxies in voids with 
-dwarf galaxies in denser regions.  Ratios of the forbidden [\ion{O}{3}] and 
-[\ion{S}{2}] transitions provide estimates of a region's electron temperature 
-and number density.  We estimate the abundances of oxygen and nitrogen using 
-these temperature and density estimates and the emission-line fluxes 
-[\ion{O}{2}] $\lambda 3727$, [\ion{O}{3}] $\lambda \lambda 4959, 5007$, and 
-[\ion{N}{2}] $\lambda \lambda 6548, 6584$ with the direct $T_e$ method.  Using 
-spectroscopic observations from the Sloan Digital Sky Survey Data Release 7, we 
-are able to estimate the N/O ratio in 42 void dwarf galaxies and 89 dwarf 
-galaxies in denser regions.  The N/O ratio for void dwarfs ($M_r > -17$) is 
-slightly lower ($\sim 12\%$) than for dwarf galaxies in denser regions.   We 
-also estimate the nitrogen and oxygen abundances of 2050 void galaxies and 3883 
-galaxies in denser regions with $M_r > -20$.  These somewhat brighter galaxies 
-(but still fainter than $L_*$) also display similar minor shifts in the N/O 
-ratio.  The shifts in the average and median element abundance values in all 
-absolute magnitude bins studied are in the same direction, suggesting that the 
-large-scale environment may influence the chemical evolution of galaxies.  We 
-discuss possible causes of such a large-scale environmental dependence of the 
-chemical evolution of galaxies, including retarded star formation and a higher 
-ratio of dark matter halo mass to stellar mass in void galaxies.
-
-% Paper 3
+% Papers 1-3
 

### 2017-06-10 KellyDouglass/Thesis/Thesis_sections/Introduction.tex
Finished writing intro

@@
 % What do we already know about the environmental influence?
+Observational studies of void galaxies have included investigation of 
+photometric properties such as luminosity \citep{Hoyle05,Croton05,Moorman15}, 
+color and morphological type \citep{Grogin00,Rojas04,Patiri06,Park07,
+vonBendaBeckmann08,Hoyle12}, star formation rates estimated from optical 
+spectroscopy and UV photometry \citep{Rojas05,Moorman15,Beygu16}, and gas 
+content \citep{Kreckel12,Moorman16,Jones16}.  When compared to galaxies in 
+denser regions, void galaxies are fainter, of late morphological types, bluer, 
+forming stars at higher rates per unit stellar mass, and more gas rich.
 
 % Dwarf galaxies
-
 \begin{figure}
@@
 
-% Galaxy structure
+In particular, we are going to study the effects of the large-scale environment 
+on the formation and evolution of dwarf galaxies.  Defined to be galaxies with 
+absolute magnitudes fainter than -17 ($M_r > -17$), the lower stellar masses of 
+these systems correspond to more shallow gravitational potential wells.  This 
+causes any environmental effects to have a more significant influence on dwarf 
+galaxies than on galaxies with larger stellar masses.  In addition, studying 
+void dwarf galaxies will complement previous studies of dwarfs in groups and 
+clusters because the assembly histories of low-mass galaxies are predicted to 
+be very different \citep[e.g.,][]{Gao07,Lackner12}.  Observations to date also 
+show that the properties of dwarf galaxies vary dramatically with the 
+environment \citep[e.g.,][]{Ann08,Geha12}.
 
@@
 %  - What is the metallicity?  O/H - Why oxygen?  and once we estimate the abundances of each ion, we add them together to get the total abundance for that element
+
+The first stars that formed are thought to have been composed of only hydrogen 
+(and maybe some trace amount of helium).  As stars burn, nucleosythesis creates 
+heavier elements at the core.  When the stars die and expel some or all of their 
+contents, the heavier elements are distributed between the surrounding 
+interstellar gas and the surrounding circumgalactic medium.  When new stars form 
+from this gas, they include both hydrogen and some of the heavier elements.  By 
+measuring the fraction of elements heavier than helium (``metals'') relative to 
+the hydrogen content (the metallicity), we measure the integrated star formation 
+history of the galaxy.
 
@@
     where the gas is re-radiating the light it absorbed from the star.}
+    \label{fig:Kirchoff}
 \end{figure}
+
+We use a galaxy's spectrum to measure various properties of the stellar 
+population and interstellar medium.  A galaxy's spectrum is a superposition of 
+light from the stars and emission lines from the gas.  Depending on our 
+viewpoint of the galaxy's light, we will see a different type of spectrum.  As 
+shown in Fig. \ref{fig:Kirchoff}, if we separate a star's light by its 
+wavelength, we will observe a continuous spectrum, since it is a blackbody.  If 
+instead we observe the starlight after it has passed through a cloud of cooler 
+gas, we will measure an absorption line spectrum; the elements in the gas cloud 
+have absorbed some of the star's light at specific wavelengths corresponding to 
+the particular ions present.  Finally, if we only observe the light emitted from 
+the cool gas cloud, we will measure an emission line spectrum.  The method we 
+employ to estimate the metallicity of a galaxy requires particular emission 
+lines.  We study the gas-phase chemical abundances of \ion{H}{2} regions in a 
+galaxy, where the light is coming from low-density gas partially ionized by UV 
+photons emitted from young, hot stars.  Therefore, we are measuring the 
+abundances of the elements produced in previous generations of stars.
 
@@
     yellow.}
+    \label{fig:spectrum}
 \end{figure}
+
+The ion transitions observed in the optical part of the spectrum (which is where 
+SDSS DR7 operates) consist of forbidden transitions.  As explained in detail in 
+Section \ref{sec:physics}, forbidden transitions have much longer lifetimes than 
+the allowed electron transitions.  These transitions depend strongly on the 
+temperature and density of the electron gas, because the long lifetimes allow 
+the atoms to easily collisionally de-excite.  By taking the ratio of the 
+[\ion{O}{3}] $\lambda$4363 auroral line to the [\ion{O}{3}] 
+$\lambda \lambda$4959,5007 doublet, we can get an estimate of the temperature of 
+the gas.  These lines are highlighted on the example SDSS DR7 spectrum shown in 
+Fig. \ref{fig:spectrum}.
+
+Oxygen is used as a proxy to measure the metallicity of an \ion{H}{2} region, 
+because oxygen is the most abundant element in the universe after hydrogen and 
+helium.  It also has strong emission lines in the visible wavelength range, so 
+it is relatively easy to observe.  Oxygen emission is the most effective cooling 
+source in an \ion{H}{2} region, so lower metallicities correspond to higher 
+temperatures.  There are three main factors which determine the strength of an 
+emission line: the temperature, density, and number of ions in the gas.  It is 
+possible to calculate the number ratios for any of the heavy elements with 
+respect to hydrogen once the electron temperature and density of the 
+interstellar gas are estimated.
 
@@
 these results tell us about the dark matter structure and history of the galaxy.  
+In Chapter \ref{ch:Paper1}, we calculate and compare the metallicity of 135 
+star-forming dwarf galaxies as a function of their large-scale environment.  We 
+continue studying this galaxy sample in Chapter \ref{ch:Paper2} by estimating 
+their ratios of nitrogen to oxygen and looking at how that depends on the 
+large-scale environment.  To expand our dwarf galaxy sample, we derive an 
+approximation for the amount of singly-ionized oxygen and repeat our analysis of 
+the large-scale environmental influence on the gas-phase chemical abundances of 
+1920 star-forming dwarf galaxies in Chapter \ref{ch:Paper3}.  In Chapter 
+\ref{ch:smallScaleEnvironment}, we investigate how the dwarf galaxies' 
+properties depend on the galaxies' distances to the nearest neighbors and 
+groups.  Finally, in an effort to better understand how galaxies evolve from 
+blue, star-forming systems to ``red and dead,'' we discover a way to classify 
+galaxies into their location on the color-magnitude diagram in Chapter 
+\ref{ch:GV}.

### 2017-06-10 KellyDouglass/Thesis/Thesis_sections/Paper1.tex
Finished writing intro

@@
-\chapter[Metallicity of dwarf galaxies]{Determining the large-scale environmental dependence of gas-phase metallicity in dwarf galaxies}
+\chapter[Metallicity of dwarf galaxies]{Determining the large-scale environmental dependence of gas-phase metallicity in dwarf galaxies}\label{ch:Paper1}
 
@@
 morphological type \citep{Grogin00, Rojas04, Patiri06, Park07, 
-vonBendaBeckmann08, Hoyle12} star formation rates estimated from optical 
+vonBendaBeckmann08, Hoyle12}, star formation rates estimated from optical 
 spectroscopy and UV photometry \citep{Rojas05, Moorman15, Beygu16}, and gas 

### 2017-06-10 KellyDouglass/Thesis/Thesis_sections/Paper2.tex
Finished writing intro

@@
-\chapter[N/O ratio in dwarf galaxies]{Large-scale environmental dependence of the abundance ratio of nitrogen to oxygen in blue, star-forming galaxies fainter than $L_*$}
+\chapter[N/O ratio in dwarf galaxies]{Large-scale environmental dependence of the abundance ratio of nitrogen to oxygen in blue, star-forming galaxies fainter than $L_*$}\label{ch:Paper2}
 

### 2017-06-10 KellyDouglass/Thesis/Thesis_sections/Paper3.tex
Beginning of intro written
Finished writing intro

@@
-\chapter{Large-scale environmental dependence of chemical abundances in dwarf galaxies and implications for connecting star formation and halo mass}
+\chapter{Large-scale environmental dependence of chemical abundances in dwarf galaxies and implications for connecting star formation and halo mass}\label{ch:Paper3}
+
+This chapter has been submitted to the \emph{Astrophysical Journal} by Kelly A. 
+Douglass, Michael S. Vogeley, and Renyue Cen; it will be referenced as Douglass 
+et. al (2017).

### 2017-06-10 KellyDouglass/Thesis/preamble.tex
Wrote thesis abstract

@@
 % Papers 1-3
-
+We investigate how the cosmic environment affects galaxy evolution in the 
+Universe by studying gas-phase chemical abundances and other galaxy properties 
+as a function of the local and cosmic density of galaxies.  Using spectroscopic 
+observations from the Sloan Digital Sky Survey Data Release 7, we estimate the 
+oxygen and nitrogen abundances of 993 star-forming void dwarf galaxies and 759 
+star-forming dwarf galaxies in denser regions.  We use the Direct $T_e$ method 
+for calculating the gas-phase chemical abundances in the dwarf galaxies because 
+it is best suited for low metallicity, low mass galaxies.  A substitute for the 
+[\ion{O}{2}] $\lambda$3727 doublet is developed, permitting oxygen abundance 
+estimates of SDSS dwarf galaxies at all redshifts with the Direct $T_e$ method.  
+We find that star-forming void dwarf galaxies have slightly higher oxygen 
+abundances than star-forming dwarf galaxies in denser environments, but we find 
+that void dwarf galaxies have slightly lower nitrogen abundances and lower N/O 
+ratios than galaxies in denser regions.  
 % Small-scale enivronment
-
+At smaller scales, we find that only the presence of a neighboring galaxy within 
+0.05 \hMpc or 0.05$r_{vir}$, or the presence of a group within 0.1 \hMpc, 
+incfluences a dwarf galaxy's evolution.  Dwarf galaxies within 0.05 \hMpc or 
+0.05$r_{vir}$ of another galaxy tend to be bluer, have higher sSFRs, and have 
+higher oxygen and nitrogen abundances than average.  In contrast, galaxies 
+within 0.1 \hMpc of the center of the closest group are redder, have lower 
+oxygen abundances, and have higher N/O ratios than average.
 % GV
+We also investigate how a galaxy transitions through the color-magnitude 
+diagram, evolving from a blue, star-forming spiral or irregular galaxy in the 
+blue sequence to a red elliptical galaxy in the red cloud via the green valley.  
+We discover that combining a galaxy's color, color gradient, and inverse 
+concentration index defines a galaxy's location on the color-magnitude diagram.  
+The results indicate that there is a higher fraction of dwarf galaxies in denser 
+regions than void dwarf galaxies in the green valley.
+% Conclusions
+From these analyses, we surmise that void dwarf galaxies experienced delayed 
+star formation as predicted by the $\Lambda$CDM cosmology and a dependence of 
+the large-scale environment on cosmic downsizing.  We present evidence that void 
+dwarf galaxies have a higher ratio of dark matter halo mass to stellar mass when 
+compared to dwarf galaxies in denser environments.
 

### 2017-06-12 KellyDouglass/Thesis/CV.tex
Updated Intro, Conclusion

@@
 \begin{itemize} %\itemsep -2pt
-	\item ``Large-scale environmental dependence of the abundance ratio of nitrogen to oxygen in blue, star-forming galaxies fainter than $L_*$".
+    \item Douglass, K.A., Vogeley, M.S., \& Cen, R.
+``Large-scale environmental dependence of chemical abundances in dwarf galaxies and implications for connecting star formation and halo mass".
+\href{https://doi.org/}{submitted to ApJ}, 2017
+	\item Douglass, K.A.
+\& Vogeley, M.S.
+``Large-scale environmental dependence of the abundance ratio of nitrogen to oxygen in blue, star-forming galaxies fainter than $L_*$".
 \href{https://doi.org/10.3847/1538-4357/aa5e53}{ApJ, 837: 42--55}, 2017
-	\item ``Determining the large-scale environmental dependence of gas-phase metallicity in dwarf galaxies". \href{https://doi.org/10.3847/1538-4357/834/2/186}{ApJ, 834: 186--198}, 2017
+	\item Douglass, K.A.
+\& Vogeley, M.S.
+``Determining the large-scale environmental dependence of gas-phase metallicity in dwarf galaxies".
+\href{https://doi.org/10.3847/1538-4357/834/2/186}{ApJ, 834: 186--198}, 2017
 \end{itemize}
@@
 \begin{itemize}[noitemsep]
-	\item \textbf{Professor Bob's Hands-On Science} \hfill \textit{June 2015 to August 2016}
-	\item \textbf{Volunteer at the Lynch Observatory} \hfill \textit{September 2011 to July 2017}
+	\item \textbf{Professor Bob's Hands-On Science} \hfill \textit{June 2015 to July 2017}
+	\item \textbf{Volunteer at the Lynch Observatory} \hfill \textit{September 2011 to June 2017}
 \end{itemize}

### 2017-06-12 KellyDouglass/Thesis/DirectMethodPhysics.tex
Added simulations appendix section
Finished writing intro
Added intro figures
Updated Intro, Conclusion

@@
-\chapter{The physics of the Direct $T_e$ method}
+\chapter[Direct method physics]{The physics of the Direct $T_e$ method}\label{sec:physics}
 
@@
 thermalize quickly \citep{DeRobertis87}.  Eventually, the free electron 
-recombines with an H$^+$ ion, forming atomic hydrogen again.  The ions that were 
+recombines with an H$^+$ ion, forming atomic hydrogen.  The ions that are 
 collisionally excited by the electron before its recombination eventually 
@@
 
-\section{Temperatures from the forbidden emission lines}
+%\section{Forbidden transitions}
+%
+%Similar to a fingerprint, every element has a unique set of wavelengths seen in 
+%its spectrum that corresponds to the atom's different energy levels.  Since 
+%electrons within an atom have discrete energy levels, transitions between levels 
+%result in either the emission (when decreasing in energy) or absorption 
+%(an increase in energy) of a photon of the same energy as the difference between 
+%the two levels.  The separation between energy levels is unique for each 
+%element, so the photon energies either emitted or absorbed by each element are 
+%unique.
+%
+%
+%\subsection{Time-dependent perturbation theory}
+%
+%A time-dependent potential is added to the Schr\"{o}dinger equation in order to 
+%solve for the forbidden transition energies.  We can assume that the time 
+%perturbation is a minor component of the potential and can thus treat it as a 
+%perturbation.  For a simplified two-level system, the time-dependent wave 
+%function is
+%\begin{equation}
+%    \Psi (t) = c_a (t) \psi_a e^{iE_a t/\hbar} + c_b (t) \psi (b) e^{-iE_b t/\hbar}
+%\end{equation}
+%To solve for the time-dependent coefficients, we substitute $\Psi (t)$ into the 
+%time-dependent Schr\"{o}dinter equation
+%\begin{equation}
+%    H\Psi = i\hbar \frac{\partial \Psi}{\partial t}, \qquad \text{where} H = H^0 + H'(t)
+%\end{equation}
+%We find that
+%\begin{align}
+%    \dot{c}_a &= -\frac{i}{\hbar} H'_{ab} e^{-i\omega_0 t} c_b\\
+%    \dot{c}_b &= -\frac{i}{\hbar} H'_{ba} e^{-i\omega_0 t} c_a
+%\end{align}
+%where
+%\begin{equation}
+%    \omega_0 \equiv \frac{E_b - E_a}{\hbar}
+%\end{equation}
+%and
+%\begin{equation}
+%    H_{ij} \equiv \langle \psi_i | H' | \psi_j \rangle
+%\end{equation}
+%The probability that transmission has occurred is $P_{b\to a} = |c_a (t)|^2$.  
+%The transmission rate $R_{a\to b} = dP/dt$.
+%
+%For an electromagnetic wave, the atom experiences an oscillating electric field.  
+%For visible light, it is safe to assume that the spatial portion of the field 
+%does not change, since the wavelength is much longer than the size of the atom.  
+%This oscillating field corresponds to our perturbing Hamiltonian:
+%\begin{equation}
+%    H' = -qE_0 z\cos (\omega t)
+%\end{equation}
+%where $q$ is the charge on the electron, and the electric field is oscillating 
+%in the $z$ direction.  Thus,
+%\begin{equation}
+%    H'_{ba} = -pE_0 \cos (\omega t), \qquad \text{where} p \equiv q \langle \psi_b |z| \psi_a \rangle
+%\end{equation}
+%
+%
+%\subsection{Selection rules}
+%
+%The transmission rates depend on a matrix element of the form 
+%$\langle \psi_b |\vec{r}| \psi_a \rangle$.  Denoting the states by the quantum 
+%numbers $n$, $l$, and $m$, the matrix elements can be written as
+%\begin{equation}
+%    \langle n'l'm' |\vec{r}| nlm \rangle
+%\end{equation}
+%By applying the various angular momentum commutators \citep[as shown in][]
+%{Griffiths05}, we can develop a set of selection rules for allowed transitions 
+%of the electron in an atom.
+
+\section[Estimating the temperature]{Temperatures from the forbidden emission lines}
 
@@
 the $^1$D$_2$ and $^1$S$_0$ levels, and $T$ is the electron temperature 
-\cite{Osterbrock89}.  The transition probabilities $A_{i,j}$ do not depend on 
+\citep{Osterbrock89}.  The transition probabilities $A_{i,j}$ do not depend on 
 the temperature, but the collision strength $\Omega (i,j)$ is 

### 2017-06-12 KellyDouglass/Thesis/Thesis_sections/Conclusion.tex
Updated Intro, Conclusion

@@
 the Direct $T_e$ method and spectroscopic line flux measurements as reprocessed 
-in the MPA-JHU catalog \citep[Douglass \& Vogeley 2017, in prep]{Douglass17a,
+in the MPA-JHU catalog \citep[Douglass et al., 2017, in prep]{Douglass17a,
 Douglass17b}.  Due to the minimum redshift limit for detecting the [\ion{O}{2}] 
-$\lambda$3727 emission line in SDSS DR7 spectra, only 135 dwarf galaxies are 
-available for analysis with the Direct $T_e$ method.  With this sample, we 
-initially see no difference in the metallicity (O/H) between dwarf galaxies in 
-voids and in denser regions.  However, upon closer inspection, we find minor 
-shifts in the distributions of gas-phase chemical abundances for void dwarf 
-galaxies when compared to star-forming dwarf galaxies in denser regions: 
-star-forming dwarf galaxies have higher oxygen abundances (O/H), lower nitrogen 
-abundances (N/H), and lower N/O ratios.
+$\lambda$3727 emission line in SDSS DR7 spectra, only 135 star-forming dwarf 
+galaxies are available for analysis with the Direct $T_e$ method.  With this 
+sample, we see no difference in the metallicity (O/H) between dwarf galaxies in 
+voids and denser regions \citep{Douglass17a}.  Upon closer inspection, we find 
+minor shifts in the distributions of gas-phase chemical abundances for void 
+dwarf galaxies when compared to dwarf galaxies in denser regions: star-forming 
+void dwarf galaxies have higher oxygen abundances (O/H), lower nitrogen 
+abundances (N/H), and lower N/O ratios \citep{Douglass17b}.
 
@@
 abundance in star-forming galaxies, we can expand our sample to consist of 1920 
-star-forming galaxies by removing the dependence on the [\ion{O}{2}] 
+star-forming dwarf galaxies by removing the dependence on the [\ion{O}{2}] 
 $\lambda$3727 doublet.  This larger sample exhibits the same shifts in the 
@@
 also investigate if and how the large-scale environment affects relationships 
-between the chemical abundances and various other physical parameters of the 
-galaxies.  We find that all of our galaxies reside on the ``nitrogen plateau'' 
-in the relationship between N/O and O/H, where the N/O ratio is predicted to be 
-independent of metallicities \OH $< 8.5$.  However, instead of a constant value 
-for the N/O ratio, we instead find that the N/O ratio decreases with increasing 
-metallicity.  This is contrary to what we see in the N/O-$M_*$ relationship, 
-where we find that some of the star-forming dwarf galaxies have a constant value 
-of N/O for a range of masses while the remainder exhibit a positive relationship 
-between the stellar mass and N/O ratio.  We make note of a different critical 
-mass in the N/O-$M_*$ relationship in the two environments, where the void dwarf 
-galaxies begin to show evidence of secondary nitrogen synthesis at a stellar 
-mass $\sim 0.4\text{ dex}$ lower than for the galaxies in denser regions.  Most 
-of our star-forming dwarf galaxies follow the established mass-metallicity 
-relation \citep[e.g.,][]{Tremonti04}.
+between the chemical abundances and various other physical properties of the 
+galaxies.  We find that the N/O ratio decreases with increasing metallicity 
+rather than a constant value for the N/O ratio as a function of O/H as observed 
+in other studies.  This is contrary to what we see in the $M_*$-N/O 
+relationship, where we find that some of the star-forming dwarf galaxies have a 
+constant value of N/O for a range of masses while the remainder exhibit a 
+positive relationship between the stellar mass and N/O ratio.  We make note of a 
+different critical mass in the $M_*$-N/O relationship in the two environments, 
+where the void dwarf galaxies begin to show evidence of secondary nitrogen 
+synthesis at a stellar mass $\sim$0.4 dex lower than for the galaxies in denser 
+regions.  Most of our star-forming dwarf galaxies follow the established 
+mass-metallicity relation \citep[e.g.,][]{Tremonti04}.
 
 No relationship is observed between the metallicity and \ion{H}{1} mass in our 
-sample of star-forming dwarf galaxies, but we do find that the N/O ratio 
-decreases with increasing \ion{H}{1} mass for a given stellar mass.  The 
-star-forming dwarf galaxies also exhibit an increase in the metallicity and 
-N/O ratio with increasing color (both $u-r$ and $g-r$).  We see very little 
-correlation with SFR for either metallicity or the N/O ratio in dwarf galaxies, 
-but the metallicity and N/O ratio decrease with increasing sSFR.  Beyond the 
-large-scale environmental influence on the distributions of the gas-phase 
-chemical abundances and the critical mass in the N/O-$M_*$ relationship, we do 
-not observe any significant differences between the star-forming void and wall 
-dwarf galaxies in any of these relationships.
+sample of star-forming dwarf galaxies, but we find that the N/O ratio decreases 
+with increasing \ion{H}{1} mass for a given stellar mass.  The star-forming 
+dwarf galaxies also exhibit an increase in the metallicity and N/O ratio with 
+increasing color (both $u-r$ and $g-r$).  We see very little correlation with 
+SFR for either metallicity or the N/O ratio in dwarf galaxies, but the 
+metallicity and N/O ratio decrease with increasing sSFR.  Beyond the large-scale 
+environmental influence on the distributions of the gas-phase chemical 
+abundances and the critical mass in the $M_*$-N/O relationship, we do not 
+observe any significant differences between the star-forming void and wall dwarf 
+galaxies in any of these relationships.
 
@@
 then they would be able to commence secondary nitrogen synthesis earlier, as 
-seen in the N/O-$M_*$ relation in Fig. \ref{fig:M_NO}.  In addition, the shift 
+seen in the $M_*$-N/O relation in Fig. \ref{fig:M_NO}.  In addition, the shift 
 towards lower N/O ratios in the star-forming dwarf galaxies might be evidence 
@@
 0.05 \hMpc or 0.05$r_{vir}$ are bluer, have a higher sSFR, and have higher 
-oxygen and nitrogen abundances than average.  In contrast, dwarf galaxies within 
-0.1 \hMpc of the center of the closest group are redder, have lower oxygen 
-abundances, and have higher N/O ratios than average.  These results are 
-independent of the maximum relative velocity required to define a nearest 
-neighbor and the sample (star-forming versus all dwarf galaxies).
+oxygen and nitrogen abundances than average.  This matches the results of 
+\cite{Park09}, who find that late-late type galaxy pairs within 0.05$r_{vir}$ 
+are bluer and have higher SFRs.  In contrast, dwarf galaxies within 0.1 \hMpc of 
+the center of the closest group are redder, have lower oxygen abundances, and 
+have higher N/O ratios than average.  These results are independent of both the 
+maximum relative velocity required to define a nearest neighbor and the sample 
+(star-forming versus all dwarf galaxies).
 
@@
 the galaxies within 0.05$r_{vir}$ are most likely strongly interacting or 
-merging with their nearest neighbor.  This matches the results of \cite{Park09}, 
-who find that late-late type galaxy pairs within 0.05$r_{vir}$ are bluer and 
-have higher SFRs.  These merging galaxies likely share the same dark matter 
-halo, indicating that the dark matter halo is more influential on a galaxy's 
-evolution than the galaxy's distance to the nearest neighbor.
+merging with their nearest neighbor.  These merging galaxies likely share the 
+same dark matter halo, suggesting that the dark matter halo is more influential 
+on a galaxy's evolution than the distance between a galaxy and its nearest 
+neighbor.
 
@@
 Finally, we also investigate the properties of galaxies residing in the green 
-valley of the color-magnitude diagram (CMD), in an effort to understand the role 
+valley of the color-magnitude diagram (CMD) in an effort to understand the role 
 of the environment on a galaxy's evolution through the color-magnitude diagram.  
@@
 green valley of the CMD by combining the galaxy's color, color gradient, and 
-inverse concentration index.  Galaxies with a magnitude less than 25 for the 
+inverse concentration index.  Galaxies with a value less than 25 for the 
 morphological type as calculated in the KIAS-VAGC exist in the green valley 
@@
 crucial to understanding the evolution of galaxies.  Understanding how the 
-presence of an AGN affects a galaxy's evolution is currently limited --- most 
-research at the moment is concentrated on the physics within an AGN.  Many 
+presence of an AGN affects a galaxy's evolution is currently limited --- at the 
+moment, most research is concentrated on the physics within an AGN.  Many 
 simulations have been done to test different theories about the role of an AGN 

### 2017-06-12 KellyDouglass/Thesis/Thesis_sections/Introduction.tex
Added intro figures
Updated Intro, Conclusion

@@
 \begin{figure}
-%    \includegraphics[width=0.9\textwidth]{Images/Intro/Millenium_simulation}
+    \includegraphics[width=0.9\textwidth]{Images/Intro/Millenium_simulation}
     \caption[Dark matter simulation]{Snapshots of a portion of the Millenium 
@@
 Large sky surveys \citep[such as the Sloan Digital Sky Survey --- 
-SDSS][]{York00} have revealed a non-uniform distribution of galaxies throughout 
-the universe.  Taking on a shape similar to that of a three-dimensional cosmic 
-web \citep{Bond96} or a sponge, galaxies clump together in clusters and along 
-filaments, leaving void regions between them.  Evidence of this distribution can 
-be seen in Fig. \ref{fig:SDSS_map} for galaxies in the SDSS Data Release 7 
-\citep[SDSS DR7][]{Abazajian09}.  Based on these observations, dark matter 
-simulations have been constructed which successfully reproduce the same 
-large-scale structure.  If we start with a mostly uniform distribution of dark 
-matter at the Big Bang, Fig. \ref{fig:DMsim} outlines the evolution of that dark 
-matter up to present day.  These snapshots from the Millenium Simulation project 
-\citep{Springel05} show that small perturbations in the initial distribution of 
-dark matter are amplified as the universe expands.  Gravity causes the slightly 
-overdense regions to collapse while simultaneously causing the underdense 
-regions to expand.  Due to dark matter's strong gravitational interaction, we 
-believe that the baryonic mattter (that which interacts electromagnetically) 
-will trace the dark matter distribution, resulting in the galaxy distribution we 
-observe today.
+SDSS;][]{York00} have revealed a non-uniform distribution of galaxies throughout 
+the universe.  Taking on a shape similar to that of a sponge or a 
+three-dimensional cosmic web \citep{Bond96}, galaxies clump together in clusters 
+and along filaments, leaving void regions between these large-scale structures.  
+Evidence of this distribution can be seen in Fig. \ref{fig:SDSS_map} for 
+galaxies in the SDSS Data Release 7 \citep[SDSS DR7;][]{Abazajian09}.  Based on 
+these observations, dark matter simulations have been constructed which 
+successfully reproduce the same large-scale structure.  If we start with a 
+mostly uniform distribution of dark matter at the Big Bang, Fig. \ref{fig:DMsim} 
+outlines the evolution of that dark matter up through the present.  These 
+snapshots from the Millenium Simulation project \citep{Springel05} show that 
+small perturbations in the initial distribution of dark matter are amplified as 
+the universe expands.  Gravity causes the slightly overdense regions to collapse 
+while simultaneously causing the underdense regions to expand.  Due to dark 
+matter's strong gravitational interaction, we believe that the baryonic mattter 
+(matter which interacts electromagnetically) will trace the dark matter 
+distribution, resulting in the galaxy distribution we observe today.
 
@@
 \begin{figure}
-%    \includegraphics[width=0.9\textwidth]{Images/Intro/void_slice}
+    \includegraphics[width=0.9\textwidth]{Images/Intro/VoidFinder}
     \caption[Sky map highlighting voids and void galaxies]{A 10 \hMpc slice of 
@@
 
-The galaxies within the underdense void environments are named ``void 
-galaxies.''  Existing in the cosmological voids, void galaxies are thought to 
-demonstrate the fundamental characteristics of galactic evolution.  Cosmic voids 
-are an important environment for studying galaxy formation \citep[see][for a 
-review]{vandeWeygaert11}.  Gravitational clustering proceeds as if in a very low 
+Existing in the cosmological voids, void galaxies are thought to demonstrate the 
+fundamental characteristics of galactic evolution.  Cosmic voids are an 
+important environment for studying galaxy formation \citep[see][for a review]
+{vandeWeygaert11}.  Gravitational clustering proceeds as if in a very low 
 density universe, where the amassment of gravitationally bound dark matter halos 
@@
 Additionally, hydrodynamical cosmological simulations by \cite{Cen11} show that 
-the gas in voids remains below the critical entropy threshold, allowing void 
-galaxies to continue to form stars.  Void galaxies evolve in a relatively 
-pristine environment where interactions are rare and star formation proceeds up 
-to the present epoch because void galaxies are able to retain their gas.  This 
+void galaxies continue to form stars because the gas in voids remains below the 
+critical entropy threshold.  Void galaxies evolve in a relatively pristine 
+environment where interactions are rare and star formation proceeds up to the 
+present epoch because void galaxies are able to retain their gas.  This 
 contrasts the denser environments, where the chemical composition and evolution 
-of galaxies are drastically altered due to mergers and tidal stripping and/or 
-ram-pressure stripping.
+of galaxies are drastically altered due to mergers and tidal and/or ram-pressure 
+stripping.
 
@@
     an absolute magnitude $M_r \approx -20$.}
+    \label{fig:Mr_SDSS}
 \end{figure}
 
-In particular, we are going to study the effects of the large-scale environment 
-on the formation and evolution of dwarf galaxies.  Defined to be galaxies with 
-absolute magnitudes fainter than -17 ($M_r > -17$), the lower stellar masses of 
-these systems correspond to more shallow gravitational potential wells.  This 
-causes any environmental effects to have a more significant influence on dwarf 
-galaxies than on galaxies with larger stellar masses.  In addition, studying 
-void dwarf galaxies will complement previous studies of dwarfs in groups and 
-clusters because the assembly histories of low-mass galaxies are predicted to 
-be very different \citep[e.g.,][]{Gao07,Lackner12}.  Observations to date also 
-show that the properties of dwarf galaxies vary dramatically with the 
-environment \citep[e.g.,][]{Ann08,Geha12}.
+In particular, we study the effects of the large-scale environment on the 
+formation and evolution of dwarf galaxies.  Fig. \ref{fig:Mr_SDSS} shows the 
+distribution of galaxies by their absolute magnitudes detected in SDSS DR7.  
+Defined to be galaxies with absolute magnitudes fainter than -17 ($M_r > -17$), 
+the low stellar masses of these systems correspond to more shallow gravitational 
+potential wells.  This causes any environmental effects to have a more 
+significant influence on dwarf galaxies than on galaxies with larger stellar 
+masses.  In addition, studying void dwarf galaxies will complement previous 
+studies of dwarfs in groups and clusters because the assembly histories of 
+low-mass galaxies are predicted to be very different \citep[e.g.,][]{Gao07,
+Lackner12}.  Observations to date also show that the properties of dwarf 
+galaxies vary dramatically with the environment \citep[e.g.,][]{Ann08,Geha12}.
 
@@
 The first stars that formed are thought to have been composed of only hydrogen 
-(and maybe some trace amount of helium).  As stars burn, nucleosythesis creates 
-heavier elements at the core.  When the stars die and expel some or all of their 
-contents, the heavier elements are distributed between the surrounding 
-interstellar gas and the surrounding circumgalactic medium.  When new stars form 
-from this gas, they include both hydrogen and some of the heavier elements.  By 
-measuring the fraction of elements heavier than helium (``metals'') relative to 
-the hydrogen content (the metallicity), we measure the integrated star formation 
-history of the galaxy.
+(and possibly some trace amount of helium).  As stars burn, nucleosythesis 
+creates heavier elements at the core.  When the stars die and expel their 
+content, the heavier elements are distributed between the surrounding 
+interstellar gas and circumgalactic medium.  When new stars form from this gas, 
+they include both hydrogen and some of the heavier elements.  By measuring the 
+fraction of elements heavier than helium (``metals'') relative to the hydrogen 
+content (the metallicity), we measure the integrated star formation history of 
+the galaxy.
 
@@
     present in the gas).  If observed off the line-of-sight of the star, the 
-    light emitted from the cloud of cooler gas is named an emission spectrum, 
+    light emitted from the cloud of cooler gas results in an emission spectrum, 
     where the gas is re-radiating the light it absorbed from the star.}
@@
 \begin{figure}
-%    \includegraphics[width=0.9\textwidth]{Images/Intro/spectrum}
+    \includegraphics[width=0.9\textwidth]{Images/Intro/spectrum}
     \caption[Sample (void) dwarf galaxy spectrum]{Example SDSS DR7 spectrum --- 
@@
 
-The ion transitions observed in the optical part of the spectrum (which is where 
-SDSS DR7 operates) consist of forbidden transitions.  As explained in detail in 
-Section \ref{sec:physics}, forbidden transitions have much longer lifetimes than 
-the allowed electron transitions.  These transitions depend strongly on the 
+The ion transitions observed in the optical part of the spectrum (where SDSS DR7 
+operates) consist of forbidden transitions.  As explained in detail in Section 
+\ref{sec:physics}, forbidden transitions have much longer lifetimes than the 
+allowed electron transitions.  These transitions depend strongly on the 
 temperature and density of the electron gas, because the long lifetimes allow 
@@
 % Pose the problem - how does the large-scale environment affect galaxy evolution?
-We want to understand how dark matter affects the evolution of a galaxy, and 
-what influence it has on a galaxy's star formation.  To do this, we compare the 
+We want to understand how dark matter affects the evolution of a galaxy and what 
+influence it has on a galaxy's star formation.  To do this, we compare the 
 properties of galaxies living in voids with galaxies in denser regions in an 

### 2017-06-12 KellyDouglass/Thesis/preamble.tex
Updated Intro, Conclusion

@@
 0.05 \hMpc or 0.05$r_{vir}$, or the presence of a group within 0.1 \hMpc, 
-incfluences a dwarf galaxy's evolution.  Dwarf galaxies within 0.05 \hMpc or 
+influences a dwarf galaxy's evolution.  Dwarf galaxies within 0.05 \hMpc or 
 0.05$r_{vir}$ of another galaxy tend to be bluer, have higher sSFRs, and have 
@@
 diagram, evolving from a blue, star-forming spiral or irregular galaxy in the 
-blue sequence to a red elliptical galaxy in the red cloud via the green valley.  
-We discover that combining a galaxy's color, color gradient, and inverse 
-concentration index defines a galaxy's location on the color-magnitude diagram.  
-The results indicate that there is a higher fraction of dwarf galaxies in denser 
-regions than void dwarf galaxies in the green valley.
+blue sequence to a red elliptical galaxy in the red cloud through the green 
+valley.  We discover that combining a galaxy's color, color gradient, and 
+inverse concentration index defines a galaxy's location on the color-magnitude 
+diagram.  The results indicate that there is a higher fraction of dwarf galaxies 
+in denser regions than void dwarf galaxies in the green valley.
 % Conclusions
-From these analyses, we surmise that void dwarf galaxies experienced delayed 
-star formation as predicted by the $\Lambda$CDM cosmology and a dependence of 
-the large-scale environment on cosmic downsizing.  We present evidence that void 
+From these analyses, we surmise that void dwarf galaxies experience delayed star 
+formation as predicted by the $\Lambda$CDM cosmology and a dependence of the 
+large-scale environment on cosmic downsizing.  We present evidence that void 
 dwarf galaxies have a higher ratio of dark matter halo mass to stellar mass when 

### 2017-06-12 KellyDouglass/Thesis/simulations.tex
Updated Intro, Conclusion

@@
 It is impossible to directly observe the formation of a galaxy.  Based on 
-detected merging galaxies, the astronomical community has surmised the galaxies 
+detected merging galaxies, the astronomical community has surmised that galaxies 
 have increased their mass largely due to the merging of smaller galaxies.  
-\cite{deRossi07} performed $\Lambda$CDM simulations of hierarchical galaxy 
-formation.  They find that the growth of systems by aggregation is responsible 
-for the mass-metallicity relation.  Less massive systems tend to increase their 
-stellar mass by either gas-rich mergers or secular evolution, resulting in a 
-stronger correlation between stellar mass and metallicity.  Evidence of this is 
-seen in the mass-metallicity relation of \cite{Tremonti04}, where there is 
-little relationship between stellar mass and the metallicity for massive 
-systems, but at intermediate and lower masses the correlation is strong between 
-the two quantities.
+$\Lambda$CDM simulations of hierarchical galaxy formation by \cite{deRossi07} 
+find that the growth of systems by aggregation is responsible for the 
+mass-metallicity relation.  Less massive systems tend to increase their stellar 
+mass by either gas-rich mergers or secular evolution, resulting in a stronger 
+correlation between stellar mass and metallicity.  Evidence of this is seen in 
+the mass-metallicity relation of \cite{Tremonti04}, where there is little 
+relationship between stellar mass and the metallicity for massive systems, but 
+at intermediate and lower masses the correlation is strong between the two 
+quantities.
 
@@
 are not yet well understood.  This is especially important when studying dwarf 
-galaxies, since their gravitational potential wells are potentially small enough 
-to be strongly influenced by star formation and/or supernovae.  Simulations by 
+galaxies, since their gravitational potential wells may be shallow enough to be 
+strongly influenced by star formation and/or supernovae.  Simulations by 
 \cite{Marcolini04} find that when ram pressure from the intergalactic medium 
@@
 % Metallicity
-In numerical simulations to study the properties of the ISM in an isolated, 
-star-forming galaxy, \cite{Hu16} finds that stellar feedback slowly increases 
-the disc metallicity.  The majority of outflows are enriched winds, which 
-reduces the metallicity of the ISM.  \cite{Muratov17} finds that outflows to the 
-CGM generated in dwarf galaxies at low redshifts are dominated by metal-poor 
-gas.  Galaxies retain most of the metals they produce, though a large fraction 
-is in the CGM.  By combining our observations with the results of these 
-simulations, we can begin to understand how star formation and supernovae 
-influence a dwarf galaxy's gas content.
+Numerical simulations that study the properties of the ISM in an isolated, 
+star-forming galaxy find that stellar feedback slowly increases the disc 
+metallicity \citep{Hu16}.  The majority of outflows are enriched winds, which 
+reduces the metallicity of the ISM.  In dwarf galaxies at low redshifts, these 
+outflows to the CGM are dominated by metal-poor gas \citep{Muratov17}.  While 
+galaxies retain most of the metals they produce, a large fraction is in the CGM.  
+By combining our observations with the results of these simulations, we can 
+begin to understand how star formation and supernovae influence a dwarf galaxy's 
+gas content.
 

### 2017-06-13 KellyDouglass/Thesis/DirectMethodPhysics.tex
Updated Appendix A

--- 2017-06-06 KellyDouglass/Thesis/DirectMethodPhysics.tex
@@
 
-\section{Temperatures from the forbidden emission lines}
+\section{Forbidden transitions}
+
+Similar to a fingerprint, every element has a unique set of wavelengths seen in 
+its spectrum that corresponds to the atom's different energy levels.  Since 
+electrons within an atom have discrete energy levels, transitions between levels 
+result in either the emission (when decreasing in energy) or absorption 
+(an increase in energy) of a photon of the same energy as the difference between 
+the two levels.  The separation between energy levels is unique for each 
+element, so the photon energies either emitted or absorbed by each element are 
+unique.
+
+\subsection{Time-dependent perturbation theory}
+
+A time-dependent potential is added to the Schr\"{o}dinger equation in order to 
+solve for the forbidden transition energies.  We can assume that the time 
+perturbation is a minor component of the potential and can thus treat it as a 
+perturbation.  For a simplified two-level system, the time-dependent wave 
+function is
+\begin{equation}
+    \Psi (t) = c_a (t) \psi_a e^{iE_a t/\hbar} + c_b (t) \psi (b) e^{-iE_b t/\hbar}
+\end{equation}
+To solve for the time-dependent coefficients, we substitute $\Psi (t)$ into the 
+time-dependent Schr\"{o}dinter equation
+\begin{equation}
+    H\Psi = i\hbar \frac{\partial \Psi}{\partial t}, \qquad \text{where } H = H^0 + H'(t)
+\end{equation}
+We find that
+\begin{align}
+    \dot{c}_a &= -\frac{i}{\hbar} H'_{ab} e^{-i\omega_0 t} c_b\\
+    \dot{c}_b &= -\frac{i}{\hbar} H'_{ba} e^{-i\omega_0 t} c_a
+\end{align}
+where
+\begin{equation}
+    \omega_0 \equiv \frac{E_b - E_a}{\hbar}
+\end{equation}
+and
+\begin{equation}
+    H_{ij} \equiv \langle \psi_i | H' | \psi_j \rangle
+\end{equation}
+The probability that transmission has occurred is $P_{b\to a} = |c_a (t)|^2$.  
+The transmission rate $R_{a\to b} = dP/dt$.
+
+For an electromagnetic wave, the atom experiences an oscillating electric field.  
+For visible light, it is typically safe to assume that the spatial portion of 
+the field does not change, since the wavelength is much longer than the size of 
+the atom.  However, if we consider a spatial variation of the field, we find 
+that the true electric field is
+\begin{equation}
+    \vec{E}(\vec{r},t) = \vec{E}_0 \cos (\vec{k}\cdot \vec{r} - \omega t)
+\end{equation}
+Expanding this to first order, we find that
+\begin{equation}
+    \vec{E}(\vec{r},t) = \vec{E}_0 [\cos (\omega t) + (\vec{k} \cdot \vec{r} \sin (\omega t)]
+\end{equation}
+The first term in this approximation represents the electric dipole transitions 
+(the canonical electron transitions).  The second term leads to forbidden 
+transitions (magnetic dipole and electric quadrupole).
+%This oscillating field corresponds to our perturbing Hamiltonian:
+%\begin{equation}
+%    H' = -qE_0 z\cos (\omega t)
+%\end{equation}
+%where $q$ is the charge on the electron, and the electric field is oscillating 
+%in the $z$ direction.  Thus,
+%\begin{equation}
+%    H'_{ba} = -pE_0 \cos (\omega t), \qquad \text{where } p \equiv q \langle \psi_b |z| \psi_a \rangle
+%\end{equation}
+
+%\subsection{Forbidden transitions --- metastable energy levels}
+
+%\subsection{Selection rules}
+%
+%The transmission rates depend on a matrix element of the form 
+%$\langle \psi_b |\vec{r}| \psi_a \rangle$.  Denoting the states by the quantum 
+%numbers $n$, $l$, and $m$, the matrix elements can be written as
+%\begin{equation}\label{eq:matrix_elements}
+%    \langle n'l'm' |\vec{r}| nlm \rangle
+%\end{equation}
+%By applying the various angular momentum commutators \citep[as shown in][]
+%{Griffiths05}, we can develop a set of selection rules for allowed transitions 
+%of the electron in an atom.
+%
+%Inserting the commutation relation $[L_z, z] = 0$ into Eqn. 
+%\ref{eq:matrix_elements}, we find that
+%\begin{align}
+%    0 &= \langle n'l'm'|[L_z, z]|nlm \rangle\\
+%    &= \langle n'l'm'|(L_z z - zL_z)|nlm \rangle\\
+%    &= \langle n'l'm'|(m'\hbar)z - z(m\hbar)|nlm \rangle\\
+%    0 &= (m' - m)\hbar \langle n'l'm'|z|nlm \rangle
+%\end{align}
+%$\langle n'l'm'|z|nlm \rangle = 0$ is a boring result, so we find that
+%\begin{equation}\label{eq:m'=m}
+%    m' = m
+%\end{equation}
+%
+%Likewise, by employing the relation $[L_z, x] = i\hbar y$, we find that
+%\begin{equation}\label{eq:Lz_x}
+%    (m' - m)\hbar \langle n'l'm'|x|nlm \rangle = i\hbar \langle n'l'm'|y|nlm \rangle
+%\end{equation}
+%With the relation $[L_z, y] = -i\hbar x$, we find that
+%\begin{equation}\label{eq:Lz_y}
+%    (m' - m)\hbar \langle n'l'm'|y|nlm \rangle = -i\hbar \langle n'l'm'|x|nlm \rangle
+%\end{equation}
+%Combining Eqns. \ref{eq:Lz_x} and \ref{eq:Lz_y} (and again, ignoring the boring 
+%result), we find that
+%\begin{equation}\label{eq:m'=+/-m}
+%    (m' - m)^2 = 1
+%\end{equation}
+%Eqns. \ref{eq:m'=m} and \ref{eq:m'=+/-m} show that transitions will only occur 
+%if $\Delta m = \pm 1,0$.
+
+\section[Estimating the temperature]{Temperatures from the forbidden emission lines}
 
@@
 \end{equation}
-where $j_\lambda$ is the emissivity of the emission line, $\Omega (i,j)$ is the 
+where
+\begin{equation}
+    \bar{\nu}(^3\text{P}, ^1\text{D}) = \frac{A_{^1\text{D}_2, ^3\text{P}_2}\nu (\lambda 5007) + A_{^1\text{D}_2, ^3\text{P}_1}\nu (\lambda 4959)}{A_{^1\text{D}_2, ^3\text{P}_2} + A_{^1\text{D}_2, ^3\text{P}_1}}
+\end{equation}
+and $j_\lambda$ is the emissivity of the emission line, $\Omega (i,j)$ is the 
 collision strength between levels $i$ and $j$, $A_{i,j}$ is the radiative 
@@
 \end{equation}
-By measuring the flux of these emission lines, we can then solve for the 
+Fig. \ref{fig:OIII_temp} shows how this ratio depends on the temperature.  By 
+measuring the flux of these emission lines, we can then solve for the 
 temperature of the gas.
 
-%\section{[\ion{O}{3}]}
-%
-%There are three significant emission lines for doubly-ionized oxygen.  The 
-%relative excitation rates to the $^1$S and $^1$D energy levels depend very 
-%strongly on the electron temperature, $T_e$; therefore, the relative strengths 
-%of these emitted lines can be used to measure the electron temperature 
-%\citep{Osterbrock89}.  In the low-density limit $(n_e < 10^5 \text{ cm}^{-3})$, 
-%most excitations to the $^1$D level result in an emission of a photon with a 
-%wavelength of either $5007\text{\AA}$ or $4959\text{\AA}$, as shown in Fig. 
-%\ref{fig:transitions_P1}.  Most excitations up to $^1$S produce a photon of 
-%wavelength $4363\text{\AA}$, followed by a photon of either of the two previous 
-%wavelengths (since the electron is now in the $^1$D level).
-%
-%At higher densities, collisional de-excitation begins to influence these 
-%emission rates \citep{Osterbrock89}.  Because the $^1$D level has a longer 
-%lifetime than the $^1$S state, it is collisionally de-excited at lower electron 
-%densities.  This weakens the $\lambda 4959$ and $\lambda 5007$ emission lines.  
-%At the same time, the additional collisional excitations of the $^1$D state 
-%permitted by the higher electron densities strengthen the $\lambda 4363$ 
-%emission line.
-%
-%[\ion{O}{3}] $\lambda 4363$ is a temperature-sensitive forbidden transition line 
-%of doubly-ionized oxygen that is the preferred line to use when measuring the 
-%metallicity of galaxies.  Since the most effective cooling channel in \ion{H}{2} 
-%regions is oxygen line emission, lower metallicity regions have higher 
-%temperatures \citep{Saintonge07}.  Collisional excitations up to this energy 
-%level are more common at higher temperatures, since there are more electrons 
-%with the kinetic energy required to excite the O$^{++}$ ion to this energy 
-%level.  As a result, the line strength of [\ion{O}{3}] $\lambda 4363$ correlates 
-%with the region's temperature and is therefore anticorrelated with the 
-%metallicity of the galaxy.
-
-%\section{[\ion{N}{2}]}
-%
-%The energy-level diagram for the various transitions of [\ion{N}{2}] is very 
-%similar to that of [\ion{O}{3}], since they have the same electron ground-state 
-%configuration ((1s)$^2$(2s)$^2$(2p)$^2$).  The similarities can be seen in Fig. 
-%\ref{fig:transitions_P2}.  Therefore, an estimate of the electron temperature can 
-%be made from the [\ion{N}{2}] $\lambda 5755$ emission line.  However, this line 
-%is weaker than the [\ion{O}{3}] $\lambda 4363$ auroral line (since there is less 
-%N than O in galaxies), so we use the [\ion{O}{3}] auroral line for our 
-%temperature estimates, as in Paper I.  After obtaining a temperature and density 
-%estimate, we use the [\ion{N}{2}] $\lambda \lambda 6548, 6584$ doublet to 
-%estimate the abundance of singly ionized nitrogen in a galaxy.
+\begin{figure}
+    \includegraphics[width=0.75\textwidth]{Images/Appendix/[OIII]}
+    \caption[{[\ion{O}{3}] ratio as a function of temperature}]{The [\ion{O}{3}] 
+    $\lambda$4363/($\lambda$4959 + $\lambda$5007) ratio as a function of 
+    temperature for various densities \citep{Luridiana15}.  Typical electron 
+    densities in \ion{H}{2} regions are $\sim$100 cm$^{-3}$.}
+    \label{fig:OIII_temp}
+\end{figure}
 
@@
 described by a Boltzmann population ratio.  There is a critical density for the 
-energy levels which describes the turning point between these two extremes.
+energy levels which describes the turning point between these two extremes.  A 
+graphical representation of this ratio as a function of density can be seen in 
+Fig. \ref{fig:SII_den}.
+
+\begin{figure}
+    \includegraphics[width=0.75\textwidth]{Images/Appendix/[SII]}
+    \caption[{[\ion{S}{2}] ratio as a function of density}]{The [\ion{S}{2}] 
+    $\lambda$6731/$\lambda$6717 ratio as a function of density for various 
+    temperatures \citep{Luridiana15}.  The gas temperatures of \ion{H}{2} 
+    regions are typically around 10$^4$ K.}
+    \label{fig:SII_den}
+\end{figure}

### 2017-06-15 KellyDouglass/Thesis/DirectMethodPhysics.tex
Edits to Abstract, Intro, Appendix

@@
 
-UV photons from young stars in an \ion{H}{2} region keep the interstellar gas 
-partially ionized.  In an \ion{H}{2} region, a photon with an energy 
+The Direct $T_e$ method is used to calculate the gas-phase chemical abundances 
+(oxygen, nitrogen, etc. relative to hydrogen) in \ion{H}{2} regions.  It differs 
+from other commonly-used methods by estimating the gas temperature and electron 
+density of the region directly from the galaxy's spectrum.  UV photons from 
+young stars in an \ion{H}{2} region keep the interstellar gas partially ionized.  
+In an \ion{H}{2} region, a photon with an energy 
 $E_\gamma \gtrsim 13.6\text{ eV}$ ionizes a hydrogen atom, producing an H$^+$ 
@@
 graphical representation of this ratio as a function of density can be seen in 
-Fig. \ref{fig:SII_den}.
+Fig. \ref{fig:SII_den}.  \ion{H}{2} regions typically have densities well within 
+the low-density regime, so we set the electron density for all our galaxies at 
+100 cm$^{-3}$.
 

### 2017-06-15 KellyDouglass/Thesis/Thesis_sections/Introduction.tex
Edits to Abstract, Intro, Appendix

@@
     \includegraphics[width=0.65\textwidth]{Images/Intro/sdss}
-    \caption[SDSS galaxy map]{A slice through the SDSS galaxy distribution; each 
+    \caption[SDSS galaxy map]{A slice through the SDSS galaxy 
+    distribution\footnote{\url{http://www.sdss.org/science/orangepie/}}; each 
     point on this plot is a galaxy.  Large sky surveys such as SDSS have 
@@
     \caption[Dark matter simulation]{Snapshots of a portion of the Millenium 
-    Simulation showing the dark matter distribution at different points in time 
-    from 0.21 Gyr after the Big Bang to the present.  Small perturbations in the 
-    initial distribution of dark matter are amplified as the universe expands.  
-    Gravity causes the slightly overdense regions to contract while 
-    simultaneously causing the underdense regions to expand.}
+    Simulation\footnote{\url{https://wwwmpa.mpa-garching.mpg.de/galform/virgo/millennium/}} 
+    showing the dark matter distribution at different points in time from 0.21 
+    Gyr after the Big Bang to the present.  Small perturbations in the initial 
+    distribution of dark matter are amplified as the universe expands.  Gravity 
+    causes the slightly overdense regions to contract while simultaneously 
+    causing the underdense regions to expand.}
     \label{fig:DMsim}
@@
 
-Large sky surveys \citep[such as the Sloan Digital Sky Survey --- 
-SDSS;][]{York00} have revealed a non-uniform distribution of galaxies throughout 
-the universe.  Taking on a shape similar to that of a sponge or a 
-three-dimensional cosmic web \citep{Bond96}, galaxies clump together in clusters 
-and along filaments, leaving void regions between these large-scale structures.  
-Evidence of this distribution can be seen in Fig. \ref{fig:SDSS_map} for 
-galaxies in the SDSS Data Release 7 \citep[SDSS DR7;][]{Abazajian09}.  Based on 
-these observations, dark matter simulations have been constructed which 
-successfully reproduce the same large-scale structure.  If we start with a 
-mostly uniform distribution of dark matter at the Big Bang, Fig. \ref{fig:DMsim} 
-outlines the evolution of that dark matter up through the present.  These 
-snapshots from the Millenium Simulation project \citep{Springel05} show that 
-small perturbations in the initial distribution of dark matter are amplified as 
-the universe expands.  Gravity causes the slightly overdense regions to collapse 
-while simultaneously causing the underdense regions to expand.  Due to dark 
-matter's strong gravitational interaction, we believe that the baryonic mattter 
-(matter which interacts electromagnetically) will trace the dark matter 
-distribution, resulting in the galaxy distribution we observe today.
+Large galaxy surveys such as the Sloan Digital Sky Survey \citep[SDSS;][]
+{York00} have revealed a non-uniform distribution of galaxies throughout 
+the universe.  Taking on a shape similar to that of a sponge-like topology 
+\citep{Gott98} or a three-dimensional cosmic web \citep{Bond96}, galaxies clump 
+together in clusters and along filaments, leaving void regions between these 
+large-scale structures.  Evidence of this distribution can be seen in Fig. 
+\ref{fig:SDSS_map} for galaxies in the SDSS Data Release 7 \citep[SDSS DR7;][]
+{Abazajian09}.  Based on these observations, dark matter simulations have been 
+constructed which successfully reproduce the same large-scale structure.  If we 
+start with a mostly uniform distribution of dark matter at the Big Bang with 
+quantum mechanical perturbations, Fig. \ref{fig:DMsim} outlines the evolution of 
+that dark matter up through the present.  These snapshots from the Millenium 
+Simulation project \citep{Springel05} show that small perturbations in the 
+initial distribution of dark matter are amplified as the universe expands.  
+Gravity causes the slightly overdense regions to collapse while simultaneously 
+causing the underdense regions to expand.  Due to dark matter's gravitational 
+attraction, we believe that the baryonic mattter (matter which interacts 
+electromagnetically) will trace the dark matter distribution, resulting in the 
+galaxy distribution we observe today.
 
@@
 Additionally, hydrodynamical cosmological simulations by \cite{Cen11} show that 
-void galaxies continue to form stars because the gas in voids remains below the 
-critical entropy threshold.  Void galaxies evolve in a relatively pristine 
-environment where interactions are rare and star formation proceeds up to the 
-present epoch because void galaxies are able to retain their gas.  This 
-contrasts the denser environments, where the chemical composition and evolution 
-of galaxies are drastically altered due to mergers and tidal and/or ram-pressure 
-stripping.
+void galaxies may continue to form stars because the gas in voids remains below 
+the critical entropy threshold (above which the cooling time exceeds the Hubble 
+time).  Void galaxies evolve in a relatively pristine environment where 
+interactions are rare and star formation proceeds up to the present epoch 
+because void galaxies are able to retain their gas.  This contrasts with denser 
+environments, where the chemical composition and evolution of galaxies are 
+drastically altered due to mergers and tidal and/or ram-pressure stripping.
 
@@
 content \citep{Kreckel12,Moorman16,Jones16}.  When compared to galaxies in 
-denser regions, void galaxies are fainter, of late morphological types, bluer, 
-forming stars at higher rates per unit stellar mass, and more gas rich.
+denser regions, void galaxies tend to be fainter, of late morphological types, 
+bluer, forming stars at higher rates per unit stellar mass, and more gas rich.
 
@@
 Defined to be galaxies with absolute magnitudes fainter than -17 ($M_r > -17$), 
-the low stellar masses of these systems correspond to more shallow gravitational 
-potential wells.  This causes any environmental effects to have a more 
-significant influence on dwarf galaxies than on galaxies with larger stellar 
-masses.  In addition, studying void dwarf galaxies will complement previous 
-studies of dwarfs in groups and clusters because the assembly histories of 
-low-mass galaxies are predicted to be very different \citep[e.g.,][]{Gao07,
+the low stellar masses of dwarf galaxies correspond to more shallow 
+gravitational potential wells.  This causes any environmental effects to have a 
+more significant influence on dwarf galaxies than on galaxies with larger 
+stellar masses.  In addition, studying void dwarf galaxies will complement 
+previous studies of dwarfs in groups and clusters because the assembly histories 
+of low-mass galaxies are predicted to be very different \citep[e.g.,][]{Gao07,
 Lackner12}.  Observations to date also show that the properties of dwarf 
@@
 
-The first stars that formed are thought to have been composed of only hydrogen 
-(and possibly some trace amount of helium).  As stars burn, nucleosythesis 
-creates heavier elements at the core.  When the stars die and expel their 
-content, the heavier elements are distributed between the surrounding 
-interstellar gas and circumgalactic medium.  When new stars form from this gas, 
-they include both hydrogen and some of the heavier elements.  By measuring the 
-fraction of elements heavier than helium (``metals'') relative to the hydrogen 
-content (the metallicity), we measure the integrated star formation history of 
-the galaxy.
+The first stars that formed are thought to have been composed of hydrogen and 
+helium (and trace amounts of other primordial elements).  As stars burn, 
+nucleosythesis creates heavier elements at the core.  When the stars expel their 
+contents in supernovae and stellar winds, the heavier elements are distributed 
+between the surrounding interstellar gas and circumgalactic medium.  By 
+measuring the ratio of elements heavier than helium (``metals'') relative to the 
+hydrogen content, we measure the integrated star formation history of the 
+galaxy.  This ``metallicity'' is commonly expressed as \OH, although it is 
+sometimes given in units of the solar metallicity, $Z/Z_\odot$.
 
@@
     light emitted from a star and/or a cool cloud of gas, representing 
-    Kirchoff's laws of spectroscopy.  A star emits light across all wavelengths, 
-    so the resulting spectrum is known as a continuous spectrum.  Star's light 
-    that has passed through a cloud of cool gas before being observed is an 
-    absorption spectrum, where the elements in the cloud have absorbed some of 
-    the light at specific wavelengths (corresponding to the particular elements 
-    present in the gas).  If observed off the line-of-sight of the star, the 
-    light emitted from the cloud of cooler gas results in an emission spectrum, 
-    where the gas is re-radiating the light it absorbed from the star.}
+    Kirchoff's laws of 
+    spectroscopy\footnote{\url{http://courses.atlas.illinois.edu/spring2011/astr/astr210/LECTURES/Lect12.html}}.  
+    A star emits light across all wavelengths, so the resulting spectrum is 
+    known as a continuous spectrum.  Star's light that has passed through a 
+    cloud of cool gas before being observed is an absorption spectrum, where the 
+    elements in the cloud have absorbed some of the light at specific 
+    wavelengths (corresponding to the particular elements present in the gas).  
+    If observed off the line-of-sight of the star, the light emitted from the 
+    cloud of cooler gas results in an emission spectrum, where the gas is 
+    re-radiating the light it absorbed from the star.}
     \label{fig:Kirchoff}
@@
 population and interstellar medium.  A galaxy's spectrum is a superposition of 
-light from the stars and emission lines from the gas.  Depending on our 
-viewpoint of the galaxy's light, we will see a different type of spectrum.  As 
-shown in Fig. \ref{fig:Kirchoff}, if we separate a star's light by its 
-wavelength, we will observe a continuous spectrum, since it is a blackbody.  If 
-instead we observe the starlight after it has passed through a cloud of cooler 
-gas, we will measure an absorption line spectrum; the elements in the gas cloud 
-have absorbed some of the star's light at specific wavelengths corresponding to 
-the particular ions present.  Finally, if we only observe the light emitted from 
-the cool gas cloud, we will measure an emission line spectrum.  The method we 
-employ to estimate the metallicity of a galaxy requires particular emission 
-lines.  We study the gas-phase chemical abundances of \ion{H}{2} regions in a 
-galaxy, where the light is coming from low-density gas partially ionized by UV 
-photons emitted from young, hot stars.  Therefore, we are measuring the 
-abundances of the elements produced in previous generations of stars.
+light from the stars and emission lines from the interstellar gas.  The 
+observer's viewpoint determines the type of spectrum measured.  As shown in Fig. 
+\ref{fig:Kirchoff}, if we separate a star's light by its wavelength, we will 
+observe a continuous spectrum, since its photosphere is close to a blackbody.  
+If instead we observe the starlight after it has passed through a cloud of 
+cooler gas (relative to the temperature of the star), we will measure an 
+absorption line spectrum; the elements in the gas cloud have absorbed some of 
+the star's light at specific wavelengths corresponding to the particular ions 
+present.  Finally, if we only observe the light emitted from the cool gas cloud, 
+we will measure an emission line spectrum.  The method we employ to estimate the 
+metallicity of a galaxy requires the detection of particular emission lines.  We 
+study the gas-phase chemical abundances of \ion{H}{2} regions in a galaxy, where 
+the light is coming from low-density gas partially ionized by UV photons emitted 
+from young, hot stars.  Therefore, we are measuring the abundances of the 
+elements produced in previous generations of stars.
 
@@
     \includegraphics[width=0.9\textwidth]{Images/Intro/spectrum}
-    \caption[Sample (void) dwarf galaxy spectrum]{Example SDSS DR7 spectrum --- 
-    this is a void dwarf galaxy whose gas-phase chemical abundances are slightly 
-    above average.  The [\ion{O}{3}] $\lambda$4363 auroral line is circled in 
-    red, while the [\ion{O}{3}] $\lambda \lambda$4959,5007 doublet is circled in 
-    yellow.}
+    \caption[Sample (void) dwarf galaxy spectrum]{Example SDSS DR7 
+    spectrum\footnote{\url{http://cas.sdss.org/dr7/en/get/specById.asp?ID=124634771904004096}} 
+    --- this is a void dwarf galaxy whose gas-phase chemical abundances are 
+    slightly above average.  The [\ion{O}{3}] $\lambda$4363 auroral line is 
+    circled in red, while the [\ion{O}{3}] $\lambda \lambda$4959,5007 doublet is 
+    circled in yellow.}
     \label{fig:spectrum}
@@
 \ref{sec:physics}, forbidden transitions have much longer lifetimes than the 
-allowed electron transitions.  These transitions depend strongly on the 
-temperature and density of the electron gas, because the long lifetimes allow 
-the atoms to easily collisionally de-excite.  By taking the ratio of the 
+allowed electric dipole electron transitions.  These transitions strongly depend 
+on the temperature and density of the electron gas, because the long lifetimes 
+allow the atoms to easily collisionally de-excite.  By taking the ratio of the 
 [\ion{O}{3}] $\lambda$4363 auroral line to the [\ion{O}{3}] 
@@
 because oxygen is the most abundant element in the universe after hydrogen and 
-helium.  It also has strong emission lines in the visible wavelength range, so 
-it is relatively easy to observe.  Oxygen emission is the most effective cooling 
-source in an \ion{H}{2} region, so lower metallicities correspond to higher 
-temperatures.  There are three main factors which determine the strength of an 
-emission line: the temperature, density, and number of ions in the gas.  It is 
-possible to calculate the number ratios for any of the heavy elements with 
-respect to hydrogen once the electron temperature and density of the 
-interstellar gas are estimated.
+helium \citep{Emsley11}.  It also has strong emission lines in the visible 
+wavelength range, so it is relatively easy to observe.  Oxygen emission is the 
+most effective cooling source in an \ion{H}{2} region, so lower metallicities 
+correspond to higher temperatures.  There are three main factors which determine 
+the strength of an emission line: the gas temperature, the electron density, and 
+the relative number of ions in the gas.  It is possible to calculate the number 
+ratios for any of the heavy elements with respect to hydrogen once the electron 
+temperature and density of the interstellar gas are estimated.
 
@@
 % Pose the problem - how does the large-scale environment affect galaxy evolution?
-We want to understand how dark matter affects the evolution of a galaxy and what 
-influence it has on a galaxy's star formation.  To do this, we compare the 
-properties of galaxies living in voids with galaxies in denser regions in an 
-effort to understand how the properties of the gas and the history of star 
-formation in a galaxy depend on the environment.  We then try to infer what 
-these results tell us about the dark matter structure and history of the galaxy.  
-In Chapter \ref{ch:Paper1}, we calculate and compare the metallicity of 135 
-star-forming dwarf galaxies as a function of their large-scale environment.  We 
-continue studying this galaxy sample in Chapter \ref{ch:Paper2} by estimating 
+We want to understand how the cosmic environment affects the evolution of a 
+galaxy and what influence it has on a galaxy's star formation.  To do this, we 
+compare the properties of galaxies living in voids with galaxies in denser 
+regions in an effort to understand how the properties of the gas and the history 
+of star formation in a galaxy depend on the environment.  We then try to infer 
+what these results tell us about the dark matter structure and history of the 
+galaxy.  In Chapter \ref{ch:Paper1}, we calculate and compare the metallicity of 
+135 star-forming dwarf galaxies as a function of their large-scale environment.  
+We continue studying this galaxy sample in Chapter \ref{ch:Paper2} by estimating 
 their ratios of nitrogen to oxygen and looking at how that depends on the 
@@
 galaxies into their location on the color-magnitude diagram in Chapter 
-\ref{ch:GV}.
+\ref{ch:GV}.  We present our conclusions and suggestions for future research in 
+Chapter \ref{ch:conclusion}.

### 2017-06-15 KellyDouglass/Thesis/preamble.tex
Edits to Abstract, Intro, Appendix

@@
 Universe by studying gas-phase chemical abundances and other galaxy properties 
-as a function of the local and cosmic density of galaxies.  Using spectroscopic 
-observations from the Sloan Digital Sky Survey Data Release 7, we estimate the 
-oxygen and nitrogen abundances of 993 star-forming void dwarf galaxies and 759 
-star-forming dwarf galaxies in denser regions.  We use the Direct $T_e$ method 
-for calculating the gas-phase chemical abundances in the dwarf galaxies because 
-it is best suited for low metallicity, low mass galaxies.  A substitute for the 
-[\ion{O}{2}] $\lambda$3727 doublet is developed, permitting oxygen abundance 
-estimates of SDSS dwarf galaxies at all redshifts with the Direct $T_e$ method.  
-We find that star-forming void dwarf galaxies have slightly higher oxygen 
-abundances than star-forming dwarf galaxies in denser environments, but we find 
-that void dwarf galaxies have slightly lower nitrogen abundances and lower N/O 
-ratios than galaxies in denser regions.  
+as a function of the large-scale environment and local density of galaxies.  
+Using spectroscopic observations from the Sloan Digital Sky Survey Data Release 
+7, we estimate the oxygen and nitrogen abundances of 993 star-forming void dwarf 
+galaxies and 759 star-forming dwarf galaxies in denser regions.  We use the 
+Direct $T_e$ method for calculating the gas-phase chemical abundances in the 
+dwarf galaxies because it is best suited for low metallicity, low mass galaxies.  
+A substitute for the [\ion{O}{2}] $\lambda$3727 doublet is developed, permitting 
+oxygen abundance estimates of SDSS dwarf galaxies at all redshifts with the 
+Direct $T_e$ method.  We find that star-forming void dwarf galaxies have 
+slightly higher oxygen abundances than star-forming dwarf galaxies in denser 
+environments, but we find that void dwarf galaxies have slightly lower nitrogen 
+abundances and lower N/O ratios than galaxies in denser regions.  
 % Small-scale enivronment
@@
 From these analyses, we surmise that void dwarf galaxies experience delayed star 
-formation as predicted by the $\Lambda$CDM cosmology and a dependence of the 
-large-scale environment on cosmic downsizing.  We present evidence that void 
-dwarf galaxies have a higher ratio of dark matter halo mass to stellar mass when 
-compared to dwarf galaxies in denser environments.
+formation as predicted by the $\Lambda$CDM cosmology.  We also conjecture that 
+there is a dependence of the large-scale environment on cosmic downsizing.  We 
+present evidence that void dwarf galaxies may have a higher ratio of dark matter 
+halo mass to stellar mass when compared to dwarf galaxies in denser 
+environments.
 

### 2017-06-15 KellyDouglass/Thesis/simulations.tex
Edits to Abstract, Intro, Appendix

@@
 
-\section{General dwarf galaxy formation and evolution}
+\section{Dwarf galaxy formation and evolution}
 
@@
 galaxies, since their gravitational potential wells may be shallow enough to be 
-strongly influenced by star formation and/or supernovae.  Simulations by 
+strongly influenced by stellar winds and/or supernovae.  Simulations by 
 \cite{Marcolini04} find that when ram pressure from the intergalactic medium 
@@
 
-\section{Environmental differences}
+\section[Environmental differences]{Environmental differences of galaxy formation and evolution}
 

### 2017-06-15 KellyDouglass/Thesis/Thesis_sections/Conclusion.tex
Edits to Abstract, Intro, Appendix
Updates to Ch. 5-7

@@
-\chapter[Conclusion]{Conclusions and suggestions for future work}
+\chapter[Conclusion]{Conclusions and suggestions for future work}\label{ch:conclusion}
 
@@
 \section[Chemical abundances]{Large-scale environmental influence on the gas-phase chemical abundances in dwarf galaxies}
+
 We find that the large-scale environment influences the chemical evolution of 
@@
 
+% Shift in O/H
 By deriving a relation between the doubly-ionized oxygen and total oxygen 
@@
 sample, but with a much higher statistical significance.  We find that 
-star-forming void dwarf galaxies have, on average, 7\% higher oxygen abundances, 
-10\% lower nitrogen abundances, and 17\% lower N/O ratios than star-forming 
-dwarf galaxies in denser regions.  The large-scale ($\sim 10$ \hMpc) environment 
-influences the chemical evolution of star-forming dwarf galaxies.
+star-forming void dwarf galaxies have, on average, 7\% higher oxygen abundances 
+than star-forming dwarf galaxies in denser regions.  This shift in the gas-phase 
+oxygen abundance distribution could be observational evidence for delayed star 
+formation in void galaxies when compared to those in denser regions.  This would 
+result in a smaller ratio of stellar mass to dark matter halo mass in void 
+galaxies than in dwarf galaxies in denser regions, as predicted in simulations 
+by \cite{Jung14} and \cite{Tonnesen15}.  If the void galaxies are retaining more 
+oxygen as a result of their deeper potential wells (relative to galaxies of the 
+same stellar mass in dense regions), then they would be able to commence 
+secondary nitrogen synthesis earlier.  We find that some of the star-forming 
+dwarf galaxies have a constant value of N/O for a range of masses while the 
+remainder exhibit a positive relationship between the stellar mass and N/O ratio 
+in the $M_*$-N/O relationship.  We make note of a different critical mass in the 
+$M_*$-N/O relationship in the two environments, where the void dwarf galaxies 
+begin to show evidence of secondary nitrogen synthesis at a stellar mass 
+$\sim$0.4 dex lower than for the galaxies in denser regions.  This indicates 
+that the void galaxies synthesize secondary nitrogen at a smaller stellar mass 
+than galaxies in denser regions.
 
+% Shift in N/O
+We also find that star-forming void dwarf galaxies have 17\% lower N/O ratios 
+than star-forming dwarf galaxies in denser regions.  This shift towards lower 
+N/O ratios in the star-forming dwarf galaxies might be evidence that 
+cosmological downsizing is environmentally dependent as predicted by 
+\cite{Cen11}.  Our results provide evidence for delayed, ongoing star formation 
+and cool gas available to fuel star formation up to the present epoch in void 
+dwarf galaxies whose dark matter halos ceased coalescing earlier than for dwarf 
+galaxies in denser regions.  We surmise that the differences in the 
+distributions of metallicity and the N/O ratio seen in the sample of 
+star-forming dwarf galaxies are due to a large-scale ($\sim$10 \hMpc) 
+environmental influence on their star formation history and evolution.
+
+% HI mass
 In addition to studying the large-scale environmental influence on the 
@@
 between the chemical abundances and various other physical properties of the 
-galaxies.  We find that the N/O ratio decreases with increasing metallicity 
-rather than a constant value for the N/O ratio as a function of O/H as observed 
-in other studies.  This is contrary to what we see in the $M_*$-N/O 
-relationship, where we find that some of the star-forming dwarf galaxies have a 
-constant value of N/O for a range of masses while the remainder exhibit a 
-positive relationship between the stellar mass and N/O ratio.  We make note of a 
-different critical mass in the $M_*$-N/O relationship in the two environments, 
-where the void dwarf galaxies begin to show evidence of secondary nitrogen 
-synthesis at a stellar mass $\sim$0.4 dex lower than for the galaxies in denser 
-regions.  Most of our star-forming dwarf galaxies follow the established 
-mass-metallicity relation \citep[e.g.,][]{Tremonti04}.
+galaxies.  Most of our star-forming dwarf galaxies follow the established 
+mass-metallicity relation \citep[e.g.,][]{Tremonti04}.  No relationship is 
+observed between the metallicity and \ion{H}{1} mass in our sample of 
+star-forming dwarf galaxies, but we find that the N/O ratio decreases with 
+increasing \ion{H}{1} mass for a given stellar mass.  Because most of our dwarf 
+galaxies are in the low metallicity tail of the mass-metallicity relation and 
+there is a strong correlation between stellar mass and \ion{H}{1} mass, it is 
+not surprising that we see no relationship between the metallicity and 
+\ion{H}{1} mass.  The inverse relationship between the N/O ratio and the 
+\ion{H}{1} mass is due to the time delay in the production of nitrogen relative 
+to oxygen.
 
-No relationship is observed between the metallicity and \ion{H}{1} mass in our 
-sample of star-forming dwarf galaxies, but we find that the N/O ratio decreases 
-with increasing \ion{H}{1} mass for a given stellar mass.  The star-forming 
-dwarf galaxies also exhibit an increase in the metallicity and N/O ratio with 
-increasing color (both $u-r$ and $g-r$).  We see very little correlation with 
-SFR for either metallicity or the N/O ratio in dwarf galaxies, but the 
-metallicity and N/O ratio decrease with increasing sSFR.  Beyond the large-scale 
-environmental influence on the distributions of the gas-phase chemical 
-abundances and the critical mass in the $M_*$-N/O relationship, we do not 
-observe any significant differences between the star-forming void and wall dwarf 
-galaxies in any of these relationships.
+% Color
+The star-forming dwarf galaxies exhibit an increase in the metallicity and N/O 
+ratio with increasing color (both $u-r$ and $g-r$).  Older, redder galaxies have 
+had more time to convert their hydrogen into heavier elements through star 
+formation, thus increasing their metallicities.  The correlation between the N/O 
+ratio and the color of a galaxy indicates a time delay between the release of 
+oxygen and nitrogen.
 
-We surmise that the differences in the distributions of metallicity and the N/O 
-ratio seen in the sample of star-forming dwarf galaxies are due to a large-scale 
-environmental influence on their star formation history and evolution.  The 
-shift in the gas-phase oxygen abundance distribution could be observational 
-evidence for delayed star formation in void galaxies when compared to those in 
-denser regions.  This would result in a smaller ratio of stellar mass to dark 
-matter halo mass in void galaxies than in dwarf galaxies in denser regions, as 
-predicted in simulations by \cite{Jung14} and \cite{Tonnesen15}.  If the void 
-galaxies are retaining more oxygen as a result of their deeper potential wells, 
-then they would be able to commence secondary nitrogen synthesis earlier, as 
-seen in the $M_*$-N/O relation in Fig. \ref{fig:M_NO}.  In addition, the shift 
-towards lower N/O ratios in the star-forming dwarf galaxies might be evidence 
-that cosmological downsizing is environmentally dependent as predicted by 
-\cite{Cen11}.  Our results provide evidence for delayed, ongoing star formation 
-in void dwarf galaxies whose dark matter halos ceased coalescing earlier than 
-for dwarf galaxies in denser regions.
+% (s)SFR
+We see very little correlation with SFR for either metallicity or the N/O ratio 
+in dwarf galaxies, but the metallicity and N/O ratio decrease with increasing 
+sSFR.  While we expect a relationship between the SFR and the metallicity due to 
+the fundamental relationship, our range of metallicity values might not extend 
+high enough to detect a significant relationship with the SFR in our sample of 
+star-forming dwarf galaxies.  The strong anti-correlation with low dispersion 
+between the N/O ratio and the sSFR in our dwarf galaxies might be evidence that 
+oxygen in produced in higher mass stars than those which synthesize nitrogen.
+
+%Beyond the large-scale 
+%environmental influence on the distributions of the gas-phase chemical 
+%abundances and the critical mass in the $M_*$-N/O relationship, we do not 
+%observe any significant differences between the star-forming void and wall dwarf 
+%galaxies in any of these relationships.
 
@@
 galaxies.  We find that only the presence of a neighboring galaxy within 0.05 
-\hMpc or 0.05$r_{vir}$, or the presence of a group within 0.1 \hMpc influences a 
+\hMpc or 0.1$r_{vir}$, or the presence of a group within 0.1 \hMpc influences a 
 dwarf galaxy's evolution.  Dwarf galaxies with a nearest neighbor galaxy within 
-0.05 \hMpc or 0.05$r_{vir}$ are bluer, have a higher sSFR, and have higher 
+0.05 \hMpc or 0.1$r_{vir}$ tend to be bluer, have a higher sSFR, and have higher 
 oxygen and nitrogen abundances than average.  This matches the results of 
-\cite{Park09}, who find that late-late type galaxy pairs within 0.05$r_{vir}$ 
-are bluer and have higher SFRs.  In contrast, dwarf galaxies within 0.1 \hMpc of 
-the center of the closest group are redder, have lower oxygen abundances, and 
-have higher N/O ratios than average.  These results are independent of both the 
-maximum relative velocity required to define a nearest neighbor and the sample 
-(star-forming versus all dwarf galaxies).
+\cite{Park09}, who find that higher luminosity late-late type galaxy pairs 
+within 0.05$r_{vir}$ are bluer and have higher SFRs.  In contrast, dwarf 
+galaxies within 0.1 \hMpc of the center of the closest group are redder, have 
+lower oxygen abundances, and have higher N/O ratios than average.  These results 
+are independent of both the maximum relative velocity required to define a 
+nearest neighbor and the sample (star-forming versus all dwarf galaxies).
 
 When we incorporate the redshift into the distance calculations, we find that 
-the galaxies within 0.05$r_{vir}$ are most likely strongly interacting or 
-merging with their nearest neighbor.  These merging galaxies likely share the 
-same dark matter halo, suggesting that the dark matter halo is more influential 
-on a galaxy's evolution than the distance between a galaxy and its nearest 
-neighbor.
+the galaxies within 0.1$r_{vir}$ are most likely strongly interacting or merging 
+with their nearest neighbor.  These merging galaxies likely share the same dark 
+matter halo, suggesting that the dark matter halo is more influential on a 
+galaxy's evolution than the distance between a galaxy and its nearest neighbor.
 
@@
 green valley of the CMD by combining the galaxy's color, color gradient, and 
-inverse concentration index.  Galaxies with a value less than 25 for the 
+inverse concentration index.  Galaxies with a value aimc$< 25$ for the 
 morphological type as calculated in the KIAS-VAGC exist in the green valley 
@@
 
-There is a higher fraction of faint galaxies from denser regions than faint void 
-galaxies in the green valley.  Combined with the previous results about the 
-large-scale environmental influence on the gas-phase chemical abundances, this 
-indicates that void dwarf galaxies are less evolved than dwarf galaxies in 
-denser environments.
+The fraction of void galaxies that are found in the green valley is 
+significantly smaller than the fraction of green valley galaxies found in denser 
+regions.  Combined with the previous results about the large-scale environmental 
+influence on the gas-phase chemical abundances, this indicates that void dwarf 
+galaxies are less evolved than dwarf galaxies in denser environments.
 
@@
 
+We find that the N/O ratio decreases with increasing metallicity rather than a 
+constant value for the N/O ratio as a function of O/H as observed in other 
+studies.  This variation of the behavior of the N/O ratio is contrary to what we 
+see in the $M_*$-N/O relationship, where our dwarf galaxies exhibit either a 
+constant value (nitrogen plateau) or an increase in (secondary nitrogen 
+production) the N/O ratio for increasing stellar mass.  It appears as though the 
+extremely low-metallicity galaxies present in the metallicity-N/O relationship 
+are causing this unusual behavior.  Detailed observations and high-resolution 
+spectra are needed of this population of galaxies, to confirm their metallicity 
+estimates and gain insight into this unique relationship.
+
 A better knowledge of the chemical abundances of galaxies with an AGN is also 

### 2017-06-15 KellyDouglass/Thesis/Thesis_sections/GV.tex
Finished writing intro
Updates to Ch. 5-7

@@
-\chapter[Green valley galaxies]{Identifying green valley galaxies}
+\chapter[Green valley galaxies]{Identifying green valley galaxies}\label{ch:GV}
 
@@
 \section{Introduction}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%    STATEMENT OF PROBLEM
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Chemical evolution and the green valley}
-
-The enrichment of the interstellar medium (ISM) and circumgalactic medium (CGM) 
-of a galaxy involves many complicated astrophysical processes, the interplay of 
-which is not yet well understood.  A critical problem in galaxy formation is to 
-understand how galaxies transition from the blue sequence to the red cloud of 
-the optical color-magnitude diagram.  Star formation is thought to be quenching 
-in galaxies moving through the green valley, but the relevant baryonic processes 
-(gas cooling, feedback, etc.) are very complex and heavily interdependent.  
-Investigating the star formation history and chemical evolution of galaxies in 
-the green valley should provide clues as to the evolution of a galaxy through 
-the color-magnitude diagram.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%    BACKGROUND AND RELEVANCE TO PREVIOUS WORK
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{The color-magnitude diagram: Galaxies in the green valley}
 
@@
 \end{figure}
+
+The enrichment of the interstellar medium (ISM) and circumgalactic medium (CGM) 
+of a galaxy involves many complicated astrophysical processes, the interplay of 
+which is not yet well understood.  A critical problem in galaxy formation is to 
+understand how galaxies transition from the blue sequence to the red cloud of 
+the optical color-magnitude diagram.  Star formation is thought to be quenching 
+in galaxies moving through the green valley, but the relevant baryonic processes 
+(gas cooling, feedback, etc.) are very complex and heavily interdependent.  
+Investigating the star formation history and chemical evolution of galaxies in 
+the green valley should provide clues as to the evolution of a galaxy through 
+the color-magnitude diagram.
 
@@
 
-A galaxy's color is the ratio of the flux emitted by the galaxy in two different 
-bands.  The stellar population of a galaxy will determine its color --- redder 
-galaxies contain much older, cooler stars, while the spectrum of a bluer galaxy 
-is produced by light from much younger, hotter stars.  A galaxy's color is 
-independent of its redshift, so only photometry is needed to calculate the 
-ratio.  While the KIAS-VAGC catalog (described below in Section \ref{sec:SDSS}) 
-provides the $u-r$ color for all galaxies in SDSS, we make use of the Petrosian 
-fluxes in the NSA (described in Section \ref{sec:GALEX}) to calculate the 
-UV--optical color.  The NUV$-r$ color is calculated by
+A galaxy's color is a logarithmic ratio of the ratio of the flux emitted by the 
+galaxy in two different bands.  The stellar population of a galaxy will 
+determine its color: redder galaxies contain much older, cooler stars, while the 
+spectrum of a bluer galaxy is produced by light from much younger, hotter stars.  
+While the KIAS-VAGC catalog (described below in Section \ref{sec:SDSS}) provides 
+the $u-r$ color for all galaxies in SDSS, we make use of the Petrosian fluxes in 
+the NSA (described in Section \ref{sec:GALEX}) to calculate the UV--optical 
+color.  The NUV$-r$ color is calculated by
 \begin{equation}
@@
 
-The SDSS Data Release 7 \citep[DR7]{Abazajian09} is a wide-field multi-band 
+The SDSS Data Release 7 \citep[DR7;][]{Abazajian09} is a wide-field multi-band 
 imaging and spectroscopic survey that uses drift scanning to map approximately 
@@
 measured by the MPA-JHU catalog\footnote{Available at 
-\url{http://www.mpa-garching.mpg.de/SDSS/DR7}} and published in Douglass \& 
-Vogeley (2017, in prep).  The large-scale environment of the galaxies is based 
-on the void catalog compiled by \cite{Pan12}.  This void catalog is constructed 
-from SDSS DR7 using the VoidFinder algorithm of \cite{Hoyle02}.  Galaxies which 
-are located within the identified voids are labeled as void galaxies; those 
-which do not reside in a void are designated as wall galaxies.  Because the 
-minimum diameter of a void is defined as 10 \hMpc , the large-scale environment 
-of galaxies within 5 \hMpc of the edge of the SDSS DR7 footprint cannot be 
+\url{http://www.mpa-garching.mpg.de/SDSS/DR7}} and published in Douglass et al. 
+(2017, in prep).  The large-scale environment of the galaxies is based on the 
+void catalog compiled by \cite{Pan12}.  This void catalog is constructed from 
+SDSS DR7 using the VoidFinder algorithm of \cite{Hoyle02}.  Galaxies which are 
+located within the identified voids are labeled as void galaxies; those which do 
+not reside in a void are designated as wall galaxies.  Because the minimum 
+diameter of a void is defined as 10 \hMpc , the large-scale environment of 
+galaxies within 5 \hMpc of the edge of the SDSS DR7 footprint cannot be 
 described, so their environment is labeled as unknown.
@@
 The Korea Institute for Advanced Study Value-Added Galaxy Catalog 
-\citep[KIAS-VAGC]{Choi10} contains galaxies from the SDSS DR7 main sky survey 
+\citep[KIAS-VAGC;][]{Choi10} contains galaxies from the SDSS DR7 main sky survey 
 based on the New York University Value-Added Galaxy Catalog Data Release 7 
-\citep[NYU-VAGC]{Blanton05}.  It provides a morphological class and type 
+\citep[NYU-VAGC;][]{Blanton05}.  It provides a morphological class and type 
 following the automated morphology classification scheme of \cite{Park05}, using 
 the color $u-r$, color gradient $\Delta (g-r)$, and inverse concentration index.  
-We use the absolute magnitudes as listed in the KIAS-VAGC.
+With these three quantities, galaxies are separated into one of three different 
+morphological types: normal late type, normal early type, blue early type, and 
+one of two different morphological classes: elliptical or lenticular and spiral 
+or irregular.  For reference, typical star-forming spiral galaxies would be 
+classified as a normal late type spiral or irregular galaxy, star-forming dwarf 
+galaxies are usually normal late type spiral or irregular galaxies, and red 
+elliptical galaxies are typically classified as normal early type elliptical or 
+lenticular galaxies.  We use the absolute magnitudes as listed in the KIAS-VAGC.
 
@@
 instrument allows imaging and spectroscopic observations in two ultraviolet 
-bands --- Far UV (FUV, 1350--1780\AA) and Near UV (NUV, 1770--2730\AA) 
+bands: Far UV (FUV, 1350--1780\AA) and Near UV (NUV, 1770--2730\AA) 
 \citep{Morrissey07}.  The NUV-$r$ colors used in this study are calculated from 
@@
 morphological types as calculated in the KIAS-VAGC; this can be seen in Fig. 
-\ref{fig:NUVr_CMD}.  Defined by the $u-r$ color and the color gradient 
-$\Delta (g-i)$, it is novel that an estimate of the morphological type of the 
-galaxies is an adequate classification for the three populations of the NUV$-r$ 
-CMD.  In addition, Fig. \ref{fig:NUVr_hist} shows a histogram of the galaxies 
-which overlap in both GALEX and SDSS, separated by their morphological 
-classification from the KIAS-VAGC.  It shows that the three populations are well 
-fit by three Gaussians --- the new population in the middle is the transient 
-galaxy population originally ``missing'' from the optical CMD.
+\ref{fig:NUVr_CMD}.  Here, we group together normal late type and blue early 
+type galaxies, and we separate into two groups the normal late type galaxies 
+based on their value of the morphological type quantity calculated in the 
+KIAS-VAGC.  Defined by the $u-r$ color and the color gradient $\Delta (g-i)$, it 
+is novel that an estimate of the morphological type of the galaxies is an 
+adequate classification for the three populations of the NUV$-r$ CMD.  In 
+addition, Fig. \ref{fig:NUVr_hist} shows a histogram of the galaxies which 
+overlap in both GALEX and SDSS, separated by their morphological classification 
+from the KIAS-VAGC.  It shows that the three populations are well fit by three 
+Gaussians --- the new population in the middle is the transient galaxy 
+population originally ``missing'' from the optical CMD.
 
@@
 although the green valley galaxies extend well into the range of sSFRs occupied 
-by the galaxies in the red cloud.  \cite{Salim14a} describes transitional 
-galaxies (those in the green valley) to have lower sSFRs than galaxies in the 
-blue sequence, specifically $-11.8 < \log(\text{sSFR}) < -10.8$.  While our 
-results do indicate that green valley galaxies have lower sSFRs than those in 
-the blue sequence, we find that their range of sSFR is almost double the width 
-of that described in \cite{Salim14a}.  The green valley galaxies have a sSFR 
-within the range $-12 \lesssim \log(\text{sSFR}) \lesssim -10$.
+by the galaxies in the red cloud.  \cite{Salim14a} finds transitional galaxies 
+(those in the green valley) to have lower sSFRs than galaxies in the blue 
+sequence, specifically $-11.8 < \log(\text{sSFR}) < -10.8$.  While our results 
+do indicate that green valley galaxies have lower sSFRs than those in the blue 
+sequence, we find that their range of sSFR is almost double the width of that 
+described in \cite{Salim14a}.  The green valley galaxies have a sSFR within the 
+range $-12 \lesssim \log(\text{sSFR}) \lesssim -10$.
 
@@
 integrated star formation histories, which can provide insight into the 
-enrichment of the ISM and CGM.  A few of the galaxies for which Douglass \& 
-Vogeley (2017, in prep) are able to estimate metallicities reside in the green 
-valley.  When compared with the metallicities of galaxies in the blue sequence 
-and red cloud, Fig. \ref{fig:Z_hist} shows that the green valley galaxies have 
-higher nitrogen abundances than star-forming galaxies in the blue sequence (and 
-some of the red cloud).  With oxygen abundances that fall within the same range 
-as the other two galaxy populations, this shift causes the N/O ratio to be much 
-higher in green valley galaxies than in the blue sequence.
+enrichment of the ISM and CGM.  A few of the galaxies for which Douglass et al. 
+(2017, in prep) are able to estimate metallicities reside in the green valley.  
+When compared with the metallicities of galaxies in the blue sequence and red 
+cloud, Fig. \ref{fig:Z_hist} shows that the green valley galaxies have higher 
+nitrogen abundances than star-forming galaxies in the blue sequence (and some of 
+the red cloud).  With oxygen abundances that fall within the same range as the 
+other two galaxy populations, this shift causes the N/O ratio to be much higher 
+in green valley galaxies than in the blue sequence.  Our interpretation of this 
+shift is described in Sec. \ref{sec:discussion_GV}.
 
@@
 
-\section[Discussion]{Understanding green valley galaxies}
+\section[Discussion]{Understanding green valley galaxies}\label{sec:discussion_GV}
 
@@
 compared to those in the blue sequence indicate that they are building up a 
-surplus of nitrogen, most likely due to the presence of heavier elements at the 
-later star formation episodes.  The surplus of heavier elements allows the CNO 
-cycle to commence earlier in the stars' lifetimes, producing nitrogen at a 
+surplus of nitrogen, most likely due to the presence of heavier elements in 
+later episodes of star formation.  The surplus of heavier elements allows the 
+CNO cycle to commence earlier in the stars' lifetimes, producing nitrogen at a 
 higher rate than oxygen.  It is also possible that the higher nitrogen 
@@
 They find that, for dwarf galaxies ($M_r > -17$), those which exist in voids may 
-have commenced their star formation at a later time and have not experienced the 
-same cosmic downsizing as dwarf galaxies residing in denser regions.  The higher 
-fraction of wall dwarf galaxies in the green valley might also point to an 
-environmental influence on the reason for transitioning through the green 
-valley, such as ram pressure stripping, which would occur much less frequently 
-in the void environment.  However, the existence of void galaxies in the green 
-valley indicate that galaxy interactions cannot be the only star formation 
-quenching mechanism.
+have commenced their star formation at a later time.  The higher fraction of 
+wall dwarf galaxies in the green valley might also point to an environmental 
+influence on the reason for transitioning through the green valley, such as ram 
+pressure stripping, which would occur much less frequently in the void 
+environment.  However, the existence of void galaxies in the green valley 
+indicate that galaxy interactions cannot be the only star formation quenching 
+mechanism.
 
@@
 
-To understand the gas-phase chemical abundances of the green valley galaxies, we 
-compare Fig. \ref{fig:Z_hist} with the distribution of the gas-phase chemical 
-abundances of star-forming and composite galaxies and galaxies with an AGN shown 
-in Fig. \ref{fig:BPT_abund}.  We see that the galaxies with an AGN have the most 
-similar distributions in the three abundance ratios as the green valley 
-galaxies: both groups have similar oxygen abundances (O/H) and higher nitrogen 
-abundances (N/H) and N/O ratios than the star-forming galaxies.  This might 
-indicate a link between green valley galaxies and a host AGN.  The presence of 
-an AGN in green valley galaxies would support other studies of the transition of 
-galaxies from the blue sequence to the red cloud, which attribute the quenching 
-of star formation to accretion of a central black hole \citep[e.g.,][]{Croton06,
-Stasinska08}.
+Galaxies can be classified into a number of categories with the use of a BPT 
+diagram \citep{Baldwin81}.  By comparing different emission line ratios to get 
+an idea of the hardness of the spectrum, we can identify if most of the energy 
+in the galaxy's spectrum is coming from a star-forming region, an AGN, or a 
+combination of both (``composite'').  To understand the gas-phase chemical 
+abundances of the green valley galaxies, we compare Fig. \ref{fig:Z_hist} with 
+the distribution of the gas-phase chemical abundances of star-forming and 
+composite galaxies and galaxies with an AGN shown in Fig. \ref{fig:BPT_abund}; 
+the BPT diagram classifications are from \cite{Brinchmann04}.  We see that the 
+galaxies with an AGN have the most similar distributions in the three abundance 
+ratios as the green valley galaxies: both groups have similar oxygen abundances 
+(O/H) and higher nitrogen abundances (N/H) and N/O ratios than the star-forming 
+galaxies.  This might indicate a link between green valley galaxies and a host 
+AGN.  The presence of an AGN in green valley galaxies would support other 
+studies of the transition of galaxies from the blue sequence to the red cloud, 
+which attribute the quenching of star formation to accretion of a central black 
+hole \citep[e.g.,][]{Croton06,Stasinska08}.
 
@@
 
-We can define galaxies which are transitioning through the green valley of the 
-color-magnitude diagram by combining the galaxy's color, color gradient, and 
-inverse concentration index.  Galaxies with a magnitude less than 25 for the 
+We find a remarkable conformity between galaxies identified by morphological 
+classification and their location in the NUV$-r$ CMD, which clearly identifies 
+the green valley.  We can define galaxies which are transitioning through the 
+green valley of the color-magnitude diagram by combining the galaxy's color, 
+color gradient, and inverse concentration index.  Using these properties for the 
+morphological classification, galaxies with a value less than 25 for the 
 morphological type as calculated in the KIAS-VAGC exist in the green valley 
@@
 the green valley.  In conjunction with the conclusions of \cite{Douglass17b} and 
-Douglass \& Vogeley (2017, in prep), this indicates that void dwarf galaxies are 
+Douglass et al. (2017, in prep), this indicates that void dwarf galaxies are 
 less evolved than dwarf galaxies in denser environments.  It would be beneficial 
-to investigate the small-scale ($\sim 1$ \hMpc) environment of galaxies in the 
+to investigate the small-scale ($\sim$1 \hMpc) environment of galaxies in the 
 green valley, to determine if any interactions are responsible for the 

### 2017-06-15 KellyDouglass/Thesis/Thesis_sections/smallScaleEnvironment.tex
Finished writing intro
Updates to Ch. 5-7

@@
-\chapter[Small-scale environment]{The influence of the small-scale environment on dwarf galaxy evolution}
+\chapter[Small-scale environment]{The influence of the small-scale environment on dwarf galaxy evolution}\label{ch:smallScaleEnvironment}
 
@@
 
-% Large-scale environment influence
-Large galaxy redshift surveys have shown that the large-scale structure of the 
-distribution of galaxies in the universe is similar to that of a 
-three-dimensional cosmic web \citep{Bond96}, where galaxy clusters are connected 
-by thin filaments of galaxies and are separated by voids (large, underdense 
-regions that occupy close to 60\% of space).  Over the last few decades, the 
-Sloan Digital Sky Survey \citep{Abazajian09,Ahn12} has accelerated the research 
-into the influence of the large-scale environment on the formation and evolution 
-of galaxies.
-
-Because gravitational clustering within a void proceeds as if in a very 
-low-density universe, cosmic voids are an important environment for studying 
-galaxy formation \citep[see][for a review]{vandeWeygaert11}.  The $\Lambda$CDM 
-cosmology predicts that galaxies formed in voids have lower masses and are 
-retarded in their star formation when compared to those in more dense 
-environments \citep{Gottlober03,Goldberg05,Cen11}.  The effects of the void 
-environment should be most obvious in dwarf galaxies due to their minimal 
-gravitational potential.  As a result, they are more sensitive to astrophysical 
-effects such as cosmological reionization, internal feedback from supernovae and 
-photoheating from star formation, small-scale details of dark matter halo 
-assembly, and the properties of dark matter.
-
-Observations have shown that the properties of dwarf galaxies vary dramatically 
-with the environment \citep[e.g.,][]{Ann08,Geha12}.  Void galaxies have been 
-found to have lower stellar mass \citep{Hoyle05,Croton05,Moorman15}, be bluer 
-and of a later type \citep{Grogin00,Rojas04,Patiri06,Park07,vonBendaBeckmann08,
-Hoyle12}, have higher star formation rates \citep{Rojas05,Moorman15,Beygu16}, 
-and be more gas rich \citep{Kreckel12,Moorman16,Jones16} than galaxies in denser 
-regions.
+%% Large-scale environment influence
+%Large galaxy redshift surveys have shown that the large-scale structure of the 
+%distribution of galaxies in the universe is similar to that of a 
+%three-dimensional cosmic web \citep{Bond96}, where galaxy clusters are connected 
+%by thin filaments of galaxies and are separated by voids (large, underdense 
+%regions that occupy close to 60\% of space).  Over the last few decades, the 
+%Sloan Digital Sky Survey \citep{Abazajian09,Ahn12} has accelerated the research 
+%into the influence of the large-scale environment on the formation and evolution 
+%of galaxies.
+%
+%Because gravitational clustering within a void proceeds as if in a very 
+%low-density universe, cosmic voids are an important environment for studying 
+%galaxy formation \citep[see][for a review]{vandeWeygaert11}.  The $\Lambda$CDM 
+%cosmology predicts that galaxies formed in voids have lower masses and are 
+%retarded in their star formation when compared to those in more dense 
+%environments \citep{Gottlober03,Goldberg05,Cen11}.  The effects of the void 
+%environment should be most obvious in dwarf galaxies due to their minimal 
+%gravitational potential.  As a result, they are more sensitive to astrophysical 
+%effects such as cosmological reionization, internal feedback from supernovae and 
+%photoheating from star formation, small-scale details of dark matter halo 
+%assembly, and the properties of dark matter.
+%
+%Observations have shown that the properties of dwarf galaxies vary dramatically 
+%with the environment \citep[e.g.,][]{Ann08,Geha12}.  Void galaxies have been 
+%found to have lower stellar mass \citep{Hoyle05,Croton05,Moorman15}, be bluer 
+%and of a later type \citep{Grogin00,Rojas04,Patiri06,Park07,vonBendaBeckmann08,
+%Hoyle12}, have higher star formation rates \citep{Rojas05,Moorman15,Beygu16}, 
+%and be more gas rich \citep{Kreckel12,Moorman16,Jones16} than galaxies in denser 
+%regions.
 
@@
 In conjunction with the large-scale environment, the small-scale environment 
-($\sim 1$ \hMpc) has also been found to influence a galaxy's evolution.  A 
+($\sim$1 \hMpc) has also been found to influence a galaxy's evolution.  A 
 well-established morphology-density relation exists \citep{Dressler80}, where 
@@
 radius of the nearest neighbor influence the evolution of the target galaxy.  
-They determine that the large-scale environment has a minimal effect on the 
-evolution of a galaxy once the luminosity and morphology are taken into account.
+Along with \cite{Park07}, they determine that the large-scale environment has a 
+minimal effect on the evolution of a galaxy once the luminosity and morphology 
+are taken into account.
 
@@
 that share the same dark matter halo.  A group member will interact 
-gravitationally with all other group members, not just its nearest neighbor.  
-And a galaxy near a group, but not within it, may also experience strong tidal 
-effects from the group similar to and stronger than those from a neighboring 
-galaxy.
+gravitationally with all other group members, not just its nearest neighbor.  In 
+groups and clusters dense enough to strip and heat the gas, galaxies will also 
+experience ram pressure stripping.  And a galaxy near a group, but not within 
+it, may also experience strong tidal effects from the group similar to and 
+stronger than those from a neighboring galaxy.
 
@@
 
-\section[Theory]{Calculating distances}\label{sec:Theory_dist}
+\section[Nearest neighbor calculations]{Identifying the nearest neighbor}\label{sec:Theory_dist}
 
 We employ two different spatial metrics to determine the best way to locate a 
-galaxy's nearest neighbor.  Within a relative velocity 
-$v_{rel} < 300\text{ km/s}$, we use either the physically closest galaxy in 
-units of \hMpc or the galaxy within the smallest fraction of its virial radius; 
-both these methods are described below in further detail.  The two methods 
-result in different neighboring galaxies for about 40\% of our dwarf galaxy 
-sample.
+galaxy's nearest neighbor.  We set a maximum velocity separation of 300 km/s 
+between a galaxy and its nearest neighbor to capture the majority of interacting 
+galaxies \citep[according to the distribution in peculiar velocity shown in][]
+{Hwang10}.  Within a relative velocity $v_{rel} < 300\text{ km/s}$, we use 
+either the physically closest galaxy in units of \hMpc or the galaxy within the 
+smallest fraction of its virial radius; both these methods are described below 
+in further detail.  The two methods result in different neighboring galaxies for 
+about 40\% of our dwarf galaxy sample.
 
@@
 where $z$ is the redshift.  We require all 
-neighbors to have a maximum relative velocity $v_{rel} < 300\text{ km/s}$.  We 
-show in Sec. \ref{sec:selection_effects} that our results are insensitive to 
-this value.
+neighbors to have a maximum relative velocity $v_{rel} < 300\text{ km/s}$, as we 
+believe those outside this range will have minimal influence on the target 
+galaxy's evolution.  We show in Sec. \ref{sec:selection_effects} that our 
+results are insensitive to this value.
 
@@
 are gravitationally bound are in a system where the relative velocity between us 
-and it is 0 and that $\bar{r}$ is the distance to the center of the system.  The 
-distance to the system is calculated as
+and it is 0 and that $\bar{r}$ is the distance to the center of the system.  For 
+redshifts $z \ll 1$, we can approximate the distance to the system is as
 \begin{equation}
@@
 
-From \cite{Hwang10}, we calculate the virial radius of a galaxy to be
+The virial radius of a galaxy defines the region within which something is 
+gravitationally bound to the galaxy.  From \cite{Hwang10}, we calculate the 
+virial radius of a galaxy to be
 \begin{equation}\label{eqn:r_vir}
@@
 $\rho_c$ is the critical density of the universe.  The critical density is the 
-density at which evenly distributed gas would collapse to form a galaxy.  The 
-mass-to-light ratio depends on the galaxy's morphology type, where 
-$\gamma_{early} = 2\gamma_{late}$.  \cite{Hwang10} defines 
-$200\rho_c = 740\bar{\rho}$, where 
+density at which evenly distributed gas would collapse to form a galaxy.
+
+\cite{Choi07} find that the velocity dispersion of a galaxy depends on its 
+morphological type, where $\sqrt{2}\sigma_{late} \approx \sigma_{early}$.  In 
+terms of the velocity dispersion, the kinetic energy of a galaxy 
+$K = 3/2 \sigma^2$.  Its gravitational potential energy $U = 3GM/5R$.  
+Therefore, the virial theorem shows us that
+\begin{align}
+    3\sigma^2 \simeq \frac{3}{5} \frac{GM}{R}\nonumber \\
+    M \simeq \frac{5\sigma^2 R}{G}
+\end{align}
+With $\gamma \equiv M/L$, at a fixed luminosity and virial radius we see that
+\begin{equation}
+    \gamma_{late} \simeq \frac{5\sigma_{late}^2 R}{GL} \qquad \gamma_{early} \simeq \frac{5\sigma_{early}^2 R}{GL}
+\end{equation}
+Taking the ratio of the two mass-to-light ratios and using the relation between 
+the velocity dispersions found by \cite{Choi07}, we find that the mass-to-light 
+ratio depends on the galaxy's morphology type: $\gamma_{early} = 2\gamma_{late}$.
+
+\cite{Hwang10} defines $200\rho_c = 740\bar{\rho}$, where 
 $\bar{\rho} = (0.0223\pm 0.0005)(\gamma_{late}L_{-20})(\text{\hMpc})^3$.  We can 
@@
 \end{equation}
-We then convert to Cartesian coordinates and use the three-dimensional 
-Pythagorean theorem to calculate the distance between the two galaxies.
+(This approximation for the distance is valid because all our target galaxies 
+are within a redshift $z \leq 0.03$.)  We then convert to Cartesian coordinates 
+and use the three-dimensional Pythagorean theorem to calculate the distance 
+between the two galaxies.
 
@@
 % SDSS
-The Sloan Digital Sky Survey Data Release 7 \citep[SDSS DR7;][]{Abazajian09} is 
-a wide-field multiband imaging and spectroscopic survey which maps approximately 
-one-quarter of the northern sky using a drift scanning technique.  Photometric 
-data in the five-band SDSS system --- $u$, $g$, $r$, $i$, and $z$ --- is taken 
-on a dedicated 2.5m telescope at the Apache Point Observatory in New Mexico 
-\citep{Fukugita96,Gunn98}.  Galaxies with Petrosian $r$-band magnitudes 
-$m_r < 17.77$ are selected for follow-up spectroscopic analysis \citep{Lupton01,
-Strauss02}.  The galaxy colors are taken from the Korean Institute for Advanced 
-Study Value-Added Galaxy Catalog \citep[KIAS-VAGC;][]{Choi10}, which contains 
-galaxies from the SDSS DR7 main sky survey based on the New York University 
-Value-Added Galaxy Catalog Data Release 7 \citep[NYU-VAGC;][]{Blanton05}.  Total 
-star formation rates (SFR) and total specific star formation rates (sSFR) are 
-from the MPA-JHU value-added catalog\footnote{Available at 
-\url{http://www.mpa-garching.mpg.de/SDSS/DR7/}}, calculated using the technique 
-described in \cite{Brinchmann04}.  The gas-phase chemical abundances used are 
-from Douglass \& Vogeley (2017, in prep.), which are calculated using the Direct 
-$T_e$ method.  The galaxies' large-scale environments are based on the void 
-catalog compiled by \cite{Pan12}, which is constructed from SDSS DR7 using the 
-VoidFinder algorithm of \cite{Hoyle02}.  Galaxies which are located within 
-identified voids are labeled as void galaxies, and those which do not fall 
-within a void are designated as a wall galaxy.  The large-scale environment 
-within 5 \hMpc of the edge of the main SDSS DR7 footprint cannot be described 
-using the VoidFinder algorithm because the minimum diameter of a void is 10 
-\hMpc.  Therefore, the large-scale environment for galaxies within 5 \hMpc of 
-the edge of the main footprint in SDSS DR7 is designated as unknown.
+%The Sloan Digital Sky Survey Data Release 7 \citep[SDSS DR7;][]{Abazajian09} is 
+%a wide-field multiband imaging and spectroscopic survey which maps approximately 
+%one-quarter of the northern sky using a drift scanning technique.  Photometric 
+%data in the five-band SDSS system --- $u$, $g$, $r$, $i$, and $z$ --- is taken 
+%on a dedicated 2.5m telescope at the Apache Point Observatory in New Mexico 
+%\citep{Fukugita96,Gunn98}.  Galaxies with Petrosian $r$-band magnitudes 
+%$m_r < 17.77$ are selected for follow-up spectroscopic analysis \citep{Lupton01,
+%Strauss02}.  The galaxy colors are taken from the Korean Institute for Advanced 
+%Study Value-Added Galaxy Catalog \citep[KIAS-VAGC;][]{Choi10}, which contains 
+%galaxies from the SDSS DR7 main sky survey based on the New York University 
+%Value-Added Galaxy Catalog Data Release 7 \citep[NYU-VAGC;][]{Blanton05}.  Total 
+%star formation rates (SFR) and total specific star formation rates (sSFR) are 
+%from the MPA-JHU value-added catalog\footnote{Available at 
+%\url{http://www.mpa-garching.mpg.de/SDSS/DR7/}}, calculated using the technique 
+%described in \cite{Brinchmann04}.  
+The gas-phase chemical abundances used are from Douglass, Vogeley, and Cen 
+(2017, in prep.), which are calculated using the Direct $T_e$ method.  The 
+galaxies' large-scale environments are based on the void catalog compiled by 
+\cite{Pan12}, which is constructed from SDSS DR7 using the VoidFinder algorithm 
+of \cite{Hoyle02}.  Galaxies that are located within identified voids are 
+labeled as void galaxies, and those that do not fall within a void are 
+designated as a wall galaxy.  The large-scale environment within 5 \hMpc of the 
+edge of the main SDSS DR7 footprint cannot be described using the VoidFinder 
+algorithm because the minimum diameter of a void is 10 \hMpc.  Therefore, the 
+large-scale environment for galaxies within 5 \hMpc of the edge of the main 
+footprint in SDSS DR7 is designated as unknown.
 
@@
 11,845 dwarf galaxies spectroscopically observed in SDSS DR7.  The second sample 
-contains those star-forming dwarf galaxies from the first set which have 
-gas-phase chemical abundances in Douglass \& Vogeley (2017, in prep.), totaling 
-2506 dwarf galaxies.  While this subset of galaxies contains only star-forming 
+contains those star-forming dwarf galaxies from the first set that have 
+gas-phase chemical abundances in Douglass et al. (2017, in prep.), totaling 2506 
+dwarf galaxies.  While this subset of galaxies contains only star-forming 
 galaxies and is not representative of all dwarf galaxies, we show in Section 
@@
 look at the relationship between the dwarf galaxies' properties and their 
-proximity to the nearest galaxy group.  We use the Mr18 Berlind group catalog 
-\cite{Berlind06} as our source of groups, which is built on the galaxies in the 
-NYU-VAGC. The catalog identifies groups using a friends-of-friends algorithm 
-\citep{Huchra82} to connect galaxies with $M_r < -18$.
+proximity to the nearest galaxy group.  We use the \emph{Mr18} Berlind group 
+catalog \cite{Berlind06} as our source of groups, which is built on the galaxies 
+in the NYU-VAGC. The catalog identifies groups using a friends-of-friends 
+algorithm \citep{Huchra82} to connect galaxies with $M_r < -18$.
 
@@
 each figure, we bin the galaxies in distance-space and show the average 
-parameter value in each bin, to see any overall trends in the data.  We also fit 
-a linear line to the data; the output of these fits are in Table \ref{tab:fits}.  
-Each of these four plots probes this distance relationship from a different 
-angle.  The top left plots in Figs. \ref{fig:ur}--\ref{fig:NO} relate the target 
+parameter value in each bin, to see any overall trends in the data.  We applied 
+a linear regression to the data; the output of these fits are in Table 
+\ref{tab:fits}.  Each of these four plots probes this distance relationship from 
+a different angle.  The top left plots in Figs. \ref{fig:ur}--\ref{fig:NO} 
+relate the target dwarf galaxy's parameter to the distance to its nearest 
+neighbor, as defined by the the closest galaxy on the sky in \hMpc with a 
+velocity difference less than 300 km/s.  The bottom left plots relate the target 
 dwarf galaxy's parameter to the distance to its nearest neighbor, as defined by 
-the the closest galaxy on the sky in \hMpc with a velocity difference less than 
-300 km/s.  The bottom left plots relate the target dwarf galaxy's parameter to 
-the distance to its nearest neighbor, as defined by the closest galaxy on the 
-sky in units of the virial radius of the neighbor galaxy with a velocity 
-difference less than 300 km/s.  The nearest galaxy is not necessarily the same 
-for these two distance measurements, as explained in Sec. \ref{sec:Theory_dist}.
+the closest galaxy on the sky in units of the virial radius of the neighbor 
+galaxy with a velocity difference less than 300 km/s.  The nearest galaxy is not 
+necessarily the same for these two distance measurements, as explained in Sec. 
+\ref{sec:Theory_dist}.
 
@@
     have some affect on the dwarf galaxy's color at separations less than 0.05 
-    \hMpc, or 0.05$r_{vir}$.  The closest group appears to have some 
-    affect on the target dwarf galaxy's color at distances less than 0.1 \hMpc 
-    to the group's center; there appears to be no relationship between a dwarf 
-    galaxy's color and its distance to the nearest group as represented by the 
-    fraction of the group's radius.}
+    \hMpc, or 0.1$r_{vir}$.  The closest group appears to have some affect on 
+    the target dwarf galaxy's color at distances less than 0.1 \hMpc to the 
+    group's center; there appears to be no relationship between a dwarf galaxy's 
+    color and its distance to the nearest group as represented by the fraction 
+    of the group's radius.}
     \label{fig:ur}
@@
 Because of the known morphology-density relation, we expect to find that a dwarf 
-galaxy's color became more blue as the distance to its nearest neighbor 
-increased.  Fig. \ref{fig:ur} shows very little relationship between the 
-distance and color, except at the smallest distance bin.  The linear fits 
+galaxy's color becomes bluer as the distance to the nearest group increases, but 
+we expect the dwarf galaxy's color to become bluer as the distance to the 
+neighbor decreases.  Fig. \ref{fig:ur} shows very little relationship between 
+the distance and color, except in the smallest distance bin.  The linear fits 
 quantify this observation --- the slopes are on the order of 10$^{-3}$.  
-However, within a distance of 0.05 \hMpc or 0.05$r_{vir}$, dwarf galaxies tend 
+However, within a distance of 0.05 \hMpc or 0.1$r_{vir}$, dwarf galaxies tend 
 to be bluer than at further distances from their nearest neighbor.  At distances 
@@
     have higher sSFRs than the wall dwarf galaxies.  Only the neighbor galaxies 
-    at separations less than 0.05 \hMpc or 0.05$r_{vir}$ appear to have some 
+    at separations less than 0.05 \hMpc or 0.1$r_{vir}$ appear to have some 
     affect on the dwarf galaxies' sSFR.  There appears to be no relationship 
@@
 
-Following our prediction for the color-distance relations, we expect that the 
-sSFR to increase with distance from the nearest neighbor.  We also see very 
-little relationship between the distance and sSFR in Fig. \ref{fig:sSFR}, except 
-in the smallest distance bin.  The linear fits quantify this observation --- the 
-slopes are on the order of 10$^{-3}$.  Within a distance of 0.05 \hMpc or 
-0.05$r_{vir}$, dwarf galaxies tend to have higher sSFRs than at further 
-distances from their nearest neighbor.  There does not appear to be any 
-relationship between a dwarf galaxy's sSFR and its distance to the center of the 
-nearest group in either distance metric.  In these distance comparisons, there 
-is a shift towards higher sSFRs in the void dwarf galaxies when compared to the 
-wall dwarf galaxies, as has been observed many times before \citep{Rojas05,
-vonBendaBeckmann08,Moorman15,Beygu16}.
+Following our prediction for the color-distance relations, we expect the 
+sSFR to decrease with distance from the nearest neighbor and increase with 
+distance from the nearest group.  We also see very little relationship between 
+the distance and sSFR in Fig. \ref{fig:sSFR}, except in the smallest distance 
+bin.  The linear fits quantify this observation --- the slopes are on the order 
+of 10$^{-3}$.  Within a distance of 0.05 \hMpc or 0.1$r_{vir}$, dwarf galaxies 
+tend to have higher sSFRs than at further distances from their nearest neighbor.  
+There does not appear to be any relationship between a dwarf galaxy's sSFR and 
+its distance to the center of the nearest group in either distance metric.  In 
+these distance comparisons, there is a shift towards higher sSFRs in the void 
+dwarf galaxies when compared to the wall dwarf galaxies, as has been observed 
+before \citep{Rojas05,vonBendaBeckmann08,Moorman15,Beygu16}.
 
@@
     Only the neighbor galaxies at separations less than 0.05 \hMpc or 
-    0.05$r_{vir}$ appear to have some affect on the dwarf galaxies' metallicity.  
+    0.1$r_{vir}$ appear to have some affect on the dwarf galaxies' metallicity.  
     When measuring the distance to the nearest group in \hMpc, it appears that 
@@
 
-Based on our hypothesis that galaxies would be redder and have lower sSFRs at 
+Based on our hypothesis that galaxies would be bluer and have higher sSFRs at 
 small distances to their nearest neighbors, we anticipated that the metallicity 
@@
 slopes are on the order of 10$^{-2}$.  Within a distance of 0.05 \hMpc or 
-0.05$r_{vir}$, dwarf galaxies tend to have higher metallicities than at further 
+0.1$r_{vir}$, dwarf galaxies tend to have higher metallicities than at further 
 distances from their nearest neighbor.  At distances less than 0.1 \hMpc from 
 the center of the nearest group, dwarf galaxies might have lower than average 
-metallicities.  However, this could be an erroneous conclusion due to low-number 
-statistics.  In these distance comparisons, there is a shift towards higher 
-metallicities in the void dwarf galaxies when compared to the wall dwarf 
-galaxies, as has been observed by \cite{Douglass17b} and Douglass \& Vogeley 
-(2017, in prep).
+metallicities.  However, this could be an erroneous conclusion due to 
+small-number statistics.  In these distance comparisons, there is a shift 
+towards higher metallicities in the void dwarf galaxies when compared to the 
+wall dwarf galaxies, as has been observed by \cite{Douglass17b} and Douglass et 
+al. (2017, in prep).
 
@@
     in N/H between the two large-scale environments.  Only the neighbor galaxies 
-    at separations less than 0.05$r_{vir}$ appear to have some affect on the 
+    at separations less than 0.1$r_{vir}$ appear to have some affect on the 
     dwarf galaxies' nitrogen abundance.  There does not appear to be any 
@@
 closest virial neighbor.  The linear fits quantify this observation --- the 
-slopes are on the order of 10$^{-2}$.  Within a distance of 0.05$r_{vir}$, dwarf 
+slopes are on the order of 10$^{-2}$.  Within a distance of 0.1$r_{vir}$, dwarf 
 galaxies tend to have higher nitrogen abundances than at distances further from 
@@
 of the nearest group.  Unlike the shifts seen with the other parameters and what 
-is observed in \cite{Douglass17b} and Douglass \& Vogeley (2017, in prep), we 
-see no significant difference in the nitrogen abundance resulting from the 
-large-scale environment.
+is observed in \cite{Douglass17b} and Douglass et al. (2017, in prep), we see no 
+significant difference in the nitrogen abundance resulting from the large-scale 
+environment.
 
@@
 We do not expect any influence on the relative synthesis of oxygen and nitrogen 
-from the proximity to a nearest neighbor.  Unlike the other parameters studied, 
+from the proximity to a nearest neighbor since nucleosynthesis is a physical 
+process unaffected by external influences.  Unlike the other parameters studied, 
 Fig. \ref{fig:NO} shows that the N/O ratio does not have any relationship with 
@@
 lower N/O ratios in star-forming void dwarf galaxies is readily apparent, as 
-\cite{Douglass17b} and Douglass \& Vogeley (2017, in prep) find.
+found by \cite{Douglass17b} and Douglass et al. (2017, in prep).
 
@@
 To quantify the results shown in Figs. \ref{fig:ur}--\ref{fig:NO}, we calculate 
-the parameters for the best fit linear line.  Any slope of significant magnitude 
+the parameters for the best linear fit.  Any slope of significant magnitude 
 shows an overall correlation between a given physical parameter and the galaxy's 
@@
 or group.  We look at how this affects our results by repeating the analysis 
-with maximum velocities of 150 km/s and 600 km/s.  The results of this 
-comparison on the color of the galaxies can be seen in Fig. 
-\ref{fig:ur_vpeculiar}.  The nearest neighbors in the left-hand panel are 
-restricted to a maximum peculiar velocity of 150 km/s, while those in the right 
-panel are restricted to 600 km/s.  When compared to each other and to the 
-left-hand panel of Fig. \ref{fig:ur}, it is clear that our choice of maximum 
-peculiar velocity has no affect on the results of the study.
+with maximum velocities of 150 km/s and 600 km/s \citep[the criteria used in][]
+{Hwang10,Guo11}.  The results of this comparison on the color of the galaxies 
+can be seen in Fig. \ref{fig:ur_vpeculiar}.  The nearest neighbors in the 
+left-hand panel are restricted to a maximum peculiar velocity of 150 km/s, while 
+those in the right panel are restricted to 600 km/s.  When compared to each 
+other and to the left-hand panel of Fig. \ref{fig:ur}, it is clear that our 
+choice of maximum peculiar velocity has no affect on the results of the study.
 
@@
     no correlation between distance and color, we do note that there is a gap in 
-    the distribution of galaxies around a distance of 0.05 \hMpc or 0.5$r_{vir}$ 
+    the distribution of galaxies around a distance of 0.05 \hMpc or 0.1$r_{vir}$ 
     from the nearest neighbor.}
@@
 Realizing that the peculiar velocity, which is included in a galaxy's redshift, 
-is not insignificant at the smaller scales, we have been careful to avoid 
+can be significant for galaxies in groups, we have been careful to avoid 
 calculating the distance between objects with the redshift.  However, we are 
@@
 We note the existence of a gap in the distribution of galaxies around a distance 
-of 0.05 \hMpc or 0.5$r_{vir}$ from the nearest neighbor that is not present in 
+of 0.05 \hMpc or 0.1$r_{vir}$ from the nearest neighbor that is not present in 
 Fig. \ref{fig:ur}.  When we incorporate the redshift into the distance 
@@
 target galaxy's immediate vicinity, implying that the small-scale environment 
-does not significantly influence a dwarf galaxy's evolution.  This is in 
-contrast to the large-scale environment, which we have seen to influence the 
-formation and evolution of dwarf galaxies.
+($\sim$1 \hMpc) does not significantly influence a dwarf galaxy's evolution.  
+This is in contrast to the large-scale environment, which we have seen to 
+influence the formation and evolution of dwarf galaxies.
 
-Only those galaxies within 0.05 \hMpc and 0.05$r_{vir}$ of a nearest neighbor, 
-or those within 0.1 \hMpc of the nearest group appear to deviate from the 
-average galaxy values.  The target galaxies within this proximity of their 
-nearest neighbor tend to be bluer, have a higher sSFR, and have higher oxygen 
-and nitrogen abundances.  Based on the shift in the distribution of galaxies 
-seen in Fig. \ref{fig:ur_xyz}, these galaxies might be merging or strongly 
-interacting with their nearest neighbor.  If so, this provides evidence that 
-galaxy interactions result in a burst of star formation that increases the 
-gas-phase chemical abundances of the dwarf galaxies.  Because merging galaxies 
-share the same dark matter halo, it appears that the sharing of a dark matter 
-halo has more influence on the evolution of a galaxy than the distance to its 
-nearest neighbor.
+Only those galaxies within 0.05 \hMpc and 0.1$r_{vir}$ of a nearest neighbor, or 
+those within 0.1 \hMpc of the nearest group appear to deviate from the average 
+galaxy values.  The target galaxies within this proximity of their nearest 
+neighbor tend to be bluer, have a higher sSFR, and have higher oxygen and 
+nitrogen abundances.  Based on the shift in the distribution of galaxies seen in 
+Fig. \ref{fig:ur_xyz}, these galaxies might be merging or strongly interacting 
+with their nearest neighbor.  If so, this provides evidence that galaxy 
+interactions result in a burst of star formation that increases the gas-phase 
+chemical abundances of the dwarf galaxies.  Because merging galaxies share the 
+same dark matter halo, it appears that the sharing of a dark matter halo has 
+more influence on the evolution of a galaxy than the distance to its nearest 
+neighbor.
 
@@
 
-\subsection{Comparison to literature results}
+\subsection{Comparison to previous results}
 
 The influence on the gas-phase oxygen abundance within 0.05 \hMpc and 
-0.05$r_{vir}$ agrees with the results of \cite{Shields91,Pustilnik06,Cooper08,
+0.1$r_{vir}$ agrees with the results of \cite{Shields91,Pustilnik06,Cooper08,
 Ellison09,Pustilnik11a,Pustilnik14}, and \cite{SanchezAlmeida16}, which all find 
@@
 A study combining the effects of interactions and the large-scale environment is 
-explained in \cite{Park09}.  They find two characteristic distances within which 
+presented in \cite{Park09}.  They find two characteristic distances within which 
 the behavior of the target galaxy changes: 0.05$r_{vir}$ and $r_{vir}$ of the 
@@
 than the target, \cite{Park09} find that the morphology and luminosity play a 
-significant role in these relationships.  Of particular note is their 
+significant role in these relationships.  Of particular interest is their 
 observation that star formation increases in late type galaxies when their 
 nearest neighbor is also of late type.  This is the same behavior we see in our 
-sample of dwarf galaxies at distances less than 0.05$r_{vir}$.  With all our 
+sample of dwarf galaxies at distances less than 0.1$r_{vir}$.  With all our 
 target galaxies actively forming stars, and more than half of their nearest 
@@
 see for those galaxies with nearest neighbors within 0.05 \hMpc and 
-0.05$r_{vir}$ warrant further study.
+0.1$r_{vir}$ warrant further study.
 
@@
 Using the star-forming dwarf galaxies in the SDSS DR7 sample with gas-phase 
-chemical abundances from Douglass \& Vogeley (2017, in prep), we investigate the 
+chemical abundances from Douglass et al. (2017, in prep), we investigate the 
 influence of the small-scale environment on the evolution of dwarf galaxies.  
 From the $\sim$2000 galaxies in the sample, there only appears to be an effect 
-from a neighboring galaxy within 0.05 \hMpc or 0.05$r_{vir}$.  The proximity of 
-a group seems to only affect the target dwarf galaxy if it is within 0.1 \hMpc.  
+from a neighboring galaxy within 0.05 \hMpc or 0.1$r_{vir}$.  The proximity of a 
+group seems to only affect the target dwarf galaxy if it is within 0.1 \hMpc.  
 Thus, the small-scale ($\sim 1$ \hMpc) environment does not appear to strongly 
@@
 and the target galaxy's color, sSFR, and gas-phase chemical abundances.  We find 
-that, for those galaxies with a neighbor within 0.05 \hMpc or 0.05$r_{vir}$, the 
+that, for those galaxies with a neighbor within 0.05 \hMpc or 0.1$r_{vir}$, the 
 dwarf galaxies are bluer, have a higher sSFR, and have higher oxygen and 
@@
 When we incorporate the redshift into the distance calculations, we find that 
-those galaxies within 0.05$r_{vir}$ are most likely mergers or strongly 
+those galaxies within 0.1$r_{vir}$ are most likely mergers or strongly 
 interacting with their nearest neighbor.  This matches the results of 
@@
 target galaxies with the nearest neighbors' properties as a function of 
-distance (``galactic conformity'').  The gas-phase chemical abundances between a 
-galaxy and its nearest neighbor could be strongly correlated.
+distance \citep[``galactic conformity'';][]{Weinmann06}.  The gas-phase chemical 
+abundances between a galaxy and its nearest neighbor could be strongly 
+correlated.

### 2017-06-16 KellyDouglass/Thesis/Thesis_sections/Paper3.tex
Added Paper 3

@@
-\chapter{Large-scale environmental dependence of chemical abundances in dwarf galaxies and implications for connecting star formation and halo mass}\label{ch:Paper3}
+\chapter[O$^+$ approximation]{Large-scale environmental dependence of chemical abundances in dwarf galaxies and implications for connecting star formation and halo mass}\label{ch:Paper3}
 
@@
 et. al (2017).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%    ABSTRACT
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{chapabstract}
+We study how the void environment affects the chemical evolution of galaxies in 
+the universe by comparing the oxygen and nitrogen abundances of dwarf galaxies 
+in voids with dwarf galaxies in denser regions.  Using spectroscopic 
+observations from the Sloan Digital Sky Survey Data Release 7, we estimate the 
+oxygen and nitrogen abundances of 993 void dwarf galaxies and 759 dwarf galaxies 
+in denser regions.  We use the Direct $T_e$ method for calculating the gas-phase 
+chemical abundances in the dwarf galaxies because it is best suited for low 
+metallicity, low mass (dwarf) galaxies.  A substitute for the [\ion{O}{2}] 
+$\lambda 3727$ doublet is developed, permitting oxygen abundance estimates of 
+SDSS dwarf galaxies at all redshifts with the Direct $T_e$ method.  We find that 
+void dwarf galaxies have slightly higher oxygen abundances ($\sim$7\%) than 
+dwarf galaxies in denser environments.  The opposite trend is seen in both the 
+nitrogen abundance and N/O ratio: void dwarf galaxies have slightly lower 
+nitrogen abundances ($\sim$10\%) and lower N/O ratios ($\sim$17\%) than dwarf 
+galaxies in denser regions.  Our mass-N/O relationship shows that the secondary 
+production of nitrogen commences at a lower stellar mass in void dwarf 
+star-forming galaxies than in dwarf star-forming galaxies in denser 
+environments.  We also find that star-forming void dwarf galaxies have higher 
+\ion{H}{1} masses than the star-forming dwarf galaxies in denser regions.  Our 
+star-forming dwarf galaxy sample demonstrates a strong anti-correlation between 
+the sSFR and N/O ratio, providing evidence that oxygen is produced in higher 
+mass stars than those which synthesize nitrogen.  The lower N/O ratios and 
+smaller stellar mass for secondary nitrogen production seen in void dwarf 
+galaxies may indicate both delayed star formation as predicted by $\Lambda$CDM 
+cosmology and a dependence of cosmic downsizing on the large-scale environment.  
+The shift toward higher oxygen abundances and higher \ion{H}{1} masses in void 
+dwarf galaxies might be evidence of larger ratios of dark matter halo mass to 
+stellar mass in voids than in denser regions.
+\end{chapabstract}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%    INTRODUCTION
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction}
+
+% Primary v. secondary production of nitrogen (reminder) & its influence on the CNO cycle
+%% What would cause less nitrogen to be produced in void galaxies?
+%Lower production rates of nitrogen relative to oxygen production in void dwarf 
+%galaxies could be a consequence of the retarded star formation predicted for 
+%dwarf galaxies in voids by the $\Lambda$CDM cosmology.  In stellar 
+%nucleosynthesis, there are two main classes of elements: primary and secondary.  
+%Primary elements are those produced which do not depend on the quantity of any 
+%other elements present in the star (excepting hydrogen, of course).  On the 
+%other hand, secondary elements can be synthesized only when other elements are 
+%already present in the star at the time of its birth.  Oxygen is a primary 
+%element in stellar nucleosynthesis.  There is evidence 
+%\textcolor{red}{(SOURCES)} to suggest that nitrogen behaves as both a primary 
+%and secondary element.  The main source of nitrogen production is during the CNO 
+%cycle, where carbon is needed as a catalyst for the reactions to begin.  If a 
+%star is born with enough carbon, then it commences the CNO cycle much earlier 
+%than in a star created with only hydrogen (or with only trace amounts of 
+%carbon).  If star formation is retarded in void dwarf galaxies, then there are 
+%fewer of the heavy elements that have been produced up to this point in time.  
+%As a result, the stars that are created have less carbon initially present in 
+%the star than in stars within wall dwarf galaxies, and less nitrogen will be 
+%produced.  Fig. \ref{fig:N_1sig} shows evidence of this fact --- there is 
+%slightly less nitrogen in void dwarf galaxies than in the dwarf galaxies in more 
+%dense environments.
+
+% Prominence of voids in large-scale structure 
+% (refs up through Pan et al., other recent void catalogs, ref to van Weygaert review)
+Galactic redshift surveys have revealed that the large-scale distribution of 
+galaxies is similar to a three-dimensional cosmic web \citep{Bond96}, with thin 
+filaments of galaxies connecting galaxy clusters separated by voids (large, 
+underdense areas which fill more than 60\% of space).  The voids first 
+identified in early surveys \citep[e.g.,][]{Gregory78,Kirshner81,deLapparent86} 
+have proven to be a universal feature of large-scale structure.  Analyses of the 
+Sloan Digital Sky Survey \citep{Abazajian09,Ahn12} have produced catalogs of 
+$10^3$ voids \citep{Pan12,Sutter14}.  Cosmic voids are an essential component for 
+understanding the role of a galaxy's environment on its formation and evolution 
+\citep[see][for a review]{vandeWeygaert11}.
+
+% Influence of the large-scale environment on galaxy properties
+%  - well-established morphology-density relation (refs starting with Dressler 1980; Postman & Geller 1984)
+%  - morphology-luminosity-density (Park et al. 2005?)
+%  - evidence that trend continues into voids, where galaxies are found to be bluer, later type, higher sSFR (Rojas et al.
+2004, 2005, who attribute this to availability of cool gas to feed star formation, and other refs)
+%  - shift of void galaxy luminosity function (Hoyle et al.; Moorman et al.)
+%  - consistent with shift of dark matter halo mass function (Goldberg et al.)
+%  - investigations of HI properties of void galaxies (Kreckel et al., Moorman et al.)
+%  - other refs to "Void galaxy survey" by Kreckel, van de Weygaert et al.
+Extensive studies have been performed to understand the role of the environment 
+in galaxy formation.  A strong relationship was found between a galaxy's 
+morphology and the local density \citep{Dressler80,Postman84}, where the 
+fraction of early-type galaxies increases with density.  A galaxy's luminosity 
+was found to also contribute to this morphology-luminosity-density relation 
+\citep{Park07}.  While much of this early work focused on trends of galaxy 
+properties in the densest regions of space, evidence was found that the same 
+trends persist into the voids, where galaxies are found to be bluer 
+\citep{Grogin99,Rojas04,Patiri06,vonBendaBeckmann08,Hoyle12}, of a later 
+morphological type \citep{Grogin00,Rojas04,Park07}, and have higher specific 
+star formation rates \citep[sSFR;][]{Rojas05,vonBendaBeckmann08,Moorman15,
+Beygu16}.  These trends are attributed to the availability of cool gas to feed 
+star formation in the void regions.  \cite{Hoyle05} and \cite{Moorman15} showed 
+that there is a shift toward fainter objects in the void galaxy luminosity 
+function.  This shift is consistent with the predicted shift of the dark matter 
+halo mass function \citep{Goldberg05}.  Investigations into the \ion{H}{1} 
+properties of void galaxies have also been performed \citep{Kreckel12,
+Moorman14}, where void galaxies tend to have lower \ion{H}{1} masses than 
+galaxies in denser environments.  All these observations are consistent with 
+predictions from the $\Lambda$CDM cosmology that void galaxies have lower masses 
+and be retarded in their star formation when compared to those in denser 
+environments \citep[e.g.,][]{Gottlober03,Goldberg05,Cen11}.
+
+% If sSFR are different, and evolutionary history different, is chemical evolution different?
+% Suggestions from previous work (Pustilnik et al, others) of very low metallicity in void galaxies
+Given that the sSFR and evolutionary history are different for galaxies in 
+voids, it follows that their chemical evolution might also be influenced by the 
+environment.  The metallicity of a galaxy (a measure of the integrated star 
+formation history) is an estimate of the percentage of the galaxy's gas that has 
+been processed in stars \citep{Guseva09}.  We would expect void galaxies to have 
+lower metallicities than those in denser regions if they have only recently 
+commenced forming stars or have recently accreted unprocessed gas.  Observations 
+by \cite{Cooper08,Deng11,Filho15,Pustilnik06,Pustilnik11a,Pustilnik11b,
+Pustilnik13,Pustilnik14}, and \cite{Pilyugin17} support the hypothesis that void 
+galaxies have lower metallicities than galaxies in denser regions.  However, 
+\cite{Kreckel15} and \cite{Douglass17a} find no influence from the large-scale 
+environment on the metallicity, and \cite{Douglass17b} find that void dwarf 
+galaxies have higher metallicities than dwarf galaxies in denser regions.  It is 
+obvious that a study of a statistically significant large sample of galaxies is 
+required to understand how the large-scale environment influences the chemical 
+evolution of galaxies.
+
+% Forcus on dwarf galaxies, which are most sensitive to effects of environment
+% SDSS allows void catalog (Pan et al.) and identification of statistically-significant samples of dwarf galaxies (Mr > -17) in voids
+% Discuss importance of careful use of metallicity (O/H) estimators - commonly used methods not calibrated for low mass galaxies, so we carefully used "direct" method
+% Summary of results in Douglass & Vogeley 2017a,b
+Environmental effects should be the most obvious on dwarf galaxies, since they 
+possess small gravitational potential wells.  As a result, they are more 
+sensitive to astrophysical effects such as cosmological reionization, internal 
+feedback from supernova and photoheating from star formation, external effects 
+from tidal interactions and ram pressure stripping, small-scale details of dark 
+matter halo assembly, and properties of dark matter.  The main galaxy sample of 
+SDSS DR7 covers a large enough volume to identify over 1000 voids \citep{Pan12} 
+along with a statistically-significant sample of dwarf galaxies ($M_r > -17$) in 
+voids.  SDSS also provides spectroscopy that permits metallicity estimates of 
+this large sample of dwarf galaxies.
+
+Numerous methods to estimate the metallicity of an object have been developed 
+over the years, as a result of the availability of various spectral features.  
+All methods except the direct $T_e$ method are calibrated on galaxies with 
+various characteristics, making it unwise to apply them to galaxies outside the 
+groups from which these calibrations were derived.  The commonly used methods 
+are not calibrated for low-mass galaxies, so we carefully chose to use the 
+Direct $T_e$ method because we are focusing on only dwarf galaxies.  A detailed 
+explanation of this and other method classes can be found in \cite{Douglass17a}.  
+With this estimator, \cite{Douglass17a} and \cite{Douglass17b} have looked at 
+the gas-phase chemical abundances of 135 star-forming dwarf galaxies.  They 
+found that the large-scale environment has very little influence on the oxygen 
+and nitrogen abundances in star-forming dwarf galaxies.  However, their sample 
+does indicate that star-forming void galaxies have lower N/O ratios than 
+star-forming dwarf galaxies in denser regions.  This is attributed to delayed 
+star formation in void galaxies, along with a possible environmental influence 
+on cosmic downsizing.  They also argue that the very slight shift towards higher 
+oxygen abundances in star-forming void dwarf galaxies could be due to a larger 
+ratio of dark matter halo mass to stellar mass in void dwarf galaxies.
+
+% In this paper...
+% New approach to O abundance estimation - allows use of larger sample.  Still using "direct" method.
+% Note that this work examines dwarf, star-forming galaxies only
+% Here we also examine HI properties
+% Known influence of environment on morphology already taken into account (well, not exactly because we select on emission lines, not morphology from photometry) - we look only at star-forming galaxies
+% Known influence of environment on luminosity already taken into account - we look only at dwarfs
+We look to expand on the work by \cite{Douglass17a,Douglass17b} by substantially 
+increasing their sample size of dwarf galaxies.  The main limiting factor in 
+their sample was due to the required detection of the [\ion{O}{2}] $\lambda$3727 
+doublet, which is needed to estimate the amount of singly-ionized oxygen 
+present.  We present a new approach to the O$^+$ abundance estimation, which 
+removes the need for this emission line.  This calculation is used in 
+conjunction with the Direct $T_e$ method to estimate the total gas-phase oxygen 
+abundance in galaxies.  We also examine the relationship between the chemical 
+abundance and \ion{H}{1} mass of star-forming dwarf galaxies.  For reasons 
+described above, this work only examines the chemical evolution of star-forming 
+dwarf galaxies.  As a result of this sample, the known influences of the 
+environment on the morphology and luminosity have already be taken into account, 
+since we concentrate only on star-forming dwarf galaxies.
+
+% THEORY
+% Discuss above as motivation or save for Discussion? - save for discusson (KAD)
+% Ref Cen simulation paper that shows that void have cool gas available for star formation
+% Ref Tonnesen & Cen simulation paper
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%    THEORY
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section[Theory]{Estimation of gas-phase chemical abundances from optical spectroscopy}
+
+We study a galaxy's oxygen and nitrogen abundances for several key reasons.  
+These two elements are relatively abundant and emit strong lines in the optical, 
+including for several ionization states in oxygen, making them relatively easy 
+to observe \citep{Kewley02}.  In addition, a ratio of oxygen's lines provides a 
+good estimate of the electron temperature, allowing for reliable measurements of 
+a galaxy's gas-phase chemical abundances.  The following is an explanation of 
+the theory and methods we employ to estimate the oxygen and nitrogen abundances 
+in dwarf galaxies.
+
+% ------------------------------------------------------------------------------
+\subsection{Direct $T_e$ method}\label{sec:DirectTe}
+
+We use the Direct $T_e$ method described in \cite{Izotov06} to estimate the 
+gas-phase abundances of oxygen and nitrogen in our sample of dwarf galaxies, 
+because this method is often regarded as the most accurate estimate of element 
+abundances.  It can be difficult to use due to the nature of the [\ion{O}{3}] 
+$\lambda$4363 auroral line \citep[for a more detailed discussion, see][]
+{Douglass17a}.  Since the strength of [\ion{O}{3}] $\lambda$4363 is inversely 
+proportional to the metallicity of a galaxy, it is best suited for low-redshift, 
+low-metallicity galaxies.  At metallicities 
+$12 + \log (\text{O}/\text{H}) \gtrsim 8.5$, [\ion{O}{3}] $\lambda$4363 becomes 
+too weak to detect in the SDSS spectra.  With the mass-metallicity (MZ) relation 
+by \cite{Tremonti04}, this metallicity limit corresponds to a maximum stellar 
+mass of
+\begin{align*}
+    12 + \log \left( \frac{\text{O}}{\text{H}} \right) &= -1.492 + 1.847(\log M_*) - 0.08026(\log M_*)^2\\
+    8.5 &= \\
+    \log \left( \frac{M_*}{M_\odot} \right) &= 8.696
+\end{align*}
+The MZ relation by \cite{Andrews13} estimates that this maximum metallicity 
+translates to a maximum stellar mass of
+\begin{align*}
+    12 + \log \left( \frac{\text{O}}{\text{H}} \right) &= 12 + \log \left( \frac{\text{O}}{\text{H}} \right)_{asm} - \log \left( 1 + \left( \frac{M_{TO}}{M_*} \right)^\gamma \right)\\
+    8.5 &= 8.798 - \log \left( 1 + \left( \frac{10^{8.901}}{M_*} \right)^{0.640} \right)\\
+    M_* &= 8.138\times 10^8 M_\odot\\
+    \log \left( \frac{M_*}{M_\odot} \right) &= 8.911
+\end{align*}
+These upper limits on the galaxy stellar masses correspond to the maximum mass 
+of a dwarf galaxy in SDSS ($\log (M_*/M_\odot) \approx 9$).  Therefore, we can 
+expect to estimate the chemical abundances of only dwarf galaxies in SDSS DR7 
+with the Direct $T_e$ method.  Higher resolution spectra would be necessary to 
+probe higher mass, higher metallicity galaxies.
+
+After solving for the temperature of the gas, we can 
+calculate the amount of each element present in each of the ionization stages.  
+The total gas-phase oxygen abundance is equal to the sum of the abundances of 
+each of the ionized populations:
+\begin{equation}
+	\frac{\text{O}}{\text{H}} = \frac{\text{O}^{++}}{\text{H}^+} + \frac{\text{O}^+}{\text{H}^+}
+\end{equation}
+
+We use an ionization correction factor (ICF) to account for the missing stages 
+of nitrogen, since we can observe nitrogen in only one of its main ionization 
+stages.  The total abundance for a particular element $X$ is 
+\begin{equation}
+    \frac{\text{X}}{\text{H}} = \sum_i ICF_i \frac{\text{X}^i}{\text{H}}
+\end{equation}
+For nitrogen, we employ the ICFs used in \cite{Douglass17b}.
+
+% ------------------------------------------------------------------------------
+\subsection{O$^+$ abundance approximation}\label{sec:Oplus_approx}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{Images/Paper3/Zlow_v_Zreal_1sig_I06_BPTclass_fits}
+    \caption{$12 + \log{\text{O}^{++}/\text{H}}$ versus 
+    $12 + \log{\text{O}/\text{H}}$ for those galaxies with $M_r > -20$ as 
+    calculated with the direct method; the galaxies are colored by their 
+    classification in the BPT diagrams (from \cite{Brinchmann04}).  Two linear 
+    models have been fit to three groups in the sample: star-forming and 
+    AGN/composite galaxies; the best fit parameters can be found in Table 
+    \ref{tab:ab}.}
+    \label{fig:lowVreal}
+\end{figure}
+
+We derive an ICF for O$^+$ to overcome some limitations on the observations of 
+dwarf galaxies in SDSS to bolster our sample size.  Because we are studying 
+dwarf galaxies, the [\ion{O}{2}] $\lambda 3727$ doublet necessary for estimating 
+the abundance of O$^+$ is only available for objects within the redshift range 
+$0.02 < z < 0.03$ \citep[see Sec. \ref{sec:SDSS_limits} and][for more 
+details]{Douglass17a}.  To be able to study SDSS galaxies at redshifts less than 
+0.02, we need to find an alternate way to estimate the abundance of O$^+$.  
+Ordinarily, we would use an ICF to replace the missing ionization stage, as 
+outlined in Sec. \ref{sec:DirectTe} for the nitrogen abundance.  Because the 
+[\ion{O}{2}] $\lambda 3727$ emission line is normally available for analysis, 
+there are no approximations available for the ICF for the amount of 
+singly-ionized oxygen.  To construct an ICF appropriate for our dwarf galaxy 
+sample, we compare $12 + \log{\text{O/H}}$ to 
+$12 + \log{\text{O}^{++}/\text{H}}$ as calculated by the Direct $T_e$ method for 
+all galaxies in SDSS with $M_r > -20$.  Recognizing that the relative amounts of 
+singly- and doubly-ionized oxygen will depend on the hardness of a galaxy's 
+spectrum, we use a Baldwin-Phillips-Terlevich (BPT) diagram \citep{Baldwin81} to 
+classify each galaxy as star-forming, AGN, or composite (containing 
+characteristics of both a star-forming region and an AGN).  Noting a strong 
+separation in the relationship between O$^{++}$/H and O/H with respect to the 
+galaxies' BPT classifications by \cite{Brinchmann04}, we fit two linear models 
+to the sample, seen in Fig. \ref{fig:lowVreal} and defined as 
+\begin{equation}\label{eq:fit}
+    12 + \log{\text{O}/\text{H}} = a(12 + \log{\text{O}^{++}/\text{H}}) + b
+\end{equation}
+The values for $a$ and $b$ for the two classes are listed in Table \ref{tab:ab}.
+
+\floattable
+\begin{deluxetable}{L|C|C|C}
+    \tablewidth{0pt}
+    \tablecaption{Coefficients of oxygen abundance fits\label{tab:ab}}
+    \tablehead{\colhead{} & \colhead{SF (dwarf)} & \colhead{SF ($M_r > -20$)} & \colhead{AGN \& Composite}}
+    \startdata
+        a & 0.84 \pm 0.013 & 0.824 \pm 0.0010 & 0.764 \pm 0.0035\\
+        b & 1.61 \pm 0.094 & 1.787 \pm 0.0065 & 2.05 \pm 0.023\\
+    \enddata
+    \tablecomments{Coefficients for the linear trends (Eqn. \ref{eq:fit}) fit to 
+    the SF galaxies (dwarf and those with $M_r > -20$) and AGN and composite 
+    galaxies.  With these trends, we can now calculate the total oxygen 
+    abundance for a galaxy with knowing only the O$^{++}$/H abundance.}
+\end{deluxetable}
+
+As expected, the star-forming galaxies have less doubly ionized oxygen than 
+both the composite and AGN galaxies.  Since the degree of ionization depends on 
+the temperature of the stars ionizing the gas, this means that the star-forming 
+galaxies have cooler ionizing sources than the composite and AGN galaxies.
+
+For those star-forming dwarf galaxies for which [\ion{O}{2}] $\lambda$3727 is 
+not observed in the SDSS spectra, we use the coefficients for the star-forming 
+dwarf galaxies with Eqn. \ref{eq:fit} to calculate the total oxygen abundance in 
+the galaxy based on the amount of doubly-ionized oxygen found with Eqn. 4 of 
+\cite{Douglass17a}.  While we list the coefficients for the linear models of 
+both those galaxies with absolute magnitudes $-17 > M_r > -20$ and the AGN and 
+composite galaxies in Table \ref{tab:ab}, we do not use them to calculate the 
+chemical abundances of these galaxies for the reasons outlined in Section 
+\ref{sec:DirectTe}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%    DATA
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{SDSS data and galaxy selection}
+
+The SDSS Data Release 7 (DR7) \citep{Abazajian09} is a wide-field multiband 
+imaging and spectroscopic survey employing a drift scanning technique to map 
+approximately one-quarter of the northern sky.  Photometric data in the 
+five-band SDSS system --- $u$, $g$, $r$, $i$, and $z$ --- are taken with a 
+dedicated 2.5-meter telescope at the Apache Point Observatory in New Mexico 
+\citep{Fukugita96, Gunn98}.  Follow-up spectroscopic analysis is performed on 
+galaxies with a Petrosian $r$-band magnitude $m_r < 17.77$ \citep{Lupton01, 
+Strauss02}.  The spectra are taken using two double fiber-fed spectrometers and 
+fiber plug plates with a minimum fiber separation of 55"; the observed 
+wavelength range is $3800\text{\AA}$ to $9200\text{\AA}$ with a resolution 
+$\lambda / \Delta \lambda \sim$1800 \citep{Blanton03}.  We use emission-line 
+flux data from the MPA-JHU value-added catalog\footnote{Available at 
+\url{http://www.mpa-garching.mpg.de/SDSS/DR7/}}, which is based on the SDSS DR7 
+sample of galaxies.  All flux values have been corrected for dust reddening with 
+the \cite{Cardelli89} extinction curve as implemented in pyNeb 
+\citep{Luridiana15}; we assume the theoretical ratio H$\alpha$/H$\beta = 2.86$ 
+at 10,000 K and 100 cm$^{-3}$ \citep{Osterbrock89}.
+
+We use the stellar mass estimates from the NASA-Sloan Atlas \citep{Blanton11}.  
+The \ion{H}{1} mass estimates are from the 70\% complete ALFALFA catalog 
+$\alpha.70$ \citep{Giovanelli05}; \ion{H}{1} detections were matched to the SDSS 
+galaxies by locating the nearest optical counterpart identified in the 
+$\alpha.70$ catalog within 1 arcmin.  Absolute magnitudes, colors, and all other 
+additional data are from the KIAS value-added galaxy catalog 
+\citep{Choi10,Blanton05}.  Galaxy colors are rest-frame colors which have been 
+$K$-corrected to a redshift of 0.1; they are corrected for galactic extinction 
+and calculated with model magnitudes.  All galaxies have been visually inspected 
+to remove any galaxy fragments or duplicates.
+
+%-------------------------------------------------------------------------------
+\subsection{Spectroscopic selection}\label{sec:SDSS_limits}
+
+We employ the same requirements for our sample as in 
+\cite{Douglass17a,Douglass17b}: all galaxies must have
+\begin{enumerate}
+    \item{$M_r > -17$ (dwarf galaxies);}
+    \item{a minimum $5\sigma$ detection of H$\beta$;}
+    \item{a minimum $1\sigma$ detection of [\ion{O}{3}] $\lambda 4363$;}
+    \item{a flux $> 0$ for [\ion{O}{2}] $\lambda 3727$, [\ion{O}{3}] $\lambda \lambda 4959,5007$, and [\ion{N}{2}] $\lambda \lambda 6548,6584$;}
+    \item{$T(\text{[\ion{O}{3}]}) > 3\times 10^4 \text{ K}$;}
+    \item{a star-forming BPT classification by \cite{Brinchmann04}.}
+\end{enumerate}
+
+For those galaxies with a redshift $z \gtrsim 0.02$, we use the 
+\texttt{oii\_flux} value from the MPA-JHU catalog in place of their [\ion{O}{2}] 
+$\lambda \lambda 3726,3729$ flux measurement.  See \cite{Douglass17a} for 
+further details on each of these requirements.
+
+%-------------------------------------------------------------------------------
+\subsection{Void classification}
+% Re-write to avoid plagarizing myself :P
+
+Void galaxies are identified using the void catalog compiled by \cite{Pan12}, 
+which was built based on the galaxies in SDSS DR7 catalog.  Starting with 
+galaxies with absolute magnitudes $M_r < -20$, the VoidFinder algorithm of 
+\cite{Hoyle02} \citep[based on the algorithm described by][]{ElAd97} removes all 
+isolated galaxies (defined as having the third nearest neighbor more than 7 
+$h^{-1}$ Mpc away).  After applying a grid to the remaining galaxies, spheres 
+are grown from all empty grid cells (cells containing no galaxies).  A sphere 
+reaches its maximum size when it encounters four galaxies on its surface.  To be 
+classified as a void (or part of one), a sphere must have a minimum 10 Mpc 
+radius.  If two spheres overlap by more than 10\%, they are considered part of 
+the same void.  See \cite{Hoyle02} for a more detailed description of the 
+VoidFinder algorithm.  Those galaxies that fall within these void spheres are 
+classified as voids.  Those galaxies that lie outside the spheres are classified 
+as wall galaxies.  Because we cannot identify any voids within 10 Mpc of the 
+edge of the survey, we do not include the galaxies that fall within this region 
+in either the void or wall sample (throughout this paper, these galaxies are 
+labeled as ``Uncertain'').
+
+Of the $\sim$800,000 galaxies with spectra available in SDSS DR7, 9519 are 
+dwarf galaxies.  Applying the spectroscopic cuts, our sample includes 993 void 
+dwarf galaxies and 759 wall dwarf galaxies.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%    ANALYSIS & RESULTS
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Abundance analysis and results}
+
+Our primary objective is to perform a relative measurement of gas-phase 
+abundances of dwarf galaxies to discern how their chemical evolution is affected 
+by the large-scale environment.
+
+%Our primary objective is to perform a relative measurement of metallicity of 
+%dwarf galaxies to discern how the large-scale environment affects their chemical 
+%evolution.  As discussed in Section \ref{sec:Theory}, the strength of and 
+%ability to observe different spectral lines between various surveys and 
+%observations require multiple methods to be developed for metallicity 
+%calculations.  In this paper, we use only the Direct $T_e$ method, because no 
+%other method has yet been calibrated using dwarf galaxies.  The results from the 
+%various methods are not directly comparable; while they all return metallicities 
+%within the same range, the same galaxy can have very different metallicity 
+%values depending on which method is used.  Conversions between methods have been 
+%developed \citep[see][]{Kewley08}, but it is not clear that these conversions 
+%would be accurate for dwarf galaxies.  Unfortunately, there are not enough 
+%galaxies available in our sample to calibrate these other methods for dwarf 
+%galaxies.
+
+All line ratios listed are ratios of the emission-line fluxes.  Galaxies with 
+low metallicities have $Z = 12 + \log (\text{O}/\text{H}) < 7.6$ 
+\citep{Pustilnik06}; galaxies with high metallicities have $Z > 8.2$ 
+\citep{Pilyugin06}.  The solar metallicity $Z_\odot = 8.86$ \citep{Delahaye06}.
+
+%-------------------------------------------------------------------------------
+\subsection{Estimation of uncertainties}
+
+% Uncertainties
+Uncertainties in the computed abundances are estimated using a Monte-Carlo 
+method.  Using the measured line fluxes and scaled uncertainty estimates, we 
+calculate 100,000 abundance estimates.  For each abundance estimate, a new 
+positive ``fake'' line flux is drawn from a normal distribution.  We use the 
+standard deviation in these sets of 100,000 calculated abundance values for the 
+error in our abundance estimate.  See \cite{Douglass17a} for a more in-depth 
+description of this process.
+
+%-------------------------------------------------------------------------------
+\subsection{Sources of systematic error}
+
+Many physical properties of galaxies exhibit a radial dependence \citep{Bell00}.  
+As a result, abundance estimates can depend on where the spectroscopic fiber is 
+placed on the galaxy.  The estimated abundance will not necessarily be 
+representative of a global abundance value if not all of the galaxy's light is 
+contained within the fiber.  \cite{Belfiore17} show that both the metallicity 
+and N/O ratio gradients are relatively flat for lower mass galaxies 
+($\log(M/M_\odot) = 9$) and steepen with increasing stellar mass.  In SDSS DR7, 
+the spectroscopic fiber diameter is 3"; this corresponds to a minimum physical 
+diameter of 1.31 $h^{-1}$kpc at a redshift $z < 0.03$.  For most of the dwarf 
+galaxies in this study, this contains the majority of their angular size.  
+Assuming the abundance gradients remain flat for dwarf galaxies as suggested by 
+the results of \cite{Belfiore17}, then our estimates of the gas-phase chemical 
+abundances for our sample of dwarf galaxies are independent of the location of 
+the spectral fiber on the galaxies' surfaces.
+
+The selection criteria outlined in Section \ref{sec:SDSS_limits} limit our 
+sample to only star-forming dwarf galaxies.  As a result, this is not a 
+representative sample of the entire dwarf galaxy population.  We are only able 
+to discuss the influence of the large-scale environment on star-forming dwarf 
+galaxies in this study.  Unfortunately, it is impossible to estimate the 
+chemical abundances of red dwarf galaxies with the direct $T_e$ method because 
+the UV photons from young stars are needed to excite the interstellar gas.
+
+%-------------------------------------------------------------------------------
+\subsection{Dwarf galaxy abundances}
+
+% Results table (machine-readable)
+\floattable
+\input{results_table_short}
+
+The abundances estimated using the direct $T_e$ method for our dwarf galaxy 
+sample are listed in Table \ref{tab:Results}.  Also included are other 
+significant characteristics and identification for the galaxies, including their 
+large-scale environmental classification.
+
+\subsubsection{Oxygen and nitrogen abundances}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.49\textwidth]{1sig_dwarf_SF_t3_12logOHrelations_dust_hist}
+    \includegraphics[width=0.49\textwidth]{1sig_dwarf_SF_t3_12logOHrelations_dust_CDF}
+    \caption{Gas-phase metallicity of void dwarf (red solid line) and wall 
+    dwarf (black dashed line) galaxies.  A two-sample K-S test of the two data 
+    sets results in an asymptotic $p$-value of 0.12, indicating a 12\% 
+    probability that a test statistic greater than the observed value of 0.06 
+    will be seen if the void sample is drawn from the wall sample.  This is 
+    reflected visually, as there appears to be a slight but statistically 
+    significant significant large-scale environmental influence on the 
+    metallicity of dwarf galaxies.}
+    \label{fig:met1sig}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.49\textwidth]{1sig_dwarf_SF_t3_12logNHrelations_dust_hist}
+    \includegraphics[width=0.49\textwidth]{1sig_dwarf_SF_t3_12logNHrelations_dust_CDF}
+    \caption{Abundance of nitrogen relative to hydrogen of void dwarf (red solid 
+    line) and wall dwarf (black dashed line) galaxies.  A two-sample K-S test of 
+    the two data sets results in an asymptotic $p$-value of 0.015, indicating a 
+    1.5\% probability that a test statistic greater than the observed value of 
+    0.08 will be seen, if the void sample is drawn from the wall sample.  This 
+    is reflected visually, as the void dwarf galaxies appear to have lower 
+    values of the N/H ratio than the wall dwarf galaxies.  There is a 
+    large-scale environmental dependence of the chemical evolution of dwarf 
+    galaxies.}
+    \label{fig:N_1sig}
+\end{figure*}
+
+The distributions of oxygen and nitrogen abundances for dwarf galaxies as a 
+function of large-scale environment are shown in Figures \ref{fig:met1sig} and 
+\ref{fig:N_1sig}, respectively.  Both histograms show a slight shift between 
+voids and walls in the chemical abundances of dwarf galaxies.  A two-sample 
+Kolmogorov-Smirnov (K-S) test quantifies this observation --- a test statistic 
+of 0.06 for oxygen and 0.08 for nitrogen are produced, corresponding to a 
+probability of 12\% and 1.5\%, respectively, that a test statistic greater than 
+or equal that observed will be measured if the void sample were drawn from the 
+wall sample.  The cumulative distribution function (CDF) for each of these 
+elements can be seen on the right in Figures \ref{fig:met1sig} and 
+\ref{fig:N_1sig}; they show that void dwarf galaxies have slightly higher oxygen 
+abundances and slightly lower nitrogen abundances than dwarf galaxies in more 
+dense regions.  The K-S test quantifies the visual interpretation of these 
+figures that the distributions of oxygen and nitrogen abundances are slightly 
+different for star-forming dwarf galaxies in voids and walls.
+
+The average and median values of the dwarf galaxy abundances also indicate a 
+shift as a result of the large-scale environment.  The average oxygen abundance 
+for void dwarf galaxies is $7.99\pm 0.007$ and the median is 8.06, while the 
+average oxygen abundance for wall dwarf galaxies is $7.96\pm 0.009$ with a 
+median value of 8.04.  This implies that the void dwarf galaxies have higher 
+oxygen abundances by about 7\% (average shift of $0.03\pm 0.012$; median shift 
+of 0.03) relative to wall dwarf galaxies.  In contrast, the average nitrogen 
+abundance for void dwarf galaxies is only $6.55\pm 0.007$ with a median of 6.58, 
+while the wall dwarf galaxies have an average nitrogen abundance of 
+$6.58\pm 0.008$ and a median of 6.60.  The void dwarf galaxies have lower 
+nitrogen abundances by about 10\% (an average shift of $0.04\pm 0.011$ and a 
+median shift of 0.02) relative to wall dwarf galaxies.  A tabular version of 
+this analysis can be found in Table \ref{tab:stats}.
+
+\subsubsection{Ratio of nitrogen to oxygen}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.49\textwidth]{1sig_dwarf_SF_t3_logNOrelations_dust_hist}
+    \includegraphics[width=0.49\textwidth]{1sig_dwarf_SF_t3_logNOrelations_dust_CDF}
+    \caption{Ratio of nitrogen to oxygen of void dwarf (red solid line) and wall 
+    dwarf (black dashed line) galaxies.  A two-sample K-S test of the two data 
+    sets results in an asymptotic $p$-value of $2.6\times 10^{-4}$, indicating 
+    only a 0.03\% probability that a test statistic greater than the observed 
+    value of 0.10 will be seen.  This is reflected visually, as there is a shift 
+    in the N/O ratio between the two populations of dwarf galaxies --- the void 
+    galaxies have a lower value of N/O than the wall galaxies.  There is a 
+    large-scale influence on the relative chemical abundances of dwarf 
+    galaxies.}
+    \label{fig:NOratio}
+\end{figure*}
+
+The ratio of nitrogen to oxygen is also important to investigate, as it 
+communicates the nucleosynthesis history of the galaxies.  As seen in Fig. 
+\ref{fig:NOratio}, the N/O abundance ratio also indicates a large-scale 
+environmental influence on the chemical evolution of dwarf galaxies --- void 
+dwarf galaxies have lower N/O ratios than dwarf galaxies in denser regions.  
+This difference is quantified in the K-S test: the test returned a probability of 
+only 0.03\% that a test statistic greater than or equal to 0.10 will be measured 
+if the void sample was drawn from the wall sample.  The distribution of N/O 
+abundance ratios for void dwarf galaxies is lower by about 17\% (an average 
+shift of $0.07\pm 0.016$ and a median shift of 0.06) relative to the 
+distribution of N/O ratios in wall dwarf galaxies.
+
+% Statistics table
+\floattable
+\begin{deluxetable}{ccccccc}
+    \tablewidth{0pt}
+    \tablecolumns{7}
+    \tablecaption{Abundance statistics\label{tab:stats}}
+    \tablehead{\colhead{Environment} & \colhead{Average} & \colhead{Median} & \colhead{Average Shift\tablenotemark{a}} & \colhead{Median Shift\tablenotemark{a}} & \colhead{$p$-value} & \colhead{K-S Test Statistic}}
+    \startdata
+        % Oxygen %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+        \cutinhead{$12 + \log (\text{O}/\text{H})$}
+        Void & $7.99\pm 0.007$ & 8.06 & \multirow{2}{*}{$-0.03\pm 0.012$} & \multirow{2}{*}{-0.03} & \multirow{2}{*}{0.1197} & \multirow{2}{*}{0.0569}\\
+        Wall & $7.96\pm 0.009$ & 8.04 & & & & \\
+        % Nitrogen %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+        \cutinhead{$12 + \log (\text{N}/\text{H})$}
+        Void & $6.55\pm 0.007$ & 6.58 & \multirow{2}{*}{$0.04\pm 0.011$} & \multirow{2}{*}{0.02} & \multirow{2}{*}{0.0149} & \multirow{2}{*}{0.0750}\\
+        Wall & $6.58\pm 0.008$ & 6.60 & & & & \\
+        % N/O %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+        \cutinhead{$\log (\text{N}/\text{O})$}
+        Void & $-1.45\pm 0.010$ & -1.43 & \multirow{2}{*}{$0.07\pm 0.016$} & \multirow{2}{*}{0.06} & \multirow{2}{*}{0.0003} & \multirow{2}{*}{0.1013}\\
+        Wall & $-1.38\pm 0.012$ & -1.37 & & & & \\
+    \enddata
+    \tablecomments{Statistics on the gas-phase oxygen, nitrogen, and nitrogen 
+    relative to oxygen abundances in dwarf void and wall galaxies.  Combined 
+    with the histograms in Figures \ref{fig:met1sig}--\ref{fig:NOratio}, these 
+    results indicate an influence on the chemical evolution of galaxies by the 
+    large-scale environment, especially on the relative abundance of nitrogen to 
+    oxygen.  Void galaxies have slightly higher oxygen and nitrogen abundances 
+    than wall galaxies, but void galaxies have slightly lower N/O ratios than 
+    wall galaxies.}
+    \tablenotetext{a}{Wall -- Void (Positive shifts indicate that the wall 
+    values are greater than the void values; negative shifts indicate that the 
+    void values are greater than the wall values.)}
+\end{deluxetable}
+
+%-------------------------------------------------------------------------------
+\subsection{Comparison to previously published oxygen abundance estimates}
+% Compare to Tremonti et al. (2004)
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{1sig_dwarf_I06relations_SF_t3_T04comparison_dust}
+    \caption{Oxygen abundance comparison between our calculated estimates with 
+    the O$^+$ approximation and those made by \cite{Tremonti04}.  Error bars 
+    have been omitted for clarity.  While the majority of our abundance 
+    estimates agree reasonably well with the values already published, it is 
+    clear that our estimates are often lower than the previously published 
+    values.  It is well known that the strong-line methods \citep[like those 
+    used by][]{Tremonti04} overestimate the oxygen abundance by as much as 0.3 
+    dex \citep{Kennicutt03}.  Therefore, it is not surprising that the oxygen 
+    abundances measured using the direct $T_e$ method are lower, particularly at 
+    very low metallicities.}
+    \label{fig:T04_comp}
+\end{figure}
+
+While no estimates of the nitrogen or N/O abundances have been made on a large 
+selection of the SDSS galaxies, we can compare our oxygen abundance estimates to 
+the metallicity values measured by \cite{Tremonti04}.  While we both use data 
+from the MPA-JHU value-added catalog, \cite{Tremonti04} employs an empirical 
+method to calculate the metallicity that is based on calibrated relationships 
+between direct $T_e$ methods and strong-line ratios.  The results of this 
+comparison are shown in Fig. \ref{fig:T04_comp}.  While the majority of our 
+abundance estimates agree reasonably well with the values calculated by 
+\cite{Tremonti04}, it is also clear that our estimates often predict abundances 
+lower than those previously published.  This is especially true for the low 
+metallicity regime ($12 + \log \left(\text{O}/\text{H}\right) < 7.6$).  Methods 
+which are based on calibrations rarely use low metallicity galaxies in their 
+source for calibrating.  As a result, empirical methods will often overestimate 
+the abundance values, especially in the low-metallicity regime.  
+\cite{Kennicutt03} show that strong-line methods (methods which make extreme use 
+of the strong emission lines) can overestimate the metallicity abundances by as 
+much as 0.3 dex.  Therefore, we are not surprised at the apparent lack of 
+correlation between our oxygen abundance estimates and those of 
+\cite{Tremonti04}.
+
+%-------------------------------------------------------------------------------
+\subsection{N/O versus O/H} \label{sec:NO_OH}
+
+\begin{figure}
+    \centering
+%    \includegraphics[width=0.5\textwidth]{1sig_I06relations_dwarf_SF_t3_dust_Z12logOH_logNO}
+%    \includegraphics[width=0.5\textwidth]{1sig_I06relations_dwarf_SF_t3_dust_Z12logOH_logNO_Mbin}
+%    \includegraphics[width=0.5\textwidth]{1sig_I06relations_dwarf_SF_t3_dust_Z12logOH_logNO_scatterMbin}
+    \includegraphics[width=0.5\textwidth]{1sig_I06relations_dwarf_SF_t3_dust_NSA_Z12logOH_logNO_scatterMbin}
+    \caption{Oxygen abundance ($12 + \log \left(\text{O}/\text{H}\right)$) 
+    versus the N/O ratio ($\log \left( \text{N}/\text{O}\right)$) for the dwarf 
+    galaxies in this study; the average values of the galaxies' abundances when 
+    binned by stellar mass in bins of width 0.1 are also shown.  As seen in 
+    \cite{Andrews13} and \cite{Douglass17b}, while most of the mass bins are 
+    scattered together around $\log (\text{N}/\text{O}) \sim$-1.5, there is a 
+    negative correlation between these two abundance ratios.  There is no 
+    evidence of secondary nitrogen production in this sample of star-forming 
+    dwarf galaxies, which would manifest as a positive relationship between 
+    O/H and N/O at high metallicities.}
+    \label{fig:NOvOH}
+\end{figure}
+
+Studying how the N/O ratio depends on the metallicity (gas-phase oxygen 
+abundance) probes the nucleosynthetic production of nitrogen in stars within the 
+galaxies.  It is believed that nitrogen can be produced as both a primary and 
+secondary element, depending on the initial metallicity of the stars.  If there 
+are enough of the heavy elements available when the stars are created (oxygen, 
+carbon, etc.), then the CNO cycle can commence much earlier in the star's 
+lifetime, resulting in a higher production of nitrogen than if the star is 
+originally created with very few heavy elements.  If this is the case, then we 
+should see no relationship between the N/O ratio and the oxygen abundance below 
+a certain metallicity value (the primary nitrogen production phase); above this 
+threshold metallicity, the N/O value should increase linearly with the oxygen 
+abundance (the secondary nitrogen production phase).
+
+As we see in Fig. \ref{fig:NOvOH}, there is no evidence of a secondary nitrogen 
+production phase in our sample of dwarf galaxies.  This is in contrast with the 
+evidence of secondary nitrogen production seen in Fig. \ref{fig:M_NO} of Sec. 
+\ref{sec:Mass}; the source of this discrepancy is unclear.  The relationship 
+between metallicity and the N/O ratio instead shows a large scatter with no 
+clear correlation between the N/O ratio and the oxygen abundance at metallicity 
+values higher than $\sim$7.9.  Below this value, we actually observe a negative 
+correlation between the N/O ratio and the oxygen abundance.  This would indicate 
+a constant value of nitrogen being synthesized in the galaxies independent of 
+the amount of oxygen being produced.  A negative correlation similar to this was 
+also observed by \cite{Andrews13} and \cite{Douglass17b}.   \cite{Andrews13} 
+note that they measure a slope of -0.21 for their stellar mass-binned galaxies 
+with metallicities $12 + \log(\text{O}/\text{H}) < 8.5$, while 
+\cite{Douglass17b} finds a slope of $-0.38\pm 0.078$ for dwarf galaxies.  A 
+linear fit to our dwarf galaxy sample has a slope of $-0.52\pm 0.041$, steeper 
+than any previously measured.
+
+\begin{figure}
+%    \includegraphics[width=0.5\textwidth]{1sig_I06relations_dwarf_SF_t3_dust_Z12logOH_N12logNH_scatterMbin}
+    \includegraphics[width=0.5\textwidth]{1sig_I06relations_dwarf_SF_t3_dust_NSA_Z12logOH_N12logNH_scatterMbin}
+    \caption{Oxygen abundance ($12 + \log \left(\text{O}/\text{H}\right)$) 
+    versus nitrogen abundance ($12 + \log \left(\text{N}/\text{H}\right)$) for 
+    the dwarf galaxies in this study; the average values of the galaxies' 
+    abundances when binned by their stellar mass in bins of width 0.1 are also 
+    shown.  There is evidence of two evolutionary tracks for the star-forming 
+    dwarf galaxies here, one with a much steeper slope than the other.}
+    \label{fig:OvN}
+\end{figure}
+
+Similar evidence of the nitrogen production phases can also be observed when 
+looking at the relationship between the nitrogen and oxygen abundances relative 
+to hydrogen.  Fig. \ref{fig:OvN} depicts a negative relationship between the 
+nitrogen and oxygen abundances.  A linear fit to the dwarf galaxies results in a 
+slope of $0.48\pm 0.041$, less than the slope of $0.62\pm 0.078$ found by 
+\cite{Douglass17b}.  These slopes both indicate that nitrogen is produced at a 
+slower rate than oxygen in dwarf galaxies.  A nitrogen plateau in Fig. 
+\ref{fig:NOvOH} would manifest itself as a relationship between the N/H and O/H 
+ratios (shown in Fig. \ref{fig:OvN}) with a linear slope of 1.  Secondary 
+nitrogen production, a positive relationship in Fig. \ref{fig:NOvOH}, would 
+correspond to a relationship between N/H and O/H in Fig. \ref{fig:OvN} with a 
+slope greater than 1.  If we split the dwarf galaxies into two populations based 
+on their metallicity, we find that dwarf galaxies with extremely low 
+metallicities ($12 + \log (\text{O}/\text{H}) \leq 7.6$) have a slope of 
+$-1.0\pm 0.21$ in Fig. \ref{fig:NOvOH} and $-0.0\pm 0.21$ in Fig. \ref{fig:OvN}, 
+while the dwarf galaxies with metallicities $12 + \log(\text{O}/\text{H} > 7.6$ 
+have a slope of $-0.41\pm 0.069$ for O/H v. N/O and $0.59\pm 0.069$ for O/H v. 
+N/H.  These slopes indicate that the production of nitrogen is independent of 
+the oxygen abundance in systems with low metallicities, supporting the results 
+found in \cite{Douglass17b}.
+
+Fig. \ref{fig:OvN} shows possible evidence for two evolutionary tracks for 
+star-forming dwarf galaxies, irrespective of the large-scale environment.  The 
+dwarf galaxies with extremely low metallicities appear to have less of a 
+correlation between their oxygen and nitrogen abundances than those dwarf 
+galaxies with higher metallicities.  The two tracks appear to merge between 
+metallicity values $8 < 12 + \log(\text{O}/\text{H}) < 8.5$.  Those galaxies 
+which have a much weaker relationship between their oxygen and nitrogen 
+abundances correspond to those galaxies in Fig. \ref{fig:NOvOH} with a negative 
+relationship between their N/O ratio and metallicity.  Further study is needed 
+to understand why these galaxies have a different relationship between their 
+oxygen and nitrogen abundances.
+
+In both Figs. \ref{fig:NOvOH} and \ref{fig:OvN}, there is no difference in the 
+abundance ratio relationships between void dwarf galaxies and dwarf galaxies in 
+denser regions.  The large-scale environment does not appear to influence the 
+nucleosynthesis of nitrogen in dwarf galaxies.
+
+%-------------------------------------------------------------------------------
+\subsection{Stellar mass-abundance relations}\label{sec:Mass}
+
+\begin{figure*}
+    \centering
+%    \includegraphics[width=0.49\textwidth]{MZ_1sig_I06relations_SF_t3_Mbin}
+    \includegraphics[width=0.49\textwidth]{MZ_1sig_I06relations_dwarf_SF_t3_dust_NSA_python}
+    \includegraphics[width=0.49\textwidth]{MNO_1sig_I06relations_dwarf_SF_t3_dust_NSA_scatterMbin}
+%    \includegraphics[width=0.49\textwidth]{MNO_1sig_I06relations_dwarf_SF_t3_dust}
+    \caption{Stellar mass versus oxygen abundance (left panel) and N/O ratio 
+    (right panel).  We include the metallicity results of \cite{Tremonti04} on 
+    the left to place our dwarf galaxy abundance results in context.  On the 
+    right, we show the average N/O values for the dwarf galaxies binned by 
+    stellar mass plotted over the individual galaxies.  While most of our dwarf 
+    galaxies follow the same trend as already seen in \cite{Tremonti04}, we note 
+    the existence of a number of dwarf galaxies with much lower oxygen abundance 
+    values than what would be predicted based on their stellar mass and the 
+    mass-metallicity relation.  There is no clear difference between void and 
+    wall dwarf galaxies in the mass-metallicity relation.  In the right-hand 
+    panel, though, we see that the turn-off for the N/O plateau occurs at 
+    different masses for the two large-scale environments.}
+    \label{fig:M_NO}
+\end{figure*}
+
+Expanding on the mass-metallicity relation investigated in \cite{Douglass17a}, 
+we look at the correlation between stellar mass and the oxygen abundance in our 
+now substantially-larger sample of dwarf galaxies.  The mass-metallicity 
+relation for our dwarf galaxies can be seen in Fig. \ref{fig:M_NO}.  We also 
+include those galaxies from the MPA-JHU catalog with metallicity estimates from 
+\cite{Tremonti04} to place our sample in context.  While most of our dwarf 
+galaxies follow the same trend seen in \cite{Tremonti04}, we note the existence 
+of a number of dwarf galaxies with much lower oxygen abundances than what would 
+be predicted based on their stellar mass and the mass-metallicity relation.  
+There is no discernible influence from the large-scale environment on the 
+mass-metallicity relation for dwarf galaxies.
+
+We also look at the N/O ratio as a function of stellar mass (Fig. 
+\ref{fig:M_NO}, right panel).  Similar to the O/H--N/O relation studied in Sec. 
+\ref{sec:NO_OH}, the N/O ratio is predicted to be constant below some critical 
+mass; above this, the N/O ratio should increase linearly with the stellar mass.  
+Unlike the relation seen in Fig. \ref{fig:NOvOH}, we see both the N/O plateau 
+and the positive correlation on the right in Fig. \ref{fig:M_NO}.  To make the 
+plot more readable, we also bin the galaxies by stellar mass in bins of width 
+0.1.  We observe a difference in this relation as a function of the large-scale 
+environment: the critical mass for void galaxies is around 
+$\log(M_*/M_\odot) \sim$7.2, while the galaxies in denser regions exhibit a 
+critical mass of $\sim$7.6.  This difference suggests that void galaxies begin 
+to synthesize secondary nitrogen at lower stellar masses than galaxies in more 
+dense regions, consistent with the results from Fig. \ref{fig:met1sig} where 
+void dwarf galaxies have higher oxygen abundances than dwarf galaxies in more 
+dense environments.
+
+%-------------------------------------------------------------------------------
+\subsection{\ion{H}{1} mass-abundance relations}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.49\textwidth]{1sig_0-17_I06relations_SF_t3_HI_hist}
+    \includegraphics[width=0.49\textwidth]{1sig_0-17_I06relations_SF_t3_HI_CDF}
+    \caption{The distribution of \ion{H}{1} mass in the sample of dwarf 
+    galaxies, separated by their large-scale environment.  There is an obvious 
+    shift towards higher \ion{H}{1} masses in the void dwarf galaxies.}
+    \label{fig:HI_hist}
+\end{figure*}
+
+In addition to looking at the stellar mass, we also investigate the relationship 
+between the amount of neutral hydrogen and the gas-phase chemical abundances in 
+our sample of star-forming dwarf galaxies.  As shown in \cite{Moorman14}, void 
+galaxies typically have lower \ion{H}{1} masses than galaxies in more dense 
+regions, consistent with the overall shift of the luminosity or stellar mass 
+function to lower luminosity or mass in voids.  In the fixed range of luminosity 
+of our dwarf galaxy sample, as Fig. \ref{fig:HI_hist} shows, our sample of void 
+dwarf galaxies have higher \ion{H}{1} masses than the dwarf galaxies in denser 
+regions.  The gas in the void environment is cooler than that found in denser 
+regions (due to less events like shock heating, etc.), which permits void 
+galaxies to have higher \ion{H}{1} masses for a given stellar mass.  Therefore, 
+because we are fixing the stellar mass in our sample of galaxies (by only 
+studying dwarf galaxies), we should find that the void dwarf galaxies have 
+higher \ion{H}{1} masses than for those dwarf galaxies in denser environments.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.49\textwidth]{HI_OH_1sig_I06relations_dwarf+T04_SF_t3_dust}
+    \includegraphics[width=0.49\textwidth]{HI_NO_1sig_I06relations_dwarf_SF_t3_dust}
+    \includegraphics[width=0.49\textwidth]{HI_OH_M_1sig_I06relations_dwarf_SF_t3_dust}
+    \includegraphics[width=0.49\textwidth]{HI_NO_M_1sig_I06relations_dwarf_SF_t3_dust}
+    \caption{\ion{H}{1} mass versus metallicity (left) and N/O ratio (right) for 
+    star-forming dwarf galaxies.  The color scheme of the top row emphasizes the 
+    large-scale environment of the star-forming dwarf galaxies, while the bottom 
+    row investigates the relationship between stellar mass, \ion{H}{1} mass, and 
+    chemical abundance.  Error bars have been omitted for clarity.  To place our 
+    oxygen abundance results in context, we show (gray stars) the dwarf galaxies 
+    in SDSS DR7 with metallicity estimates from \cite{Tremonti04}.  From these 
+    plots, there is no significant influence from the large-scale environment on 
+    the relationship between the \ion{H}{1} mass and gas-phase chemical 
+    abundances of star-forming dwarf galaxies.}
+    \label{fig:HI}
+\end{figure*}
+
+The \ion{H}{1} mass-metallicity and \ion{H}{1} mass-N/O relations can be seen in 
+Fig. \ref{fig:HI}, extending the results of \cite{Bothwell13} down to 
+$\log(M_*/M_\odot) \approx 6$.  Unlike the correlation between the stellar mass 
+and the chemical abundances, there is very little correlation between the 
+abundances and the \ion{H}{1} mass.  There is no significant relationship 
+between the \ion{H}{1} mass and the metallicity of a galaxy --- a linear fit to 
+the data in the left panel of Fig. \ref{fig:HI} reveals a slope of only 
+$0.05\pm 0.085$ for the void population and $-0.04\pm 0.060$ for the wall 
+population.  This is not surprising, as our sample of star-forming dwarf 
+galaxies probes the low metallicity range of the MZ relation where there is no 
+strong relationship between the metallicity and stellar mass.  There is a very 
+small, but statistically significant, relationship between the \ion{H}{1} mass 
+and the N/O ratio for the dwarf galaxies: a linear fit to the data in the right 
+panel of Fig. \ref{fig:HI} reveals a slope of $0.11\pm 0.083$ for the void dwarf 
+galaxies and $0.09\pm 0.060$ for the wall dwarf galaxies.
+
+Due to the time delay in the production of nitrogen relative to oxygen, we 
+expect the N/O ratio to decrease with increasing \ion{H}{1} mass, since more 
+evolved galaxies have higher N/O ratios and will have used up most of their 
+neutral hydrogen.  \cite{Bothwell13} demonstrates the existence of this 
+relationship at a fixed stellar mass.  The first row of Fig. \ref{fig:HI} shows 
+little, if any, relationship between the \ion{H}{1} mass and the chemical 
+abundances.  However, the bottom row of Fig. \ref{fig:HI} shows that there is an 
+inverse relationship between the chemical abundance and the \ion{H}{1} mass for 
+fixed stellar mass (indicated by the colors of the points).
+
+%-------------------------------------------------------------------------------
+\subsection{Color-abundance relations}
+
+\begin{figure*}
+    \centering
+%    \includegraphics[width=0.49\textwidth]{ur_OH_1sig_I06relations_dwarf_SF_t3_dust_python}
+%    \includegraphics[width=0.49\textwidth]{ur_OH_1sig_I06relations_dwarf_SF_t3_dust}
+    \includegraphics[width=0.49\textwidth]{ur_OH_1sig_I06relations_dwarf+T04_SF_t3_dust}
+    \includegraphics[width=0.49\textwidth]{ur_NO_1sig_I06relations_dwarf_SF_t3_dust_scatterURbin}
+    \caption{Color ($u-r$) versus the gas-phase oxygen abundance (left) and the 
+    N/O ratio (right) for star-forming dwarf galaxies.  Error bars on individual 
+    points have been omitted for clarity.  For reference, the dwarf galaxies in 
+    SDSS DR7 that have estimated metallicities from \cite{Tremonti04} are shown 
+    in the left panel in gray.  To discern any environmental trends in the 
+    results, we have binned the galaxies by their color (in bins of width 0.1) 
+    on the right.  The large-scale environment does not influence the 
+    relationship between the color and chemical abundances of dwarf galaxies.}
+    \label{fig:ur}
+\end{figure*}
+
+The gas-phase chemical abundance is expected to have a positive correlation with 
+a galaxy's color.  Older galaxies have had more time to convert their gas into 
+heavier elements through star formation, increasing their metallicities.  The 
+color-metallicity and color-N/O relations for our sample of star-forming dwarf 
+galaxies can be seen in Figures \ref{fig:ur} and \ref{fig:gr}.  As we see, bluer 
+galaxies have lower O/H and N/O ratios when we look at both the $u-r$ and $g-r$ 
+colors.  While there is a subset of dwarf galaxies with extremely low 
+metallicities that do not follow this trend (seen in the left-hand panels of 
+Figures \ref{fig:ur} and \ref{fig:gr}), this population follows the color-N/O 
+trend seen on the right in each of these figures.  While these galaxies have 
+unusually low oxygen abundances, they have normal N/O ratios.
+
+\begin{figure*}
+    \centering
+%    \includegraphics[width=0.49\textwidth]{gr_OH_1sig_I06relations_dwarf_SF_t3_dust_python}
+%    \includegraphics[width=0.49\textwidth]{gr_OH_1sig_I06relations_dwarf_SF_t3_dust}
+    \includegraphics[width=0.49\textwidth]{gr_OH_1sig_I06relations_dwarf+T04_SF_t3_dust}
+    \includegraphics[width=0.49\textwidth]{gr_NO_1sig_I06relations_dwarf_SF_t3_dust_scatterGRbin}
+    \caption{Color ($g-r$) versus the gas-phase oxygen abundance (left) and the 
+    N/O ratio (right) for star-forming dwarf galaxies.  Error bars on individual 
+    points have been omitted for clarity.  For reference, the galaxies in SDSS 
+    DR7 that have estimated metallicities from \cite{Tremonti04} are shown in 
+    the left panel in gray.  To discern any environmental trends in the results, 
+    we have binned the galaxies by their color (in bins of width 0.1) on the 
+    right.  The large-scale environment does not influence the relationship 
+    between the color and chemical abundances of dwarf galaxies.}
+    \label{fig:gr}
+\end{figure*}
+
+The presence of a relationship between the N/O ratio and the color of a galaxy 
+can indicate a time delay between the release of nitrogen and oxygen 
+\citep{vanZee06a,Berg12}.  If higher-mass stars are the main source of oxygen, 
+then the oxygen will be released on a shorter time scale than nitrogen for a 
+given star formation episode (since higher-mass stars turn off the main sequence 
+earlier than the intermediate-mass stars that synthesize nitrogen).  Therefore, 
+the amount of nitrogen relative to oxygen should increase as the hotter, more 
+massive stars burn out and the galaxy becomes redder.  This trend can be seen in 
+the star-forming dwarf galaxies on the right of Figures \ref{fig:ur} and 
+\ref{fig:gr}, matching the trends seen in \cite{Douglass17b,vanZee06a,Berg12}.
+
+There does not appear to be any influence from the large-scale environment on 
+the relationship between the color and chemical abundances for star-forming 
+dwarf galaxies.  There is no obvious difference between the void and wall dwarf 
+galaxies in the left-hand panels of Figures \ref{fig:ur} and \ref{fig:gr}, when 
+we concentrate on the oxygen abundance as a function of color.  To help discern 
+any influence from the environment on the N/O ratio as a function of color, we 
+bin the star-forming dwarf galaxies by their color in bins of width 0.1 --- 
+these results are overlaid on the left-hand plots of Figures \ref{fig:ur} and 
+\ref{fig:gr}.  The shift toward higher N/O ratios seen in the wall bins in both 
+figures is the same shift identified in the histograms in Fig. 
+\ref{fig:NOratio}.  Any variation in the color-abundance relationship between 
+the void and wall populations except a vertical shift would be evidence of the 
+large-scale environment influencing the relationship.  There is a modest 
+difference in the slope of these bins in N/O, where the colors of star-forming 
+void dwarf galaxies are more strongly correlated with their N/O ratios than 
+star-forming wall dwarf galaxies.  The Pearson correlation coefficient between 
+$u-r$ and $\log (\text{N}/\text{O})$ for the star-forming void dwarf galaxies is 
+$0.63\pm 0.019$ and $0.52\pm 0.027$ for the star-forming wall dwarf galaxies.  
+The correlation coefficients between $g-r$ and $\log (\text{N}/\text{O})$ for 
+the void dwarf galaxies is $0.74\pm 0.014$ and $0.67\pm 0.020$ for the wall 
+dwarf galaxies.  
+% What does it mean, for void galaxies to more correlated in their color v. N/O?
+
+%-------------------------------------------------------------------------------
+\subsection{(s)SFR-abundance relations}
+
+\begin{figure*}
+    \centering
+%    \includegraphics[width=0.49\textwidth]{SFR_OH_1sig_I06relations_dwarf_SF_t3_dust_python}
+    \includegraphics[width=0.49\textwidth]{SFR_OH_1sig_I06relations_dwarf+T04_SF_t3_dust}
+    \includegraphics[width=0.49\textwidth]{SFR_NO_1sig_I06relations_dwarf_SF_t3_dust_scatterSFRbin}
+    \caption{SFR versus metallicity (left) and the N/O ratio (right) for 
+    star-forming dwarf galaxies.  Error bars for individual galaxies have been 
+    omitted for clarity.  To place our oxygen abundance results in context, we 
+    show (gray stars) the dwarf galaxies in SDSS DR7 with metallicity estimates 
+    from \cite{Tremonti04}.  To discern any environmental effects on the 
+    relation between SFR and the N/O ratio, we bin the dwarf galaxies by SFR (in 
+    bins of width 0.1).  From these plots, the large-scale environment has no 
+    discernible influence on the relationship between the SFR and gas-phase 
+    chemical abundances of star-forming dwarf galaxies.}
+    \label{fig:SFR}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+%    \includegraphics[width=0.49\textwidth]{sSFR_OH_1sig_I06relations_dwarf_SF_t3_dust_python}
+    \includegraphics[width=0.49\textwidth]{sSFR_OH_1sig_I06relations_dwarf+T04_SF_t3_dust}
+    \includegraphics[width=0.49\textwidth]{sSFR_NO_1sig_I06relations_dwarf_SF_t3_dust_scattersSFRbin}
+    \caption{Specific star formation rate (sSFR) versus metallicity (left) and 
+    the N/O ratio (right) for star-forming dwarf galaxies.  Error bars on 
+    individual galaxies have been omitted for clarity.  To place our oxygen 
+    abundance results in context, we show (gray stars) the dwarf galaxies in 
+    SDSS DR7 with metallicity estimates from \cite{Tremonti04}.  To discern any 
+    environmental effects on the relation between sSFR and the N/O ratio, we bin 
+    the dwarf galaxies by sSFR (in bins of width 0.1).  From these figures, 
+    there is no significant influence on the relationship between the sSFR and 
+    gas-phase chemical abundances of star-forming dwarf galaxies.}
+    \label{fig:sSFR}
+\end{figure*}
+
+There is thought to be a fundamental relationship between the stellar mass, star 
+formation rate (SFR), and metallicity of a galaxy \citep{Mannucci10,LaraLopez10,
+Andrews13}; the metallicity of a galaxy should increase with stellar mass and 
+decrease as a function of the SFR.  \cite{Henry13} observe an inverse 
+relationship between the metallicity and SFR of low-mass galaxies.  However, as 
+was seen in \cite{Douglass17a}, Fig. \ref{fig:SFR} shows very little correlation 
+between the SFR and metallicity or N/O ratio of the star-forming dwarf galaxies.  
+When we separate the dwarf galaxies by their large-scale environment, we see no 
+difference in the correlation coefficients between the two environments; there 
+is no discernible influence on the relationship between the SFR and the chemical 
+abundances by the large-scale environment.
+
+We also inspect the relationship between the specific star formation rate (sSFR) 
+and the gas-phase chemical abundances in star-forming dwarf galaxies.  As shown 
+in Fig. \ref{fig:sSFR}, there is a stronger correlation between the sSFR of a 
+dwarf galaxy and its metallicity and N/O ratio.  The left-hand panel of Fig. 
+\ref{fig:sSFR} shows the relationship between the gas-phase oxygen abundance and 
+the sSFR for star-forming dwarf galaxies; to place our results in context, we 
+also include (gray stars) those dwarf galaxies in SDSS DR7 for which 
+\cite{Tremonti04} was able to estimate metallicities.  In the metallicity regime 
+we are able to probe ($12 + \log (\text{O}/\text{H}) \leq 8.5$), the 
+star-forming dwarf galaxies display relatively little relationship between their 
+sSFR and metallicity.  The group of extremely low metallicity dwarf galaxies 
+($12 + \log (\text{O}/\text{H}) < 7.6$) in our sample has some of the lowest 
+sSFR of our dwarf galaxies.
+
+As we see on the right in Fig. \ref{fig:sSFR}, though, there is a strong 
+anti-correlation between the sSFR and N/O ratio for the star-forming dwarf 
+galaxies.  Galaxies with higher sSFRs may be producing more massive stars than 
+galaxies with lower sSFRs.  If oxygen is produced in more massive stars than 
+those which produce nitrogen, then the galaxies with higher sSFRs will produce 
+more oxygen earlier than those galaxies with lower sSFRs.  Increasing the 
+gas-phase oxygen abundance relative to nitrogen will decrease the N/O ratio in 
+these galaxies with higher sSFRs.  Therefore, an anti-correlation between the 
+sSFR and N/O ratio is further evidence that oxygen is produced in higher mass 
+stars than those which synthesize nitrogen.
+
+There is also very little scatter in the right-hand panel of Fig. 
+\ref{fig:sSFR}, indicating a significant relationship between the sSFR and N/O 
+ratio for dwarf galaxies.  The Pearson correlation coefficients for our sample 
+of star-forming void dwarf galaxies is $-0.62\pm 0.020$; the correlation 
+coefficient for the star-forming wall dwarf galaxies is $-0.55\pm 0.025$.  It is 
+interesting to note that the void dwarf galaxies exhibit a stronger correlation 
+between their sSFR and N/O ratio than the dwarf galaxies in denser environments.  
+This can be seen in the binned data points plotted on top of the individual 
+dwarf galaxies; we have taken the average of the galaxies binned by their sSFR 
+(in bins of width 0.1) to help discern any large-scale environmental influence 
+on the relationship between the sSFR and the N/O ratio.
+% Again, what is the physical interpretation of the stronger correlation in the void galaxies?
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%    DISCUSSION
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Large-scale environmental influence}
+
+We see small, statistically significant shifts in each of the three gas-phase 
+abundance ratios studied as a function of the large-scale environment, implying 
+that the large-scale environment influences the chemical abundances of 
+star-forming dwarf galaxies.  Previous work by \cite{Douglass17b} suggests that 
+the oxygen abundance (O/H), nitrogen abundance (N/H), and N/O ratio depend on a 
+galaxy's environment.  Work by \cite{Shields91} finds no shift in the N/O ratio 
+between cluster and field galaxies, though they do find that cluster galaxies 
+have higher metallicities than field galaxies.  \cite{Contini02} and 
+\cite{Pilyugin02} find a statistically insignificant shift in the N/O ratio 
+between cluster and field galaxies, where cluster galaxies have lower N/O ratios 
+than field spiral galaxies.  The shifts seen in each of these latter three 
+sources are opposite to what we observe in this paper, though these previous 
+studies concentrate on the galaxies in the Virgo cluster, which are more massive 
+than our dwarf galaxy ($M_r > -17$) sample.  On average, we find that 
+star-forming void dwarf galaxies have $\sim$7\% higher oxygen abundances, 
+$\sim$10\% lower nitrogen abundances, and $\sim$17\% lower N/O ratios than 
+star-forming dwarf galaxies in denser regions.
+
+As outlined in \cite{Douglass17a}, there have been numerous previous studies 
+that investigate the influence of the environment on the metallicity of a 
+galaxy, resulting in mixed conclusions.  When a difference in the metallicity 
+was attributed to the environment \citep[as in][for example]{Pustilnik06,
+Pustilnik11b,Pustilnik14,SanchezAlmeida16,Cooper08}, it was found that those 
+galaxies with higher metallicities preferentially reside in denser regions.  
+This is the opposite of the trend seen in Fig. \ref{fig:met1sig} in the 
+star-forming dwarf galaxies, although our results are not a direct comparison 
+with their conclusions (do to our requirement of the [\ion{O}{3}] $\lambda$4363 
+auroral line, we are not able to probe the high-metallicity regime).  We observe 
+an average metallicity that is $\sim$7\% higher in void dwarf galaxies than in 
+dwarf galaxies in denser regions.
+
+\subsection{Higher metallicities in void dwarf galaxies}
+
+% The direction of the shift implies more O in voids
+%  - How do we get more O in void galaxies?  M_DM/M_* |v > M_DM/M_* |w
+We posit that the slightly higher metallicities seen in the star-forming void 
+dwarf galaxies in Fig. \ref{fig:met1sig} is due to a large-scale environmental 
+effect on the ratio of a galaxy's dark matter halo mass to stellar mass 
+($M_{DM}/M_*$).  \cite{Goldberg04} show that gravitational clustering within a 
+void proceeds as if in a very low density universe, where the growth of 
+gravitationally bound dark matter halos ends relatively early.  Afterwards, 
+there is relatively little interaction between the void galaxies because of the 
+lower density and faster local Hubble expansion.  Simulations by \cite{Jung14} 
+and \cite{Tonnesen15} show that, for a fixed dark matter halo mass, the stellar 
+masses of central galaxies located in voids are smaller than those of central 
+galaxies living in denser regions.  The $\Lambda$CDM cosmology predicts that 
+galaxies formed in voids will be retarded in their star formation when compared 
+to those in denser environments.  Therefore, void dwarf galaxies could have 
+higher $M_{DM}/M_*$ ratios than dwarf galaxies in denser regions.
+
+If this is the case, then the potential well and virial radius of the void 
+galaxies are large enough to retain more of the heavy elements that are blown 
+from the ISM to the CGM of a galaxy (from a supernova, for example).  The 
+simulation results of \cite{Tonnesen15} find that, for central galaxies with 
+halo masses between $10^{11}$ and $10^{12.9}$, void galaxies have $\sim$10\% 
+larger ratios of dark matter halo mass to stellar mass than wall galaxies at 
+$z = 0$.  In wall galaxies, more of these heavy elements can escape the dwarf 
+galaxy, while in void galaxies they are confined to the CGM and eventually fall 
+back onto the galaxy's ISM.  If star-forming void dwarf galaxies are able to 
+retain more oxygen relative to their hydrogen abundance, then they will reach 
+the critical value of O/H for secondary nitrogen production (via the CNO cycle) 
+earlier than the star-forming wall dwarf galaxies, for a given stellar mass.  We 
+see this in Fig. \ref{fig:M_NO}, where the N/O plateau for the void dwarf 
+galaxies exists for stellar masses $\log(M_*/M_\odot) \lesssim 7.2$.  In 
+contrast, the N/O plateau for the wall dwarf galaxies exists for stellar masses 
+$\log(M_*/M_\odot) \lesssim 7.6$.
+
+% What other proof do we have that this might be true?
+If void dwarf galaxies have higher $M_{DM}/M_*$ ratios than dwarf galaxies in 
+denser environments, we would expect to see an environmental influence on other 
+characteristics of these galaxies.  First, the ratio of neutral hydrogen mass to 
+stellar mass of the dwarf galaxies would be higher in star-forming void galaxies 
+than star-forming wall galaxies, under the assumption that neutral hydrogen 
+traces dark matter.  We see this effect both in Fig. 9 of \cite{Moorman16} and 
+in Fig. \ref{fig:HI_hist} above.  Second, the \ion{H}{1} mass function should 
+shift less from wall to void galaxies than the shift seen in the luminosity 
+function.  Indeed, \cite{Moorman16} finds a shift of characteristic \ion{H}{1} 
+mass by a factor of 1.4 in the \ion{H}{1} mass function, while \cite{Hoyle05} 
+measures a shift by a factor of 2.5 in luminosity in the luminosity function 
+between these two environments.
+
+\subsection{Lower N/O ratios in void dwarf galaxies}
+
+% Shift in N/O due to environmental influence on cosmic downsizing
+As we see in Fig. \ref{fig:NOratio}, star-forming void dwarf galaxies have a 
+lower N/O ratio than wall dwarf galaxies.  This strengthens the preliminary 
+results found in \cite{Douglass17b} and the simulation results of \cite{Cen11}, 
+indicating that void galaxies are retarded in their star formation and that 
+cosmic downsizing might depend on the large-scale environment.  As suggested by 
+\cite{vanZee06a}, a galaxy with a declining SFR at late times (a wall galaxy) 
+will have a higher N/O ratio than a galaxy with a constant SFR (a void galaxy); 
+the ongoing star formation in the void galaxies will release more oxygen into 
+the ISM, decreasing their N/O ratio relative to the galaxies with declining 
+SFRs.  This concept is supported by the color-N/O diagram in Figures 
+\ref{fig:ur} and \ref{fig:gr}, where the bluer galaxies have lower N/O ratios.  
+The correlations between color and the N/O ratio found in \cite{vanZee06a}, 
+\cite{Berg12}, \cite{Douglass17b}, and this work are a result of declining SFRs 
+\citep{vanZee06a}.  The average lower N/O ratios we see in star-forming void 
+dwarf galaxies may be observational evidence that cosmic downsizing is 
+environmentally dependent.
+
+\subsection{Extremely low metallicity dwarf galaxies}
+
+Previous studies have either hypothesized \citep{Pustilnik06,Pustilnik11b,
+Pustilnik13} or concluded \citep{Filho15} that low-metallicity objects 
+preferentially reside in low-density environments.  \cite{Douglass17a} find 
+that, out of 135 dwarf galaxies studied, there is no difference in the fraction 
+of low-metallicity dwarf galaxies that reside in voids and denser regions.  Of 
+the 1920 dwarf galaxies we analyze, 287 have extremely low metallicity values 
+($12 + \log (\text{O}/\text{H}) \leq 7.6$).  Of these 287 low-metallicity dwarf 
+galaxies, 144 are found in voids (approximately 15\% of the star-forming void 
+dwarf galaxy population studied) and 122 are located in denser regions (16\% of 
+the star-forming wall dwarf galaxy population studied).  These population 
+fractions do not support the existence of a special population of extremely 
+metal-poor dwarf galaxies in voids.
+
+We find that these 287 extremely metal-poor galaxies are only slightly lower in 
+their nitrogen abundances when compared to the total star-forming dwarf galaxy 
+population studied.  The low oxygen abundances causes these dwarf galaxies to 
+have higher N/O ratios than the total star-forming dwarf galaxy population 
+studied.  From Figures \ref{fig:ur} and \ref{fig:gr}, it is apparent that these 
+extremely metal-poor star-forming dwarf galaxies are redder than their oxygen 
+abundances would typically indicate, although their colors align with their N/O 
+ratios.  Fig. \ref{fig:SFR} also shows that the sSFRs for these low-metallicity 
+dwarf galaxies are lower than expected for their oxygen abundances, though their 
+sSFRs conform with the observed relationship between the N/O ratio and the sSFR.  
+The 287 extremely metal-poor galaxies are isolated from our main sample of 
+star-forming dwarf galaxies only when comparing their gas-phase oxygen 
+abundances to other physical characteristics; their N/O ratios are not unusual.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%    CONCLUSION
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusions}
+
+% Need a topic sentence that refers back to the introduction
+We estimate the gas-phase oxygen and nitrogen abundances and the N/O ratio of 
+star-forming dwarf galaxies in SDSS DR7 using the direct $T_e$ method and 
+spectroscopic line flux measurements as reprocessed in the MPA-JHU catalog.  We 
+expand upon the previous work of \cite{Douglass17a} and \cite{Douglass17b} by 
+deriving a relation between the doubly-ionized oxygen and total oxygen abundance 
+in star-forming galaxies; removing the dependence on the [\ion{O}{3}] 
+$\lambda$3727 doublet, this relation allows us to probe those dwarf galaxies at 
+$z < 0.02$ in SDSS DR7.  The 1920 dwarf galaxies analyzed indicate that the 
+large-scale environment influences their chemical evolution: star-forming void 
+dwarf galaxies have higher oxygen abundances by an average of 7\%, lower 
+nitrogen abundances by an average of 10\%, and 17\% lower N/O ratios than 
+star-forming dwarf galaxies in denser regions.  The large-scale ($\sim$10 
+$h^{-1}$Mpc) environment influences the chemical evolution of star-forming dwarf 
+galaxies.
+
+% Summary of comparison with physical characteristics
+In addition, we also look at the relationship between the metallicity and the 
+N/O ratio and other physical characteristics of our star-forming dwarf galaxy 
+sample.  In the relationship between N/O and O/H, all our dwarf galaxies reside 
+on the so-called ``nitrogen plateau,'' where the N/O ratio is predicted to be 
+independent of the gas-phase oxygen abundance for metallicities 
+$12 + \log (\text{O}/\text{H}) < 8.5$.  Instead of a constant value for the N/O 
+ratio, we instead find that the N/O ratio decreases with increasing metallicity.  
+However, we do find a plateau in our relationship between the stellar mass and 
+N/O ratio.  Most of our star-forming dwarf galaxies follow the typical 
+mass-metallicity relation \citep{Tremonti04}.  There is no relationship between 
+the metallicity and \ion{H}{1} mass of the galaxies, but the N/O ratio decreases 
+with increasing \ion{H}{1} mass for fixed stellar mass.  The star-forming dwarf 
+galaxies exhibit an increase in the metallicity (O/H) and N/O ratio with 
+increasing color (both $u-r$ and $g-r$).  We see very little correlation with 
+SFR for either metallicity (O/H) or N/O ratio of dwarf galaxies, but the 
+metallicity and N/O ratio decrease with increasing sSFR.  Beyond the large-scale 
+environmental influence on the chemical abundance distributions in the sample of 
+star-forming dwarf galaxies, we do not observe any significant differences 
+between the star-forming void and wall dwarf galaxies in any of these 
+relationships.
+
+% Physical interpretation for the shift in O/H, N/O
+We surmise that the differences in the distributions of metallicity and the N/O 
+ratio seen in the sample of star-forming dwarf galaxies are due to a large-scale 
+environmental influence on their formation history and evolution.  The shift in 
+the gas-phase oxygen abundance distribution could be observational evidence for 
+delayed star formation in void galaxies when compared to those in denser 
+regions.  This would result in a smaller ratio of stellar mass to dark matter 
+halo mass in void galaxies than in wall dwarf galaxies, as predicted in 
+simulations by \cite{Jung14} and \cite{Tonnesen15}.  Simulations looking at how 
+the retention fraction of supernovae ejecta depends on the halo mass or dark 
+matter potential would be useful in understanding if a $\sim$10\% increase in 
+the dark matter halo mass for void dwarf galaxies is enough to result in a 
+$\sim$7\% increase in the metallicity.  If the void galaxies are retaining more 
+oxygen as a result of their deeper potential wells, then they will be able to 
+commence the synthesis of secondary nitrogen earlier, as is seen in the mass-N/O 
+relation in Fig. \ref{fig:M_NO}.  In addition, the shift towards lower N/O 
+ratios in the star-forming void dwarf galaxies may be evidence that cosmological 
+downsizing is environmentally dependent.  Our results provide evidence for 
+delayed, ongoing star formation in void dwarf galaxies whose dark matter halos 
+ceased coalescing earlier than for dwarf galaxies in denser regions.
+
+% XMP dwarf galaxies
+No special population of extremely metal-poor star-forming dwarf galaxies is 
+found in the voids, as we note an equal fraction of low metallicity dwarf 
+galaxies in both the voids and denser regions.  Due to their low gas-phase 
+oxygen abundances, the 287 dwarf galaxies have some of the larger N/O ratios of 
+the star-forming dwarf galaxy sample studied.  While the metallicities of these 
+galaxies cause them to stand out when looking at the relationship between the 
+metallicity and other physical characteristics of the galaxies (stellar mass, 
+color, (s)SFR), they are not unusual when studying the relationship between the 
+N/O ratio and the other galaxy properties.

### 2017-06-16 KellyDouglass/Thesis/Tables/Paper3/results_table_short.tex
Updated Paper 3

\begin{sidewaystable}

    \begin{tabular}{cccccccccccc}
    Index\footnote{KIAS-VAGC galaxy index number} & R.A. & Decl. & Redshift & $M_r$ & \multicolumn{2}{c}{$12 + \log \left( \frac{\text{O}}{\text{H}} \right)$} & \multicolumn{2}{c}{$12 + \log \left( \frac{\text{N}}{\text{H}} \right)$} & \multicolumn{2}{c}{$\log \left( \frac{\text{N}}{\text{O}} \right)$} & Void/Wall\\
    \hline
	40726 & \RA{11}{25}{52}{.10} & -\dec{00}{39}{41}{.76} & 0.0187 & -16.73 & 8.18 & $\pm$0.07 & 6.70 & $\pm$0.07 & -1.49 & $\pm$0.10 & Wall \\
	40916 & \RA{11}{52}{47}{.52} & -\dec{00}{40}{07}{.64} & 0.0046 & -13.36 & 8.09 & $\pm$0.02 & 5.90 & $\pm$0.02 & -2.18 & $\pm$0.03 & Wall \\
	41257 & \RA{12}{41}{12}{.41} & -\dec{00}{45}{24}{.55} & 0.0113 & -16.87 & 8.13 & $\pm$0.20 & 6.98 & $\pm$0.18 & -1.15 & $\pm$0.27 & Wall \\
	42296 & \RA{14}{39}{50}{.03} & -\dec{00}{42}{22}{.85} & 0.0060 & -13.77 & 7.99 & $\pm$0.10 & 6.67 & $\pm$0.10 & -1.32 & $\pm$0.14 & Wall \\
	42829 & \RA{15}{40}{18}{.50} & -\dec{00}{48}{45}{.04} & 0.0125 & -16.71 & 8.06 & $\pm$0.31 & 6.95 & $\pm$0.28 & -1.11 & $\pm$0.42 & Wall
    \end{tabular}

    \caption[Analyzed dwarf galaxies]{Five of the 1920 dwarf galaxies analyzed from SDSS DR7.  The flux values for all required emission lines can be found in the MPA-JHU value-added catalog.  Abundance values are calculated using the direct $T_e$ method and the O$^+$ approximation defined in Sec. \ref{sec:Oplus_approx}, with error estimates via a Monte Carlo method.  The void catalog of \cite{Pan12} is used to classify the galaxies as either Void or Wall.  If a galaxy is located too close to the boundary of the SDSS to identify whether or not it is inside a void, it is labeled as Uncertain.  (This table is available in its entirety in machine-readable format.)}

\label{tab:Results_P3}

\end{sidewaystable}

### 2017-06-16 KellyDouglass/Thesis/Thesis_sections/Paper2.tex
Updated Paper 3

@@
 oxygen and nitrogen abundances of these brighter galaxies.  The results of a 
-two-sample K-S test (listed in Table \ref{tab:stats}) mostly support this 
+two-sample K-S test (listed in Table \ref{tab:stats_P2}) mostly support this 
 conclusion.  In the brightest magnitude bin (galaxies with $-19 > M_r > -20$), 
@@
     (bottom).  The results of a two-sample K-S test of the two data sets in each 
-    absolute magnitude range can be found in Table \ref{tab:stats}.  These 
+    absolute magnitude range can be found in Table \ref{tab:stats_P2}.  These 
     results are reflected visually, as there appears to be very little 
@@
 up through $M_r > -20$; the results of this analysis can be seen in Fig. 
-\ref{fig:NO_bright} and in Table \ref{tab:stats}.  The shift toward lower N/O 
+\ref{fig:NO_bright} and in Table \ref{tab:stats_P2}.  The shift toward lower N/O 
 ratios for the void galaxies is small for all magnitude bins.  The direction of 
@@
     test of the two data sets in each absolute magnitude range can be found in 
-    Table \ref{tab:stats}, in addition to other statistics of the samples.  Both 
-    the histograms, CDFs, and statistics suggest a very slight difference 
+    Table \ref{tab:stats_P2}, in addition to other statistics of the samples.  
+    Both the histograms, CDFs, and statistics suggest a very slight difference 
     between the two populations, indicating a mild large-scale environmental 
@@
 
-	\label{tab:stats}
+	\label{tab:stats_P2}
 
@@
 ratios than field spiral galaxies.  Based on Fig. \ref{fig:NOratio} and the 
-statistics in Table \ref{tab:stats}, we find weak evidence that void dwarf 
+statistics in Table \ref{tab:stats_P2}, we find weak evidence that void dwarf 
 galaxies have a smaller N/O ratio than dwarf galaxies in denser regions.  This 
@@
 
-Table \ref{tab:stats} suggests a slight large-scale environmental dependence of 
-the oxygen and nitrogen abundances (relative to hydrogen), where void galaxies 
-have slightly more O/H and N/H than wall galaxies.  This small difference is 
-not apparent when looking at Figs. \ref{fig:met1sig} and \ref{fig:N_1sig}.  
-However, the N/O ratio amplifies this large-scale environmental effect so that a 
-shift in the mean (or median) of the two populations can be seen in Fig. 
-\ref{fig:NOratio}.  We hesitate to combine the results across all magnitude bins 
-in an effort to improve their significance.  Instead, we look toward the future 
-to analyze a larger sample of galaxies to increase the statistical significance 
-of these results.
+Table \ref{tab:stats_P2} suggests a slight large-scale environmental dependence 
+of the oxygen and nitrogen abundances (relative to hydrogen), where void 
+galaxies have slightly more O/H and N/H than wall galaxies.  This small 
+difference is not apparent when looking at Figs. \ref{fig:met1sig} and 
+\ref{fig:N_1sig}.  However, the N/O ratio amplifies this large-scale 
+environmental effect so that a shift in the mean (or median) of the two 
+populations can be seen in Fig. \ref{fig:NOratio}.  We hesitate to combine the 
+results across all magnitude bins in an effort to improve their significance.  
+Instead, we look toward the future to analyze a larger sample of galaxies to 
+increase the statistical significance of these results.
 
@@
 galaxies would have higher metallicities than wall dwarf galaxies, matching what 
-we see in Table \ref{tab:stats}.
+we see in Table \ref{tab:stats_P2}.
 

### 2017-06-16 KellyDouglass/Thesis/Thesis_sections/Paper3.tex
Updated Paper 3

@@
 proportional to the metallicity of a galaxy, it is best suited for low-redshift, 
-low-metallicity galaxies.  At metallicities 
-$12 + \log (\text{O}/\text{H}) \gtrsim 8.5$, [\ion{O}{3}] $\lambda$4363 becomes 
-too weak to detect in the SDSS spectra.  With the mass-metallicity (MZ) relation 
-by \cite{Tremonti04}, this metallicity limit corresponds to a maximum stellar 
-mass of
+low-metallicity galaxies.  At metallicities \OH $\gtrsim 8.5$, [\ion{O}{3}] 
+$\lambda$4363 becomes too weak to detect in the SDSS spectra.  With the 
+mass-metallicity (MZ) relation by \cite{Tremonti04}, this metallicity limit 
+corresponds to a maximum stellar mass of
 \begin{align*}
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{Images/Paper3/Zlow_v_Zreal_1sig_I06_BPTclass_fits}
-    \caption{$12 + \log{\text{O}^{++}/\text{H}}$ versus 
-    $12 + \log{\text{O}/\text{H}}$ for those galaxies with $M_r > -20$ as 
-    calculated with the direct method; the galaxies are colored by their 
-    classification in the BPT diagrams (from \cite{Brinchmann04}).  Two linear 
-    models have been fit to three groups in the sample: star-forming and 
-    AGN/composite galaxies; the best fit parameters can be found in Table 
-    \ref{tab:ab}.}
+    \includegraphics[width=0.65\textwidth]{Images/Paper3/Zlow_v_Zreal_1sig_I06_BPTclass_fits}
+    \caption[O$^++$/H versus O/H]{$12 + \log{\text{O}^{++}/\text{H}}$ versus \OH 
+    for those galaxies with $M_r > -20$ as calculated with the direct method; 
+    the galaxies are colored by their classification in the BPT diagrams 
+    \citep[from][]{Brinchmann04}.  Two linear models have been fit to three 
+    groups in the sample: star-forming and AGN/composite galaxies; the best fit 
+    parameters can be found in Table \ref{tab:ab}.}
     \label{fig:lowVreal}
@@
 the abundance of O$^+$ is only available for objects within the redshift range 
-$0.02 < z < 0.03$ \citep[see Sec. \ref{sec:SDSS_limits} and][for more 
+$0.02 < z < 0.03$ \citep[see Sec. \ref{sec:SDSS_limits_P3} and][for more 
 details]{Douglass17a}.  To be able to study SDSS galaxies at redshifts less than 
@@
 singly-ionized oxygen.  To construct an ICF appropriate for our dwarf galaxy 
-sample, we compare $12 + \log{\text{O/H}}$ to 
-$12 + \log{\text{O}^{++}/\text{H}}$ as calculated by the Direct $T_e$ method for 
-all galaxies in SDSS with $M_r > -20$.  Recognizing that the relative amounts of 
-singly- and doubly-ionized oxygen will depend on the hardness of a galaxy's 
-spectrum, we use a Baldwin-Phillips-Terlevich (BPT) diagram \citep{Baldwin81} to 
-classify each galaxy as star-forming, AGN, or composite (containing 
-characteristics of both a star-forming region and an AGN).  Noting a strong 
-separation in the relationship between O$^{++}$/H and O/H with respect to the 
-galaxies' BPT classifications by \cite{Brinchmann04}, we fit two linear models 
-to the sample, seen in Fig. \ref{fig:lowVreal} and defined as 
+sample, we compare \OH to $12 + \log{\text{O}^{++}/\text{H}}$ as calculated by 
+the Direct $T_e$ method for all galaxies in SDSS with $M_r > -20$.  Recognizing 
+that the relative amounts of singly- and doubly-ionized oxygen will depend on 
+the hardness of a galaxy's spectrum, we use a Baldwin-Phillips-Terlevich (BPT) 
+diagram \citep{Baldwin81} to classify each galaxy as star-forming, AGN, or 
+composite (containing characteristics of both a star-forming region and an AGN).  
+Noting a strong separation in the relationship between O$^{++}$/H and O/H with 
+respect to the galaxies' BPT classifications by \cite{Brinchmann04}, we fit two 
+linear models to the sample, seen in Fig. \ref{fig:lowVreal} and defined as 
 \begin{equation}\label{eq:fit}
@@
 
-\floattable
-\begin{deluxetable}{L|C|C|C}
-    \tablewidth{0pt}
-    \tablecaption{Coefficients of oxygen abundance fits\label{tab:ab}}
-    \tablehead{\colhead{} & \colhead{SF (dwarf)} & \colhead{SF ($M_r > -20$)} & \colhead{AGN \& Composite}}
-    \startdata
-        a & 0.84 \pm 0.013 & 0.824 \pm 0.0010 & 0.764 \pm 0.0035\\
-        b & 1.61 \pm 0.094 & 1.787 \pm 0.0065 & 2.05 \pm 0.023\\
-    \enddata
-    \tablecomments{Coefficients for the linear trends (Eqn. \ref{eq:fit}) fit to 
-    the SF galaxies (dwarf and those with $M_r > -20$) and AGN and composite 
-    galaxies.  With these trends, we can now calculate the total oxygen 
-    abundance for a galaxy with knowing only the O$^{++}$/H abundance.}
-\end{deluxetable}
+\begin{table}
+\centering
+
+    \begin{tabular}{l|c|c|c}
+         & SF (dwarf) & SF ($M_r > -20$) & AGN \& Composite\\
+        \hline
+        $a$ & $0.84 \pm 0.013$ & $0.824 \pm 0.0010$ & $0.764 \pm 0.0035$\\
+        $b$ & $1.61 \pm 0.094$ & $1.787 \pm 0.0065$ & $2.05 \pm 0.023$
+    \end{tabular}
+
+    \caption[Coefficients of oxygen abundance fits]{Coefficients for the linear 
+    trends (Eqn. \ref{eq:fit}) fit to the SF galaxies (dwarf and those with 
+    $M_r > -20$) and AGN and composite galaxies.  With these trends, we can now 
+    calculate the total oxygen abundance for a galaxy with knowing only the 
+    O$^{++}$/H abundance.}
+
+    \label{tab:ab}
+
+\end{table}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{SDSS data and galaxy selection}
+\section[Data]{SDSS data and galaxy selection}
 
@@
 %-------------------------------------------------------------------------------
-\subsection{Spectroscopic selection}\label{sec:SDSS_limits}
+\subsection{Spectroscopic selection}\label{sec:SDSS_limits_P3}
 
@@
 \subsection{Void classification}
-% Re-write to avoid plagarizing myself :P
-
-Void galaxies are identified using the void catalog compiled by \cite{Pan12}, 
-which was built based on the galaxies in SDSS DR7 catalog.  Starting with 
-galaxies with absolute magnitudes $M_r < -20$, the VoidFinder algorithm of 
-\cite{Hoyle02} \citep[based on the algorithm described by][]{ElAd97} removes all 
-isolated galaxies (defined as having the third nearest neighbor more than 7 
-$h^{-1}$ Mpc away).  After applying a grid to the remaining galaxies, spheres 
-are grown from all empty grid cells (cells containing no galaxies).  A sphere 
-reaches its maximum size when it encounters four galaxies on its surface.  To be 
-classified as a void (or part of one), a sphere must have a minimum 10 Mpc 
-radius.  If two spheres overlap by more than 10\%, they are considered part of 
-the same void.  See \cite{Hoyle02} for a more detailed description of the 
-VoidFinder algorithm.  Those galaxies that fall within these void spheres are 
-classified as voids.  Those galaxies that lie outside the spheres are classified 
-as wall galaxies.  Because we cannot identify any voids within 10 Mpc of the 
-edge of the survey, we do not include the galaxies that fall within this region 
-in either the void or wall sample (throughout this paper, these galaxies are 
-labeled as ``Uncertain'').
+
+The large-scale environment of the galaxies is determined using the void catalog 
+compiled by \cite{Pan12}, which was constructed with the galaxies in SDSS DR7 
+catalog.  The VoidFinder algorithm of \cite{Hoyle02} \citep[based on the 
+algorithm described by][]{ElAd97} removes all isolated galaxies (defined as 
+having the third nearest neighbor more than 7 \hMpc away) using only galaxies 
+with absolute magnitudes $M_r < -20$.  After applying a grid to the remaining 
+galaxies, spheres are grown from all cells containing no galaxies until it 
+encounters four galaxies on its surface.  A sphere must have a minimum 10 \hMpc 
+radius to be classified as a void (or part of one).  If two spheres overlap by 
+more than 10\%, they are considered part of the same void.  See \cite{Hoyle02} 
+for a more detailed description of the VoidFinder algorithm.  Those galaxies 
+that fall within these void spheres are classified as voids.  Galaxies that lie 
+outside the spheres are classified as wall galaxies.  Because we cannot identify 
+any voids within 5 \hMpc of the edge of the survey, we classify these galaxies 
+as ``Uncertain.''
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Abundance analysis and results}
+\section[Results]{Abundance analysis and results}
 
@@
 
-%Our primary objective is to perform a relative measurement of metallicity of 
-%dwarf galaxies to discern how the large-scale environment affects their chemical 
-%evolution.  As discussed in Section \ref{sec:Theory}, the strength of and 
-%ability to observe different spectral lines between various surveys and 
-%observations require multiple methods to be developed for metallicity 
-%calculations.  In this paper, we use only the Direct $T_e$ method, because no 
-%other method has yet been calibrated using dwarf galaxies.  The results from the 
-%various methods are not directly comparable; while they all return metallicities 
-%within the same range, the same galaxy can have very different metallicity 
-%values depending on which method is used.  Conversions between methods have been 
-%developed \citep[see][]{Kewley08}, but it is not clear that these conversions 
-%would be accurate for dwarf galaxies.  Unfortunately, there are not enough 
-%galaxies available in our sample to calibrate these other methods for dwarf 
-%galaxies.
-
 All line ratios listed are ratios of the emission-line fluxes.  Galaxies with 
-low metallicities have $Z = 12 + \log (\text{O}/\text{H}) < 7.6$ 
-\citep{Pustilnik06}; galaxies with high metallicities have $Z > 8.2$ 
-\citep{Pilyugin06}.  The solar metallicity $Z_\odot = 8.86$ \citep{Delahaye06}.
+low metallicities have $Z =$ \OH $< 7.6$ \citep{Pustilnik06}; galaxies with high 
+metallicities have $Z > 8.2$ \citep{Pilyugin06}.  The solar metallicity 
+$Z_\odot = 8.86$ \citep{Delahaye06}.
 
@@
 
-The selection criteria outlined in Section \ref{sec:SDSS_limits} limit our 
+The selection criteria outlined in Section \ref{sec:SDSS_limits_P3} limit our 
 sample to only star-forming dwarf galaxies.  As a result, this is not a 
@@
 % Results table (machine-readable)
-\floattable
-\input{results_table_short}
+\input{Tables/Paper3/results_table_short}
 
 The abundances estimated using the direct $T_e$ method for our dwarf galaxy 
-sample are listed in Table \ref{tab:Results}.  Also included are other 
+sample are listed in Table \ref{tab:Results_P3}.  Also included are other 
 significant characteristics and identification for the galaxies, including their 
@@
     \centering
-    \includegraphics[width=0.49\textwidth]{1sig_dwarf_SF_t3_12logOHrelations_dust_hist}
-    \includegraphics[width=0.49\textwidth]{1sig_dwarf_SF_t3_12logOHrelations_dust_CDF}
-    \caption{Gas-phase metallicity of void dwarf (red solid line) and wall 
-    dwarf (black dashed line) galaxies.  A two-sample K-S test of the two data 
-    sets results in an asymptotic $p$-value of 0.12, indicating a 12\% 
-    probability that a test statistic greater than the observed value of 0.06 
-    will be seen if the void sample is drawn from the wall sample.  This is 
-    reflected visually, as there appears to be a slight but statistically 
-    significant significant large-scale environmental influence on the 
-    metallicity of dwarf galaxies.}
-    \label{fig:met1sig}
+    \includegraphics[width=0.49\textwidth]{Images/Paper3/1sig_dwarf_SF_t3_12logOHrelations_dust_hist}
+    \includegraphics[width=0.49\textwidth]{Images/Paper3/1sig_dwarf_SF_t3_12logOHrelations_dust_CDF}
+    \caption[O/H distribution for dwarf galaxy sample]{Gas-phase metallicity of 
+    void dwarf (red solid line) and wall dwarf (black dashed line) galaxies.  A 
+    two-sample K-S test of the two data sets results in an asymptotic $p$-value 
+    of 0.12, indicating a 12\% probability that a test statistic greater than 
+    the observed value of 0.06 will be seen if the void sample is drawn from the 
+    wall sample.  This is reflected visually, as there appears to be a slight 
+    but statistically significant significant large-scale environmental 
+    influence on the metallicity of dwarf galaxies.}
+    \label{fig:met1sig_P3}
 \end{figure*}
@@
     \centering
-    \includegraphics[width=0.49\textwidth]{1sig_dwarf_SF_t3_12logNHrelations_dust_hist}
-    \includegraphics[width=0.49\textwidth]{1sig_dwarf_SF_t3_12logNHrelations_dust_CDF}
-    \caption{Abundance of nitrogen relative to hydrogen of void dwarf (red solid 
-    line) and wall dwarf (black dashed line) galaxies.  A two-sample K-S test of 
-    the two data sets results in an asymptotic $p$-value of 0.015, indicating a 
-    1.5\% probability that a test statistic greater than the observed value of 
-    0.08 will be seen, if the void sample is drawn from the wall sample.  This 
-    is reflected visually, as the void dwarf galaxies appear to have lower 
-    values of the N/H ratio than the wall dwarf galaxies.  There is a 
-    large-scale environmental dependence of the chemical evolution of dwarf 
-    galaxies.}
-    \label{fig:N_1sig}
+    \includegraphics[width=0.49\textwidth]{Images/Paper3/1sig_dwarf_SF_t3_12logNHrelations_dust_hist}
+    \includegraphics[width=0.49\textwidth]{Images/Paper3/1sig_dwarf_SF_t3_12logNHrelations_dust_CDF}
+    \caption[N/H distribution for dwarf galaxy sample]{Abundance of nitrogen 
+    relative to hydrogen of void dwarf (red solid line) and wall dwarf (black 
+    dashed line) galaxies.  A two-sample K-S test of the two data sets results 
+    in an asymptotic $p$-value of 0.015, indicating a 1.5\% probability that a 
+    test statistic greater than the observed value of 0.08 will be seen, if the 
+    void sample is drawn from the wall sample.  This is reflected visually, as 
+    the void dwarf galaxies appear to have lower values of the N/H ratio than 
+    the wall dwarf galaxies.  There is a large-scale environmental dependence of 
+    the chemical evolution of dwarf galaxies.}
+    \label{fig:N_1sig_P3}
 \end{figure*}
@@
 The distributions of oxygen and nitrogen abundances for dwarf galaxies as a 
-function of large-scale environment are shown in Figures \ref{fig:met1sig} and 
-\ref{fig:N_1sig}, respectively.  Both histograms show a slight shift between 
-voids and walls in the chemical abundances of dwarf galaxies.  A two-sample 
-Kolmogorov-Smirnov (K-S) test quantifies this observation --- a test statistic 
-of 0.06 for oxygen and 0.08 for nitrogen are produced, corresponding to a 
-probability of 12\% and 1.5\%, respectively, that a test statistic greater than 
-or equal that observed will be measured if the void sample were drawn from the 
-wall sample.  The cumulative distribution function (CDF) for each of these 
-elements can be seen on the right in Figures \ref{fig:met1sig} and 
-\ref{fig:N_1sig}; they show that void dwarf galaxies have slightly higher oxygen 
-abundances and slightly lower nitrogen abundances than dwarf galaxies in more 
-dense regions.  The K-S test quantifies the visual interpretation of these 
+function of large-scale environment are shown in Figures \ref{fig:met1sig_P3} 
+and \ref{fig:N_1sig_P3}, respectively.  Both histograms show a slight shift 
+between voids and walls in the chemical abundances of dwarf galaxies.  A 
+two-sample Kolmogorov-Smirnov (K-S) test quantifies this observation --- a test 
+statistic of 0.06 for oxygen and 0.08 for nitrogen are produced, corresponding 
+to a probability of 12\% and 1.5\%, respectively, that a test statistic greater 
+than or equal that observed will be measured if the void sample were drawn from 
+the wall sample.  The cumulative distribution function (CDF) for each of these 
+elements can be seen on the right in Figures \ref{fig:met1sig_P3} and 
+\ref{fig:N_1sig_P3}; they show that void dwarf galaxies have slightly higher 
+oxygen abundances and slightly lower nitrogen abundances than dwarf galaxies in 
+more dense regions.  The K-S test quantifies the visual interpretation of these 
 figures that the distributions of oxygen and nitrogen abundances are slightly 
@@
 median shift of 0.02) relative to wall dwarf galaxies.  A tabular version of 
-this analysis can be found in Table \ref{tab:stats}.
+this analysis can be found in Table \ref{tab:stats_p3}.
 
@@
     \centering
-    \includegraphics[width=0.49\textwidth]{1sig_dwarf_SF_t3_logNOrelations_dust_hist}
-    \includegraphics[width=0.49\textwidth]{1sig_dwarf_SF_t3_logNOrelations_dust_CDF}
-    \caption{Ratio of nitrogen to oxygen of void dwarf (red solid line) and wall 
-    dwarf (black dashed line) galaxies.  A two-sample K-S test of the two data 
-    sets results in an asymptotic $p$-value of $2.6\times 10^{-4}$, indicating 
-    only a 0.03\% probability that a test statistic greater than the observed 
-    value of 0.10 will be seen.  This is reflected visually, as there is a shift 
-    in the N/O ratio between the two populations of dwarf galaxies --- the void 
-    galaxies have a lower value of N/O than the wall galaxies.  There is a 
-    large-scale influence on the relative chemical abundances of dwarf 
-    galaxies.}
-    \label{fig:NOratio}
+    \includegraphics[width=0.49\textwidth]{Images/Paper3/1sig_dwarf_SF_t3_logNOrelations_dust_hist}
+    \includegraphics[width=0.49\textwidth]{Images/Paper3/1sig_dwarf_SF_t3_logNOrelations_dust_CDF}
+    \caption[N/O distribution of dwarf galaxy sample]{Ratio of nitrogen to 
+    oxygen of void dwarf (red solid line) and wall dwarf (black dashed line) 
+    galaxies.  A two-sample K-S test of the two data sets results in an 
+    asymptotic $p$-value of $2.6\times 10^{-4}$, indicating only a 0.03\% 
+    probability that a test statistic greater than the observed value of 0.10 
+    will be seen.  This is reflected visually, as there is a shift in the N/O 
+    ratio between the two populations of dwarf galaxies --- the void galaxies 
+    have a lower value of N/O than the wall galaxies.  There is a large-scale 
+    influence on the relative chemical abundances of dwarf galaxies.}
+    \label{fig:NOratio_P3}
 \end{figure*}
@@
 communicates the nucleosynthesis history of the galaxies.  As seen in Fig. 
-\ref{fig:NOratio}, the N/O abundance ratio also indicates a large-scale 
+\ref{fig:NOratio_P3}, the N/O abundance ratio also indicates a large-scale 
 environmental influence on the chemical evolution of dwarf galaxies --- void 
@@
 % Statistics table
-\floattable
-\begin{deluxetable}{ccccccc}
-    \tablewidth{0pt}
-    \tablecolumns{7}
-    \tablecaption{Abundance statistics\label{tab:stats}}
-    \tablehead{\colhead{Environment} & \colhead{Average} & \colhead{Median} & \colhead{Average Shift\tablenotemark{a}} & \colhead{Median Shift\tablenotemark{a}} & \colhead{$p$-value} & \colhead{K-S Test Statistic}}
-    \startdata
+\begin{table}
+    \centering
+
+    \begin{tabular}{ccccccc}
+        Environment & Average & Median & Average Shift\footnote{Wall -- Void (Positive shifts indicate that the wall values are greater than the void values; negative shifts indicate that the void values are greater than the wall values.)} & Median Shift & $p$-value & K-S Test Statistic\\
+        \hline
         % Oxygen %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-        \cutinhead{$12 + \log (\text{O}/\text{H})$}
+        \hline
+        \multicolumn{7}{c}{\OH}\\
+        \hline
         Void & $7.99\pm 0.007$ & 8.06 & \multirow{2}{*}{$-0.03\pm 0.012$} & \multirow{2}{*}{-0.03} & \multirow{2}{*}{0.1197} & \multirow{2}{*}{0.0569}\\
@@
         % Nitrogen %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-        \cutinhead{$12 + \log (\text{N}/\text{H})$}
+        \hline
+        \multicolumn{7}{c}{\NH}\\
+        \hline
         Void & $6.55\pm 0.007$ & 6.58 & \multirow{2}{*}{$0.04\pm 0.011$} & \multirow{2}{*}{0.02} & \multirow{2}{*}{0.0149} & \multirow{2}{*}{0.0750}\\
@@
         % N/O %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-        \cutinhead{$\log (\text{N}/\text{O})$}
+        \hline
+        \multicolumn{7}{c}{\NO}\\
+        \hline
         Void & $-1.45\pm 0.010$ & -1.43 & \multirow{2}{*}{$0.07\pm 0.016$} & \multirow{2}{*}{0.06} & \multirow{2}{*}{0.0003} & \multirow{2}{*}{0.1013}\\
         Wall & $-1.38\pm 0.012$ & -1.37 & & & & \\
-    \enddata
-    \tablecomments{Statistics on the gas-phase oxygen, nitrogen, and nitrogen 
-    relative to oxygen abundances in dwarf void and wall galaxies.  Combined 
-    with the histograms in Figures \ref{fig:met1sig}--\ref{fig:NOratio}, these 
-    results indicate an influence on the chemical evolution of galaxies by the 
-    large-scale environment, especially on the relative abundance of nitrogen to 
-    oxygen.  Void galaxies have slightly higher oxygen and nitrogen abundances 
-    than wall galaxies, but void galaxies have slightly lower N/O ratios than 
-    wall galaxies.}
-    \tablenotetext{a}{Wall -- Void (Positive shifts indicate that the wall 
-    values are greater than the void values; negative shifts indicate that the 
-    void values are greater than the wall values.)}
-\end{deluxetable}
+    \end{tabular}
+
+    \caption[Abundance statistics]{Statistics on the gas-phase oxygen, nitrogen, 
+    and nitrogen relative to oxygen abundances in dwarf void and wall galaxies.  
+    Combined with the histograms in Figures 
+    \ref{fig:met1sig_P3}--\ref{fig:NOratio_P3}, these results indicate an 
+    influence on the chemical evolution of galaxies by the large-scale 
+    environment, especially on the relative abundance of nitrogen to oxygen.  
+    Void galaxies have slightly higher oxygen and nitrogen abundances than wall 
+    galaxies, but void galaxies have slightly lower N/O ratios than wall 
+    galaxies.}
+
+    \label{tab:stats_p3}
+
+\end{table}
 
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{1sig_dwarf_I06relations_SF_t3_T04comparison_dust}
-    \caption{Oxygen abundance comparison between our calculated estimates with 
-    the O$^+$ approximation and those made by \cite{Tremonti04}.  Error bars 
-    have been omitted for clarity.  While the majority of our abundance 
-    estimates agree reasonably well with the values already published, it is 
-    clear that our estimates are often lower than the previously published 
+    \includegraphics[width=0.65\textwidth]{Images/Paper3/1sig_dwarf_I06relations_SF_t3_T04comparison_dust}
+    \caption[Comparison of O$^+$ approximation metallicities to 
+    \cite{Tremonti04}]{Oxygen abundance comparison between our calculated 
+    estimates with the O$^+$ approximation and those made by \cite{Tremonti04}.  
+    Error bars have been omitted for clarity.  While the majority of our 
+    abundance estimates agree reasonably well with the values already published, 
+    it is clear that our estimates are often lower than the previously published 
     values.  It is well known that the strong-line methods \citep[like those 
@@
     \centering
-%    \includegraphics[width=0.5\textwidth]{1sig_I06relations_dwarf_SF_t3_dust_Z12logOH_logNO}
-%    \includegraphics[width=0.5\textwidth]{1sig_I06relations_dwarf_SF_t3_dust_Z12logOH_logNO_Mbin}
-%    \includegraphics[width=0.5\textwidth]{1sig_I06relations_dwarf_SF_t3_dust_Z12logOH_logNO_scatterMbin}
-    \includegraphics[width=0.5\textwidth]{1sig_I06relations_dwarf_SF_t3_dust_NSA_Z12logOH_logNO_scatterMbin}
-    \caption{Oxygen abundance ($12 + \log \left(\text{O}/\text{H}\right)$) 
-    versus the N/O ratio ($\log \left( \text{N}/\text{O}\right)$) for the dwarf 
-    galaxies in this study; the average values of the galaxies' abundances when 
-    binned by stellar mass in bins of width 0.1 are also shown.  As seen in 
-    \cite{Andrews13} and \cite{Douglass17b}, while most of the mass bins are 
-    scattered together around $\log (\text{N}/\text{O}) \sim$-1.5, there is a 
-    negative correlation between these two abundance ratios.  There is no 
-    evidence of secondary nitrogen production in this sample of star-forming 
-    dwarf galaxies, which would manifest as a positive relationship between 
-    O/H and N/O at high metallicities.}
+    \includegraphics[width=0.65\textwidth]{Images/Paper3/1sig_I06relations_dwarf_SF_t3_dust_NSA_Z12logOH_logNO_scatterMbin}
+    \caption[O/H versus N/O for star-forming dwarf galaxies]{Oxygen abundance 
+    (\OH) versus the N/O ratio (\NO) for the dwarf galaxies in this study; the 
+    average values of the galaxies' abundances when binned by stellar mass in 
+    bins of width 0.1 are also shown.  As seen in \cite{Andrews13} and 
+    \cite{Douglass17b}, while most of the mass bins are scattered together 
+    around \NO $\sim$-1.5, there is a negative correlation between these two 
+    abundance ratios.  There is no evidence of secondary nitrogen production in 
+    this sample of star-forming dwarf galaxies, which would manifest as a 
+    positive relationship between O/H and N/O at high metallicities.}
     \label{fig:NOvOH}
@@
 note that they measure a slope of -0.21 for their stellar mass-binned galaxies 
-with metallicities $12 + \log(\text{O}/\text{H}) < 8.5$, while 
-\cite{Douglass17b} finds a slope of $-0.38\pm 0.078$ for dwarf galaxies.  A 
-linear fit to our dwarf galaxy sample has a slope of $-0.52\pm 0.041$, steeper 
-than any previously measured.
+with metallicities \OH $< 8.5$, while \cite{Douglass17b} finds a slope of 
+$-0.38\pm 0.078$ for dwarf galaxies.  A linear fit to our dwarf galaxy sample 
+has a slope of $-0.52\pm 0.041$, steeper than any previously measured.
 
 \begin{figure}
-%    \includegraphics[width=0.5\textwidth]{1sig_I06relations_dwarf_SF_t3_dust_Z12logOH_N12logNH_scatterMbin}
-    \includegraphics[width=0.5\textwidth]{1sig_I06relations_dwarf_SF_t3_dust_NSA_Z12logOH_N12logNH_scatterMbin}
-    \caption{Oxygen abundance ($12 + \log \left(\text{O}/\text{H}\right)$) 
-    versus nitrogen abundance ($12 + \log \left(\text{N}/\text{H}\right)$) for 
-    the dwarf galaxies in this study; the average values of the galaxies' 
-    abundances when binned by their stellar mass in bins of width 0.1 are also 
-    shown.  There is evidence of two evolutionary tracks for the star-forming 
-    dwarf galaxies here, one with a much steeper slope than the other.}
-    \label{fig:OvN}
+    \includegraphics[width=0.65\textwidth]{Images/Paper3/1sig_I06relations_dwarf_SF_t3_dust_NSA_Z12logOH_N12logNH_scatterMbin}
+    \caption[O/H versus N/H for star-forming dwarf galaxies]{Oxygen abundance 
+    (\OH) versus nitrogen abundance (\NH) for the dwarf galaxies in this study; 
+    the average values of the galaxies' abundances when binned by their stellar 
+    mass in bins of width 0.1 are also shown.  There is evidence of two 
+    evolutionary tracks for the star-forming dwarf galaxies here, one with a 
+    much steeper slope than the other.}
+    \label{fig:OvN_P3}
 \end{figure}
@@
 looking at the relationship between the nitrogen and oxygen abundances relative 
-to hydrogen.  Fig. \ref{fig:OvN} depicts a negative relationship between the 
+to hydrogen.  Fig. \ref{fig:OvN_P3} depicts a negative relationship between the 
 nitrogen and oxygen abundances.  A linear fit to the dwarf galaxies results in a 
@@
 \ref{fig:NOvOH} would manifest itself as a relationship between the N/H and O/H 
-ratios (shown in Fig. \ref{fig:OvN}) with a linear slope of 1.  Secondary 
+ratios (shown in Fig. \ref{fig:OvN_P3}) with a linear slope of 1.  Secondary 
 nitrogen production, a positive relationship in Fig. \ref{fig:NOvOH}, would 
-correspond to a relationship between N/H and O/H in Fig. \ref{fig:OvN} with a 
+correspond to a relationship between N/H and O/H in Fig. \ref{fig:OvN_P3} with a 
 slope greater than 1.  If we split the dwarf galaxies into two populations based 
 on their metallicity, we find that dwarf galaxies with extremely low 
-metallicities ($12 + \log (\text{O}/\text{H}) \leq 7.6$) have a slope of 
-$-1.0\pm 0.21$ in Fig. \ref{fig:NOvOH} and $-0.0\pm 0.21$ in Fig. \ref{fig:OvN}, 
-while the dwarf galaxies with metallicities $12 + \log(\text{O}/\text{H} > 7.6$ 
-have a slope of $-0.41\pm 0.069$ for O/H v. N/O and $0.59\pm 0.069$ for O/H v. 
-N/H.  These slopes indicate that the production of nitrogen is independent of 
-the oxygen abundance in systems with low metallicities, supporting the results 
-found in \cite{Douglass17b}.
-
-Fig. \ref{fig:OvN} shows possible evidence for two evolutionary tracks for 
+metallicities (\OH $\leq 7.6$) have a slope of $-1.0\pm 0.21$ in Fig. 
+\ref{fig:NOvOH} and $-0.0\pm 0.21$ in Fig. \ref{fig:OvN_P3}, while the dwarf 
+galaxies with metallicities \OH $> 7.6$ have a slope of $-0.41\pm 0.069$ for O/H 
+v. N/O and $0.59\pm 0.069$ for O/H v. N/H.  These slopes indicate that the 
+production of nitrogen is independent of the oxygen abundance in systems with 
+low metallicities, supporting the results found in \cite{Douglass17b}.
+
+Fig. \ref{fig:OvN_P3} shows possible evidence for two evolutionary tracks for 
 star-forming dwarf galaxies, irrespective of the large-scale environment.  The 
@@
 
-In both Figs. \ref{fig:NOvOH} and \ref{fig:OvN}, there is no difference in the 
-abundance ratio relationships between void dwarf galaxies and dwarf galaxies in 
-denser regions.  The large-scale environment does not appear to influence the 
+In both Figs. \ref{fig:NOvOH} and \ref{fig:OvN_P3}, there is no difference in 
+the abundance ratio relationships between void dwarf galaxies and dwarf galaxies 
+in denser regions.  The large-scale environment does not appear to influence the 
 nucleosynthesis of nitrogen in dwarf galaxies.
@@
     \centering
-%    \includegraphics[width=0.49\textwidth]{MZ_1sig_I06relations_SF_t3_Mbin}
-    \includegraphics[width=0.49\textwidth]{MZ_1sig_I06relations_dwarf_SF_t3_dust_NSA_python}
-    \includegraphics[width=0.49\textwidth]{MNO_1sig_I06relations_dwarf_SF_t3_dust_NSA_scatterMbin}
-%    \includegraphics[width=0.49\textwidth]{MNO_1sig_I06relations_dwarf_SF_t3_dust}
-    \caption{Stellar mass versus oxygen abundance (left panel) and N/O ratio 
-    (right panel).  We include the metallicity results of \cite{Tremonti04} on 
-    the left to place our dwarf galaxy abundance results in context.  On the 
-    right, we show the average N/O values for the dwarf galaxies binned by 
-    stellar mass plotted over the individual galaxies.  While most of our dwarf 
-    galaxies follow the same trend as already seen in \cite{Tremonti04}, we note 
-    the existence of a number of dwarf galaxies with much lower oxygen abundance 
-    values than what would be predicted based on their stellar mass and the 
-    mass-metallicity relation.  There is no clear difference between void and 
-    wall dwarf galaxies in the mass-metallicity relation.  In the right-hand 
-    panel, though, we see that the turn-off for the N/O plateau occurs at 
-    different masses for the two large-scale environments.}
+    \includegraphics[width=0.49\textwidth]{Images/Paper3/MZ_1sig_I06relations_dwarf_SF_t3_dust_NSA_python}
+    \includegraphics[width=0.49\textwidth]{Images/Paper3/MNO_1sig_I06relations_dwarf_SF_t3_dust_NSA_scatterMbin}
+    \caption[$M_*$ versus N/O for star-forming dwarf galaxies]{Stellar mass 
+    versus oxygen abundance (left panel) and N/O ratio (right panel).  We 
+    include the metallicity results of \cite{Tremonti04} on the left to place 
+    our dwarf galaxy abundance results in context.  On the right, we show the 
+    average N/O values for the dwarf galaxies binned by stellar mass plotted 
+    over the individual galaxies.  While most of our dwarf galaxies follow the 
+    same trend as already seen in \cite{Tremonti04}, we note the existence of a 
+    number of dwarf galaxies with much lower oxygen abundance values than what 
+    would be predicted based on their stellar mass and the mass-metallicity 
+    relation.  There is no clear difference between void and wall dwarf galaxies 
+    in the mass-metallicity relation.  In the right-hand panel, though, we see 
+    that the turn-off for the N/O plateau occurs at different masses for the two 
+    large-scale environments.}
     \label{fig:M_NO}
@@
 to synthesize secondary nitrogen at lower stellar masses than galaxies in more 
-dense regions, consistent with the results from Fig. \ref{fig:met1sig} where 
+dense regions, consistent with the results from Fig. \ref{fig:met1sig_P3} where 
 void dwarf galaxies have higher oxygen abundances than dwarf galaxies in more 
@@
     \centering
-    \includegraphics[width=0.49\textwidth]{1sig_0-17_I06relations_SF_t3_HI_hist}
-    \includegraphics[width=0.49\textwidth]{1sig_0-17_I06relations_SF_t3_HI_CDF}
-    \caption{The distribution of \ion{H}{1} mass in the sample of dwarf 
-    galaxies, separated by their large-scale environment.  There is an obvious 
-    shift towards higher \ion{H}{1} masses in the void dwarf galaxies.}
+    \includegraphics[width=0.49\textwidth]{Images/Paper3/1sig_0-17_I06relations_SF_t3_HI_hist}
+    \includegraphics[width=0.49\textwidth]{Images/Paper3/1sig_0-17_I06relations_SF_t3_HI_CDF}
+    \caption[\ion{H}{1} mass distribution]{The distribution of \ion{H}{1} mass 
+    in the sample of dwarf galaxies, separated by their large-scale environment.  
+    There is an obvious shift towards higher \ion{H}{1} masses in the void dwarf 
+    galaxies.}
     \label{fig:HI_hist}
@@
     \centering
-    \includegraphics[width=0.49\textwidth]{HI_OH_1sig_I06relations_dwarf+T04_SF_t3_dust}
-    \includegraphics[width=0.49\textwidth]{HI_NO_1sig_I06relations_dwarf_SF_t3_dust}
-    \includegraphics[width=0.49\textwidth]{HI_OH_M_1sig_I06relations_dwarf_SF_t3_dust}
-    \includegraphics[width=0.49\textwidth]{HI_NO_M_1sig_I06relations_dwarf_SF_t3_dust}
-    \caption{\ion{H}{1} mass versus metallicity (left) and N/O ratio (right) for 
-    star-forming dwarf galaxies.  The color scheme of the top row emphasizes the 
-    large-scale environment of the star-forming dwarf galaxies, while the bottom 
-    row investigates the relationship between stellar mass, \ion{H}{1} mass, and 
-    chemical abundance.  Error bars have been omitted for clarity.  To place our 
-    oxygen abundance results in context, we show (gray stars) the dwarf galaxies 
-    in SDSS DR7 with metallicity estimates from \cite{Tremonti04}.  From these 
-    plots, there is no significant influence from the large-scale environment on 
-    the relationship between the \ion{H}{1} mass and gas-phase chemical 
-    abundances of star-forming dwarf galaxies.}
+    \includegraphics[width=0.49\textwidth]{Images/Paper3/HI_OH_1sig_I06relations_dwarf+T04_SF_t3_dust}
+    \includegraphics[width=0.49\textwidth]{Images/Paper3/HI_NO_1sig_I06relations_dwarf_SF_t3_dust}
+    \includegraphics[width=0.49\textwidth]{Images/Paper3/HI_OH_M_1sig_I06relations_dwarf_SF_t3_dust}
+    \includegraphics[width=0.49\textwidth]{Images/Paper3/HI_NO_M_1sig_I06relations_dwarf_SF_t3_dust}
+    \caption[\ion{H}{1} mass versus O/H and N/O]{\ion{H}{1} mass versus 
+    metallicity (left) and N/O ratio (right) for star-forming dwarf galaxies.  
+    The color scheme of the top row emphasizes the large-scale environment of 
+    the star-forming dwarf galaxies, while the bottom row investigates the 
+    relationship between stellar mass, \ion{H}{1} mass, and chemical abundance.  
+    Error bars have been omitted for clarity.  To place our oxygen abundance 
+    results in context, we show (gray stars) the dwarf galaxies in SDSS DR7 with 
+    metallicity estimates from \cite{Tremonti04}.  From these plots, there is no 
+    significant influence from the large-scale environment on the relationship 
+    between the \ion{H}{1} mass and gas-phase chemical abundances of 
+    star-forming dwarf galaxies.}
     \label{fig:HI}
@@
     \centering
-%    \includegraphics[width=0.49\textwidth]{ur_OH_1sig_I06relations_dwarf_SF_t3_dust_python}
-%    \includegraphics[width=0.49\textwidth]{ur_OH_1sig_I06relations_dwarf_SF_t3_dust}
-    \includegraphics[width=0.49\textwidth]{ur_OH_1sig_I06relations_dwarf+T04_SF_t3_dust}
-    \includegraphics[width=0.49\textwidth]{ur_NO_1sig_I06relations_dwarf_SF_t3_dust_scatterURbin}
-    \caption{Color ($u-r$) versus the gas-phase oxygen abundance (left) and the 
-    N/O ratio (right) for star-forming dwarf galaxies.  Error bars on individual 
-    points have been omitted for clarity.  For reference, the dwarf galaxies in 
-    SDSS DR7 that have estimated metallicities from \cite{Tremonti04} are shown 
-    in the left panel in gray.  To discern any environmental trends in the 
-    results, we have binned the galaxies by their color (in bins of width 0.1) 
-    on the right.  The large-scale environment does not influence the 
-    relationship between the color and chemical abundances of dwarf galaxies.}
-    \label{fig:ur}
-\end{figure*}
-
-The gas-phase chemical abundance is expected to have a positive correlation with 
-a galaxy's color.  Older galaxies have had more time to convert their gas into 
-heavier elements through star formation, increasing their metallicities.  The 
-color-metallicity and color-N/O relations for our sample of star-forming dwarf 
-galaxies can be seen in Figures \ref{fig:ur} and \ref{fig:gr}.  As we see, bluer 
-galaxies have lower O/H and N/O ratios when we look at both the $u-r$ and $g-r$ 
-colors.  While there is a subset of dwarf galaxies with extremely low 
-metallicities that do not follow this trend (seen in the left-hand panels of 
-Figures \ref{fig:ur} and \ref{fig:gr}), this population follows the color-N/O 
-trend seen on the right in each of these figures.  While these galaxies have 
-unusually low oxygen abundances, they have normal N/O ratios.
-
-\begin{figure*}
-    \centering
-%    \includegraphics[width=0.49\textwidth]{gr_OH_1sig_I06relations_dwarf_SF_t3_dust_python}
-%    \includegraphics[width=0.49\textwidth]{gr_OH_1sig_I06relations_dwarf_SF_t3_dust}
-    \includegraphics[width=0.49\textwidth]{gr_OH_1sig_I06relations_dwarf+T04_SF_t3_dust}
-    \includegraphics[width=0.49\textwidth]{gr_NO_1sig_I06relations_dwarf_SF_t3_dust_scatterGRbin}
-    \caption{Color ($g-r$) versus the gas-phase oxygen abundance (left) and the 
-    N/O ratio (right) for star-forming dwarf galaxies.  Error bars on individual 
-    points have been omitted for clarity.  For reference, the galaxies in SDSS 
+    \includegraphics[width=0.49\textwidth]{Images/Paper3/ur_OH_1sig_I06relations_dwarf+T04_SF_t3_dust}
+    \includegraphics[width=0.49\textwidth]{Images/Paper3/ur_NO_1sig_I06relations_dwarf_SF_t3_dust_scatterURbin}
+    \caption[$u-r$ versus O/H and N/O for star-forming dwarf galaxies]{Color 
+    ($u-r$) versus the gas-phase oxygen abundance (left) and the N/O ratio 
+    (right) for star-forming dwarf galaxies.  Error bars on individual points 
+    have been omitted for clarity.  For reference, the dwarf galaxies in SDSS 
     DR7 that have estimated metallicities from \cite{Tremonti04} are shown in 
@@
     between the color and chemical abundances of dwarf galaxies.}
+    \label{fig:ur_P3}
+\end{figure*}
+
+The gas-phase chemical abundance is expected to have a positive correlation with 
+a galaxy's color.  Older galaxies have had more time to convert their gas into 
+heavier elements through star formation, increasing their metallicities.  The 
+color-metallicity and color-N/O relations for our sample of star-forming dwarf 
+galaxies can be seen in Figures \ref{fig:ur_P3} and \ref{fig:gr}.  As we see, 
+bluer galaxies have lower O/H and N/O ratios when we look at both the $u-r$ and 
+$g-r$ colors.  While there is a subset of dwarf galaxies with extremely low 
+metallicities that do not follow this trend (seen in the left-hand panels of 
+Figures \ref{fig:ur_P3} and \ref{fig:gr}), this population follows the color-N/O 
+trend seen on the right in each of these figures.  While these galaxies have 
+unusually low oxygen abundances, they have normal N/O ratios.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.49\textwidth]{Images/Paper3/gr_OH_1sig_I06relations_dwarf+T04_SF_t3_dust}
+    \includegraphics[width=0.49\textwidth]{Images/Paper3/gr_NO_1sig_I06relations_dwarf_SF_t3_dust_scatterGRbin}
+    \caption[$g-r$ versus O/H and N/O for star-forming dwarf galaxies]{Color 
+    ($g-r$) versus the gas-phase oxygen abundance (left) and the N/O ratio 
+    (right) for star-forming dwarf galaxies.  Error bars on individual points 
+    have been omitted for clarity.  For reference, the galaxies in SDSS DR7 that 
+    have estimated metallicities from \cite{Tremonti04} are shown in the left 
+    panel in gray.  To discern any environmental trends in the results, we have 
+    binned the galaxies by their color (in bins of width 0.1) on the right.  The 
+    large-scale environment does not influence the relationship between the 
+    color and chemical abundances of dwarf galaxies.}
     \label{fig:gr}
@@
 massive stars burn out and the galaxy becomes redder.  This trend can be seen in 
-the star-forming dwarf galaxies on the right of Figures \ref{fig:ur} and 
+the star-forming dwarf galaxies on the right of Figures \ref{fig:ur_P3} and 
 \ref{fig:gr}, matching the trends seen in \cite{Douglass17b,vanZee06a,Berg12}.
@@
 dwarf galaxies.  There is no obvious difference between the void and wall dwarf 
-galaxies in the left-hand panels of Figures \ref{fig:ur} and \ref{fig:gr}, when 
-we concentrate on the oxygen abundance as a function of color.  To help discern 
-any influence from the environment on the N/O ratio as a function of color, we 
-bin the star-forming dwarf galaxies by their color in bins of width 0.1 --- 
-these results are overlaid on the left-hand plots of Figures \ref{fig:ur} and 
-\ref{fig:gr}.  The shift toward higher N/O ratios seen in the wall bins in both 
-figures is the same shift identified in the histograms in Fig. 
-\ref{fig:NOratio}.  Any variation in the color-abundance relationship between 
-the void and wall populations except a vertical shift would be evidence of the 
-large-scale environment influencing the relationship.  There is a modest 
+galaxies in the left-hand panels of Figures \ref{fig:ur_P3} and \ref{fig:gr}, 
+when we concentrate on the oxygen abundance as a function of color.  To help 
+discern any influence from the environment on the N/O ratio as a function of 
+color, we bin the star-forming dwarf galaxies by their color in bins of width 
+0.1 --- these results are overlaid on the left-hand plots of Figures 
+\ref{fig:ur_P3} and \ref{fig:gr}.  The shift toward higher N/O ratios seen in 
+the wall bins in both figures is the same shift identified in the histograms in 
+Fig. \ref{fig:NOratio_P3}.  Any variation in the color-abundance relationship 
+between the void and wall populations except a vertical shift would be evidence 
+of the large-scale environment influencing the relationship.  There is a modest 
 difference in the slope of these bins in N/O, where the colors of star-forming 
@@
     \centering
-%    \includegraphics[width=0.49\textwidth]{SFR_OH_1sig_I06relations_dwarf_SF_t3_dust_python}
-    \includegraphics[width=0.49\textwidth]{SFR_OH_1sig_I06relations_dwarf+T04_SF_t3_dust}
-    \includegraphics[width=0.49\textwidth]{SFR_NO_1sig_I06relations_dwarf_SF_t3_dust_scatterSFRbin}
-    \caption{SFR versus metallicity (left) and the N/O ratio (right) for 
-    star-forming dwarf galaxies.  Error bars for individual galaxies have been 
-    omitted for clarity.  To place our oxygen abundance results in context, we 
-    show (gray stars) the dwarf galaxies in SDSS DR7 with metallicity estimates 
-    from \cite{Tremonti04}.  To discern any environmental effects on the 
-    relation between SFR and the N/O ratio, we bin the dwarf galaxies by SFR (in 
-    bins of width 0.1).  From these plots, the large-scale environment has no 
+    \includegraphics[width=0.49\textwidth]{Images/Paper3/SFR_OH_1sig_I06relations_dwarf+T04_SF_t3_dust}
+    \includegraphics[width=0.49\textwidth]{Images/Paper3/SFR_NO_1sig_I06relations_dwarf_SF_t3_dust_scatterSFRbin}
+    \caption[SFR versus O/H and N/O for star-forming dwarf galaxies]{SFR versus 
+    metallicity (left) and the N/O ratio (right) for star-forming dwarf 
+    galaxies.  Error bars for individual galaxies have been omitted for clarity.  
+    To place our oxygen abundance results in context, we show (gray stars) the 
+    dwarf galaxies in SDSS DR7 with metallicity estimates from 
+    \cite{Tremonti04}.  To discern any environmental effects on the relation 
+    between SFR and the N/O ratio, we bin the dwarf galaxies by SFR (in bins of 
+    width 0.1).  From these plots, the large-scale environment has no 
     discernible influence on the relationship between the SFR and gas-phase 
@@
     \centering
-%    \includegraphics[width=0.49\textwidth]{sSFR_OH_1sig_I06relations_dwarf_SF_t3_dust_python}
-    \includegraphics[width=0.49\textwidth]{sSFR_OH_1sig_I06relations_dwarf+T04_SF_t3_dust}
-    \includegraphics[width=0.49\textwidth]{sSFR_NO_1sig_I06relations_dwarf_SF_t3_dust_scattersSFRbin}
-    \caption{Specific star formation rate (sSFR) versus metallicity (left) and 
-    the N/O ratio (right) for star-forming dwarf galaxies.  Error bars on 
-    individual galaxies have been omitted for clarity.  To place our oxygen 
-    abundance results in context, we show (gray stars) the dwarf galaxies in 
-    SDSS DR7 with metallicity estimates from \cite{Tremonti04}.  To discern any 
-    environmental effects on the relation between sSFR and the N/O ratio, we bin 
-    the dwarf galaxies by sSFR (in bins of width 0.1).  From these figures, 
-    there is no significant influence on the relationship between the sSFR and 
-    gas-phase chemical abundances of star-forming dwarf galaxies.}
-    \label{fig:sSFR}
+    \includegraphics[width=0.49\textwidth]{Images/Paper3/sSFR_OH_1sig_I06relations_dwarf+T04_SF_t3_dust}
+    \includegraphics[width=0.49\textwidth]{Images/Paper3/sSFR_NO_1sig_I06relations_dwarf_SF_t3_dust_scattersSFRbin}
+    \caption[sSFR versus O/H and N/O for star-forming dwarf galaxies]{Specific 
+    star formation rate (sSFR) versus metallicity (left) and the N/O ratio 
+    (right) for star-forming dwarf galaxies.  Error bars on individual galaxies 
+    have been omitted for clarity.  To place our oxygen abundance results in 
+    context, we show (gray stars) the dwarf galaxies in SDSS DR7 with 
+    metallicity estimates from \cite{Tremonti04}.  To discern any environmental 
+    effects on the relation between sSFR and the N/O ratio, we bin the dwarf 
+    galaxies by sSFR (in bins of width 0.1).  From these figures, there is no 
+    significant influence on the relationship between the sSFR and gas-phase 
+    chemical abundances of star-forming dwarf galaxies.}
+    \label{fig:sSFR_P3}
 \end{figure*}
@@
 and the gas-phase chemical abundances in star-forming dwarf galaxies.  As shown 
-in Fig. \ref{fig:sSFR}, there is a stronger correlation between the sSFR of a 
+in Fig. \ref{fig:sSFR_P3}, there is a stronger correlation between the sSFR of a 
 dwarf galaxy and its metallicity and N/O ratio.  The left-hand panel of Fig. 
-\ref{fig:sSFR} shows the relationship between the gas-phase oxygen abundance and 
-the sSFR for star-forming dwarf galaxies; to place our results in context, we 
-also include (gray stars) those dwarf galaxies in SDSS DR7 for which 
+\ref{fig:sSFR_P3} shows the relationship between the gas-phase oxygen abundance 
+and the sSFR for star-forming dwarf galaxies; to place our results in context, 
+we also include (gray stars) those dwarf galaxies in SDSS DR7 for which 
 \cite{Tremonti04} was able to estimate metallicities.  In the metallicity regime 
-we are able to probe ($12 + \log (\text{O}/\text{H}) \leq 8.5$), the 
-star-forming dwarf galaxies display relatively little relationship between their 
-sSFR and metallicity.  The group of extremely low metallicity dwarf galaxies 
-($12 + \log (\text{O}/\text{H}) < 7.6$) in our sample has some of the lowest 
-sSFR of our dwarf galaxies.
-
-As we see on the right in Fig. \ref{fig:sSFR}, though, there is a strong 
+we are able to probe (\OH $\leq 8.5$), the star-forming dwarf galaxies display 
+relatively little relationship between their sSFR and metallicity.  The group of 
+extremely low metallicity dwarf galaxies (\OH $< 7.6$) in our sample has some of 
+the lowest sSFR of our dwarf galaxies.
+
+As we see on the right in Fig. \ref{fig:sSFR_P3}, though, there is a strong 
 anti-correlation between the sSFR and N/O ratio for the star-forming dwarf 
@@
 There is also very little scatter in the right-hand panel of Fig. 
-\ref{fig:sSFR}, indicating a significant relationship between the sSFR and N/O 
-ratio for dwarf galaxies.  The Pearson correlation coefficients for our sample 
-of star-forming void dwarf galaxies is $-0.62\pm 0.020$; the correlation 
+\ref{fig:sSFR_P3}, indicating a significant relationship between the sSFR and 
+N/O ratio for dwarf galaxies.  The Pearson correlation coefficients for our 
+sample of star-forming void dwarf galaxies is $-0.62\pm 0.020$; the correlation 
 coefficient for the star-forming wall dwarf galaxies is $-0.55\pm 0.025$.  It is 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Large-scale environmental influence}
+\section[Discussion]{Large-scale environmental influence}
 
@@
 galaxies with higher metallicities preferentially reside in denser regions.  
-This is the opposite of the trend seen in Fig. \ref{fig:met1sig} in the 
+This is the opposite of the trend seen in Fig. \ref{fig:met1sig_P3} in the 
 star-forming dwarf galaxies, although our results are not a direct comparison 
@@
 We posit that the slightly higher metallicities seen in the star-forming void 
-dwarf galaxies in Fig. \ref{fig:met1sig} is due to a large-scale environmental 
-effect on the ratio of a galaxy's dark matter halo mass to stellar mass 
-($M_{DM}/M_*$).  \cite{Goldberg04} show that gravitational clustering within a 
-void proceeds as if in a very low density universe, where the growth of 
+dwarf galaxies in Fig. \ref{fig:met1sig_P3} is due to a large-scale 
+environmental effect on the ratio of a galaxy's dark matter halo mass to stellar 
+mass ($M_{DM}/M_*$).  \cite{Goldberg04} show that gravitational clustering 
+within a void proceeds as if in a very low density universe, where the growth of 
 gravitationally bound dark matter halos ends relatively early.  Afterwards, 
@@
 % Shift in N/O due to environmental influence on cosmic downsizing
-As we see in Fig. \ref{fig:NOratio}, star-forming void dwarf galaxies have a 
+As we see in Fig. \ref{fig:NOratio_P3}, star-forming void dwarf galaxies have a 
 lower N/O ratio than wall dwarf galaxies.  This strengthens the preliminary 
@@
 SFRs.  This concept is supported by the color-N/O diagram in Figures 
-\ref{fig:ur} and \ref{fig:gr}, where the bluer galaxies have lower N/O ratios.  
-The correlations between color and the N/O ratio found in \cite{vanZee06a}, 
-\cite{Berg12}, \cite{Douglass17b}, and this work are a result of declining SFRs 
-\citep{vanZee06a}.  The average lower N/O ratios we see in star-forming void 
-dwarf galaxies may be observational evidence that cosmic downsizing is 
-environmentally dependent.
+\ref{fig:ur_P3} and \ref{fig:gr}, where the bluer galaxies have lower N/O 
+ratios.  The correlations between color and the N/O ratio found in 
+\cite{vanZee06a}, \cite{Berg12}, \cite{Douglass17b}, and this work are a result 
+of declining SFRs \citep{vanZee06a}.  The average lower N/O ratios we see in 
+star-forming void dwarf galaxies may be observational evidence that cosmic 
+downsizing is environmentally dependent.
 
@@
 the 1920 dwarf galaxies we analyze, 287 have extremely low metallicity values 
-($12 + \log (\text{O}/\text{H}) \leq 7.6$).  Of these 287 low-metallicity dwarf 
-galaxies, 144 are found in voids (approximately 15\% of the star-forming void 
-dwarf galaxy population studied) and 122 are located in denser regions (16\% of 
-the star-forming wall dwarf galaxy population studied).  These population 
-fractions do not support the existence of a special population of extremely 
-metal-poor dwarf galaxies in voids.
+(\OH $\leq 7.6$).  Of these 287 low-metallicity dwarf galaxies, 144 are found in 
+voids (approximately 15\% of the star-forming void dwarf galaxy population 
+studied) and 122 are located in denser regions (16\% of the star-forming wall 
+dwarf galaxy population studied).  These population fractions do not support the 
+existence of a special population of extremely metal-poor dwarf galaxies in 
+voids.
 
@@
 have higher N/O ratios than the total star-forming dwarf galaxy population 
-studied.  From Figures \ref{fig:ur} and \ref{fig:gr}, it is apparent that these 
-extremely metal-poor star-forming dwarf galaxies are redder than their oxygen 
-abundances would typically indicate, although their colors align with their N/O 
-ratios.  Fig. \ref{fig:SFR} also shows that the sSFRs for these low-metallicity 
-dwarf galaxies are lower than expected for their oxygen abundances, though their 
-sSFRs conform with the observed relationship between the N/O ratio and the sSFR.  
-The 287 extremely metal-poor galaxies are isolated from our main sample of 
-star-forming dwarf galaxies only when comparing their gas-phase oxygen 
-abundances to other physical characteristics; their N/O ratios are not unusual.
+studied.  From Figures \ref{fig:ur_P3} and \ref{fig:gr}, it is apparent that 
+these extremely metal-poor star-forming dwarf galaxies are redder than their 
+oxygen abundances would typically indicate, although their colors align with 
+their N/O ratios.  Fig. \ref{fig:SFR} also shows that the sSFRs for these 
+low-metallicity dwarf galaxies are lower than expected for their oxygen 
+abundances, though their sSFRs conform with the observed relationship between 
+the N/O ratio and the sSFR.  The 287 extremely metal-poor galaxies are isolated 
+from our main sample of star-forming dwarf galaxies only when comparing their 
+gas-phase oxygen abundances to other physical characteristics; their N/O ratios 
+are not unusual.
 
@@
 nitrogen abundances by an average of 10\%, and 17\% lower N/O ratios than 
-star-forming dwarf galaxies in denser regions.  The large-scale ($\sim$10 
-$h^{-1}$Mpc) environment influences the chemical evolution of star-forming dwarf 
-galaxies.
+star-forming dwarf galaxies in denser regions.  The large-scale ($\sim$10 \hMpc) 
+environment influences the chemical evolution of star-forming dwarf galaxies.
 
@@
 on the so-called ``nitrogen plateau,'' where the N/O ratio is predicted to be 
-independent of the gas-phase oxygen abundance for metallicities 
-$12 + \log (\text{O}/\text{H}) < 8.5$.  Instead of a constant value for the N/O 
-ratio, we instead find that the N/O ratio decreases with increasing metallicity.  
-However, we do find a plateau in our relationship between the stellar mass and 
-N/O ratio.  Most of our star-forming dwarf galaxies follow the typical 
-mass-metallicity relation \citep{Tremonti04}.  There is no relationship between 
-the metallicity and \ion{H}{1} mass of the galaxies, but the N/O ratio decreases 
-with increasing \ion{H}{1} mass for fixed stellar mass.  The star-forming dwarf 
-galaxies exhibit an increase in the metallicity (O/H) and N/O ratio with 
-increasing color (both $u-r$ and $g-r$).  We see very little correlation with 
-SFR for either metallicity (O/H) or N/O ratio of dwarf galaxies, but the 
-metallicity and N/O ratio decrease with increasing sSFR.  Beyond the large-scale 
-environmental influence on the chemical abundance distributions in the sample of 
-star-forming dwarf galaxies, we do not observe any significant differences 
-between the star-forming void and wall dwarf galaxies in any of these 
-relationships.
+independent of the gas-phase oxygen abundance for metallicities \OH $< 8.5$.  
+Instead of a constant value for the N/O ratio, we instead find that the N/O 
+ratio decreases with increasing metallicity.  However, we do find a plateau in 
+our relationship between the stellar mass and N/O ratio.  Most of our 
+star-forming dwarf galaxies follow the typical mass-metallicity relation 
+\citep{Tremonti04}.  There is no relationship between the metallicity and 
+\ion{H}{1} mass of the galaxies, but the N/O ratio decreases with increasing 
+\ion{H}{1} mass for fixed stellar mass.  The star-forming dwarf galaxies exhibit 
+an increase in the metallicity (O/H) and N/O ratio with increasing color (both 
+$u-r$ and $g-r$).  We see very little correlation with SFR for either 
+metallicity (O/H) or N/O ratio of dwarf galaxies, but the metallicity and N/O 
+ratio decrease with increasing sSFR.  Beyond the large-scale environmental 
+influence on the chemical abundance distributions in the sample of star-forming 
+dwarf galaxies, we do not observe any significant differences between the 
+star-forming void and wall dwarf galaxies in any of these relationships.
 

### 2017-06-17 KellyDouglass/Thesis/Acknowledgments.tex
Added acknowledgments and dedication

\chapter*{Technical Acknowledgments}

Funding for the SDSS and SDSS-II has been provided by the Alfred P. Sloan 
Foundation, the Participating Institutions, the National Science Foundation, the 
U.S. Department of Energy, the National Aeronautics and Space Administration, 
the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education 
Funding Council for England.  The SDSS Web Site is \emph{http://www.sdss.org/}.

The SDSS is managed by the Astrophysical Research Consortium for the 
Participating Institutions.  The Participating Institutions are the American 
Museum of Natural History, Astrophysical Institute Potsdam, University of Basil, 
University of Cambridge, Case Western Reserve University, University of Chicago, 
Drexel University, Fermilab, the Institute for Advanced Study, the Japan 
Participation Group, Johns Hopkins University, the Joint Institute for Nuclear 
Astrophysics, the Kavli Institute for Particle Astrophysics and Cosmology, the 
Korean Scientist Group, the Chinese Academy of Sciences (LAMOST), Los Alamos 
National Laboratory, the Max-Planck-Institute for Astronomy (MPIA), the 
Max-Planck-Institute for Astrophysics (MPA), New Mexico State University, Ohio 
State University, University of Pittsburgh, University of Portsmouth, Princeton 
University, the United States Naval Observatory, and the University of 
Washington.

\vspace{1in}

{\let\clearpage\relax \chapter*{Funding Acknowledgments}}

\noindent
K.A.D. and M.S.V. acknowledge support from NSF grant AST--1410525.

\noindent
R.C. acknowledges support from NSF grant AST-1515389.

### 2017-06-17 KellyDouglass/Thesis/Thesis_sections/Conclusion.tex
Added acknowledgments and dedication

@@
 the Direct $T_e$ method and spectroscopic line flux measurements as reprocessed 
-in the MPA-JHU catalog \citep[Douglass et al., 2017, in prep]{Douglass17a,
+in the MPA-JHU catalog \citep[Douglass et al., 2017, submitted]{Douglass17a,
 Douglass17b}.  Due to the minimum redshift limit for detecting the [\ion{O}{2}] 

### 2017-06-17 KellyDouglass/Thesis/Thesis_sections/GV.tex
Added acknowledgments and dedication

@@
-\chapter[Green valley galaxies]{Identifying green valley galaxies}\label{ch:GV}
+\chapter[Green Valley Galaxies]{Identifying Green Valley Galaxies}\label{ch:GV}
 
@@
 
-\section[Theory]{Calculating the color of a galaxy}
+\section[Color Calculations]{Calculating the color of a galaxy}
 
@@
 
-\section[Data]{SDSS and GALEX data}
+\section[SDSS Data]{SDSS and GALEX data}
 
@@
 \url{http://www.mpa-garching.mpg.de/SDSS/DR7}} and published in Douglass et al. 
-(2017, in prep).  The large-scale environment of the galaxies is based on the 
+(2017, submitted).  The large-scale environment of the galaxies is based on the 
 void catalog compiled by \cite{Pan12}.  This void catalog is constructed from 
@@
 
-\section[Results]{Classification of galaxies in the color-magnitude diagram}
+\section[Classifying the CMD]{Classification of galaxies in the color-magnitude diagram}
 
@@
 \begin{figure}
-    \includegraphics[width=0.65\textwidth]{Images/GV/NUVr_CMD_3pop_scatter}
+    \includegraphics[width=0.75\textwidth]{Images/GV/NUVr_CMD_3pop_scatter}
     \caption[NUV-$r$ color-magnitude diagram of SDSS galaxies]{The NUV$-r$ 
@@
 \begin{figure}
-    \includegraphics[width=0.65\textwidth]{Images/GV/NUVr_CMDclassifications}
+    \includegraphics[width=0.75\textwidth]{Images/GV/NUVr_CMDclassifications}
     \caption[Distribution of NUV-$r$ of SDSS galaxies]{A histogram of the 
@@
 \begin{figure}
-    \includegraphics[width=0.65\textwidth]{Images/GV/Mstar_hist}
+    \includegraphics[width=0.75\textwidth]{Images/GV/Mstar_hist}
     \caption[Stellar mass distribution by morphological type]{The distribution 
@@
 enrichment of the ISM and CGM.  A few of the galaxies for which Douglass et al. 
-(2017, in prep) are able to estimate metallicities reside in the green valley.  
+(2017, submitted) are able to estimate metallicities reside in the green valley.  
 When compared with the metallicities of galaxies in the blue sequence and red 
@@
 
-\section[Discussion]{Understanding green valley galaxies}\label{sec:discussion_GV}
+\section[GV galaxy properties]{Understanding green valley galaxies}\label{sec:discussion_GV}
 
@@
 on the $\Lambda$CDM cosmology.  These results also coincide with the 
-observations of \cite{Douglass17b} and Douglass \& Vogeley (2017, in prep).  
+observations of \cite{Douglass17b} and Douglass \& Vogeley (2017, submitted).  
 They find that, for dwarf galaxies ($M_r > -17$), those which exist in voids may 
@@
 
-\section[Conclusions]{Conclusions}
+\section{Conclusions}
 
@@
 the green valley.  In conjunction with the conclusions of \cite{Douglass17b} and 
-Douglass et al. (2017, in prep), this indicates that void dwarf galaxies are 
+Douglass et al. (2017, submitted), this indicates that void dwarf galaxies are 
 less evolved than dwarf galaxies in denser environments.  It would be beneficial 

### 2017-06-17 KellyDouglass/Thesis/Thesis_sections/Paper1.tex
Added acknowledgments and dedication

@@
-\chapter[Metallicity of dwarf galaxies]{Determining the large-scale environmental dependence of gas-phase metallicity in dwarf galaxies}\label{ch:Paper1}
+\chapter[Metallicity of Dwarf Galaxies]{Determining the Large-Scale Environmental Dependence of GasPphase Metallicity in Dwarf Galaxies}\label{ch:Paper1}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section[Theory]{Estimation of galaxy metallicity from optical spectroscopy}
+\section[Calculating metallicity]{Estimation of galaxy metallicity from optical spectroscopy}
 \label{sec:Theory_P1}
@@
 	\centering
-    \includegraphics[width=0.5\textwidth]{Images/Paper1/energy_level_diagram-figure0}
+    \includegraphics[width=0.75\textwidth]{Images/Paper1/energy_level_diagram-figure0}
 	\caption[{[\ion{O}{3}] and [\ion{S}{2}] energy-level diagram}]{Energy-level 
@@
 \begin{figure}
-    \includegraphics[width=0.5\textwidth]{Images/Paper1/1sig_I06_dwarf_SF_t3_OpOpp_Z12logOH}
+    \includegraphics[width=0.75\textwidth]{Images/Paper1/1sig_I06_dwarf_SF_t3_OpOpp_Z12logOH}
     \caption[O$^+$/O$^{++}$ versus metallicity]{Metallicity of our 135 dwarf 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section[Data]{SDSS data and galaxy selection}\label{sec:Data}
+\section[SDSS Data]{SDSS data and galaxy selection}\label{sec:Data}
 % What are the assumptions?
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section[Results]{Metallicity analysis and results}
+\section[Analysis \& Results]{Metallicity analysis and results}
 
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{Images/Paper1/Yin07_comparison_fit}
+    \includegraphics[width=0.75\textwidth]{Images/Paper1/Yin07_comparison_fit}
     \caption[Metallicity comparison to \cite{Yin07}]{Metallicity (\OH) 
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{Images/Paper1/1sig_dwarf_I06_SF_t3_T04comparison}
+    \includegraphics[width=0.75\textwidth]{Images/Paper1/1sig_dwarf_I06_SF_t3_T04comparison}
     \caption[Metallicity comparison to \cite{Tremonti04}]{Metallicity (\OH) 
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{Images/Paper1/MZ_1sig_I06_dwarf_SF_t3_python}
+    \includegraphics[width=0.75\textwidth]{Images/Paper1/MZ_1sig_I06_dwarf_SF_t3_python}
     \caption[Stellar mass versus metallicity for 135 dwarf galaxy sample]
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{Images/Paper1/urHist_1sig_I06_dwarf_SF_t3}
+    \includegraphics[width=0.75\textwidth]{Images/Paper1/urHist_1sig_I06_dwarf_SF_t3}
     \caption[Color distribution of 135 dwarf galaxy sample compared to SDSS]{The 

### 2017-06-17 KellyDouglass/Thesis/Thesis_sections/Paper2.tex
Added acknowledgments and dedication

@@
-\chapter[N/O ratio in dwarf galaxies]{Large-scale environmental dependence of the abundance ratio of nitrogen to oxygen in blue, star-forming galaxies fainter than $L_*$}\label{ch:Paper2}
+\chapter[N/O Ratio in Dwarf Galaxies]{Large-Scale Environmental Dependence of the Abundance Ratio of Nitrogen to Oxygen in Blue, Star-Forming Galaxies Fainter than $L_*$}\label{ch:Paper2}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section[Theory]{Estimation of gas-phase chemical abundances from optical spectroscopy}
+\section[Calculating N/H \& N/O]{Estimation of gas-phase chemical abundances from optical spectroscopy}
 \label{sec:Theory}
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{Images/Paper2/NIIOIII_energy_level_diagram-figure0}
+    \includegraphics[width=0.75\textwidth]{Images/Paper2/NIIOIII_energy_level_diagram-figure0}
     \caption[{[\ion{O}{3}] and [\ion{N}{2}] energy-level diagram}]{Energy-level 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section[Data]{SDSS data and galaxy selection}
+\section[SDSS Data]{SDSS data and galaxy selection}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section[Results]{Abundance analysis and results}
+\section[Analysis \& Results]{Abundance analysis and results}
 
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{Images/Paper2/1sig_I06_dwarf_0-20_SF_t3_logNpOp_logNO_fit}
+    \includegraphics[width=0.75\textwidth]{Images/Paper2/1sig_I06_dwarf_0-20_SF_t3_logNpOp_logNO_fit}
     \caption[N/O versus N$^+$/O$^+$]{Comparison of the N/O and N$^+$/O$^+$ 
@@
 
-	\begin{tabu} to 0.75\textwidth {ccccccccc}
+	\begin{tabular}{ccccccccc}
 	    Abs.
 Mag.
-Range & Environment & \# of Galaxies & Average & Median & Average Shift\footnote[1]{Wall -- Void (positive shifts indicate that the wall values are greater than the void values; negative shifts indicate that the void values are greater than the wall values)} & Median Shift\footnote[1] & K-S Test Statistic & $p$-value \\
+Range & Environment & \# of Galaxies & Average & Median & Average Shift\footnote{Wall -- Void (positive shifts indicate that the wall values are greater than the void values; negative shifts indicate that the void values are greater than the wall values)\label{fnote_P2}} & Median Shift\textsuperscript{\ref{fnote_P2}} & K-S Test Statistic & $p$-value \\
 	    \hline
@@
          \hline
-	\end{tabu}
+	\end{tabular}
 
@@
 \begin{figure}
-    \includegraphics[width=0.5\textwidth]{Images/Paper2/1sig_I06_dwarf_0-20_SF_t3_Z12logOH_logNO}
+    \includegraphics[width=0.75\textwidth]{Images/Paper2/1sig_I06_dwarf_0-20_SF_t3_Z12logOH_logNO}
     \caption[N/O versus metallicity of 135 dwarf galaxy sample]{N/O as a 
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{Images/Paper2/1sig_I06_dwarf_0-20_SF_t3_Z12logOH_N12logNH}
+    \includegraphics[width=0.75\textwidth]{Images/Paper2/1sig_I06_dwarf_0-20_SF_t3_Z12logOH_N12logNH}
     \caption[N/H versus metallicity for 135 dwarf galaxy sample]{N/H as a 
@@
 \begin{figure}
-    \includegraphics[width=0.5\textwidth]{Images/Paper2/MNO_1sig_I06_dwarf_0-20_SF_t3}
+    \includegraphics[width=0.75\textwidth]{Images/Paper2/MNO_1sig_I06_dwarf_0-20_SF_t3}
     \caption[Stellar mass versus N/O for 135 dwarf galaxy sample]{Mass--N/O 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section[Discussion]{Large-scale environmental influence}\label{sec:environment}
+\section[Environmental influence]{Large-scale environmental influence}\label{sec:environment}
 

### 2017-06-17 KellyDouglass/Thesis/Thesis_sections/Paper3.tex
Added acknowledgments and dedication

@@
-\chapter[O$^+$ approximation]{Large-scale environmental dependence of chemical abundances in dwarf galaxies and implications for connecting star formation and halo mass}\label{ch:Paper3}
+\chapter[O$^+$ Approximation]{Large-Scale Environmental Dependence of Chemical Abundances in Dwarf Galaxies and Implications for Connecting Star Formation and Halo Mass}\label{ch:Paper3}
 
@@
 Douglass, Michael S. Vogeley, and Renyue Cen; it will be referenced as Douglass 
-et. al (2017).
+et. al (2017, submitted).
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section[Theory]{Estimation of gas-phase chemical abundances from optical spectroscopy}
+\section[Abundance calculations]{Estimation of gas-phase chemical abundances from optical spectroscopy}
 
@@
     \centering
-    \includegraphics[width=0.65\textwidth]{Images/Paper3/Zlow_v_Zreal_1sig_I06_BPTclass_fits}
+    \includegraphics[width=0.75\textwidth]{Images/Paper3/Zlow_v_Zreal_1sig_I06_BPTclass_fits}
     \caption[O$^++$/H versus O/H]{$12 + \log{\text{O}^{++}/\text{H}}$ versus \OH 
@@
     \begin{tabular}{ccccccc}
-        Environment & Average & Median & Average Shift\footnote{Wall -- Void (Positive shifts indicate that the wall values are greater than the void values; negative shifts indicate that the void values are greater than the wall values.)} & Median Shift & $p$-value & K-S Test Statistic\\
+        Environment & Average & Median & Average Shift\footnote{Wall -- Void (Positive shifts indicate that the wall values are greater than the void values; negative shifts indicate that the void values are greater than the wall values.)\label{fnote_P3}} & Median Shift\textsuperscript{\ref{fnote_P3}} & $p$-value & K-S Test Statistic\\
         \hline
@@
     \centering
-    \includegraphics[width=0.65\textwidth]{Images/Paper3/1sig_dwarf_I06relations_SF_t3_T04comparison_dust}
+    \includegraphics[width=0.75\textwidth]{Images/Paper3/1sig_dwarf_I06relations_SF_t3_T04comparison_dust}
     \caption[Comparison of O$^+$ approximation metallicities to 
@@
     \centering
-    \includegraphics[width=0.65\textwidth]{Images/Paper3/1sig_I06relations_dwarf_SF_t3_dust_NSA_Z12logOH_logNO_scatterMbin}
+    \includegraphics[width=0.75\textwidth]{Images/Paper3/1sig_I06relations_dwarf_SF_t3_dust_NSA_Z12logOH_logNO_scatterMbin}
     \caption[O/H versus N/O for star-forming dwarf galaxies]{Oxygen abundance 
@@
 \begin{figure}
-    \includegraphics[width=0.65\textwidth]{Images/Paper3/1sig_I06relations_dwarf_SF_t3_dust_NSA_Z12logOH_N12logNH_scatterMbin}
+    \includegraphics[width=0.75\textwidth]{Images/Paper3/1sig_I06relations_dwarf_SF_t3_dust_NSA_Z12logOH_N12logNH_scatterMbin}
     \caption[O/H versus N/H for star-forming dwarf galaxies]{Oxygen abundance 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section[Discussion]{Large-scale environmental influence}
+\section[Environmental influence]{Large-scale environmental influence}
 

### 2017-06-17 KellyDouglass/Thesis/Thesis_sections/smallScaleEnvironment.tex
Added acknowledgments and dedication

@@
-\chapter[Small-scale environment]{The influence of the small-scale environment on dwarf galaxy evolution}\label{ch:smallScaleEnvironment}
+\chapter[Small-Scale Environment]{The Influence of the Small-Scale Environment on Dwarf Galaxy Evolution}\label{ch:smallScaleEnvironment}
 
@@
 
-\section[Introduction]{Introduction}
+\section{Introduction}
 
@@
 
-\section[Data]{SDSS Data and galaxy selection}
+\section[SDSS Data]{SDSS Data and galaxy selection}
 
@@
 The gas-phase chemical abundances used are from Douglass, Vogeley, and Cen 
-(2017, in prep.), which are calculated using the Direct $T_e$ method.  The 
+(2017, submitted), which are calculated using the Direct $T_e$ method.  The 
 galaxies' large-scale environments are based on the void catalog compiled by 
@@
 contains those star-forming dwarf galaxies from the first set that have 
-gas-phase chemical abundances in Douglass et al. (2017, in prep.), totaling 2506 
+gas-phase chemical abundances in Douglass et al. (2017, submitted), totaling 2506 
 dwarf galaxies.  While this subset of galaxies contains only star-forming 
@@
 
-\section[Results]{Distance analysis and results}
+\section[Analysis \& Results]{Distance analysis and results}
 
@@
 wall dwarf galaxies, as has been observed by \cite{Douglass17b} and Douglass et 
-al. (2017, in prep).
+al. (2017, submitted).
 
@@
 of the nearest group.  Unlike the shifts seen with the other parameters and what 
-is observed in \cite{Douglass17b} and Douglass et al. (2017, in prep), we see no 
+is observed in \cite{Douglass17b} and Douglass et al. (2017, submitted), we see no 
 significant difference in the nitrogen abundance resulting from the large-scale 
@@
 lower N/O ratios in star-forming void dwarf galaxies is readily apparent, as 
-found by \cite{Douglass17b} and Douglass et al. (2017, in prep).
+found by \cite{Douglass17b} and Douglass et al. (2017, submitted).
 
@@
 \begin{figure}
-    \includegraphics[width=0.5\textwidth]{Images/smallScaleEnvironment/ALLdwarf_ur_300}
+    \includegraphics[width=0.75\textwidth]{Images/smallScaleEnvironment/ALLdwarf_ur_300}
     \caption[Color versus distance of full SDSS dwarf population]{Color versus 
@@
 \begin{figure}
-    \includegraphics[width=0.5\textwidth]{Images/smallScaleEnvironment/dwarf_ur_xyz}
+    \includegraphics[width=0.75\textwidth]{Images/smallScaleEnvironment/dwarf_ur_xyz}
     \caption[Color versus distance calculated with redshift]{Color versus 
@@
 
-\section[Discussion]{Discussion}
+\section[Environmental influence]{Small-scale environmental influence}
 
@@
 
-\section[Conclusions]{Conclusions}
+\section{Conclusions}
 
 Using the star-forming dwarf galaxies in the SDSS DR7 sample with gas-phase 
-chemical abundances from Douglass et al. (2017, in prep), we investigate the 
+chemical abundances from Douglass et al. (2017, submitted), we investigate the 
 influence of the small-scale environment on the evolution of dwarf galaxies.  

### 2017-06-17 KellyDouglass/Thesis/preamble.tex
Updates to Ch. 5-7
Added acknowledgments and dedication

@@
 \begin{center}
-Dedications
+To my parents\\
+You told me to reach for the stars\\
+Will galaxies do?
 \end{center}
@@
 % Advisor
-
-% Thesis committee and collaborators (Renyue, Daniele, Jinfu, Brean, Salvatore)
-I would like to thank our collaborator Renyue Cen for his help in the 
-interpretation of these results.  I would also like to acknowledge Crystal 
-Moorman for her help and support throughout this work.  Finally, I would like to 
-thank the referees (including Burcu Beygu) for their detailed comments and 
-critique of my work.
+I would like to begin by thanking my advisor, Prof. Michael Vogeley, for being a 
+fantastic advisor and role model.  Thank you for helping me expand my knowledge 
+and research skills over the last six years.  And thank you for giving me the 
+opportunity to help advise students.  I would like to thank our collaborator 
+Renyue Cen for his help in the theoretical interpretation of these results, and 
+for confirming that our explanations were not completely ridiculous.  To my 
+committee members Profs. Gordon Richards, Steve McMillan, Masao Sako, and 
+Michelle Dolinksi --- thank you for your time and guidance throughout the years.  
+And a big shout-out to my advisees: Daniele Schneider, Jinfu Dai, Brean 
+Prefontaine, and Salvatore Zerbo.  Thank you for all your hard work!
 
 % Grad students & PLBD
+Thank you to all the graduate students in the Drexel Physics department for the 
+wonderful, supportive, collaborative community.  You helped make grad school so 
+much more bearable (and almost enjoyable, if I dare say).  To my physics boys 
+Justin, Matt, and Matt: we made it!  I would be remiss in not acknowledging my 
+office mates over the last few years, particularly Josh, Jackie, Justin, 
+Crystal, Austen, and Vish, for help with code, ideas, and keeping the moral up.  
+And, of course, thank you to all the members of PLBD for providing me an outlet 
+from physics.  You guys are the best!
 
 % Family
+Of course, none of this would be possible without the infinite love and support 
+from my family.  Thank you Dad, Mom, Kelly, and Ren\'{e}e for always pushing me 
+to work my hardest and do my best.  Thank you for challenging me in so many 
+ways.  I love you guys, and I it means so much that you are here today!
 
 % Steve
-
-%Support for this work was provided by NSF grant AST--1410525.
-%
-%Funding for the SDSS and SDSS-II has been provided by the Alfred P. Sloan 
-%Foundation, the Participating Institutions, the National Science Foundation, the 
-%U.S. Department of Energy, the National Aeronautics and Space Administration, 
-%the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education 
-%Funding Council for England.  The SDSS Web Site is \emph{http://www.sdss.org/}.
-%
-%The SDSS is managed by the Astrophysical Research Consortium for the 
-%Participating Institutions.  The Participating Institutions are the American 
-%Museum of Natural History, Astrophysical Institute Potsdam, University of Basil, 
-%University of Cambridge, Case Western Reserve University, University of Chicago, 
-%Drexel University, Fermilab, the Institute for Advanced Study, the Japan 
-%Participation Group, Johns Hopkins University, the Joint Institute for Nuclear 
-%Astrophysics, the Kavli Institute for Particle Astrophysics and Cosmology, the 
-%Korean Scientist Group, the Chinese Academy of Sciences (LAMOST), Los Alamos 
-%National Laboratory, the Max-Planck-Institute for Astronomy (MPIA), the 
-%Max-Planck-Institute for Astrophysics (MPA), New Mexico State University, Ohio 
-%State University, University of Pittsburgh, University of Portsmouth, Princeton 
-%University, the United States Naval Observatory, and the University of 
-%Washington.
-
+To Steve, my dance partner --- thank you for understanding the time and energy 
+a thesis takes to write.  And to Steve, my not dance partner --- thank you for 
+helping and supporting me in any and all ways possible throughout this process; 
+you made this so much easier.
 \end{acknowledgments}
@@
 formation as predicted by the $\Lambda$CDM cosmology.  We also conjecture that 
-there is a dependence of the large-scale environment on cosmic downsizing.  We 
-present evidence that void dwarf galaxies may have a higher ratio of dark matter 
-halo mass to stellar mass when compared to dwarf galaxies in denser 
-environments.
+cosmic downsizing corresponds to a shift towards star formation in both lower 
+mass objects and void regions closer to the present epoch.  We present evidence 
+that void dwarf galaxies may have a higher ratio of dark matter halo mass to 
+stellar mass when compared to dwarf galaxies in denser environments.
 

### 2017-06-21 KellyDouglass/Thesis/Tables/Paper1/XMPtable.tex
Updated Paper 3
Changed table names

@@
 
-\begin{tabu} to 0.75\linewidth {ccccccc}
-Index\footnote[1]{KIAS-VAGC galaxy index number} & R.A. & Decl. & Redshift & \multicolumn{2}{c}{$12 + \log \left( \frac{\text{O}}{\text{H}} \right)$} & Void/Wall \\
+\begin{tabular}{ccccccc}
+Index\footnote{KIAS-VAGC galaxy index number} & R.A. & Decl. & Redshift & \multicolumn{2}{c}{$12 + \log \left( \frac{\text{O}}{\text{H}} \right)$} & Void/Wall \\
 \hline \\
@@
 1322765 & \RA{14}{15}{05}{.58} & +\dec{36}{22}{57}{.77} & 0.0273 & 7.57 & $\pm$0.40 & Wall\\
-\end{tabu}
+\end{tabular}
 
-\caption[Extreme low-metallicity dwarf galaxies]{Details of the 21 extreme low gas-phase metallicity ($12 + \log(\text{O}/\text{H}) < 7.6$) galaxies found.
+\caption[Extremely low-metallicity dwarf galaxies in 135 galaxy sample]{Details of the 21 extreme low gas-phase metallicity ($12 + \log(\text{O}/\text{H}) < 7.6$) galaxies found.
 Four of these galaxies are located in voids (about 10\% of the void dwarf population measured) and seventeen are in more dense regions (about 19\% of the wall dwarf population measured); thus, there does not seem to be a special population of extreme low-metallicity galaxies in voids.

### 2017-06-21 KellyDouglass/Thesis/Tables/Paper1/results_table_short.tex
Updated Paper 3
Changed table names

@@
 
-\begin{tabu} to 0.75\linewidth {cccccccc}
-Index\footnote[1]{KIAS-VAGC galaxy index number} & R.A. & Decl. & Redshift & $M_r$ & \multicolumn{2}{c}{$12 + \log \left( \frac{\text{O}}{\text{H}} \right)$} & Void/Wall \\
+\begin{tabular}{cccccccc}
+Index\footnote{KIAS-VAGC galaxy index number} & R.A. & Decl. & Redshift & $M_r$ & \multicolumn{2}{c}{$12 + \log \left( \frac{\text{O}}{\text{H}} \right)$} & Void/Wall \\
 \hline \\
@@
 184308 & \RA{09}{39}{09}{.38} & +\dec{00}{59}{04}{.15} & 0.0244 & -16.73 & 7.36 & $\pm$0.43 & Wall\\
-\end{tabu}
+\end{tabular}
 
-\caption[Dwarf galaxy properties]{Five of the 135 dwarf galaxies analyzed from SDSS DR7.
+\caption[Properties of subseet of 135 dwarf galaxies]{Five of the 135 dwarf galaxies analyzed from SDSS DR7.
 The flux values for all required emission lines can be found in the MPA-JHU value-added catalog.

### 2017-06-21 KellyDouglass/Thesis/Tables/Paper2/results_table_short.tex
Updated Paper 3
Changed table names

@@
 
-\begin{tabu} to \textwidth {cccccccccccc}
-Index\footnote[1]{KIAS-VAGC galaxy index number} & R.A.
+\begin{tabular}{cccccccccccc}
+Index\footnote{KIAS-VAGC galaxy index number} & R.A.
 & Decl.
@@
 184308 & \RA{09}{39}{09}{.38} & +\dec{00}{59}{04}{.15} & 0.0244 & -16.73 & 7.36 & $\pm$0.43 & 6.71 & $\pm$0.31 & -0.65 & $\pm$0.53 & Wall\\
-\end{tabu}
+\end{tabular}
 
-\caption[Analyzed dwarf galaxies]{Five of the 135 dwarf galaxies analyzed from SDSS DR7.
+\caption[Chemical abundances of subset of 135 dwarf galaxies]{Five of the 135 dwarf galaxies analyzed from SDSS DR7.
 The flux values for all required emission lines can be found in the MPA-JHU value-added catalog.

### 2017-06-21 KellyDouglass/Thesis/Thesis_sections/Paper2.tex
Changed table names

@@
 
-    \caption[Abundance statistics]{Statistics of the gas-phase oxygen, nitrogen, 
-    and nitrogen relative to oxygen abundances in void and wall galaxies in each 
-    of the absolute magnitude ranges listed.  Most of these results are not 
-    statistically significant, as shown in Figs. 
+    \caption[Abundance statistics of 135 dwarf galaxy sample]{Statistics of the 
+    gas-phase oxygen, nitrogen, and nitrogen relative to oxygen abundances in 
+    void and wall galaxies in each of the absolute magnitude ranges listed.  
+    Most of these results are not statistically significant, as shown in Figs. 
     \ref{fig:met1sig}--\ref{fig:NO_bright}.  However, the shifts in chemical 

### 2017-06-21 KellyDouglass/Thesis/Thesis_sections/Paper3.tex
Changed table names

@@
 
-    \caption[Abundance statistics]{Statistics on the gas-phase oxygen, nitrogen, 
-    and nitrogen relative to oxygen abundances in dwarf void and wall galaxies.  
-    Combined with the histograms in Figures 
+    \caption[Abundance statistics of full dwarf galaxy sample]{Statistics on the 
+    gas-phase oxygen, nitrogen, and nitrogen relative to oxygen abundances in 
+    dwarf void and wall galaxies.  Combined with the histograms in Figures 
     \ref{fig:met1sig_P3}--\ref{fig:NOratio_P3}, these results indicate an 

### 2017-07-10 KellyDouglass/Thesis/Thesis_sections/smallScaleEnvironment.tex
Added figures for small-scale and GV to presentation; minor changes to Thesis
Updated some figures, fit values in small-scale environ. chapter

@@
 \begin{figure}
-    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_ur_300}
-    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_ur_300_group}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_absDist_ur}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_groupAbsDist_ur}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_virDist_ur}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_groupRDist_ur}
+%    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_ur_300}
+%    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_ur_300_group}
     \caption[$u-r$ versus distance to nearest neighbor and group]{Color ($u-r$) 
@@
     have some affect on the dwarf galaxy's color at separations less than 0.05 
-    \hMpc, or 0.1$r_{vir}$.  The closest group appears to have some affect on 
-    the target dwarf galaxy's color at distances less than 0.1 \hMpc to the 
-    group's center; there appears to be no relationship between a dwarf galaxy's 
-    color and its distance to the nearest group as represented by the fraction 
-    of the group's radius.}
+    \hMpc, or 0.1$r_{vir}$.  %The closest group appears to have some affect on 
+%    the target dwarf galaxy's color at distances less than 0.1 \hMpc to the 
+%    group's center; there appears to be no relationship between a dwarf galaxy's 
+%    color and its distance to the nearest group as represented by the fraction 
+%    of the group's radius.}
+    There appears to be no relationship between a dwarf galaxy's color and its 
+    distance to the nearest group.}
     \label{fig:ur}
@@
 However, within a distance of 0.05 \hMpc or 0.1$r_{vir}$, dwarf galaxies tend 
-to be bluer than at further distances from their nearest neighbor.  At distances 
-less than 0.1 \hMpc from the center of the nearest groups, the dwarf galaxies 
-are redder than average.  However, there does not appear to be any relationship 
-between a dwarf galaxy's color and its distance to the center of the nearest 
-group in units of the group's rms radius.  It has been well-established that 
+to be bluer than at further distances from their nearest neighbor.  %At distances 
+%less than 0.1 \hMpc from the center of the nearest groups, the dwarf galaxies 
+%are redder than average.  However, there does not appear to be any relationship 
+%between a dwarf galaxy's color and its distance to the center of the nearest 
+%group in units of the group's rms radius.  
+There does not appear to be any relationship between a dwarf galaxy's color and 
+its distance to the center of the nearest group.  
+It has been well-established that 
 void galaxies tend to be bluer than galaxies in denser environments 
@@
 \begin{figure}
-    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_sSFR_300}
-    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_sSFR_300_group}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_absDist_sSFR}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_groupAbsDist_sSFR}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_virDist_sSFR}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_groupRDist_sSFR}
+%    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_sSFR_300}
+%    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_sSFR_300_group}
     \caption[sSFR versus distance to nearest neighbor and group]{sSFR versus 
@@
 \begin{figure}
-    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_OH_300}
-    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_OH_300_group}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_absDist_OH}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_groupAbsDist_OH}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_virDist_OH}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_groupRDist_OH}
+%    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_OH_300}
+%    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_OH_300_group}
     \caption[Metallicity versus distance to nearest neighbor and group]
@@
 \begin{figure}
-    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_NH_300}
-    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_NH_300_group}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_absDist_NH}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_groupAbsDist_NH}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_virDist_NH}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_groupRDist_NH}
+%    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_NH_300}
+%    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_NH_300_group}
     \caption[N/H versus distance to nearest neighbor and group]{Gas-phase 
@@
 \begin{figure}
-    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_NO_300}
-    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_NO_300_group}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_absDist_NO}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_groupAbsDist_NO}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_virDist_NO}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_groupRDist_NO}
+%    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_NO_300}
+%    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_NO_300_group}
     \caption[N/O versus distance to nearest neighbor and group]{N/O ratio versus 
@@
     ratios than the wall dwarf galaxies, but there is no distinct relationship 
-    between the distance to the nearest neighbor and the N/O ratio.  The N/O 
-    ratio might be higher in dwarf galaxies within 0.05 \hMpc of the center of 
-    the closest group.}
+    between the distance to the nearest neighbor and the N/O ratio.  %The N/O 
+%    ratio might be higher in dwarf galaxies within 0.05 \hMpc of the center of 
+%    the closest group.
+    }
     \label{fig:NO}
@@
 linear fits to the data --- the slopes are on the order of 10$^{-2}$ and 
-smaller.  When looking at the relationship between the N/O ratio and the 
-distance to the nearest group, though, the N/O ratio might be higher than 
-average in galaxies within 0.1 \hMpc of the group's center.  The shift towards 
+smaller.  %When looking at the relationship between the N/O ratio and the 
+%distance to the nearest group, though, the N/O ratio might be higher than 
+%average in galaxies within 0.1 \hMpc of the group's center.  
+There is also no apparent relationship between the N/O ratio and the target 
+galaxy's distance to the center of the nearest group.  
+The shift towards 
 lower N/O ratios in star-forming void dwarf galaxies is readily apparent, as 
@@
     \begin{tabular}{lcccc}
-        Property & Slope (wall) & Slope (void) & Intercept (wall) & Intercept (void)\\
+        Property & Slope (void) & Slope (wall) & Intercept (void) & Intercept (wall)\\
         \hline
@@
         \hline
-        $u-r$ & $1.25\pm 1.17\times 10^{-3}$ & $-9.14\pm 0.56\times 10^{-3}$ & $1.15\pm 0.00076$ & $1.09\pm0.00049$\\
-        sSFR & $2.07\pm 0.18\times 10^{-2}$ & $-0.16\pm 0.08\times 10^{-3}$ & $-9.45\pm 0.001$ & $-9.34\pm 0.0007$\\
+        $u-r$ & $-0.01\pm 0.027$ & $0.02\pm 0.063$ & $1.05\pm 0.024$ & $1.06\pm 0.031$\\
+        sSFR & $0.01\pm 0.042$ & $0.0\pm 0.10$ & $-9.28\pm 0.037$ & $-9.33\pm 0.049$\\
         \OH & $5.35\pm 0.17\times 10^{-2}$ & $0.33\pm 0.08\times 10^{-2}$ & $7.75\pm 0.0011$ & $7.86\pm 0.0007$\\
@@
         \hline
-        $u-r$ & $-3.81\pm 0.04\times 10^{-3}$ & $-0.46\pm 0.01\times 10^{-3}$ & $1.16\pm 0.00014$ & $1.09\pm0.00008$\\
-        sSFR & $5.96\pm 0.06\times 10^{-3}$ & $-0.41\pm 0.02\times 10^{-3}$ & $-9.45\pm 0.0002$ & $-9.33\pm 0.0001$\\
+        $u-r$ & $-0.001\pm 0.0043$ & $-0.004\pm 0.0099$ & $1.05\pm 0.026$ & $1.08\pm 0.031$\\
+        sSFR & $0.000\pm 0.0066$ & $0.00\pm 0.016$ & $-9.28\pm 0.040$ & $-9.34\pm 0.049$\\
         \OH & $1.41\pm 0.005\times 10^{-2}$ & $0.12\pm 0.08\times 10^{-2}$ & $7.74\pm 0.0002$ & $7.86\pm 0.0001$\\
@@
         \hline
-        $u-r$ & $-2.53\pm 0.01\times 10^{-3}$ & $1.34\pm 0.01\times 10^{-3}$ & $1.16\pm 0.00008$ & $1.08\pm0.0001$\\
-        sSFR & $7.77\pm 0.02\times 10^{-3}$ & $-1.68\pm 0.02\times 10^{-3}$ & $-9.48\pm 0.001$ & $-9.33\pm 0.0001$\\
+        $u-r$ & $0.002\pm 0.0042$ & $-0.002\pm 0.0041$ & $1.03\pm 0.029$ & $1.08\pm 0.033$\\
+        sSFR & $-0.003\pm 0.0064$ & $0.006\pm 0.0065$ & $-9.26\pm 0.045$ & $-9.36\pm 0.053$\\
         \OH & $3.65\pm 0.16\times 10^{-4}$ & $2.06\pm 0.19\times 10^{-4}$ & $7.77\pm 0.0001$ & $7.86\pm 0.0001$\\
@@
         \hline
-        $u-r$ & $-1.00\pm 0.002\times 10^{-3}$ & $0.90\pm 0.002\times 10^{-3}$ & $1.16\pm 0.00003$ & $1.07\pm0.00003$\\
-        sSFR & $2.70\pm 0.002\times 10^{-3}$ & $-1.71\pm 0.002\times 10^{-3}$ & $-9.48\pm 0.00005$ & $-9.31\pm 0.00005$\\
+        $u-r$ & $0.001\pm 0.0015$ & $-0.001\pm 0.0015$ & $1.03\pm 0.031$ & $1.08\pm 0.036$\\
+        sSFR & $-0.002\pm 0.0023$ & $0.002\pm 0.0024$ & $-9.24\pm 0.048$ & $-9.37\pm 0.057$\\
         \OH & $8.81\pm 0.02\times 10^{-4}$ & $-8.74\pm 0.19\times 10^{-4}$ & $7.76\pm 0.00005$ & $7.88\pm 0.00005$\\
@@
 \begin{figure}
-    \includegraphics[width=0.75\textwidth]{Images/smallScaleEnvironment/ALLdwarf_ur_300}
+    \includegraphics[width=0.5\textwidth]{Images/smallScaleEnvironment/ALLdwarf_ur_300}
     \caption[Color versus distance of full SDSS dwarf population]{Color versus 
@@
 \begin{figure}
-    \includegraphics[width=0.75\textwidth]{Images/smallScaleEnvironment/dwarf_ur_xyz}
+    \includegraphics[width=0.5\textwidth]{Images/smallScaleEnvironment/dwarf_ur_xyz}
     \caption[Color versus distance calculated with redshift]{Color versus 

### 2017-07-18 KellyDouglass/Thesis/Thesis_sections/smallScaleEnvironment.tex
Updated figures in small scale environment chapter

@@
     are shown in orange and blue, respectively.  There is very little difference 
-    in N/H between the two large-scale environments.  Only the neighbor galaxies 
-    at separations less than 0.1$r_{vir}$ appear to have some affect on the 
-    dwarf galaxies' nitrogen abundance.  There does not appear to be any 
-    relationship between the dwarf galaxies' nitrogen abundance and the distance 
-    to their nearest group.}
+    in N/H between the two large-scale environments.  There does not appear to 
+    be any relationship between the dwarf galaxies' nitrogen abundance and the 
+    distance to their nearest neighbor or group.}
     \label{fig:NH}
@@
         \hline
-        $u-r$ & $-0.01\pm 0.027$ & $0.02\pm 0.063$ & $1.05\pm 0.024$ & $1.06\pm 0.031$\\
+        $u-r$ & $-0.02\pm 0.027$ & $0.02\pm 0.063$ & $1.05\pm 0.024$  & $1.06\pm 0.031$\\
         sSFR  & $0.01\pm 0.042$  & $0.0\pm 0.10$   & $-9.28\pm 0.037$ & $-9.33\pm 0.049$\\
-        \OH & $5.35\pm 0.17\times 10^{-2}$ & $0.33\pm 0.08\times 10^{-2}$ & $7.75\pm 0.0011$ & $7.86\pm 0.0007$\\
-        \NH & $1.64\pm 0.11\times 10^{-2}$ & $0.62\pm 0.06\times 10^{-2}$ & $6.53\pm 0.0007$ & $6.52\pm 0.0006$\\
-        \NO & $-3.70\pm 0.13\times 10^{-2}$ & $0.29\pm 0.07\times 10^{-2}$ & $-1.23\pm 0.0009$ & $-1.35\pm 0.0006$\\
+        \OH   & $0.01\pm 0.027$  & $0.06\pm 0.062$ & $7.988\pm 0.024$ & $7.94\pm 0.030$\\
+        \NH   & $0.02\pm 0.028$  & $0.10\pm 0.059$ & $6.54\pm 0.026$  & $6.55\pm 0.029$\\
+        \NO   & $0.00\pm 0.028$  & $0.04\pm 0.062$ & $-1.45\pm 0.026$ & $-1.39\pm 0.030$\\
         \hline
@@
         sSFR  & $0.000\pm 0.0066$  & $0.00\pm 0.016$    & $-9.28\pm 0.040$ & $-9.34\pm 0.049$\\
-        \OH & $1.41\pm 0.005\times 10^{-2}$ & $0.12\pm 0.08\times 10^{-2}$ & $7.74\pm 0.0002$ & $7.86\pm 0.0001$\\
-        \NH & $1.82\pm 0.11\times 10^{-3}$ & $-1.14\pm 0.002\times 10^{-3}$ & $6.53\pm 0.0001$ & $6.52\pm 0.0001$\\
-        \NO & $-1.22\pm 0.004\times 10^{-2}$ & $-0.41\pm 0.02\times 10^{-3}$ & $-1.21\pm 0.0002$ & $-1.33\pm 0.0001$\\
+        \OH   & $0.001\pm 0.0042$  & $0.012\pm 0.0099$  & $7.992\pm 0.025$ & $7.94\pm 0.031$\\
+        \NH   & $0.000\pm 0.0045$  & $0.009\pm 0.0094$  & $6.55\pm 0.027$  & $6.56\pm 0.029$\\
+        \NO   & $-0.001\pm 0.0045$ & $-0.003\pm 0.0098$ & $-1.44\pm 0.027$ & $-1.37\pm 0.031$\\
         \hline
@@
         sSFR  & $-0.003\pm 0.0064$ & $0.006\pm 0.0065$  & $-9.26\pm 0.045$ & $-9.36\pm 0.053$\\
-        \OH & $3.65\pm 0.16\times 10^{-4}$ & $2.06\pm 0.19\times 10^{-4}$ & $7.77\pm 0.0001$ & $7.86\pm 0.0001$\\
-        \NH & $4.84\pm 0.01\times 10^{-3}$ & $6.30\pm 0.01\times 10^{-3}$ & $6.51\pm 0.00008$ & $6.49\pm 0.0001$\\
-        \NO & $4.47\pm 0.01\times 10^{-3}$ & $6.09\pm 0.01\times 10^{-3}$ & $-1.26\pm 0.0001$ & $-1.38\pm 0.0001$\\
+        \OH   & $0.001\pm 0.0041$  & $0.002\pm 0.0041$  & $7.989\pm 0.029$ & $7.95\pm 0.033$\\
+        \NH   & $0.007\pm 0.0043$  & $0.006\pm 0.0038$  & $6.51\pm 0.031$  & $6.55\pm 0.031$\\
+        \NO   & $0.006\pm 0.0044$  & $0.005\pm 0.0040$  & $-1.48\pm 0.031$ & $-1.40\pm 0.033$\\
         \hline
@@
         \hline
-        $u-r$ & $0.001\pm 0.0015$ & $-0.001\pm 0.0015$ & $1.03\pm 0.031$ & $1.08\pm 0.036$\\
-        sSFR & $-0.002\pm 0.0023$ & $0.002\pm 0.0024$ & $-9.24\pm 0.048$ & $-9.37\pm 0.057$\\
-        \OH & $8.81\pm 0.02\times 10^{-4}$ & $-8.74\pm 0.19\times 10^{-4}$ & $7.76\pm 0.00005$ & $7.88\pm 0.00005$\\
-        \NH & $2.31\pm 0.001\times 10^{-3}$ & $2.47\pm 0.001\times 10^{-3}$ & $6.49\pm 0.00003$ & $6.47\pm 0.00004$\\
-        \NO & $1.43\pm 0.002\times 10^{-3}$ & $3.35\pm 0.002\times 10^{-3}$ & $-1.26\pm 0.00005$ & $-1.40\pm 0.00005$
+        $u-r$ & $0.001\pm 0.0018$  & $-0.001\pm 0.0017$ & $1.02\pm 0.033$  & $1.08\pm 0.036$\\
+        sSFR  & $-0.002\pm 0.0027$ & $0.002\pm 0.0028$  & $-9.24\pm 0.051$ & $-9.37\pm 0.058$\\
+        \OH   & $0.000\pm 0.0017$  & $0.001\pm 0.0017$  & $7.99\pm 0.033$  & $7.95\pm 0.036$\\
+        \NH   & $0.003\pm 0.0018$  & $0.004\pm 0.0016$  & $6.50\pm 0.034$  & $6.53\pm 0.034$\\
+        \NO   & $0.003\pm 0.0018$  & $0.002\pm 0.0017$  & $-1.50\pm 0.034$ & $-1.42\pm 0.036$
     \end{tabular}
@@
 \begin{figure}
-    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_ur_150}
-    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_ur_600}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_absDist150_ur}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_absDist600_ur}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_virDist150_ur}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_virDist600_ur}
+%    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_ur_150}
+%    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_ur_600}
     \caption[Sensitivity to peculiar velocity maximum]{Color versus distance to 
@@
 \begin{figure}
-    \includegraphics[width=0.5\textwidth]{Images/smallScaleEnvironment/ALLdwarf_ur_300}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_absDist_ur}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_groupAbsDist_ur}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_virDist_ur}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_groupRDist_ur}
+%    \includegraphics[width=0.5\textwidth]{Images/smallScaleEnvironment/ALLdwarf_ur_300}
     \caption[Color versus distance of full SDSS dwarf population]{Color versus 
-    distance to the nearest galaxy (in units of \hMpc on top and virial radii on 
-    the bottom) for the entire dwarf galaxy population in SDSS DR7.  When 
-    compared to the left-hand panel of Fig. \ref{fig:ur}, we see that there is 
-    no difference in the results of the analysis by studying only star-forming 
-    galaxies with sufficient detection of the various emission lines necessary 
-    to estimate the gas-phase chemical abundances.}
+    distance to the nearest galaxy (in units of \hMpc on top left and virial 
+    radius on the bottom left) and to the center of the nearest group (in units 
+    of \hMpc on the top right and group radius on the bottom right) for the 
+    entire dwarf galaxy population in SDSS DR7.  When compared to Fig. 
+    \ref{fig:ur}, we see that there are some differences in the results of the 
+    analysis by studying only star-forming galaxies with sufficient detection of 
+    the various emission lines necessary to estimate the gas-phase chemical 
+    abundances.  The addition of redder dwarf galaxies to the sample produces an 
+    overall inverse relationship between a wall dwarf galaxy's color and the 
+    distance to the nearest neighbor in \hMpc.}
     \label{fig:ur_allDwarf}
@@
 color, to understand how our results depend on our sample.  When we compare Fig. 
-\ref{fig:ur_allDwarf} with the left-hand panel of Fig. \ref{fig:ur}, we see that 
-there is no difference in the correlation between color and distance to the 
-nearest neighbor.  It is clear that our selection bias to star-forming dwarf 
-galaxies does not influence any trends we observe in our analysis.
+\ref{fig:ur_allDwarf} with Fig. \ref{fig:ur}, we see that there are some 
+differences in the correlation between color and distance to the nearest 
+neighbor.  Let us first look at the linear fits to the data.  The upper left 
+panel of Fig. \ref{fig:ur_allDwarf} shows that wall dwarf galaxies become redder 
+with decreasing distance to their nearest neighbors, while the upper left panel 
+of Fig. \ref{fig:ur} shows no such global trend.  In addition, the full dwarf 
+galaxy sample also exhibits different behaviors between the void dwarf galaxies 
+and the wall dwarf galaxies.  While there is very little relationship between a 
+void dwarf galaxy's color and its distance to a nearest neighbor (as seen in 
+Fig. \ref{fig:ur}), wall dwarf galaxies are significantly redder than void dwarf 
+galaxies within distances of 0.2 \hMpc.  The wall dwarf galaxies in Fig. 
+\ref{fig:ur_allDwarf} also show a shift towards bluer colors within 0.05 \hMpc 
+of the nearest neighbor.
+
+A similar pattern in seen when the distance to the nearest neighbor is measured 
+by $r_{vir}$.  Within $r_{vir}$, the bottom left panel of Fig. 
+\ref{fig:ur_allDwarf} shows that wall dwarf galaxies are redder than void dwarf 
+galaxies.  Within 0.1$r_{vir}$, wall dwarf galaxies are bluer than the global 
+trend.  Similar trends are seen in the relationship between color and distance 
+to the nearest group, seen in the right panel of Fig. \ref{fig:ur_allDwarf}.  It 
+is clear that our selection bias to star-forming dwarf galaxies influences the 
+trends we observe in our analysis.
 
@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{Images/smallScaleEnvironment/Mr_distribution}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_rabsmag_abs_hist}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_Drabsmag_abs_hist}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_rabsmag_vir_hist}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_Drabsmag_vir_hist}
+%    \includegraphics[width=\textwidth]{Images/smallScaleEnvironment/Mr_distribution}
     \caption[Distribution of absolute magnitudes of nearest neighbors]{The 
@@
 \begin{figure}
-    \includegraphics[width=0.5\textwidth]{Images/smallScaleEnvironment/dwarf_ur_xyz}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_zAbsDist_ur}
+    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_zVirDist_ur}
+%    \includegraphics[width=0.5\textwidth]{Images/smallScaleEnvironment/dwarf_ur_xyz}
     \caption[Color versus distance calculated with redshift]{Color versus 
-    distance to the nearest galaxy (in units of \hMpc on top and virial radii on 
-    the bottom) for the star-forming dwarf galaxies.  The redshift is included 
-    when calculating the distance to the nearest neighbor.  While there is still 
-    no correlation between distance and color, we do note that there is a gap in 
-    the distribution of galaxies around a distance of 0.05 \hMpc or 0.1$r_{vir}$ 
-    from the nearest neighbor.}
+    distance to the nearest galaxy (in units of \hMpc on the left and virial 
+    radius on the right) for the star-forming dwarf galaxies.  The redshift is 
+    included when calculating the distance to the nearest neighbor.  While there 
+    is still no correlation between distance and color, we do note that there is 
+    a gap in the distribution of galaxies around a distance of 0.05 \hMpc or 
+    0.2$r_{vir}$ from the nearest neighbor.}
     \label{fig:ur_xyz}

### 2017-07-19 KellyDouglass/Thesis/Thesis_sections/Conclusion.tex
Updated text in small scale environment chapter

--- 2017-06-15 KellyDouglass/Thesis/Thesis_sections/Conclusion.tex
@@
 the Direct $T_e$ method and spectroscopic line flux measurements as reprocessed 
-in the MPA-JHU catalog \citep[Douglass et al., 2017, in prep]{Douglass17a,
-Douglass17b}.  Due to the minimum redshift limit for detecting the [\ion{O}{2}] 
-$\lambda$3727 emission line in SDSS DR7 spectra, only 135 star-forming dwarf 
-galaxies are available for analysis with the Direct $T_e$ method.  With this 
-sample, we see no difference in the metallicity (O/H) between dwarf galaxies in 
-voids and denser regions \citep{Douglass17a}.  Upon closer inspection, we find 
-minor shifts in the distributions of gas-phase chemical abundances for void 
-dwarf galaxies when compared to dwarf galaxies in denser regions: star-forming 
-void dwarf galaxies have higher oxygen abundances (O/H), lower nitrogen 
-abundances (N/H), and lower N/O ratios \citep{Douglass17b}.
+in the MPA-JHU catalog \citep{Douglass17a,Douglass17b,Douglass17c}.  Due to the 
+minimum redshift limit for detecting the [\ion{O}{2}] $\lambda$3727 emission 
+line in SDSS DR7 spectra, only 135 star-forming dwarf galaxies are available for 
+analysis with the Direct $T_e$ method.  With this sample, we see no difference 
+in the metallicity (O/H) between dwarf galaxies in voids and denser regions 
+\citep{Douglass17a}.  Upon closer inspection, we find minor shifts in the 
+distributions of gas-phase chemical abundances for void dwarf galaxies when 
+compared to dwarf galaxies in denser regions: star-forming void dwarf galaxies 
+have higher oxygen abundances (O/H), lower nitrogen abundances (N/H), and lower 
+N/O ratios \citep{Douglass17b}.
 

### 2017-07-19 KellyDouglass/Thesis/Thesis_sections/GV.tex
Updated text in small scale environment chapter

@@
 measured by the MPA-JHU catalog\footnote{Available at 
-\url{http://www.mpa-garching.mpg.de/SDSS/DR7}} and published in Douglass et al. 
-(2017, submitted).  The large-scale environment of the galaxies is based on the 
+\url{http://www.mpa-garching.mpg.de/SDSS/DR7}} and published in 
+\cite{Douglass17c}.  The large-scale environment of the galaxies is based on the 
 void catalog compiled by \cite{Pan12}.  This void catalog is constructed from 
@@
 integrated star formation histories, which can provide insight into the 
-enrichment of the ISM and CGM.  A few of the galaxies for which Douglass et al. 
-(2017, submitted) are able to estimate metallicities reside in the green valley.  
-When compared with the metallicities of galaxies in the blue sequence and red 
-cloud, Fig. \ref{fig:Z_hist} shows that the green valley galaxies have higher 
-nitrogen abundances than star-forming galaxies in the blue sequence (and some of 
-the red cloud).  With oxygen abundances that fall within the same range as the 
-other two galaxy populations, this shift causes the N/O ratio to be much higher 
-in green valley galaxies than in the blue sequence.  Our interpretation of this 
-shift is described in Sec. \ref{sec:discussion_GV}.
+enrichment of the ISM and CGM.  A few of the galaxies for which 
+\cite{Douglass17c} are able to estimate metallicities reside in the green 
+valley.  When compared with the metallicities of galaxies in the blue sequence 
+and red cloud, Fig. \ref{fig:Z_hist} shows that the green valley galaxies have 
+higher nitrogen abundances than star-forming galaxies in the blue sequence (and 
+some of the red cloud).  With oxygen abundances that fall within the same range 
+as the other two galaxy populations, this shift causes the N/O ratio to be much 
+higher in green valley galaxies than in the blue sequence.  Our interpretation 
+of this shift is described in Sec. \ref{sec:discussion_GV}.
 
@@
 on the $\Lambda$CDM cosmology.  These results also coincide with the 
-observations of \cite{Douglass17b} and Douglass \& Vogeley (2017, submitted).  
-They find that, for dwarf galaxies ($M_r > -17$), those which exist in voids may 
-have commenced their star formation at a later time.  The higher fraction of 
-wall dwarf galaxies in the green valley might also point to an environmental 
-influence on the reason for transitioning through the green valley, such as ram 
-pressure stripping, which would occur much less frequently in the void 
-environment.  However, the existence of void galaxies in the green valley 
-indicate that galaxy interactions cannot be the only star formation quenching 
-mechanism.
+observations of \cite{Douglass17b} and \cite{Douglass17c}.  They find that, for 
+dwarf galaxies ($M_r > -17$), those which exist in voids may have commenced 
+their star formation at a later time.  The higher fraction of wall dwarf 
+galaxies in the green valley might also point to an environmental influence on 
+the reason for transitioning through the green valley, such as ram pressure 
+stripping, which would occur much less frequently in the void environment.  
+However, the existence of void galaxies in the green valley indicate that galaxy 
+interactions cannot be the only star formation quenching mechanism.
 
@@
 the green valley.  In conjunction with the conclusions of \cite{Douglass17b} and 
-Douglass et al. (2017, submitted), this indicates that void dwarf galaxies are 
-less evolved than dwarf galaxies in denser environments.  It would be beneficial 
-to investigate the small-scale ($\sim$1 \hMpc) environment of galaxies in the 
-green valley, to determine if any interactions are responsible for the 
-transitional state.
+\cite{Douglass17c}, this indicates that void dwarf galaxies are less evolved 
+than dwarf galaxies in denser environments.  It would be beneficial to 
+investigate the small-scale ($\sim$1 \hMpc) environment of galaxies in the green 
+valley, to determine if any interactions are responsible for the transitional 
+state.

### 2017-07-19 KellyDouglass/Thesis/Thesis_sections/Introduction.tex
Updated text in small scale environment chapter

@@
     black.  Existing in the cosmological voids (space between the galactic 
-    filaments), void galaxies are though to demonstrate the fundamental 
+    filaments), void galaxies are thought to demonstrate the fundamental 
     characteristics of galactic evolution.}

### 2017-07-19 KellyDouglass/Thesis/Thesis_sections/Paper1.tex
Updated text in small scale environment chapter

@@
 galaxies.  Dwarf galaxies are sensitive to many astrophysical effects, including 
-cosmological reionization, internal feedback from supernova and photoheating 
+cosmological reionization, internal feedback from supernovae and photoheating 
 from star formation, external effects from tidal interactions and ram pressure 

### 2017-07-19 KellyDouglass/Thesis/Thesis_sections/smallScaleEnvironment.tex
Updated text in small scale environment chapter

@@
 Likewise, \cite{Rupke08} concluded that interacting galaxies have suppressed 
-metallicities, because interactions induce flows of hydrogen.  \cite{Park09} 
-found that, for galaxies with $M_r < -19$, galaxy interactions out to the virial 
+metallicities because interactions induce flows of hydrogen.  For galaxies with 
+$M_r < -19$, \cite{Park09} found that galaxy interactions out to the virial 
 radius of the nearest neighbor influence the evolution of the target galaxy.  
@@
 in further detail.  The two methods result in different neighboring galaxies for 
-about 40\% of our dwarf galaxy sample.
+about 46\% of our dwarf galaxy sample.
 
@@
 A galaxy's redshift is composed of both the expansion of the universe and the 
-galaxy's peculiar velocity (its motion relative to its surrounding galaxies and 
+galaxy's peculiar velocity (its motion relative to the surrounding galaxies and 
 environment).  Known as the ``Finger of God'' effect, the peculiar velocity 
@@
 
-The projected distance between two galaxies is found by projecting the two 
+The distance on the sky between two galaxies is found by projecting the two 
 galaxies onto a sphere of radius $\bar{r}$, where $\bar{r}$ is the average 
@@
 are gravitationally bound are in a system where the relative velocity between us 
-and it is 0 and that $\bar{r}$ is the distance to the center of the system.  For 
-redshifts $z \ll 1$, we can approximate the distance to the system is as
+and the system is 0 and that $\bar{r}$ is the distance to the center of the 
+system.  For redshifts $z \ll 1$, we can approximate the distance to the system 
+as
 \begin{equation}
@@
 the velocity dispersions found by \cite{Choi07}, we find that the mass-to-light 
-ratio depends on the galaxy's morphology type: $\gamma_{early} = 2\gamma_{late}$.
+ratio depends on the galaxy's morphological type: 
+$\gamma_{early} = 2\gamma_{late}$.
 
-\cite{Hwang10} defines $200\rho_c = 740\bar{\rho}$, where 
+\cite{Hwang10} define $200\rho_c = 740\bar{\rho}$, where 
 $\bar{\rho} = (0.0223\pm 0.0005)(\gamma_{late}L_{-20})(\text{\hMpc})^3$.  We can 
@@
 %described in \cite{Brinchmann04}.  
-The gas-phase chemical abundances used are from Douglass, Vogeley, and Cen 
-(2017, submitted), which are calculated using the Direct $T_e$ method.  The 
-galaxies' large-scale environments are based on the void catalog compiled by 
-\cite{Pan12}, which is constructed from SDSS DR7 using the VoidFinder algorithm 
-of \cite{Hoyle02}.  Galaxies that are located within identified voids are 
-labeled as void galaxies, and those that do not fall within a void are 
-designated as a wall galaxy.  The large-scale environment within 5 \hMpc of the 
-edge of the main SDSS DR7 footprint cannot be described using the VoidFinder 
-algorithm because the minimum diameter of a void is 10 \hMpc.  Therefore, the 
-large-scale environment for galaxies within 5 \hMpc of the edge of the main 
-footprint in SDSS DR7 is designated as unknown.
+The gas-phase chemical abundances used are from \cite{Douglass17c}, which are 
+calculated using the Direct $T_e$ method.  The galaxies' large-scale 
+environments are based on the void catalog compiled by \cite{Pan12}, which is 
+constructed from SDSS DR7 using the VoidFinder algorithm of \cite{Hoyle02}.  
+Galaxies that are located within identified voids are labeled as void galaxies, 
+and those that do not fall within a void are designated as wall galaxies.  The 
+large-scale environment within 5 \hMpc of the edge of the main SDSS DR7 
+footprint cannot be described using the VoidFinder algorithm because the minimum 
+diameter of a void is 10 \hMpc.  Therefore, the large-scale environment for 
+galaxies within 5 \hMpc of the edge of the main footprint in SDSS DR7 is 
+designated as unknown.
 
@@
 Two galaxy samples are used in this analysis.  The largest one contains the 
-11,845 dwarf galaxies spectroscopically observed in SDSS DR7.  The second sample 
+11,002 dwarf galaxies spectroscopically observed in SDSS DR7.  The second sample 
 contains those star-forming dwarf galaxies from the first set that have 
-gas-phase chemical abundances in Douglass et al. (2017, submitted), totaling 2506 
-dwarf galaxies.  While this subset of galaxies contains only star-forming 
-galaxies and is not representative of all dwarf galaxies, we show in Section 
-\ref{sec:selection_effects} that this does not affect our results.
+gas-phase chemical abundances in \cite{Douglass17c}, totaling 1920 dwarf 
+galaxies.  Because this subset of galaxies contains only star-forming galaxies 
+and is not representative of all dwarf galaxies, we show in Section 
+\ref{sec:selection_effects} that this selection effect may affect our results.
 
@@
 proximity to the nearest galaxy group.  We use the \emph{Mr18} Berlind group 
-catalog \cite{Berlind06} as our source of groups, which is built on the galaxies 
-in the NYU-VAGC. The catalog identifies groups using a friends-of-friends 
-algorithm \citep{Huchra82} to connect galaxies with $M_r < -18$.
+catalog \citep{Berlind06} as our source of groups, which is built on the 
+galaxies in the NYU-VAGC. The catalog identifies groups using a 
+friends-of-friends algorithm \citep{Huchra82} to connect galaxies with 
+$M_r < -18$.
 
@@
 shown in Figs. \ref{fig:ur}--\ref{fig:NO}.  In each of the four plots within 
-each figure, we bin the galaxies in distance-space and show the average 
-parameter value in each bin, to see any overall trends in the data.  We applied 
-a linear regression to the data; the output of these fits are in Table 
-\ref{tab:fits}.  Each of these four plots probes this distance relationship from 
-a different angle.  The top left plots in Figs. \ref{fig:ur}--\ref{fig:NO} 
-relate the target dwarf galaxy's parameter to the distance to its nearest 
-neighbor, as defined by the the closest galaxy on the sky in \hMpc with a 
-velocity difference less than 300 km/s.  The bottom left plots relate the target 
+each figure, we bin the galaxies in distance-space and show the median parameter 
+value in each bin, to discern any overall trends in the data.  We apply a linear 
+regression to the data; the output of these fits are in Table \ref{tab:fits}.  
+Each of these four plots probes the distance relationship from a different 
+angle.  The top left plots in Figs. \ref{fig:ur}--\ref{fig:NO} relate the target 
 dwarf galaxy's parameter to the distance to its nearest neighbor, as defined by 
-the closest galaxy on the sky in units of the virial radius of the neighbor 
-galaxy with a velocity difference less than 300 km/s.  The nearest galaxy is not 
-necessarily the same for these two distance measurements, as explained in Sec. 
-\ref{sec:Theory_dist}.
+the closest galaxy on the sky in \hMpc with a velocity difference less than 300 
+km/s.  The bottom left plots relate the target dwarf galaxy's parameter to the 
+distance to its nearest neighbor, as defined by the closest galaxy on the sky in 
+units of the virial radius of the neighbor galaxy with a velocity difference 
+less than 300 km/s.  The nearest galaxy is not necessarily the same for these 
+two distance measurements, as explained in Sec. \ref{sec:Theory_dist}.
 
-We repeat this same analysis on the nearest groups to the target dwarf galaxy.  
+We repeat this same analysis on the nearest group to the target dwarf galaxy.  
 The top right plots in Figs. \ref{fig:ur}--\ref{fig:NO} relate the target dwarf 
@@
 as defined by the closest group on the sky in units of the group's rms radius 
-with a velocity difference of less than 300 km/s.  Groups are very rare in the 
-void environment (by nature of the void environment), so the uncertainty in the 
-binned values shown in these plots is much larger than in the galaxy neighbor 
-plots.
+with a velocity difference of less than 300 km/s.  Groups are very rare in voids 
+(by nature of the void environment), so the uncertainty in the binned values 
+shown in these plots is much larger than in the galaxy neighbor plots.
 
@@
     versus distance to the nearest galaxy (on the left) and nearest group (on 
-    the right).  The top panel shows the color as a function of the sky 
+    the right).  The top panels show the color as a function of the sky 
     separation in \hMpc between the target dwarf galaxy and the neighbor, while 
-    the bottom panel shows the color as a function of the closest virial 
+    the bottom panels show the color as a function of the closest virial 
     neighbor.  Void galaxies are shown in red, while wall galaxies are shown in 
-    black and unknown in green.  We have also included the average color for the 
+    black and unknown in green.  We have also included the median color for the 
     galaxies after binning by distance, to discern any finer behavior in the 
@@
     have some affect on the dwarf galaxy's color at separations less than 0.05 
-    \hMpc, or 0.1$r_{vir}$.  %The closest group appears to have some affect on 
-%    the target dwarf galaxy's color at distances less than 0.1 \hMpc to the 
-%    group's center; there appears to be no relationship between a dwarf galaxy's 
-%    color and its distance to the nearest group as represented by the fraction 
-%    of the group's radius.}
+    \hMpc, or 0.1$r_{vir}$ (for wall galaxies; 0.2$r_{vir}$ for void galaxies).  
     There appears to be no relationship between a dwarf galaxy's color and its 
@@
 we expect the dwarf galaxy's color to become bluer as the distance to the 
-neighbor decreases.  Fig. \ref{fig:ur} shows very little relationship between 
-the distance and color, except in the smallest distance bin.  The linear fits 
-quantify this observation --- the slopes are on the order of 10$^{-3}$.  
-However, within a distance of 0.05 \hMpc or 0.1$r_{vir}$, dwarf galaxies tend 
-to be bluer than at further distances from their nearest neighbor.  %At distances 
-%less than 0.1 \hMpc from the center of the nearest groups, the dwarf galaxies 
-%are redder than average.  However, there does not appear to be any relationship 
-%between a dwarf galaxy's color and its distance to the center of the nearest 
-%group in units of the group's rms radius.  
-There does not appear to be any relationship between a dwarf galaxy's color and 
-its distance to the center of the nearest group.  
-It has been well-established that 
-void galaxies tend to be bluer than galaxies in denser environments 
-\citep{Grogin99,Rojas04,Patiri06,vonBendaBeckmann08,Hoyle12}; this shift is 
-apparent in Fig. \ref{fig:ur}, where the void dwarf galaxies are slightly bluer 
-than the wall dwarf galaxies.
+neighboring galaxy decreases.  Fig. \ref{fig:ur} shows very little relationship 
+between the distance and color, except in the smallest distance bin.  The linear 
+fits quantify this observation --- the slopes are on the order of 10$^{-3}$.  
+However, within a distance of 0.05 \hMpc or 0.1$r_{vir}$ (for wall galaxies; 
+0.2$r_{vir}$ for void galaxies), dwarf galaxies tend to be bluer than at further 
+distances from their nearest neighbor.  There does not appear to be any 
+relationship between a dwarf galaxy's color and its distance to the center of 
+the nearest group.  It has been well-established that void galaxies tend to be 
+bluer than galaxies in denser environments \citep{Grogin99,Rojas04,Patiri06,
+vonBendaBeckmann08,Hoyle12}; this shift is apparent in Fig. \ref{fig:ur}, where 
+the void dwarf galaxies are slightly bluer than the wall dwarf galaxies at all 
+distances.
 
-\subsubsection{sSFR}
+\subsubsection{Specific star formation rate}
 
@@
     distance to the nearest galaxy (on the left) and nearest group (on the 
-    right).  The top panel shows the sSFR as a function of the sky separation in 
+    right).  The top panels show the sSFR as a function of the sky separation in 
     \hMpc between the target dwarf galaxy and the neighbor, while the bottom 
-    panel shows the sSFR as a function of the closest virial neighbor.  Void 
+    panels show the sSFR as a function of the closest virial neighbor.  Void 
     galaxies are shown in red, while wall galaxies are shown in black and 
-    unknown in green.  We have also included the average sSFR for the galaxies 
+    unknown in green.  We have also included the median sSFR for the galaxies 
     after binning by distance, to discern any finer behavior in the 
@@
     have higher sSFRs than the wall dwarf galaxies.  Only the neighbor galaxies 
-    at separations less than 0.05 \hMpc or 0.1$r_{vir}$ appear to have some 
-    affect on the dwarf galaxies' sSFR.  There appears to be no relationship 
-    between a dwarf galaxy's sSFR and its distance to the nearest group.}
+    at separations less than 0.05 \hMpc or 0.1$r_{vir}$ (for wall galaxies; 
+    0.2$r_{vir}$ for void galaxies) appear to have some affect on the dwarf 
+    galaxies' sSFR.  There appears to be no relationship between a dwarf 
+    galaxy's sSFR and its distance to the nearest group.}
     \label{fig:sSFR}
@@
 Following our prediction for the color-distance relations, we expect the 
-sSFR to decrease with distance from the nearest neighbor and increase with 
-distance from the nearest group.  We also see very little relationship between 
-the distance and sSFR in Fig. \ref{fig:sSFR}, except in the smallest distance 
-bin.  The linear fits quantify this observation --- the slopes are on the order 
-of 10$^{-3}$.  Within a distance of 0.05 \hMpc or 0.1$r_{vir}$, dwarf galaxies 
+specific star formation rate (sSFR) to decrease with distance from the nearest 
+neighbor and increase with distance from the nearest group.  We also see very 
+little relationship between the distance and sSFR in Fig. \ref{fig:sSFR}, except 
+in the smallest distance bin.  The linear fits quantify this observation --- the 
+slopes are on the order of 10$^{-3}$.  Within a distance of 0.05 \hMpc or 
+0.1$r_{vir}$ (for wall galaxies; 0.2$r_{vir}$ for void galaxies), dwarf galaxies 
 tend to have higher sSFRs than at further distances from their nearest neighbor.  
@@
 these distance comparisons, there is a shift towards higher sSFRs in the void 
-dwarf galaxies when compared to the wall dwarf galaxies, as has been observed 
-before \citep{Rojas05,vonBendaBeckmann08,Moorman15,Beygu16}.
+dwarf galaxies when compared to the wall dwarf galaxies, as has been previously 
+observed \citep{Rojas05,vonBendaBeckmann08,Moorman15,Beygu16}.
 
@@
     {Metallicity versus distance to the nearest galaxy (on the left) and nearest 
-    group (on the right).  The top panel shows the metallicity as a function of 
+    group (on the right).  The top panels show the metallicity as a function of 
     the sky separation in \hMpc between the target dwarf galaxy and the 
-    neighbor, while the bottom panel shows the metallicity as a function of the 
+    neighbor, while the bottom panels show the metallicity as a function of the 
     closest virial neighbor.  Void galaxies are shown in red, while wall 
     galaxies are shown in black and unknown in green.  We have also included the 
-    average metallicity for the galaxies after binning by distance, to discern 
+    median metallicity for the galaxies after binning by distance, to discern 
     any finer behavior in the relationships.  Linear fits to the void and wall 
@@
     void dwarf galaxies have higher metallicities than the wall dwarf galaxies.  
-    Only the neighbor galaxies at separations less than 0.05 \hMpc or 
-    0.1$r_{vir}$ appear to have some affect on the dwarf galaxies' metallicity.  
-    When measuring the distance to the nearest group in \hMpc, it appears that 
-    the dwarf galaxies have lower metallicities at distances less than 0.1 \hMpc 
-    from their nearest group.}
+    Only the neighbor galaxies at separations less than 0.15 \hMpc appear to 
+    have some affect on the dwarf galaxies' metallicity.  When measuring the 
+    distance to the nearest group in \hMpc, it appears that the dwarf galaxies 
+    have lower metallicities at distances less than 0.05 \hMpc from their 
+    nearest group.}
     \label{fig:OH}
@@
 Based on our hypothesis that galaxies would be bluer and have higher sSFRs at 
-small distances to their nearest neighbors, we anticipated that the metallicity 
+small distances to their nearest neighbors, we anticipate that the metallicity 
 of the galaxies would decrease with increasing distance.  As before, we only see 
 a relationship between the distance and metallicity in the smallest distance 
-bin in Fig. \ref{fig:OH}.  The linear fits quantify this observation --- the 
-slopes are on the order of 10$^{-2}$.  Within a distance of 0.05 \hMpc or 
-0.1$r_{vir}$, dwarf galaxies tend to have higher metallicities than at further 
-distances from their nearest neighbor.  At distances less than 0.1 \hMpc from 
-the center of the nearest group, dwarf galaxies might have lower than average 
-metallicities.  However, this could be an erroneous conclusion due to 
-small-number statistics.  In these distance comparisons, there is a shift 
-towards higher metallicities in the void dwarf galaxies when compared to the 
-wall dwarf galaxies, as has been observed by \cite{Douglass17b} and Douglass et 
-al. (2017, submitted).
+bins in Fig. \ref{fig:OH}.  The linear fits quantify this observation --- the 
+slopes are on the order of 10$^{-3}$.  Within a distance of 0.15 \hMpc, dwarf 
+galaxies tend to have higher metallicities than at further distances from their 
+nearest neighbor.  At distances less than 0.05 \hMpc from the center of the 
+nearest group, dwarf galaxies might have lower than average metallicities.  
+However, this could be an erroneous conclusion due to small-number statistics.  
+In these distance comparisons, there is a shift towards higher metallicities in 
+the void dwarf galaxies when compared to the wall dwarf galaxies, as has been 
+observed by \cite{Douglass17b} and \cite{Douglass17c}.
 
@@
     nitrogen abundance versus distance to the nearest galaxy (on the left) and 
-    nearest group (on the right).  The top panel shows N/H as a function of the 
+    nearest group (on the right).  The top panels show N/H as a function of the 
     sky separation in \hMpc between the target dwarf galaxy and the neighbor, 
-    while the bottom panel shows N/H as a function of the closest virial 
+    while the bottom panels show N/H as a function of the closest virial 
     neighbor.  Void galaxies are shown in red, while wall galaxies are shown in 
-    black and unknown in green.  We have also included the average nitrogen 
+    black and unknown in green.  We have also included the median nitrogen 
     abundance for the galaxies after binning by distance, to discern any finer 
     behavior in the relationships.  Linear fits to the void and wall galaxies 
-    are shown in orange and blue, respectively.  There is very little difference 
-    in N/H between the two large-scale environments.  There does not appear to 
-    be any relationship between the dwarf galaxies' nitrogen abundance and the 
-    distance to their nearest neighbor or group.}
+    are shown in orange and blue, respectively.  Void dwarf galaxies have 
+    slightly lower N/H ratios than dwarf galaxies in denser environments.  
+    Otherwise, there does not appear to be any relationship between the dwarf 
+    galaxies' nitrogen abundance and the distance to their nearest neighbor.  It 
+    appears that void dwarf galaxies within 0.05 \hMpc of a group have slightly 
+    lower nitrogen abundances.}
     \label{fig:NH}
@@
 with the other parameters, Fig. \ref{fig:NH} shows very little relationship 
-between the distance and N/H, except in the smallest distance bin for the 
-closest virial neighbor.  The linear fits quantify this observation --- the 
-slopes are on the order of 10$^{-2}$.  Within a distance of 0.1$r_{vir}$, dwarf 
-galaxies tend to have higher nitrogen abundances than at distances further from 
-their nearest neighbor.  There does not seem to be any relationship between the 
-nitrogen abundance of the star-forming dwarf galaxies and distance to the center 
-of the nearest group.  Unlike the shifts seen with the other parameters and what 
-is observed in \cite{Douglass17b} and Douglass et al. (2017, submitted), we see no 
-significant difference in the nitrogen abundance resulting from the large-scale 
-environment.
+between the distance and N/H.  The linear fits quantify this observation --- the 
+slopes are on the order of 10$^{-3}$, except for the wall dwarf galaxies when 
+the distance to the nearest neighbor is measured in \hMpc.  Here, wall dwarf 
+galaxies exhibit an increase in the N/H ratio with increasing distance to the 
+nearest neighbor.  Within a distance of 0.05 \hMpc of the nearest group, void 
+dwarf galaxies tend to have lower nitrogen abundances.  There does not seem to 
+be any relationship between the nitrogen abundance of the star-forming dwarf 
+galaxies and distance to the nearest galaxy.  We see a slight difference in the 
+nitrogen abundance resulting from the large-scale environment, similar to what 
+is observed in \cite{Douglass17b} and \cite{Douglass17c}.
 
@@
     distance to the nearest galaxy (on the left) and nearest group (on the 
-    right).  The top panel shows the N/O ratio as a function of the sky 
+    right).  The top panels show the N/O ratio as a function of the sky 
     separation in \hMpc between the target dwarf galaxy and the neighbor, while 
-    the bottom panel shows N/O as a function of the closest virial neighbor.  
+    the bottom panels show N/O as a function of the closest virial neighbor.  
     Void galaxies are shown in red, while wall galaxies are shown in black and 
-    unknown in green.  We have also included the average nitrogen abundance for 
+    unknown in green.  We have also included the median nitrogen abundance for 
     the galaxies after binning by distance, to discern any finer behavior in the 
@@
     orange and blue, respectively.  The void dwarf galaxies have lower N/O 
-    ratios than the wall dwarf galaxies, but there is no distinct relationship 
-    between the distance to the nearest neighbor and the N/O ratio.  %The N/O 
-%    ratio might be higher in dwarf galaxies within 0.05 \hMpc of the center of 
-%    the closest group.
-    }
+    ratios than the wall dwarf galaxies.  Within a distance of 0.05 \hMpc from 
+    the nearest galaxy, dwarf galaxies appear to have lower N/O ratios.}
     \label{fig:NO}
@@
 
-We do not expect any influence on the relative synthesis of oxygen and nitrogen 
-from the proximity to a nearest neighbor since nucleosynthesis is a physical 
-process unaffected by external influences.  Unlike the other parameters studied, 
-Fig. \ref{fig:NO} shows that the N/O ratio does not have any relationship with 
-the distance to a nearest neighbor at any separation.  This is reflected in the 
-linear fits to the data --- the slopes are on the order of 10$^{-2}$ and 
-smaller.  %When looking at the relationship between the N/O ratio and the 
-%distance to the nearest group, though, the N/O ratio might be higher than 
-%average in galaxies within 0.1 \hMpc of the group's center.  
-There is also no apparent relationship between the N/O ratio and the target 
-galaxy's distance to the center of the nearest group.  
-The shift towards 
-lower N/O ratios in star-forming void dwarf galaxies is readily apparent, as 
-found by \cite{Douglass17b} and Douglass et al. (2017, submitted).
+Since nucleosynthesis is a physical process unaffected by external influences, 
+we do not expect any influence on the relative synthesis of oxygen and nitrogen 
+from the proximity to a nearest neighbor.  The upper left plot of Fig. 
+\ref{fig:NO} shows that the N/O ratio is lower in dwarf galaxies within 0.05 
+\hMpc to a nearest neighbor.  The lack of any other correlation is reflected in 
+the linear fits to the data --- the slopes are on the order of 10$^{-3}$.  The 
+shift towards lower N/O ratios in star-forming void dwarf galaxies is readily 
+apparent, as found by \cite{Douglass17b} and \cite{Douglass17c}.
 
@@
         sSFR  & $0.01\pm 0.042$  & $0.0\pm 0.10$   & $-9.28\pm 0.037$ & $-9.33\pm 0.049$\\
-        \OH   & $0.01\pm 0.027$  & $0.06\pm 0.062$ & $7.988\pm 0.024$ & $7.94\pm 0.030$\\
+        \OH   & $0.01\pm 0.027$  & $0.06\pm 0.062$ & $7.99\pm 0.024$  & $7.94\pm 0.030$\\
         \NH   & $0.02\pm 0.028$  & $0.10\pm 0.059$ & $6.54\pm 0.026$  & $6.55\pm 0.029$\\
@@
         sSFR  & $0.000\pm 0.0066$  & $0.00\pm 0.016$    & $-9.28\pm 0.040$ & $-9.34\pm 0.049$\\
-        \OH   & $0.001\pm 0.0042$  & $0.012\pm 0.0099$  & $7.992\pm 0.025$ & $7.94\pm 0.031$\\
+        \OH   & $0.001\pm 0.0042$  & $0.012\pm 0.0099$  & $7.99\pm 0.025$  & $7.94\pm 0.031$\\
         \NH   & $0.000\pm 0.0045$  & $0.009\pm 0.0094$  & $6.55\pm 0.027$  & $6.56\pm 0.029$\\
@@
         sSFR  & $-0.003\pm 0.0064$ & $0.006\pm 0.0065$  & $-9.26\pm 0.045$ & $-9.36\pm 0.053$\\
-        \OH   & $0.001\pm 0.0041$  & $0.002\pm 0.0041$  & $7.989\pm 0.029$ & $7.95\pm 0.033$\\
+        \OH   & $0.001\pm 0.0041$  & $0.002\pm 0.0041$  & $7.99\pm 0.029$  & $7.95\pm 0.033$\\
         \NH   & $0.007\pm 0.0043$  & $0.006\pm 0.0038$  & $6.51\pm 0.031$  & $6.55\pm 0.031$\\
@@
     units of \hMpc, and the nearest group in units of the group's rms radius; 
-    all objects must be within 300 km/s of the target galaxy.  The slopes are 
-    all negligible, quantifying the observations made that the proximity to a 
+    all objects must be within 300 km/s of the target galaxy.  Except for the 
+    relationship between the nitrogen abundance of wall dwarf galaxies and the 
+    distance to the nearest neighbor in units of \hMpc, the slopes are all 
+    negligible.  This quantifies the observations made that the proximity to a 
     galaxy or group has little influence on a dwarf galaxy's evolution.}
@@
 To quantify the results shown in Figs. \ref{fig:ur}--\ref{fig:NO}, we calculate 
-the parameters for the best linear fit.  Any slope of significant magnitude 
-shows an overall correlation between a given physical parameter and the galaxy's 
-distance to its nearest neighbor or group.  The results of this analysis are 
-listed in Table \ref{tab:fits}.  These slopes reflect the observations described 
-in Section \ref{sec:Relations}: there is no correlation between the distance to 
-the nearest neighbor and a galaxy's color, sSFR, or gas-phase chemical 
-abundances.  This analysis does not capture any variations within the range of 
-distances for all dwarf galaxies included in this study.
+the parameters for the best linear fit for each physical parameter and distance 
+metric combination.  Any slope of significant magnitude shows an overall 
+correlation between a given physical parameter and the galaxy's distance to its 
+nearest neighbor or group.  The results of this analysis are listed in Table 
+\ref{tab:fits}.  These slopes reflect the observations described in Section 
+\ref{sec:Relations}: there is no correlation between the distance to the nearest 
+neighbor and a galaxy's color, sSFR, or gas-phase chemical abundances, except 
+for wall dwarf galaxies and their nitrogen abundances when compared to the 
+distance to the nearest galaxy in \hMpc.  This analysis does not capture any 
+small variations within the range of distances for all dwarf galaxies included 
+in this study.
 
@@
 sensitive our results are to any initial conditions.  The first parameter we 
-discuss is the sensitivity of our results on the maximum peculiar velocity to 
-define a match.  Throughout our analysis, we use 300 km/s as the maximum 
+discuss is the sensitivity of our results on the maximum peculiar velocity used 
+to define a match.  Throughout our analysis, we use 300 km/s as the maximum 
 velocity separation allowed between the target galaxy and its nearest neighbor 
@@
     overall inverse relationship between a wall dwarf galaxy's color and the 
-    distance to the nearest neighbor in \hMpc.}
+    distance to the nearest neighbor in \hMpc and $r_{vir}$.}
     \label{fig:ur_allDwarf}
@@
 Fig. \ref{fig:ur}), wall dwarf galaxies are significantly redder than void dwarf 
-galaxies within distances of 0.2 \hMpc.  The wall dwarf galaxies in Fig. 
-\ref{fig:ur_allDwarf} also show a shift towards bluer colors within 0.05 \hMpc 
-of the nearest neighbor.
+galaxies within distances of 0.3 \hMpc.
 
@@
 is clear that our selection bias to star-forming dwarf galaxies influences the 
-trends we observe in our analysis.
+trends we observe for wall dwarf galaxies in our analysis.
 
@@
 
-For about 41\% of our dwarf galaxy sample, the two different metrics by which to 
+For about 46\% of our dwarf galaxy sample, the two different metrics by which to 
 define the nearest neighbor (minimum in units of \hMpc or virial radius of the 
@@
 using these two different distance metrics, we are able to probe the 
-relationship between a dwarf galaxy and its nearest neighbor and nearest dark 
+relationships between a dwarf galaxy and its nearest neighbor and nearest dark 
 matter halo.
@@
 can be significant for galaxies in groups, we have been careful to avoid 
-calculating the distance between objects with the redshift.  However, we are 
-interested to see how the inclusion of redshift in the distance calculations 
-affects the results of our analysis.  Therefore, we repeat the same analysis on 
-the relationship between color and distance, but this time we include redshift 
-as a third component in the distance calculations.  Consequently, we no longer 
-limit our sample by a peculiar velocity separation.  Fig. \ref{fig:ur_xyz} shows 
-the relationship between these distances and the color of the star-forming dwarf 
+calculating the distance between objects with redshift.  However, we are curious 
+to see how the inclusion of redshift in the distance calculations affects the 
+results of our analysis.  Therefore, we repeat the same analysis on the 
+relationship between color and distance, but this time we include redshift as a 
+third component in the distance calculations.  Consequently, we no longer limit 
+our sample by a peculiar velocity separation.  Fig. \ref{fig:ur_xyz} shows the 
+relationship between these distances and the color of the star-forming dwarf 
 galaxies.  When compared to Fig. \ref{fig:ur}, we see that there is no change in 
@@
 We note the existence of a gap in the distribution of galaxies around a distance 
-of 0.05 \hMpc or 0.1$r_{vir}$ from the nearest neighbor that is not present in 
+of 0.05 \hMpc or 0.2$r_{vir}$ from the nearest neighbor that is not present in 
 Fig. \ref{fig:ur}.  When we incorporate the redshift into the distance 
@@
 
-Only those galaxies within 0.05 \hMpc and 0.1$r_{vir}$ of a nearest neighbor, or 
-those within 0.1 \hMpc of the nearest group appear to deviate from the average 
-galaxy values.  The target galaxies within this proximity of their nearest 
-neighbor tend to be bluer, have a higher sSFR, and have higher oxygen and 
-nitrogen abundances.  Based on the shift in the distribution of galaxies seen in 
-Fig. \ref{fig:ur_xyz}, these galaxies might be merging or strongly interacting 
-with their nearest neighbor.  If so, this provides evidence that galaxy 
-interactions result in a burst of star formation that increases the gas-phase 
-chemical abundances of the dwarf galaxies.  Because merging galaxies share the 
-same dark matter halo, it appears that the sharing of a dark matter halo has 
-more influence on the evolution of a galaxy than the distance to its nearest 
-neighbor.
+Only those galaxies within 0.05 \hMpc and 0.1$r_{vir}$ (for wall galaxies; 
+0.2$r_{vir}$ for void galaxies) of a nearest neighbor appear to deviate from the 
+average galaxy values.  The target galaxies within this proximity of their 
+nearest neighbor tend to be bluer, have a higher sSFR, and have higher oxygen 
+abundances and lower N/O ratios.  Based on the shift in the distribution of 
+galaxies seen in Fig. \ref{fig:ur_xyz}, these galaxies might be merging or 
+strongly interacting with their nearest neighbor.  If so, this provides evidence 
+that galaxy interactions result in a burst of star formation that increases the 
+gas-phase chemical abundances of the dwarf galaxies.  Because merging galaxies 
+share the same dark matter halo, it appears that the sharing of a dark matter 
+halo has more influence on the evolution of a galaxy than the distance to its 
+nearest neighbor.
 
-In contrast, dwarf galaxies within 0.1 \hMpc of the center of the nearest group 
-are redder, have lower oxygen abundances (O/H), and have higher N/O ratios than 
-average.  Being so close to the center of a group seems to prevent more recent 
-episodes of star formation.  Due to their proximity to the group center, it is 
-also likely that these dwarf galaxies are not able to retain as much of their 
-heavy elements as a more isolated galaxy, thereby reducing their gas-phase 
-oxygen abundance (and increasing their N/O ratio).
+In contrast, dwarf galaxies within 0.05 \hMpc of the center of the nearest group 
+have lower oxygen (O/H) and nitrogen (N/H) abundances (O/H) than average.  Due 
+to their proximity to the group center, it is likely that these dwarf galaxies 
+are not able to retain as much of their heavy elements as a more isolated 
+galaxy, thereby reducing their gas-phase oxygen and nitrogen abundances.
 
@@
 
-The influence on the gas-phase oxygen abundance within 0.05 \hMpc and 
-0.1$r_{vir}$ agrees with the results of \cite{Shields91,Pustilnik06,Cooper08,
-Ellison09,Pustilnik11a,Pustilnik14}, and \cite{SanchezAlmeida16}, which all find 
-that galaxies with higher metallicities preferentially reside in denser regions.  
-Work by \cite{Rupke08} finds that interacting galaxies have suppressed 
-metallicities due to interaction- or merger-induced gas flows into the galaxy 
-centers.
+The influence on the gas-phase oxygen abundance within 0.15 \hMpc agrees with 
+the results of \cite{Shields91,Pustilnik06,Cooper08,Ellison09,Pustilnik11a,
+Pustilnik14}, and \cite{SanchezAlmeida16}, which all find that galaxies with 
+higher metallicities preferentially reside in denser regions.  Work by 
+\cite{Rupke08} find that interacting galaxies have suppressed metallicities due 
+to interaction- or merger-induced gas flows into the galaxy centers.
 
@@
 see for those galaxies with nearest neighbors within 0.05 \hMpc and 
-0.1$r_{vir}$ warrant further study.
+0.1$r_{vir}$ (for wall galaxies; 0.2$r_{vir}$ for void galaxies) warrant further 
+study.
 
@@
 Using the star-forming dwarf galaxies in the SDSS DR7 sample with gas-phase 
-chemical abundances from Douglass et al. (2017, submitted), we investigate the 
-influence of the small-scale environment on the evolution of dwarf galaxies.  
+chemical abundances from \cite{Douglass17c}, we investigate the influence of the 
+small-scale environment ($\sim 1$ \hMpc) on the evolution of dwarf galaxies.  
 From the $\sim$2000 galaxies in the sample, there only appears to be an effect 
-from a neighboring galaxy within 0.05 \hMpc or 0.1$r_{vir}$.  The proximity of a 
-group seems to only affect the target dwarf galaxy if it is within 0.1 \hMpc.  
-Thus, the small-scale ($\sim 1$ \hMpc) environment does not appear to strongly 
-influence the evolution of dwarf galaxies.
+from a neighboring galaxy within 0.05 \hMpc or 0.1$r_{vir}$ (for wall galaxies; 
+0.2$r_{vir}$ for void galaxies).  The proximity of a group seems to only affect 
+the target dwarf galaxy if it is within 0.05 \hMpc.  Thus, the small-scale 
+environment does not appear to strongly influence the evolution of dwarf 
+galaxies.
 
@@
 and the target galaxy's color, sSFR, and gas-phase chemical abundances.  We find 
-that, for those galaxies with a neighbor within 0.05 \hMpc or 0.1$r_{vir}$, the 
-dwarf galaxies are bluer, have a higher sSFR, and have higher oxygen and 
-nitrogen abundances than average.  In contrast, dwarf galaxies within 0.1 \hMpc 
-of the center of the closest group are redder, have lower oxygen abundances, and 
-have higher N/O ratios than average.  These results do not depend on the maximum 
-peculiar velocity difference or on the sample (star-forming versus all 
-galaxies).
+that, for those galaxies with a neighbor within 0.05 \hMpc or 0.1$r_{vir}$ (for 
+wall galaxies; 0.2$r_{vir}$ for void galaxies), the dwarf galaxies are bluer, 
+have a higher sSFR, have higher oxygen abundances, and have lower N/O ratios 
+than average.  In contrast, dwarf galaxies within 0.05 \hMpc of the center of 
+the closest group have lower oxygen and nitrogen abundances.  These results do 
+not depend on the maximum peculiar velocity difference, but they may depend on 
+the sample (star-forming versus all galaxies).
 

### 2017-07-19 KellyDouglass/Thesis/preamble.tex
Added figures for small-scale and GV to presentation; minor changes to Thesis
Updated text in small scale environment chapter

@@
 To my parents\\
-You told me to reach for the stars\\
+You always encouraged me to reach for the stars\\
 Will galaxies do?
@@
 to work my hardest and do my best.  Thank you for challenging me in so many 
-ways.  I love you guys, and I it means so much that you are here today!
+ways.  I love you guys, and it means so much that you are here today!
 

### 2017-07-19 KellyDouglass/Thesis/DirectMethodPhysics.tex
Added acknowledgments and dedication
Fixed typos

@@
-\chapter[Direct method physics]{The physics of the Direct $T_e$ method}\label{sec:physics}
+\chapter[Direct Method Physics]{Physics of the Direct $T_e$ Method}\label{sec:physics}
 
@@
 A time-dependent potential is added to the Schr\"{o}dinger equation in order to 
-solve for the forbidden transition energies.  We can assume that the time 
-perturbation is a minor component of the potential and can thus treat it as a 
-perturbation.  For a simplified two-level system, the time-dependent wave 
-function is
+solve for the forbidden transition energies.  We can assume that this 
+time-dependent potential is a minor component of the potential and can thus 
+treat it as a perturbation.  For a simplified two-level system, the 
+time-dependent wave function is
 \begin{equation}
@@
 To solve for the time-dependent coefficients, we substitute $\Psi (t)$ into the 
-time-dependent Schr\"{o}dinter equation
+time-dependent Schr\"{o}dinger equation
 \begin{equation}

### 2017-07-19 KellyDouglass/Thesis/Tables/Paper1/XMPtable.tex
Fixed typos

@@
 
-\caption[Extremely low-metallicity dwarf galaxies in 135 galaxy sample]{Details of the 21 extreme low gas-phase metallicity ($12 + \log(\text{O}/\text{H}) < 7.6$) galaxies found.
+\caption[Extremely low-metallicity dwarf galaxies in 135 dwarf galaxy sample]{Details of the 21 extreme low gas-phase metallicity ($12 + \log(\text{O}/\text{H}) < 7.6$) galaxies found.
 Four of these galaxies are located in voids (about 10\% of the void dwarf population measured) and seventeen are in more dense regions (about 19\% of the wall dwarf population measured); thus, there does not seem to be a special population of extreme low-metallicity galaxies in voids.

### 2017-07-19 KellyDouglass/Thesis/Thesis_sections/Conclusion.tex
Fixed typos

@@
-\chapter[Conclusion]{Conclusions and suggestions for future work}\label{ch:conclusion}
+\chapter[Conclusions]{Conclusions and suggestions for future work}\label{ch:conclusion}
 
@@
 gas-phase chemical abundances as the smaller, 135 star-forming dwarf galaxy 
-sample, but with a much higher statistical significance.  We find that 
+sample but with a much higher statistical significance.  We find that 
 star-forming void dwarf galaxies have, on average, 7\% higher oxygen abundances 
@@
 begin to show evidence of secondary nitrogen synthesis at a stellar mass 
-$\sim$0.4 dex lower than for the galaxies in denser regions.  This indicates 
-that the void galaxies synthesize secondary nitrogen at a smaller stellar mass 
-than galaxies in denser regions.
+$\sim$0.4 dex lower than for dwarf galaxies in denser regions.  This indicates 
+that the void dwarf galaxies begin to synthesize secondary nitrogen at a smaller 
+stellar mass than dwarf galaxies in denser regions.
 
@@
 regions.  Due to their low gas-phase oxygen abundances, these 287 dwarf galaxies 
-have some of the larger N/O ratios of the star-forming dwarf galaxies sample 
+have some of the higher N/O ratios of the star-forming dwarf galaxies sample 
 studied.  While the metallicities of these galaxies cause them to stand out in 
@@
 galaxies.  We find that only the presence of a neighboring galaxy within 0.05 
-\hMpc or 0.1$r_{vir}$, or the presence of a group within 0.1 \hMpc influences a 
+\hMpc or 0.1$r_{vir}$, or the presence of a group within 0.05 \hMpc influences a 
 dwarf galaxy's evolution.  Dwarf galaxies with a nearest neighbor galaxy within 
-0.05 \hMpc or 0.1$r_{vir}$ tend to be bluer, have a higher sSFR, and have higher 
-oxygen and nitrogen abundances than average.  This matches the results of 
-\cite{Park09}, who find that higher luminosity late-late type galaxy pairs 
-within 0.05$r_{vir}$ are bluer and have higher SFRs.  In contrast, dwarf 
-galaxies within 0.1 \hMpc of the center of the closest group are redder, have 
-lower oxygen abundances, and have higher N/O ratios than average.  These results 
-are independent of both the maximum relative velocity required to define a 
-nearest neighbor and the sample (star-forming versus all dwarf galaxies).
+0.05 \hMpc or 0.1$r_{vir}$ tend to be bluer, have a higher sSFR, have higher 
+oxygen abundances, and have lower N/O ratios than average.  This matches the 
+results of \cite{Park09}, who find that higher luminosity late-late type galaxy 
+pairs within 0.05$r_{vir}$ are bluer and have higher SFRs.  In contrast, dwarf 
+galaxies within 0.05 \hMpc of the center of the closest group have lower oxygen 
+and nitrogen abundances than average.  These results are independent of both the 
+maximum relative velocity required to define a nearest neighbor, but they may 
+depend on the sample (star-forming versus all dwarf galaxies).
 
@@
 green valley of the CMD by combining the galaxy's color, color gradient, and 
-inverse concentration index.  Galaxies with a value aimc$< 25$ for the 
+inverse concentration index.  Galaxies with a value aimc $< 25$ for the 
 morphological type as calculated in the KIAS-VAGC exist in the green valley 
@@
 oxygen (O/H), high nitrogen (N/H), and high N/O ratio is also seen in galaxies 
-classified as AGN, indicating that galaxies in the green valley have an AGN.
+classified as AGN, indicating that galaxies in the green valley may have an AGN.
 
@@
 significantly smaller than the fraction of green valley galaxies found in denser 
-regions.  Combined with the previous results about the large-scale environmental 
+regions.  Combined with the previous results of the large-scale environmental 
 influence on the gas-phase chemical abundances, this indicates that void dwarf 
-galaxies are less evolved than dwarf galaxies in denser environments.
+galaxies may be less evolved than dwarf galaxies in denser environments.
 
@@
 valley, but the relevant baryonic processes (gas cooling, feedback, etc.) are 
-very complex and heavily independent.  The enrichment of the interstellar medium 
+very complex and heavily dependent.  The enrichment of the interstellar medium 
 (ISM) and circumgalactic medium (CGM) of a galaxy involves many complicated 
@@
 With the advent of 2-dimensional spectroscopic data from SDSS MaNGA \citep{MaNGA,
-SDSS13}, it is possible to examine how the ISM and CGM are enriched over time.  
-MaNGA is the first large-scale survey using integral-field spectroscopy, which 
-would permit the study of spatially-resolved physical properties of galaxies 
+SDSS13}, it is now possible to examine how the ISM and CGM are enriched over 
+time.  MaNGA is the first large-scale survey using integral-field spectroscopy, 
+which permits the study of spatially-resolved physical properties of galaxies 
 across many different environments, morphologies, and stages of evolution.  In 
@@
 simulations have been done to test different theories about the role of an AGN 
-in a galaxy, and observations are now needed to test the results of the 
+in a galaxy, and observations are now needed to test the results of these 
 simulations.
@@
 The work done here on the small-scale environment is only the beginning of what 
-can be done in this subject area.  In addition to studying the relationship 
-between a galaxy's physical parameters and its distance to the nearest neighbor, 
-it is also important to look at the ratio of the galaxy's parameters to its 
-neighbor's and the distance to the nearest neighbor --- ``galactic 
-conformity.''  These comparisons should include a morphological comparison, 
-similar to the analysis done by \cite{Park09}.  We also find evidence of 
-possible mergers when studying the influence of the small-scale environment.  
-Visual inspection of these dwarf galaxies is imperative to confirming this 
-conclusion.
+can be done.  In addition to studying the relationship between a galaxy's 
+physical parameters and its distance to the nearest neighbor, it is also 
+important to look at the ratio of the galaxy's parameters to its neighbor's and 
+the distance to the nearest neighbor --- ``galactic conformity.''  These 
+comparisons should include a morphological comparison, similar to the analysis 
+done by \cite{Park09}.  We also find evidence of possible mergers when studying 
+the influence of the small-scale environment.  Visual inspection of these dwarf 
+galaxies is imperative to verify this conclusion.

### 2017-07-19 KellyDouglass/Thesis/Thesis_sections/GV.tex
Fixed typos

@@
 There are a number of different astrophysical processes which simultaneously 
-evolve a galaxy's stellar and gas content.  AGN feedback strongly affects 
-massive galaxies, while dwarf galaxy feedback is dominated by supernovae.  Both 
-AGN and supernovae can inject enough energy into a galaxy's ISM to prevent its 
-cooling, thereby quenching star formation.  In addition to internal mechanisms, 
-galaxies will often experience interactions in denser environmental regions.  
-Depending on the properties of the galaxies involved (mass, speed, etc.), these 
-interactions can either strip gas from the galaxy (removing a primary source of 
-fuel for future star formation), or they can trigger a burst of star formation.
+evolve a galaxy's stellar and gas content.  Active galactic nuclei (AGN) 
+feedback strongly affects massive galaxies, while dwarf galaxy feedback is 
+dominated by supernovae.  Both AGN and supernovae can inject enough energy into 
+a galaxy's ISM to prevent its cooling, thereby quenching star formation.  In 
+addition to internal mechanisms, galaxies in denser environmental regions will 
+often experience interactions.  Depending on the properties of the galaxies 
+involved (mass, speed, etc.), these interactions can either strip gas from the 
+galaxy (removing a primary source of fuel for future star formation), or they 
+can trigger a burst of star formation.
 
@@
 
-A galaxy's color is a logarithmic ratio of the ratio of the flux emitted by the 
-galaxy in two different bands.  The stellar population of a galaxy will 
-determine its color: redder galaxies contain much older, cooler stars, while the 
-spectrum of a bluer galaxy is produced by light from much younger, hotter stars.  
-While the KIAS-VAGC catalog (described below in Section \ref{sec:SDSS}) provides 
-the $u-r$ color for all galaxies in SDSS, we make use of the Petrosian fluxes in 
-the NSA (described in Section \ref{sec:GALEX}) to calculate the UV--optical 
-color.  The NUV$-r$ color is calculated by
+A galaxy's color is a logarithmic ratio of the flux emitted by the galaxy in two 
+different bands.  The stellar population of a galaxy will determine its color: 
+red galaxies contain much older, cooler stars, while the spectrum of a blue 
+galaxy is produced by light from much younger, hotter stars.  While the 
+KIAS-VAGC catalog (described below in Section \ref{sec:SDSS}) provides the $u-r$ 
+color for all galaxies in SDSS, we make use of the Petrosian fluxes in the NSA 
+(described in Section \ref{sec:GALEX}) to calculate the UV--optical color.  The 
+NUV$-r$ color is calculated by
 \begin{equation}
@@
 We use the photometric data from SDSS (optical) and GALEX (ultraviolet) as 
-cross-matched in the NSA.
+cross-matched in the NASA-Sloan Atlas\footnote{\url{http://www.nsatlas.org}} 
+(NSA).
 
-\subsection{Optical data --- SDSS}\label{sec:SDSS}
+\subsection{Optical data: SDSS}\label{sec:SDSS}
 % Should we use NSA for abs. mag. instead? - yes, but not for the thesis
@@
 abundances are calculated via the Direct $T_e$ method using emission-line fluxes 
-measured by the MPA-JHU catalog\footnote{Available at 
+as measured in the MPA-JHU catalog\footnote{Available at 
 \url{http://www.mpa-garching.mpg.de/SDSS/DR7}} and published in 
@@
 galaxies within 5 \hMpc of the edge of the SDSS DR7 footprint cannot be 
-described, so their environment is labeled as unknown.
+described, and so their environment is labeled as unknown.
 
@@
 With these three quantities, galaxies are separated into one of three different 
-morphological types: normal late type, normal early type, blue early type, and 
-one of two different morphological classes: elliptical or lenticular and spiral 
-or irregular.  For reference, typical star-forming spiral galaxies would be 
-classified as a normal late type spiral or irregular galaxy, star-forming dwarf 
+morphological types: normal late type, normal early type, or blue early type, 
+and one of two different morphological classes: elliptical or lenticular and 
+spiral or irregular.  For reference, typical star-forming spiral galaxies are 
+classified as normal late type spiral or irregular galaxies, star-forming dwarf 
 galaxies are usually normal late type spiral or irregular galaxies, and red 
@@
 
-\subsection{UV data --- GALEX}\label{sec:GALEX}
-The Galaxy Evolution Explorer \citep[GALEX]{Martin05} is an orbiting space 
+\subsection{UV data: GALEX}\label{sec:GALEX}
+The Galaxy Evolution Explorer \citep[GALEX;][]{Martin05} is an orbiting space 
 telescope conducting an extra-galactic ultraviolet all-sky survey.  The 
@@
 \citep{Morrissey07}.  The NUV-$r$ colors used in this study are calculated from 
-the azimuthally-averaged SDSS-style Petrosian fluxes provided in the NASA-Sloan 
-Atlas version 0.1.2 \citep[NSA]{Blanton11}.
+the azimuthally-averaged SDSS-style Petrosian fluxes provided in the NSA version 
+0.1.2 \citep{Blanton11}.
 
@@
     \includegraphics[width=0.75\textwidth]{Images/GV/NUVr_CMD_3pop_scatter}
-    \caption[NUV-$r$ color-magnitude diagram of SDSS galaxies]{The NUV$-r$ 
-    color-magnitude diagram of galaxies in SDSS DR7.  Those galaxies in the red 
+    \caption[NUV-$r$ color-magnitude diagram of NSA galaxies]{The NUV$-r$ 
+    color-magnitude diagram of galaxies in the NSA.  Those galaxies in the red 
     contours have morphological classifications of either normal early types 
@@
     less than 25, excluding those with values of 1 or 2), and the blue contours 
-    represents the remaining normal late type galaxies (aimc greater than 25).  
+    represent the remaining normal late type galaxies (aimc greater than 25).  
     It is clear that this morphological classification defines those galaxies 
@@
     \includegraphics[width=0.75\textwidth]{Images/GV/NUVr_CMDclassifications}
-    \caption[Distribution of NUV-$r$ of SDSS galaxies]{A histogram of the 
+    \caption[Distribution of NUV-$r$ for SDSS galaxies]{A histogram of the 
     NUV$-r$ color of those SDSS DR7 galaxies which are also detected in GALEX.  
@@
 
-This analysis reveals a population of galaxies that lie in the Green Valley on 
+This analysis reveals a population of galaxies that lie in the green valley on 
 the NUV$-r$ color-magnitude diagram, identified independent of their location on 
@@
 If the green valley galaxies represent those galaxies transitioning between the 
-blue sequence and red cloud, then their stellar masses should overlap the masses 
-in both these populations.  The distribution of the stellar masses for the 
-galaxies in SDSS DR7 is shown in Fig. \ref{fig:M_hist}.  We can see that the 
+blue sequence and the red cloud, then their stellar masses should overlap the 
+masses in both these populations.  The distribution of the stellar masses for 
+the galaxies in SDSS DR7 is shown in Fig. \ref{fig:M_hist}.  We can see that the 
 galaxies in the green valley have stellar masses comparable to those in the red 
@@
     \includegraphics[width=0.49\textwidth]{Images/GV/logNO_I06relations_t3}
-    \caption[Distribution of gas-phase chemical abundances in cross-matched SDSS 
-    DR7 -- GALEX galaxies]{Histograms of the oxygen abundance (top left), 
-    nitrogen abundance (top right), and N/O ratio (bottom center) of the 
-    cross-matched SDSS DR7 -- GALEX galaxies, separated into their locations on 
-    the NUV$-r$ color-magnitude diagram according to the morphological type 
-    listed in the KIAS-VAGC.  It is readily apparent that the green valley 
-    galaxies have higher nitrogen abundances than those in the blue sequence 
-    (and some of the red cloud).  This, therefore, corresponds to them having 
-    high N/O ratios.}
+    \caption[Distribution of abundances in cross-matched SDSS DR7 -- GALEX 
+    galaxies]{Histograms of the oxygen abundance (top left), nitrogen abundance 
+    (top right), and N/O ratio (bottom center) of the cross-matched SDSS DR7 -- 
+    GALEX galaxies, separated by their locations on the NUV$-r$ color-magnitude 
+    diagram according to the morphological type listed in the KIAS-VAGC.  It is 
+    readily apparent that the green valley galaxies have higher nitrogen 
+    abundances than those in the blue sequence (and some of the red cloud).  
+    This, therefore, corresponds to them having high N/O ratios.}
     \label{fig:Z_hist}
@@
 galaxies in the green valley depends on the large-scale environment, even at 
-fixed stellar mass or luminosity.  A larger fraction of faint wall galaxies are 
-found in the green valley than for faint void galaxies.
+fixed stellar mass or luminosity.  There is a larger fraction of faint wall 
+galaxies than faint void galaxies in the green valley.
 
@@
 
-\section[GV galaxy properties]{Understanding green valley galaxies}\label{sec:discussion_GV}
+\section[Understanding GV galaxies]{Understanding green valley galaxies}\label{sec:discussion_GV}
 
-Galaxies in the green valley are described to be in a transitional period of the 
-galaxy's life cycle, where they are being quenched in their star formation or 
-are beginning to form stars after being quiescent.  Here, we are able to 
+Galaxies in the green valley are thought to be in a transitional period of the 
+galaxy's life cycle, where their star formation is quenching or they are 
+beginning to form stars after a quiescent period.  Here, we are able to 
 quantitatively define galaxies in the green valley of the UV-optical CMD.  We 
@@
 As explained in \cite{Douglass17b}, nitrogen is thought to be produced in both a 
-primary and secondary stage, depending on the presence of other heavy elements.  
-The fact that the galaxies in the green valley have higher nitrogen abundances 
-compared to those in the blue sequence indicate that they are building up a 
-surplus of nitrogen, most likely due to the presence of heavier elements in 
-later episodes of star formation.  The surplus of heavier elements allows the 
-CNO cycle to commence earlier in the stars' lifetimes, producing nitrogen at a 
-higher rate than oxygen.  It is also possible that the higher nitrogen 
+primary and secondary stage depending on the presence of other heavy elements.  
+When compared to those in the blue sequence, the higher nitrogen abundances of 
+galaxies in the green valley indicate that green valley galaxies are building up 
+a surplus of nitrogen, most likely due to the presence of heavier elements in 
+later episodes of star formation.  The surplus of these heavier elements allows 
+the CNO cycle to commence earlier in the stars' lifetimes, producing nitrogen at 
+a higher rate than oxygen.  It is also possible that the higher nitrogen 
 abundances are a sign that the galaxies' intermediate mass stars (those 
@@
     \includegraphics[width=0.49\textwidth]{Images/GV/1sig_all_BPT_t3_logNOrelations_dust_hist}
-    \caption[Gas-phase chemical abundance distributions for star-forming, 
-    composite, and AGN galaxies]{Distribution of the gas-phase oxygen abundance 
-    (O/H, top left), nitrogen abundance (N/H, top right), and N/O ratio (bottom 
-    center) of the SDSS DR7 galaxies with detectable emission lines for 
-    abundance calculations with the Direct $T_e$ method.  Star-forming galaxies 
-    are shown with a solid cyan line, while composite galaxies are a dashed 
-    orange line and galaxies with an AGN are represented as a dotted magenta 
-    line.  Composite galaxies have lower oxygen abundances than both 
-    star-forming galaxies and those with an AGN.  The nitrogen abundance range 
-    is different for each of the three classes, with star-forming galaxies 
-    having the lowest nitrogen abundances, AGN having the highest, and 
-    composite galaxies in the middle.  Therefore, star-forming galaxies have 
-    N/O ratios $< 0$, while composite galaxies and galaxies with an AGN have 
-    N/O ratios between -1 and 0.5.}
+    \caption[Abundance distributions for star-forming, composite, and AGN 
+    galaxies]{Distribution of the gas-phase oxygen abundance (O/H, top left), 
+    nitrogen abundance (N/H, top right), and N/O ratio (bottom center) of the 
+    SDSS DR7 galaxies with detectable emission lines for abundance calculations 
+    with the Direct $T_e$ method.  Star-forming galaxies are shown with a solid 
+    cyan line, while composite galaxies are a dashed orange line and galaxies 
+    with an AGN are represented as a dotted magenta line.  Composite galaxies 
+    have lower oxygen abundances than both star-forming galaxies and those with 
+    an AGN.  The nitrogen abundance range is different for each of the three 
+    classes, with star-forming galaxies having the lowest nitrogen abundances, 
+    AGN having the highest, and composite galaxies in the middle.  Therefore, 
+    star-forming galaxies have N/O ratios $< 0$, while composite galaxies and 
+    galaxies with an AGN have N/O ratios between -1 and 0.5.}
     \label{fig:BPT_abund}
@@
 high N/O ratio) is also seen in galaxies classified as AGN, indicating that the 
-galaxies in the green valley have an AGN.
+galaxies in the green valley may have an AGN.
 
@@
 the green valley.  In conjunction with the conclusions of \cite{Douglass17b} and 
-\cite{Douglass17c}, this indicates that void dwarf galaxies are less evolved 
+\cite{Douglass17c}, this may indicate that void dwarf galaxies are less evolved 
 than dwarf galaxies in denser environments.  It would be beneficial to 
 investigate the small-scale ($\sim$1 \hMpc) environment of galaxies in the green 
-valley, to determine if any interactions are responsible for the transitional 
+valley, to determine if any interactions are responsible for their transitional 
 state.

### 2017-07-19 KellyDouglass/Thesis/Thesis_sections/Introduction.tex
Fixed typos

@@
 constructed which successfully reproduce the same large-scale structure.  If we 
-start with a mostly uniform distribution of dark matter at the Big Bang with 
-quantum mechanical perturbations, Fig. \ref{fig:DMsim} outlines the evolution of 
-that dark matter up through the present.  These snapshots from the Millenium 
-Simulation project \citep{Springel05} show that small perturbations in the 
-initial distribution of dark matter are amplified as the universe expands.  
-Gravity causes the slightly overdense regions to collapse while simultaneously 
-causing the underdense regions to expand.  Due to dark matter's gravitational 
-attraction, we believe that the baryonic mattter (matter which interacts 
-electromagnetically) will trace the dark matter distribution, resulting in the 
-galaxy distribution we observe today.
+start with a mostly uniform distribution of dark matter at the Big Bang 
+containing quantum mechanical perturbations, Fig. \ref{fig:DMsim} outlines the 
+evolution of that dark matter distribution up through the present epoch.  These 
+snapshots from the Millenium Simulation project \citep{Springel05} show that 
+small perturbations in the initial distribution of dark matter are amplified as 
+the universe expands.  Gravity causes the slightly overdense regions to collapse 
+while simultaneously causing the underdense regions to expand.  Due to dark 
+matter's gravitational attraction, we believe that the baryonic mattter (matter 
+which interacts electromagnetically) will trace the dark matter distribution, 
+resulting in the galaxy distribution we observe today.
 
@@
 % What do we already know about the environmental influence?
-Observational studies of void galaxies have included investigation of 
+Observational studies of void galaxies have included investigations of 
 photometric properties such as luminosity \citep{Hoyle05,Croton05,Moorman15}, 
@@
 formation and evolution of dwarf galaxies.  Fig. \ref{fig:Mr_SDSS} shows the 
-distribution of galaxies by their absolute magnitudes detected in SDSS DR7.  
-Defined to be galaxies with absolute magnitudes fainter than -17 ($M_r > -17$), 
-the low stellar masses of dwarf galaxies correspond to more shallow 
-gravitational potential wells.  This causes any environmental effects to have a 
-more significant influence on dwarf galaxies than on galaxies with larger 
-stellar masses.  In addition, studying void dwarf galaxies will complement 
-previous studies of dwarfs in groups and clusters because the assembly histories 
-of low-mass galaxies are predicted to be very different \citep[e.g.,][]{Gao07,
-Lackner12}.  Observations to date also show that the properties of dwarf 
+distribution in absolute magnitudes of galaxies detected in SDSS DR7.  Defined 
+to be galaxies with absolute magnitudes fainter than -17 ($M_r > -17$), the low 
+stellar masses of dwarf galaxies correspond to more shallow gravitational 
+potential wells.  This causes any environmental effects to have a more 
+significant influence on dwarf galaxies than on galaxies with larger stellar 
+masses.  In addition, studying void dwarf galaxies will complement previous 
+studies of dwarfs in groups and clusters because the assembly histories of 
+low-mass galaxies are predicted to be very different \citep[e.g.,][]{Gao07,
+Lackner12}.  Observations to date have also shown that the properties of dwarf 
 galaxies vary dramatically with the environment \citep[e.g.,][]{Ann08,Geha12}.
@@
 [\ion{O}{3}] $\lambda$4363 auroral line to the [\ion{O}{3}] 
-$\lambda \lambda$4959,5007 doublet, we can get an estimate of the temperature of 
-the gas.  These lines are highlighted on the example SDSS DR7 spectrum shown in 
-Fig. \ref{fig:spectrum}.
+$\lambda \lambda$4959,5007 doublet, we can estimate the temperature of the gas.  
+These lines are highlighted on the example SDSS DR7 spectrum shown in Fig. 
+\ref{fig:spectrum}.
 
-Oxygen is used as a proxy to measure the metallicity of an \ion{H}{2} region, 
-because oxygen is the most abundant element in the universe after hydrogen and 
+Oxygen is used as a proxy to measure the metallicity of an \ion{H}{2} region 
+because it is the most abundant element in the universe after hydrogen and 
 helium \citep{Emsley11}.  It also has strong emission lines in the visible 
@@
 the relative number of ions in the gas.  It is possible to calculate the number 
-ratios for any of the heavy elements with respect to hydrogen once the electron 
+ratio for any of the heavy elements with respect to hydrogen once the electron 
 temperature and density of the interstellar gas are estimated.
@@
 We continue studying this galaxy sample in Chapter \ref{ch:Paper2} by estimating 
-their ratios of nitrogen to oxygen and looking at how that depends on the 
+their ratios of nitrogen to oxygen and looking at how this ratio depends on the 
 large-scale environment.  To expand our dwarf galaxy sample, we derive an 
@@
 \ref{ch:smallScaleEnvironment}, we investigate how the dwarf galaxies' 
-properties depend on the galaxies' distances to the nearest neighbors and 
+properties depend on the galaxies' distances to their nearest neighbors and 
 groups.  Finally, in an effort to better understand how galaxies evolve from 
-blue, star-forming systems to ``red and dead,'' we discover a way to classify 
-galaxies into their location on the color-magnitude diagram in Chapter 
+blue, star-forming systems to ``red and dead'' galaxies, we discover a way to 
+classify the location of galaxies on the color-magnitude diagram in Chapter 
 \ref{ch:GV}.  We present our conclusions and suggestions for future research in 

### 2017-07-19 KellyDouglass/Thesis/Thesis_sections/Paper3.tex
Fixed typos

@@
 sensitive to astrophysical effects such as cosmological reionization, internal 
-feedback from supernova and photoheating from star formation, external effects 
+feedback from supernovae and photoheating from star formation, external effects 
 from tidal interactions and ram pressure stripping, small-scale details of dark 
@@
 described above, this work only examines the chemical evolution of star-forming 
-dwarf galaxies.  As a result of this sample, the known influences of the 
-environment on the morphology and luminosity have already be taken into account, 
-since we concentrate only on star-forming dwarf galaxies.
+dwarf galaxies.  As a result of this sample being limited to only star-forming 
+galaxies, the known influences of the environment on the morphology and 
+luminosity have already be taken into account.
 
@@
     \includegraphics[width=0.75\textwidth]{Images/Paper3/Zlow_v_Zreal_1sig_I06_BPTclass_fits}
-    \caption[O$^++$/H versus O/H]{$12 + \log{\text{O}^{++}/\text{H}}$ versus \OH 
-    for those galaxies with $M_r > -20$ as calculated with the direct method; 
-    the galaxies are colored by their classification in the BPT diagrams 
+    \caption[O$^{++}$/H versus O/H]{$12 + \log{\text{O}^{++}/\text{H}}$ versus 
+    \OH for those galaxies with $M_r > -20$ as calculated with the direct 
+    method; the galaxies are colored by their classification in the BPT diagrams 
     \citep[from][]{Brinchmann04}.  Two linear models have been fit to three 
@@
 
-    \caption[Coefficients of oxygen abundance fits]{Coefficients for the linear 
+    \caption[Coefficients of O$^+$ approximation]{Coefficients for the linear 
     trends (Eqn. \ref{eq:fit}) fit to the SF galaxies (dwarf and those with 

### 2017-07-19 KellyDouglass/Thesis/preamble.tex
Fixed typos

@@
 and research skills over the last six years.  And thank you for giving me the 
-opportunity to help advise students.  I would like to thank our collaborator 
-Renyue Cen for his help in the theoretical interpretation of these results, and 
-for confirming that our explanations were not completely ridiculous.  To my 
-committee members Profs. Gordon Richards, Steve McMillan, Masao Sako, and 
-Michelle Dolinksi --- thank you for your time and guidance throughout the years.  
-And a big shout-out to my advisees: Daniele Schneider, Jinfu Dai, Brean 
-Prefontaine, and Salvatore Zerbo.  Thank you for all your hard work!
+opportunity to help advise students.  I would also like to thank our 
+collaborator, Renyue Cen, for his help in the theoretical interpretation of 
+these results and for confirming that our explanations are not completely 
+ridiculous.  To my committee members: Profs. Gordon Richards, Steve McMillan, 
+Masao Sako, and Michelle Dolinski --- thank you for your time and guidance 
+throughout the years.  And a big shout-out to my advisees: Daniele Schneider, 
+Jinfu Dai, Brean Prefontaine, and Salvatore Zerbo.  Thank you for all your hard 
+work!
 
@@
 much more bearable (and almost enjoyable, if I dare say).  To my physics boys 
-Justin, Matt, and Matt: we made it!  I would be remiss in not acknowledging my 
-office mates over the last few years, particularly Josh, Jackie, Justin, 
-Crystal, Austen, and Vish, for help with code, ideas, and keeping the moral up.  
+Justin, Matt, and Matt: we made it!  I would also be remiss in not acknowledging 
+my office mates over the last few years, particularly Josh, Jackie, Justin, 
+Crystal, Austen, and Vish, for help with code, ideas, and keeping up the moral.  
 And, of course, thank you to all the members of PLBD for providing me an outlet 
@@
 % Family
-Of course, none of this would be possible without the infinite love and support 
-from my family.  Thank you Dad, Mom, Kelly, and Ren\'{e}e for always pushing me 
-to work my hardest and do my best.  Thank you for challenging me in so many 
+None of this would have been possible without the infinite love and support from 
+my family.  Thank you Dad, Mom, Kelly, and Ren\'{e}e for always pushing me to 
+work my hardest and to do my best.  Thank you for challenging me in so many 
 ways.  I love you guys, and it means so much that you are here today!
@@
 At smaller scales, we find that only the presence of a neighboring galaxy within 
-0.05 \hMpc or 0.05$r_{vir}$, or the presence of a group within 0.1 \hMpc, 
+0.05 \hMpc or 0.1$r_{vir}$, or the presence of a group within 0.05 \hMpc, 
 influences a dwarf galaxy's evolution.  Dwarf galaxies within 0.05 \hMpc or 
-0.05$r_{vir}$ of another galaxy tend to be bluer, have higher sSFRs, and have 
-higher oxygen and nitrogen abundances than average.  In contrast, galaxies 
-within 0.1 \hMpc of the center of the closest group are redder, have lower 
-oxygen abundances, and have higher N/O ratios than average.
+0.1$r_{vir}$ of another galaxy tend to be bluer, have higher sSFRs, have higher 
+oxygen abundances, and have lower N/O ratios than average.  In contrast, 
+galaxies within 0.05 \hMpc of the center of the closest group have lower oxygen 
+and nitrogen abundances than average.
 % GV
@@
 valley.  We discover that combining a galaxy's color, color gradient, and 
-inverse concentration index defines a galaxy's location on the color-magnitude 
-diagram.  The results indicate that there is a higher fraction of dwarf galaxies 
-in denser regions than void dwarf galaxies in the green valley.
+inverse concentration index determines a galaxy's location on the 
+color-magnitude diagram.  The results indicate that, in the green valley, there 
+is a lower fraction of void dwarf galaxies than dwarf galaxies in denser 
+regions.
 % Conclusions

### 2017-07-19 KellyDouglass/Thesis/simulations.tex
Added acknowledgments and dedication
Fixed typos

@@
-\chapter[Simulations]{Simulations of dwarf galaxy formation and evolution}
+\chapter[Simulations]{Simulations of Dwarf Galaxy Formation and Evolution}
 
@@
 understand the formation and evolution of our universe.  As observers, it is 
-important to connect our observations with the theory in order to grow our ideas 
-about the universe.
+important to connect our observations with the theory in order to expand our 
+ideas about the universe.
 
@@
 % Hierarchical formation of halos
-It is impossible to directly observe the formation of a galaxy.  Based on 
-detected merging galaxies, the astronomical community has surmised that galaxies 
-have increased their mass largely due to the merging of smaller galaxies.  
-$\Lambda$CDM simulations of hierarchical galaxy formation by \cite{deRossi07} 
-find that the growth of systems by aggregation is responsible for the 
-mass-metallicity relation.  Less massive systems tend to increase their stellar 
-mass by either gas-rich mergers or secular evolution, resulting in a stronger 
-correlation between stellar mass and metallicity.  Evidence of this is seen in 
-the mass-metallicity relation of \cite{Tremonti04}, where there is little 
-relationship between stellar mass and the metallicity for massive systems, but 
-at intermediate and lower masses the correlation is strong between the two 
-quantities.
+Due to the vast time scales over which galaxy formation occurs, it is impossible 
+to directly observe the formation of a galaxy.  Based on observed merging 
+galaxies, the astronomical community has surmised that galaxies increase their 
+mass largely due to the merging of smaller galaxies.  $\Lambda$CDM simulations 
+of hierarchical galaxy formation by \cite{deRossi07} find that the growth of 
+systems by aggregation is responsible for the mass-metallicity relation.  Less 
+massive systems tend to increase their stellar mass by either gas-rich mergers 
+or secular evolution, resulting in a stronger correlation between stellar mass 
+and metallicity.  Evidence of this is seen in the mass-metallicity relation of 
+\cite{Tremonti04}, where there is little relationship between stellar mass and 
+the metallicity for massive systems, but at intermediate and lower masses the 
+correlation is strong between the two quantities.
 
@@
 (IGM) is comparable to the thermal pressure of the central interstellar medium 
-(ISM), stripping and superwind influence each other and increase the gas removal 
-rate.  They find that the amount of metal-rich ejecta is sensitive to the ram 
-pressure.  
+(ISM), stripping and superwinds influence each other and increase the gas 
+removal rate.  They find that the amount of metal-rich ejecta is sensitive to 
+the ram pressure.  
 % supernova
@@
 supernova-driven galactic outflows push metal-rich gas into the halo.  A small 
-fraction of the gas eventually escapes the halo, while most falls back onto the 
+fraction of this gas eventually escapes the halo, while most falls back onto the 
 disc.  This results in the halo metallicity being about 20\% higher than the 
@@
 % star formation
-Unlike the supernovae, \cite{Melioli15} finds that the ISM material does not 
-have a strong likelihood of being expelled from a galaxy due to star formation.  
-In contrast, \cite{Muratov15} finds that a large portion of material is ejected 
-in galactic outflows after a bust of star formation, which collects in the 
+Unlike the supernovae, \cite{Melioli15} find that the ISM material does not have 
+a strong likelihood of being expelled from a galaxy due to star formation.  In 
+contrast, \cite{Muratov15} find that a large portion of material is ejected in 
+galactic outflows after a bust of star formation, which collects in the 
 circumgalactic medium (CGM) and is sometimes recycled in later star formation 
@@
 % Metallicity
-Numerical simulations that study the properties of the ISM in an isolated, 
-star-forming galaxy find that stellar feedback slowly increases the disc 
-metallicity \citep{Hu16}.  The majority of outflows are enriched winds, which 
-reduces the metallicity of the ISM.  In dwarf galaxies at low redshifts, these 
-outflows to the CGM are dominated by metal-poor gas \citep{Muratov17}.  While 
-galaxies retain most of the metals they produce, a large fraction is in the CGM.  
-By combining our observations with the results of these simulations, we can 
-begin to understand how star formation and supernovae influence a dwarf galaxy's 
-gas content.
+Numerical simulations that study properties of the ISM in isolated, star-forming 
+galaxies find that stellar feedback slowly increases the disc metallicity 
+\citep{Hu16}.  The majority of outflows are enriched winds, which reduce the 
+metallicity of the ISM.  In dwarf galaxies at low redshifts, metal-poor gas 
+dominates these outflows to the CGM \citep{Muratov17}.  While galaxies retain 
+most of the metals they produce, a large fraction is in the CGM.  By combining 
+our observations with the results of these simulations, we can begin to 
+understand how star formation and supernovae influence a dwarf galaxy's gas 
+content.
 
@@
 occur, and so galaxies in the voids maintain a high sSFR in the present epoch.  
-While this is the overall trend, there still exists some galaxies at $z=0$ which 
-have a high sSFR but reside in the more dense environments.
+While this is the overall trend, there still exist some galaxies at $z=0$ which 
+have a high sSFR but reside in the denser environments.

### 2017-07-20 KellyDouglass/Thesis/Thesis_sections/smallScaleEnvironment.tex
Fixed typo

@@
 In contrast, dwarf galaxies within 0.05 \hMpc of the center of the nearest group 
-have lower oxygen (O/H) and nitrogen (N/H) abundances (O/H) than average.  Due 
-to their proximity to the group center, it is likely that these dwarf galaxies 
-are not able to retain as much of their heavy elements as a more isolated 
-galaxy, thereby reducing their gas-phase oxygen and nitrogen abundances.
+have lower oxygen (O/H) and nitrogen (N/H) abundances than average.  Due to 
+their proximity to the group center, it is likely that these dwarf galaxies are 
+not able to retain as much of their heavy elements as a more isolated galaxy, 
+thereby reducing their gas-phase oxygen and nitrogen abundances.
 
